### 2018-04-06 doc/tlla2018/main.tex
Imported source for extended abstract

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018} % Name of the event you are submitting to
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek} % Minimal dependencies for bibTeX.
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}
\renewcommand*{\hccp}{HTA\xspace}

\title{Taking Linear Logic Apart}
\author{%
  Wen Kokke
  \institute{University of Edinburgh\\ Edinburgh, Scotland}
  \email{wen.kokke@ed.ac.uk}}
\def\titlerunning{Taking Linear Logic Apart}
\def\authorrunning{Wen Kokke}

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

%% Classical Processes
\begin{figure*}[!htb]
  Structural Rules.
  \begin{center} \cpInfAx     \cpInfCut      \end{center}

  Logical Rules.
  \begin{center} \cpInfTens   \cpInfParr     \end{center}
  \begin{center} \cpInfOne    \cpInfBot      \end{center}
  \begin{center} \cpInfPlus1  \cpInfPlus2    \end{center}
  \begin{center} \cpInfWith                  \end{center}
  \begin{center} \cpInfNil    \cpInfTop      \end{center}

  \caption{Classical Processes (\cp)}
  \label{fig:cp}
\end{figure*}

%% Hypersequent Classical Processes
\begin{figure*}[!htb]
  Structural Rules.
  \begin{center} \hcpInfAx     \hcpInfCut    \end{center}
  \begin{center} \hcpInfMix    \hcpInfHalt   \end{center}

  Logical Rules.
  \begin{center} \hcpInfTens   \hcpInfParr   \end{center}
  \begin{center} \hcpInfOne    \hcpInfBot    \end{center}
  \begin{center} \hcpInfPlus1  \hcpInfPlus2  \end{center}
  \begin{center} \hcpInfWith                 \end{center}
  \begin{center} \hcpInfNil    \hcpInfTop    \end{center}

  \caption{Hypersequent Classical Processes (\hcp)}
  \label{fig:hcp}
\end{figure*}

\begin{theorem}\label{thm:cp2hcp-typing}
  If $\seq[P]{\Gamma}$ in \cp, then $\seq[P]{\Gamma}$ in \hcp.
\end{theorem}
\begin{theorem}\label{thm:hcp2cp-typing}
  If $\seq[P]{\Gamma}$ in \hcp, then $\seq[P]{\Gamma}$ in \cp.
\end{theorem}
\begin{definition}\label{def:hcp-bigtens}
  \(\!%
  \begin{array}{lcl}
    \ty{\bigparr\emptycontext}
    & = & \ty{\bot}
    \\
    \ty{\bigparr(\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n})}
    & = & \ty{A_1 \parr \dots \parr A_n}
  \end{array}
  \)
\end{definition}
\begin{lemma}\label{lem:hcp-bigparr}
  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
\end{lemma}
\begin{definition}\label{def:hcp-bigtens}
  \(\!%
  \begin{array}{lcl}
    \ty{\bigtens\emptyhypercontext}
    & = & \ty{\one}
    \\
    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
  \end{array}
  \)
\end{definition}
\begin{theorem}\label{thm:hcp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \hcp.
\end{theorem}
\begin{corollary}[Conservative Extension]
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{corollary}

%% Hypersequent Classical Processes Taken Apart
\begin{figure*}[!htb]
  Structural Rules.
  \begin{center} \hccpInfAx        \hccpInfCycle \end{center}
  \begin{center} \hccpInfMix       \hccpInfHalt  \end{center}

  Logical Rules.

  \begin{center} \hccpInfBoundTens \hccpInfParr  \end{center}
  \begin{center} \hccpInfOne       \hccpInfBot   \end{center}
  \begin{center} \hccpInfPlus1     \hccpInfPlus2 \end{center}
  \begin{center} \hccpInfWith                    \end{center}
  \begin{center} \hccpInfNil       \hccpInfTop   \end{center}

  \centering
  (Where each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.)

  \caption{Hypersequent Classical Processes \emph{Taken Apart} (\hccp)}
  \label{fig:hccp}
\end{figure*}

\begin{theorem}\label{thm:hcp2hccp-typing}
  If $\seq[P]{\mathcal{G}}$ in \hcp, then $\seq[P]{\mathcal{G}}$ in \hccp.
\end{theorem}
\begin{theorem}\label{thm:hccp2hcp-typing}
  If $\seq{\mathcal{G}}$ in \hccp, then $\seq{\mathcal{G}}$ in \hcp.
\end{theorem}

\bibliographystyle{eptcs}
\bibliography{main}
\end{document}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-04-06 doc/tlla2018/main.tex
Removed PDF; fixed .travis.yml; added theorems to main.tex

@@
 \input{preamble-typing}
-\renewcommand*{\hccp}{HTA\xspace}
 
@@
 \end{theorem}
-\begin{corollary}[Conservative Extension]
+\begin{corollary}\label{cor:hcp-bigtens}
   If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
@@
 
-\begin{theorem}\label{thm:hcp2hccp-typing}
+\begin{theorem}\label{cor:hcp2hccp-typing}
   If $\seq[P]{\mathcal{G}}$ in \hcp, then $\seq[P]{\mathcal{G}}$ in \hccp.
 \end{theorem}
+\begin{corollary}\label{thm:cp2hccp-typing}
+  If $\seq[P]{\Gamma}$ in \cp, then $\seq[P]{\Gamma}$ in \hccp. 
+\end{corollary}
 \begin{theorem}\label{thm:hccp2hcp-typing}
@@
 \end{theorem}
+\begin{corollary}\label{cor:hccp2cp-typing}
+  If $\seq{\mathcal{G}}$ in \hccp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
+\end{corollary}
 

### 2018-04-18 doc/tlla2018/main.tex
Copied over more definitions...

--- 2018-04-06 doc/tlla2018/main.tex
@@
 \documentclass[submission,copyright,creativecommons]{eptcs}
-\providecommand{\event}{Linearity and TLLA 2018} % Name of the event you are submitting to
+\providecommand{\event}{Linearity and TLLA 2018}
 \usepackage{breakurl} % Not needed if you use pdflatex only.
 \usepackage{underscore} % Only needed if you use pdflatex.
-\usepackage{textcomp,textgreek,upgreek} % Minimal dependencies for bibTeX.
+\usepackage{textcomp,textgreek,upgreek}
 \usepackage{amsthm}
@@
 %% Classical Processes
+
+\begin{definition}[Terms]\label{def:cp-terms}
+  \begin{gather*}
+    \begin{array}{rllrll}
+      \tm{P}, \tm{Q}, \tm{R}
+           :=& \tm{\cpLink{x}{y}}       &\text{link}
+      &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
+      \\ \mid& \tm{\cpSend{x}{y}{P}{Q}} &\text{``output''}
+      &  \mid& \tm{\cpRecv{x}{y}{P}}    &\text{``input''}
+      \\ \mid& \tm{\cpHalt{x}}          &\text{halt}
+      &  \mid& \tm{\cpWait{x}{P}}       &\text{wait}
+      \\ \mid& \tm{\cpInl{x}{P}}        &\text{select left choice}
+      &  \mid& \tm{\cpInr{x}{P}}        &\text{select right choice}
+      \\ \mid& \tm{\cpCase{x}{P}{Q}}    &\text{offer binary choice}
+      &  \mid& \tm{\cpAbsurd{x}}        &\text{offer nullary choice}
+    \end{array}
+  \end{gather*}
+\end{definition}
+
+\begin{definition}[Structural congruence]\label{def:cp-equiv}
+  We define the structural congruence $\equiv$ as the congruence closure over
+  terms which satisfies the following additional axioms:
+  \begin{gather*}
+    \setlength{\arraycolsep}{3pt}
+    \begin{array}{llcll}
+      \cpEquivLinkComm
+      & \tm{\cpLink{x}{y}}
+      & \equiv
+      & \tm{\cpLink{y}{x}}
+      \\
+      \cpEquivCutComm
+      & \tm{\cpCut{x}{P}{Q}}
+      & \equiv
+      & \tm{\cpCut{x}{Q}{P}}
+      \\
+      \cpEquivCutAss1
+      & \tm{\cpCut{x}{P}{\cpCut{y}{Q}{R}}}
+      & \equiv
+      & \tm{\cpCut{y}{\cpCut{x}{P}{Q}}{R}}
+      & \text{if }\notFreeIn{x}{R}\text{ and }\notFreeIn{y}{P}
+    \end{array}
+  \end{gather*}
+\end{definition}
+
+\begin{definition}[Reduction]\label{def:cp-reduction}
+  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
+  to the process $\tm{Q}$ in a single step.
+  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
+  $\Longrightarrow$.
+  Reductions can only be constructed as follows:
+  \begin{gather*}
+    \begin{array}{llcll}
+      \cpRedAxCut1
+      & \tm{\cpCut{x}{\cpLink{w}{x}}{P}}
+      & \Longrightarrow
+      & \tm{\cpSub{w}{x}{P}} 
+      \\
+      \cpRedBetaTensParr
+      & \tm{\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{z}{R}}}
+      & \Longrightarrow
+      & \tm{\cpCut{y}{P}{\cpCut{x}{Q}{\cpSub{y}{z}{R}}}}
+      \\
+      \cpRedBetaOneBot
+      & \tm{\cpCut{x}{\cpHalt{x}}{\cpWait{x}{P}}}
+      & \Longrightarrow
+      & \tm{P}
+      \\
+      \cpRedBetaPlusWith1
+      & \tm{\cpCut{x}{\cpInl{x}{P}}{\cpCase{x}{Q}{R}}}
+      & \Longrightarrow
+      & \tm{\cpCut{x}{P}{Q}}
+      \\
+      \cpRedBetaPlusWith2
+      & \tm{\cpCut{x}{\cpInr{x}{P}}{\cpCase{x}{Q}{R}}}
+      & \Longrightarrow
+      & \tm{\cpCut{x}{P}{R}}
+      \\
+      \cpRedKappaTens1
+      & \tm{\cpCut{x}{\cpSend{y}{z}{P}{Q}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpSend{y}{z}{\cpCut{x}{P}{R}}{Q}}
+        \quad \text{if} \; \notFreeIn{x}{Q}
+      \\
+      \cpRedKappaTens2
+      & \tm{\cpCut{x}{\cpSend{y}{z}{P}{Q}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpSend{y}{z}{P}{\cpCut{x}{Q}{R}}}
+        \quad \text{if} \; \notFreeIn{x}{P}
+      \\
+      \cpRedKappaParr
+      & \tm{\cpCut{x}{\cpRecv{y}{z}{P}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpRecv{y}{z}{\cpCut{x}{P}{R}}}
+      \\
+      \cpRedKappaBot
+      & \tm{\cpCut{x}{\cpWait{y}{P}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpWait{y}{\cpCut{x}{P}{R}}}
+      \\
+      \cpRedKappaPlus1
+      & \tm{\cpCut{x}{\cpInl{y}{P}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpInl{y}{\cpCut{x}{P}{R}}}
+      \\
+      \cpRedKappaPlus2
+      &\tm{\cpCut{x}{\cpInr{y}{P}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpInr{y}{\cpCut{x}{P}{R}}}
+      \\
+      \cpRedKappaWith
+      & \tm{\cpCut{x}{\cpCase{y}{P}{Q}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpCase{y}{\cpCut{x}{P}{R}}{\cpCut{x}{Q}{R}}}
+      \\
+      \cpRedKappaTop
+      & \tm{\cpCut{x}{\cpAbsurd{y}}{R}}
+      & \Longrightarrow \;
+      & \tm{\cpAbsurd{y}}
+    \end{array}
+  \end{gather*}
+  \begin{center}
+    \begin{prooftree*}
+      \AXC{$\reducesto{P}{P^\prime}$}
+      \SYM{\cpRedGammaCut}
+      \UIC{$\reducesto{\cpCut{x}{P}{Q}}{\cpCut{x}{P^\prime}{Q}}$}
+    \end{prooftree*}
+    \begin{prooftree*}
+      \AXC{$\tm{P}\equiv\tm{Q}$}
+      \AXC{$\reducesto{Q}{Q^\prime}$}
+      \AXC{$\tm{Q^\prime}\equiv\tm{P^\prime}$}
+      \SYM{\cpRedGammaEquiv}
+      \TIC{$\reducesto{P}{P^\prime}$}
+    \end{prooftree*}
+  \end{center}
+\end{definition}
+
+\begin{definition}[Types]\label{def:cp-types}
+  \begin{gather*}
+    \begin{array}{rclrcl}
+      \ty{A}, \ty{B}, \ty{C}
+           :=& \ty{A \tens B} &\text{pair of independent processes}
+      &  \mid& \ty{\one}      &\text{unit for} \; {\tens}
+      \\ \mid& \ty{A \parr B} &\text{pair of interdependent processes}
+      &  \mid& \ty{\bot}      &\text{unit for} \; {\parr}
+      \\ \mid& \ty{A \plus B} &\text{internal choice}
+      &  \mid& \ty{\nil}      &\text{unit for} \; {\plus}
+      \\ \mid& \ty{A \with B} &\text{external choice}
+      &  \mid& \ty{\top}      &\text{unit for} \; {\with}
+    \end{array}
+  \end{gather*}
+\end{definition}
+
 \begin{figure*}[!htb]
@@
 %% Hypersequent Classical Processes
-\begin{figure*}[!htb]
-  Structural Rules.
-  \begin{center} \hcpInfAx     \hcpInfCut    \end{center}
-  \begin{center} \hcpInfMix    \hcpInfHalt   \end{center}
 
-  Logical Rules.
-  \begin{center} \hcpInfTens   \hcpInfParr   \end{center}
-  \begin{center} \hcpInfOne    \hcpInfBot    \end{center}
-  \begin{center} \hcpInfPlus1  \hcpInfPlus2  \end{center}
-  \begin{center} \hcpInfWith                 \end{center}
-  \begin{center} \hcpInfNil    \hcpInfTop    \end{center}
+\begin{definition}[Terms]\label{def:hcp-terms}
+  \begin{gather*}
+    \begin{array}{rllrll}
+      \tm{P}, \tm{Q}, \tm{R}
+           :=& \tm{\cpLink{x}{y}}         &\text{link}
+      &  \mid& \tm{\piHalt}               &\text{terminated process}
+      \\ \mid& \tm{\piNew{x}{P}}          &\text{name restriction, ``new''}
+      &  \mid& \tm{( \piPar{P}{Q} )}      &\text{parallel composition, ``mix''}
+      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{output}
+      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{input}
+      \\ \mid& \tm{\piBoundSend{x}{}{P}}  &\text{``halt''}
+      &  \mid& \tm{\cpWait{x}{}{P}}       &\text{wait}
+      \\ \mid& \tm{\cpInl{x}{P}}          &\text{select left choice}
+      &  \mid& \tm{\cpInr{x}{P}}          &\text{select right choice}
+      \\ \mid& \tm{\cpCase{x}{P}{Q}}      &\text{offer binary choice}
+      &  \mid& \tm{\cpAbsurd{x}}          &\text{offer nullary choice}
+    \end{array}
+  \end{gather*}
+\end{definition}
 
-  \caption{Hypersequent Classical Processes (\hcp)}
-  \label{fig:hcp}
-\end{figure*}
+\begin{definition}[Structural congruence]\label{def:hcp-equiv}
+  We define the structural congruence $\equiv$ as the congruence closure over
+  terms which satisfies the following additional axioms:
+  \begin{gather*}
+    \setlength{\arraycolsep}{3pt}
+    \begin{array}{llcllllcll}
+        \cpEquivLinkComm
+      & \tm{\cpLink{x}{y}}
+      & \equiv
+      & \tm{\cpLink{y}{x}}
+      &
+      &
+        \hccpEquivMixHalt1
+      & \tm{\piPar{P}{\piHalt}}
+      & \equiv
+      & \tm{P}
+      &
+      \\
+        \hccpEquivMixComm
+      & \tm{\piPar{P}{Q}}
+      & \equiv
+      & \tm{\piPar{Q}{P}}
+      &
+      &
+        \hccpEquivMixAss1
+      & \tm{\piPar{P}{( \piPar{Q}{R} )}}
+      & \equiv
+      & \tm{\piPar{( \piPar{P}{Q} )}{R}}
+      &
+      \\
+        \hccpEquivNewComm
+      & \tm{\piNew{x}{\piNew{y}{P}}}
+      & \equiv
+      & \tm{\piNew{y}{\piNew{x}{P}}}
+      &
+      &
+        \hccpEquivScopeExt1
+      & \tm{\piNew{x}{( \piPar{P}{Q} )}}
+      & \equiv
+      & \tm{\piPar{P}{\piNew{x}{Q}}}
+      & \text{if }\notFreeIn{x}{P} 
+    \end{array}
+  \end{gather*}
+\end{definition}
 
-\begin{theorem}\label{thm:cp2hcp-typing}
-  If $\seq[P]{\Gamma}$ in \cp, then $\seq[P]{\Gamma}$ in \hcp.
-\end{theorem}
-\begin{theorem}\label{thm:hcp2cp-typing}
-  If $\seq[P]{\Gamma}$ in \hcp, then $\seq[P]{\Gamma}$ in \cp.
-\end{theorem}
-\begin{definition}\label{def:hcp-bigtens}
-  \(\!%
-  \begin{array}{lcl}
-    \ty{\bigparr\emptycontext}
-    & = & \ty{\bot}
+\begin{definition}[Reduction]\label{def:hcp-reduction}
+  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
+  to the process $\tm{Q}$ in a single step. Reductions can only be constructed
+  as follows:
+  \begin{gather*}
+    \begin{array}{llcll}
+      &
+      & \vdots
+      &
       \\
-    \ty{\bigparr(\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n})}
-    & = & \ty{A_1 \parr \dots \parr A_n}
+      \cpRedBetaTensParr
+      & \tm{\cpCut{x}{\piSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
+      & \Longrightarrow
+      & \tm{\piNew{x}{\piNew{y}{(\piPar{P}{\cpSub{y}{z}{R}})}}}
+      \\
+      \cpRedBetaOneBot
+      & \tm{\cpCut{x}{\piSend{x}{}{P}}{\piRecv{x}{}{P}}}
+      & \Longrightarrow
+      & \tm{\piPar{P}{Q}}
+      \\
+      &
+      & \vdots
+      &
     \end{array}
-  \)
+  \end{gather*}
+  \begin{center}
+    \begin{prooftree*}
+      \AXC{$\reducesto{P}{P^\prime}$}
+      \SYM{\hccpRedGammaNew}
+      \UIC{$\reducesto{\piNew{x}{P}}{\piNew{x}{P^\prime}}$}
+    \end{prooftree*}
+    \begin{prooftree*}
+      \AXC{$\reducesto{P}{P^\prime}$}
+      \SYM{\hccpRedGammaMix}
+      \UIC{$\reducesto{\piPar{P}{Q}}{\piPar{P^\prime}{Q}}$}
+    \end{prooftree*}
+    \begin{prooftree*}
+      \AXC{$\tm{P}\equiv\tm{Q}$}
+      \AXC{$\reducesto{Q}{Q^\prime}$}
+      \AXC{$\tm{Q^\prime}\equiv\tm{P^\prime}$}
+      \SYM{\hccpRedGammaEquiv}
+      \TIC{$\reducesto{P}{P^\prime}$}
+    \end{prooftree*}
+  \end{center}
+  The relations $\Longrightarrow^{?}$, $\Longrightarrow^{+}$, and
+  $\Longrightarrow^\star$ are the reflexive, transitive and reflexive,
+  transitive closures of $\Longrightarrow$. 
 \end{definition}
-\begin{lemma}\label{lem:hcp-bigparr}
-  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
-\end{lemma}
-\begin{definition}\label{def:hcp-bigtens}
-  \(\!%
-  \begin{array}{lcl}
-    \ty{\bigtens\emptyhypercontext}
-    & = & \ty{\one}
-    \\
-    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
-    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
-  \end{array}
-  \)
-\end{definition}
-\begin{theorem}\label{thm:hcp-bigtens}
-  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \hcp.
-\end{theorem}
-\begin{corollary}[Conservative Extension]
-  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
-\end{corollary}
 
-%% Hypersequent Classical Processes Taken Apart
 \begin{figure*}[!htb]
@@
   \centering
-  (Where each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.)
+  (Where each logical rule has the side condition that $\tm{x} \not\in
+  \ty{\mathcal{G}}$.)
 
-  \caption{Hypersequent Classical Processes \emph{Taken Apart} (\hccp)}
+  \caption{Hypersequent Classical Processes (\hcp)}
   \label{fig:hccp}
@@
 
-\begin{theorem}\label{thm:hcp2hccp-typing}
-  If $\seq[P]{\mathcal{G}}$ in \hcp, then $\seq[P]{\mathcal{G}}$ in \hccp.
+\begin{theorem}\label{thm:cp2hcp-typing}
+  If $\seq[P]{\Gamma}$ in \cp, then $\seq[\mtf{P}]{\Gamma}$ in \hcp.
 \end{theorem}
-\begin{theorem}\label{thm:hccp2hcp-typing}
-  If $\seq{\mathcal{G}}$ in \hccp, then $\seq{\mathcal{G}}$ in \hcp.
+\begin{proof}
+  By induction on the structure of the derivation of $\seq[P]{\Gamma}$.
+    \begin{itemize}
+  \item 
+    Case \textsc{Cut}.
+    We rewrite as follows:
+    \begin{center}
+      \scalebox{0.9}{\(
+        \begin{array}{lcl}
+          \AXC{$\seq[P]{\mathcal{G} \hsep \tmty{x}{A}, \Gamma}$}
+          \AXC{$\seq[Q]{\mathcal{H} \hsep \tmty{x}{A^\bot}, \Delta}$}
+          \NOM{Cut}
+          \BIC{$\seq[\cpCut{x}{P}{Q}]{
+          \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+          \DisplayProof
+          & \Rightarrow
+          & \AXC{$\seq[\mtf{P}]{\mathcal{G} \hsep \tmty{x}{A}, \Gamma}$}
+            \AXC{$\seq[\mtf{Q}]{\mathcal{H} \hsep \tmty{x}{A^\bot}, \Delta}$}
+            \NOM{H-Mix} 
+            \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
+            \mathcal{G} \hsep \mathcal{H} \hsep
+            \tmty{x}{A}, \Gamma \hsep \tmty{x}{A^\bot}, \Delta}$}
+            \NOM{H-Cycle}
+            \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
+            \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+            \DisplayProof
+        \end{array}
+        \)}
+    \end{center}
+  \item
+    Case $(\tens)$.
+    We rewrite as follows:
+    \begin{center}
+      \scalebox{0.9}{\(
+        \begin{array}{lcl}
+          \AXC{$\seq[P]{\mathcal{G} \hsep \tmty{y}{A}, \Gamma}$}
+          \AXC{$\seq[Q]{\mathcal{H} \hsep \tmty{x}{B}, \Delta}$}
+          \SYM{\tens}
+          \BIC{$\seq[\cpSend{x}{y}{P}{Q}]{
+          \mathcal{G} \hsep \mathcal{H} \hsep \tmty{x}{A \tens B}, \Gamma, \Delta}$}
+          \DisplayProof
+          & \Rightarrow
+          & \AXC{$\seq[\mtf{P}]{\mathcal{G} \hsep \tmty{y}{A}, \Gamma}$}
+            \AXC{$\seq[\mtf{Q}]{\mathcal{H} \hsep \tmty{x}{B}, \Delta}$}
+            \NOM{H-Mix}
+            \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
+            \mathcal{G} \hsep \mathcal{H} \hsep
+            \tmty{y}{A}, \Gamma \hsep \tmty{x}{B}, \Delta}$}
+            \NOM{H-Cycle}
+            \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
+            \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+            \DisplayProof
+        \end{array}
+        \)}
+    \end{center}
+  \item
+    Case $(\one)$.
+    We rewrite as follows:
+    \begin{center}
+      \scalebox{0.9}{\(
+        \begin{array}{lcl}
+          \AXC{}\SYM{\one}
+          \UIC{$\seq[\cpHalt{x}]{\tmty{x}{\one}}$}
+          \DisplayProof
+          & \Rightarrow
+          & \AXC{}
+            \NOM{H-Halt}
+            \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
+            \SYM{\one}
+            \UIC{$\seq[\piBoundSend{x}{}{\piHalt}]{\tmty{x}{\one}}$}
+            \DisplayProof
+        \end{array}      
+        \)}
+    \end{center}
+  \end{itemize}
+  The other cases are trivial.
+\end{proof}
+
+\begin{definition}\label{def:hcp-bigparr}
+  We can interpret environments as types by collapsing them using a series
+  of pars.
+  \begin{gather*}
+    \begin{array}{lcl}
+      \ty{\bigparr(\emptycontext)}
+      & = & \ty{\bot}
+      \\
+      \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
+      & = & \ty{A_1 \parr \dots \parr A_n}
+    \end{array}
+  \end{gather*}
+\end{definition}
+
+\begin{lemma}\label{lem:hcp-bigparr}
+  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
+\end{lemma}
+\begin{proof}
+  By induction on the structure of $\Gamma$.
+  \begin{itemize}
+  \item
+    If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
+  \item
+    If $\ty{\Gamma} = \ty{A, B, \Gamma'}$,
+    then we apply $(\parr)$ to get $\seq{A \parr B, \Gamma'}$,\\
+    and apply the induction hypothesis.
+  \end{itemize}
+\end{proof}
+
+\begin{definition}\label{def:hcp-bigtens}
+  We can interpret hyper-environments as types by collapsing them using a series
+  of tensors. In the case of the empty hyper-environment
+  $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
+  \begin{gather*}
+    \begin{array}{lcl}
+      \ty{\bigtens(\emptyhypercontext)}
+      & = & \ty{\one}
+      \\
+      \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
+      & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
+    \end{array}
+  \end{gather*}
+\end{definition}
+
+\begin{theorem}\label{thm:hcp2cp-bigtens}
+  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
 \end{theorem}

### 2018-04-20 doc/tlla2018/main.tex
Finished proofs for TLLA

@@
 \providecommand{\event}{Linearity and TLLA 2018}
+\usepackage{nameref,hyperref,cleveref}
+\usepackage[inline]{enumitem}
 \usepackage{breakurl} % Not needed if you use pdflatex only.
@@
 
-%% Classical Processes
+\section{Classical Processes}
 
@@
 
-%% Hypersequent Classical Processes
+\section{Hypersequent Classical Processes}
 
@@
       &  \mid& \tm{( \piPar{P}{Q} )}      &\text{parallel composition, ``mix''}
-      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{output}
-      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{input}
+      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{``output''}
+      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{``input''}
       \\ \mid& \tm{\piBoundSend{x}{}{P}}  &\text{``halt''}
@@
   A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
-  to the process $\tm{Q}$ in a single step. Reductions can only be constructed
-  as follows:
+  to the process $\tm{Q}$ in a single step.
+  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
+  $\Longrightarrow$.
+  Reductions can be constructed as using the rules from \cref{def:cp-reduction},
+  with the following changes:
   \begin{gather*}
@@
   \end{center}
-  The relations $\Longrightarrow^{?}$, $\Longrightarrow^{+}$, and
-  $\Longrightarrow^\star$ are the reflexive, transitive and reflexive,
-  transitive closures of $\Longrightarrow$. 
 \end{definition}
@@
 
+\section{Relation between \cp and \hcp}
+
+\begin{definition}\label{def:cp2hcp-terms}
+  We define a translation from terms in \cp to terms in \hcp which breaks down
+  the term constructs in \cp into their more atomic constructs in \hcp.
+  \[
+    \begin{array}{lcllcl}
+         \tm{\mtf{\cpLink{x}{y}}}
+      &  := & \tm{\cpLink{x}{y}}
+      &  \tm{\mtf{\cpCut{x}{P}{Q}}}
+      &  := & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      \\ \tm{\mtf{\cpSend{x}{y}{P}{Q}}}
+      &  := & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  \tm{\mtf{\cpRecv{x}{y}{P}}}
+      &  := & \tm{\piRecv{x}{y}{\mtf{P}}}
+      \\ \tm{\mtf{\cpHalt{x}}}
+      &  := & \tm{\piBoundSend{x}{}{\piHalt}}
+      &  \tm{\mtf{\cpWait{x}{P}}}
+      &  := & \tm{\piRecv{x}{}{\mtf{P}}}
+      \\ \tm{\mtf{\cpInl{x}{P}}}
+      &  := & \tm{\cpInl{x}{\mtf{P}}}
+      &  \tm{\mtf{\cpInr{x}{P}}}
+      &  := & \tm{\cpInr{x}{\mtf{P}}}
+      \\ \tm{\mtf{\cpCase{x}{P}{Q}}}
+      &  := & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
+      &  \tm{\mtf{\cpAbsurd{x}}}
+      &  := & \tm{\cpAbsurd{x}}
+    \end{array}
+  \]
+\end{definition}
+
 \begin{theorem}\label{thm:cp2hcp-typing}
@@
     Case \textsc{Cut}.
-    We rewrite as follows:
-    \begin{center}
-      \scalebox{0.9}{\(
+    We rewrite to:
+    \[
       \begin{array}{lcl}
-          \AXC{$\seq[P]{\mathcal{G} \hsep \tmty{x}{A}, \Gamma}$}
-          \AXC{$\seq[Q]{\mathcal{H} \hsep \tmty{x}{A^\bot}, \Delta}$}
+        \AXC{$\seq[P]{\Gamma, \tmty{x}{A}}$}
+        \AXC{$\seq[Q]{\Delta, \tmty{x}{A^\bot}}$}
         \NOM{Cut}
-          \BIC{$\seq[\cpCut{x}{P}{Q}]{
-          \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+        \BIC{$\seq[\cpCut{x}{P}{Q}]{\Gamma, \Delta}$}
         \DisplayProof
         & \Rightarrow
-          & \AXC{$\seq[\mtf{P}]{\mathcal{G} \hsep \tmty{x}{A}, \Gamma}$}
-            \AXC{$\seq[\mtf{Q}]{\mathcal{H} \hsep \tmty{x}{A^\bot}, \Delta}$}
+        & \AXC{$\seq[\mtf{P}]{\Gamma, \tmty{x}{A}}$}
+          \AXC{$\seq[\mtf{Q}]{\Delta, \tmty{x}{A^\bot}}$}
           \NOM{H-Mix} 
           \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
-            \mathcal{G} \hsep \mathcal{H} \hsep
-            \tmty{x}{A}, \Gamma \hsep \tmty{x}{A^\bot}, \Delta}$}
+          \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
           \NOM{H-Cycle}
           \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
-            \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+          \Gamma, \Delta}$}
           \DisplayProof
       \end{array}
-        \)}
-    \end{center}
+    \]
   \item
@@
     We rewrite as follows:
-    \begin{center}
-      \scalebox{0.9}{\(
+    \[
       \begin{array}{lcl}
-          \AXC{$\seq[P]{\mathcal{G} \hsep \tmty{y}{A}, \Gamma}$}
-          \AXC{$\seq[Q]{\mathcal{H} \hsep \tmty{x}{B}, \Delta}$}
+        \AXC{$\seq[P]{\Gamma, \tmty{y}{A}}$}
+        \AXC{$\seq[Q]{\Delta, \tmty{x}{B}}$}
         \SYM{\tens}
-          \BIC{$\seq[\cpSend{x}{y}{P}{Q}]{
-          \mathcal{G} \hsep \mathcal{H} \hsep \tmty{x}{A \tens B}, \Gamma, \Delta}$}
+        \BIC{$\seq[\cpSend{x}{y}{P}{Q}]{\Gamma, \Delta, \tmty{x}{A \tens B}}$}
         \DisplayProof
         & \Rightarrow
-          & \AXC{$\seq[\mtf{P}]{\mathcal{G} \hsep \tmty{y}{A}, \Gamma}$}
-            \AXC{$\seq[\mtf{Q}]{\mathcal{H} \hsep \tmty{x}{B}, \Delta}$}
+        & \AXC{$\seq[\mtf{P}]{\Gamma, \tmty{y}{A}}$}
+          \AXC{$\seq[\mtf{Q}]{\Delta, \tmty{x}{B}}$}
           \NOM{H-Mix}
           \BIC{$\seq[\piPar{\mtf{P}}{\mtf{Q}}]{
-            \mathcal{G} \hsep \mathcal{H} \hsep
-            \tmty{y}{A}, \Gamma \hsep \tmty{x}{B}, \Delta}$}
-            \NOM{H-Cycle}
-            \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
-            \mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+          \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
+          \SYM{\tens}
+          \UIC{$\seq[\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
+          \Gamma, \Delta, \tmty{x}{A \tens B}}$}
           \DisplayProof
       \end{array}
-        \)}
-    \end{center}
+    \]
   \item
@@
     We rewrite as follows:
-    \begin{center}
-      \scalebox{0.9}{\(
+    \[
       \begin{array}{lcl}
@@
       \end{array}      
-        \)}
-    \end{center}
+    \]
   \end{itemize}
@@
 
-\begin{definition}\label{def:hcp-bigparr}
+\begin{theorem}\label{thm:cp2hcp-equiv}
+  If $\tm{P}\equiv\tm{Q}$ in \cp, then $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
+\end{theorem}
+\begin{proof}
+  By induction on the structure of the derivation of $\tm{P}\equiv\tm{Q}$.
+  \begin{itemize}
+  \item
+    Case \cpEquivCutComm.
+    \[
+      \begin{array}{lcl}
+        \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+        & \equiv & \text{by \hccpEquivMixComm}
+        \\
+        \tm{\piNew{x}{(\piPar{\mtf{Q}}{\mtf{P}})}}
+      \end{array}
+    \]
+  \item
+    Case \cpEquivCutAss1.
+    \[
+      \begin{array}{lcl}
+        \tm{\piNew{x}{(\piPar{\mtf{P}}{\piNew{y}{(\piPar{\mtf{Q}}{\mtf{R}})}})}}
+        & \equiv & \text{by \hccpEquivScopeExt2}
+        \\
+        \tm{\piNew{x}{\piNew{y}{(\piPar{\mtf{P}}{(\piPar{\mtf{Q}}{\mtf{R}})})}}}
+        & \equiv & \text{by \hccpEquivNewComm}
+        \\
+        \tm{\piNew{y}{\piNew{x}{(\piPar{\mtf{P}}{(\piPar{\mtf{Q}}{\mtf{R}})})}}}
+        & \equiv & \text{by \hccpEquivMixAss1}
+        \\
+        \tm{\piNew{y}{\piNew{x}{(\piPar{(\piPar{\mtf{P}}{\mtf{Q}})}{\mtf{R}})}}}
+        & \equiv & \text{by \hccpEquivScopeExt1 and \hccpEquivMixComm}
+        \\
+        \tm{\piNew{y}{(\piPar{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}{\mtf{R}})}}
+      \end{array}
+    \]
+  \end{itemize}
+  The other cases are trivial.
+\end{proof}
+
+\begin{theorem}\label{thm:cp2hcp-reduction}
+  If $\reducesto{P}{Q}$ in \cp, then $\reducesto{\mtf{P}}{\mtf{Q}}$ in \hcp.
+\end{theorem}
+\begin{proof}
+  By induction on the structure of the derivation of $\reducesto{P}{Q}$.
+  \begin{itemize}
+  \item
+    Case \cpRedBetaTensParr.
+    \begin{gather*}
+      \begin{array}{lcl}
+        \tm{\piNew{x}{(\piPar{\piBoundSend{x}{y}{(\piPar{P}{Q})}}{\piRecv{x}{z}{R}})}}
+        & \Longrightarrow & \text{by \hccpRedBetaTensParr}
+        \\
+        \tm{\piNew{x}{\piNew{y}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
+        & \equiv & \text{by \hccpEquivNewComm}
+        \\
+        \tm{\piNew{y}{\piNew{x}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
+        & \equiv & \text{by \hccpEquivMixAss1}
+        \\
+        \tm{\piNew{y}{\piNew{x}{(\piPar{P}{(\piPar{Q}{\cpSub{y}{z}{R}})})}}}
+        & \equiv & \text{by \hccpEquivScopeExt1}
+        \\
+        \tm{\piNew{y}{(\piPar{P}{\piNew{x}{(\piPar{Q}{\cpSub{y}{z}{R}})}})}}
+      \end{array}
+    \end{gather*}
+  \item
+    Case \cpRedBetaOneBot.
+    \begin{gather*}
+      \begin{array}{lcl}
+        \tm{\piNew{x}{(\piPar{\piBoundSend{x}{}{\piHalt}}{\piRecv{x}{}{\mtf{Q}}})}}
+        & \Longrightarrow & \text{by \hccpRedBetaOneBot}
+        \\
+        \tm{(\piPar{\piHalt}{\mtf{Q}})}
+        & \equiv & \text{by \hccpEquivMixHalt1}
+        \\
+        \tm{\mtf{Q}}
+      \end{array}
+    \end{gather*}
+  \end{itemize}
+  The other cases are trivial.
+\end{proof}
+
+\begin{definition}\label{def:bigparr}
   We can interpret environments as types by collapsing them using a series
@@
     \begin{array}{lcl}
-      \ty{\bigparr(\emptycontext)}
-      & = & \ty{\bot}
-      \\
       \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
@@
 
-\begin{lemma}\label{lem:hcp-bigparr}
-  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
+\begin{lemma}\label{lem:cp-bigparr}
+  If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
 \end{lemma}
@@
 
-\begin{definition}\label{def:hcp-bigtens}
+\begin{definition}\label{def:bigtens}
   We can interpret hyper-environments as types by collapsing them using a series
@@
 
+\begin{lemma}\label{lem:hcp2cp-split}
+  If $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp,
+  then there exist $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp.
+\end{lemma}
+\begin{proof}  
+  By induction on the structure of the derivation of
+  $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
+  taking care to remember the continuation of the derivation.
+  \begin{itemize}
+  \item 
+    Case \textsc{Cycle}. We know there \emph{must} be a corresponding
+    \textsc{H-Mix} deeper in the derivation. We have:
+    \[
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
+      \DisplayProof
+      \; \cdots f \cdots \;
+      \AXC{}\noLine
+      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, A \hsep \Delta, A^\bot}$}
+      \NOM{H-Cycle}
+      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, \Delta}$}
+      \DisplayProof
+      \; \cdots h \cdots \;
+      \AXC{}\noLine
+      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+      \DisplayProof
+    \]
+    By induction, we obtain some number of proofs in \cp corresponding
+    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
+    Each rule in $f$ modifies only one of these proofs (or joins two).
+    Therefore we can split $f$, applying each rule to its corresponding proof
+    (joining proofs as necessary).
+    We now have several proofs, including two of $\seq{\Gamma, A}$ and
+    $\seq{\Delta, A^\bot}$, which we join using \textsc{Cut}.
+    Then we do the same for the rules in $h$.
+  \item
+    Case $(\tens)$. We know there \emph{must} be a corresponding
+    \textsc{H-Mix} deeper in the derivation. We have:
+    \[
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
+      \DisplayProof
+      \; \cdots f \cdots \;
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, A \hsep \Delta, B}$}
+      \SYM{\tens}
+      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, \Delta, {A \tens B}}$}
+      \DisplayProof
+      \; \cdots h \cdots \;
+      \AXC{}\noLine\UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+      \DisplayProof
+    \]
+    By induction, we obtain some number of proofs in \cp corresponding
+    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
+    Each rule in $f$ modifies only one of these proofs (or joins two).
+    Therefore we can split $f$, applying each rule to its corresponding proof
+    (joining proofs as necessary).
+    We now have several proofs, including two of $\seq{\Gamma, A}$ and
+    $\seq{\Delta, B}$, which we join using $(\tens)$.
+    Then we do the same for the rules in $h$.
+  \item
+    Case $(\one)$. We know there \emph{must} be a corresponding \textsc{H-Halt}
+    deeper in the derivation. There are two cases: either the corresponding
+    \textsc{H-Halt} follows immediately, in which case we rewrite the both rules
+    to an application of $(\one)$ in \cp, or it is deeper in the proof, in which
+    case it must be followed by an application of \textsc{Mix}. We have:
+    \[
+      \AXC{}
+      \NOM{H-Halt}
+      \UIC{\seq{\emptyhypercontext}}
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1}$}
+      \DisplayProof
+      \; \cdots f \cdots \;
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$} 
+      \SYM{\one}
+      \UIC{$\seq{\mathcal{G}_2 \hsep \one}$}
+      \DisplayProof
+      \; \cdots h \cdots \;
+      \AXC{}\noLine
+      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+      \DisplayProof
+    \]
+    By induction, we obtain some number of proofs in \cp corresponding
+    to the sequents in $\ty{\mathcal{G}_1}$.
+    Each rule in $f$ modifies only one of these proofs (or joins two).
+    Therefore we can split $f$, applying each rule to its corresponding proof
+    (joining proofs as necessary).
+    We now have several proofs corresponding to the sequents in
+    $\ty{\mathcal{G}_2}$.
+    Then we do the same for the rules in $h$.
+  \item
+    Case \textsc{Mix}. We know that there is no application of \textsc{H-Cycle}
+    or $(\tens)$ which eliminates the hypersequent separator introduced by this
+    application of \textsc{Mix}. We have:
+    \[
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
+      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
+      \DisplayProof
+      \; \cdots f \cdots \;
+      \AXC{}\noLine
+      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+      \DisplayProof
+    \]
+    By induction, we obtain some number of proofs in \cp corresponding
+    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
+    Each rule in $f$ modifies only one of these proofs (or joins two).
+    Therefore we can split $f$, applying each rule to its corresponding proof
+    (joining proofs as necessary).
+  \end{itemize}
+\end{proof}
+
 \begin{theorem}\label{thm:hcp2cp-bigtens}
@@
 \end{theorem}
+\begin{proof}
+  By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
+  \begin{itemize}
+  \item
+    If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
+  \item
+    If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
+    we apply \cref{lem:hcp2cp-split} to obtain proofs of $\seq{\Gamma_1}, \dots,
+    \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of
+    those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
+    \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single
+    proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
+  \end{itemize}
+\end{proof}
 

### 2018-04-23 doc/tlla2018/main.tex
Loading cleverref after amsmath
Rewrote & reordered proofs

@@
 \providecommand{\event}{Linearity and TLLA 2018}
+\usepackage{amsthm,amsmath}
 \usepackage{nameref,hyperref,cleveref}
@@
 \usepackage{textcomp,textgreek,upgreek}
-\usepackage{amsthm}
 \newtheorem{definition}{Definition}
@@
 \begin{definition}[Terms]\label{def:cp-terms}
-  \begin{gather*}
+  \[
     \begin{array}{rllrll}
@@
     \end{array}
-  \end{gather*}
+  \]
 \end{definition}
@@
     \begin{array}{llcll}
-      &
-      & \vdots
-      &
+      \hccpRedAxCut1
+      & \tm{\cpCut{x}{\cpLink{w}{x}}{P}}
+      & \Longrightarrow
+      & \tm{\cpSub{w}{x}{P}} 
       \\
-      \cpRedBetaTensParr
+      \hccpRedBetaTensParr
       & \tm{\cpCut{x}{\piSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
@@
       \\
-      \cpRedBetaOneBot
+      \hccpRedBetaOneBot
       & \tm{\cpCut{x}{\piSend{x}{}{P}}{\piRecv{x}{}{P}}}
@@
       \\
-      &
-      & \vdots
-      &
+      \hccpRedBetaPlusWith1
+      & \tm{\cpCut{x}{\cpInl{x}{P}}{\cpCase{x}{Q}{R}}}
+      & \Longrightarrow
+      & \tm{\cpCut{x}{P}{Q}}
+      \\
+      \hccpRedBetaPlusWith2
+      & \tm{\cpCut{x}{\cpInr{x}{P}}{\cpCase{x}{Q}{R}}}
+      & \Longrightarrow
+      & \tm{\cpCut{x}{P}{R}}
+      \\
+      \hccpRedKappaNuTens
+      & \tm{\piNew{x}{\piBoundSend{y}{z}{P}}}
+      & \Longrightarrow
+      & \tm{\piBoundSend{y}{z}{\piNew{x}{P}}}
+      \\
+      \hccpRedKappaNuParr
+      & \tm{\piNew{x}{\piRecv{y}{z}{P}}}
+      & \Longrightarrow
+      & \tm{\piRecv{y}{z}{\piNew{x}{P}}}
+      \\
+      \hccpRedKappaNuOne
+      & \tm{\piNew{x}{\piBoundSend{y}{}{P}}}
+      & \Longrightarrow
+      & \tm{\piBoundSend{y}{}{\piNew{x}{P}}}
+      \\
+      \hccpRedKappaNuBot
+      & \tm{\piNew{x}{\piRecv{y}{}{P}}}
+      & \Longrightarrow
+      & \tm{\piRecv{y}{}{\piNew{x}{P}}}
+      \\
+      \hccpRedKappaNuPlus1
+      & \tm{\piNew{x}{\cpInl{y}{P}}}
+      & \Longrightarrow
+      & \tm{\cpInl{y}{\piNew{x}{P}}}
+      \\
+      \hccpRedKappaNuPlus2
+      & \tm{\piNew{x}{\cpInr{y}{P}}}
+      & \Longrightarrow
+      & \tm{\cpInr{y}{\piNew{x}{P}}}
+      \\
+      \hccpRedKappaNuWith
+      & \tm{\piNew{x}{\cpCase{y}{P}{Q}}}
+      & \Longrightarrow
+      & \tm{\cpCase{y}{\piNew{x}{P}}{\piNew{x}{Q}}}
+      \\
+      \hccpRedKappaNuTop
+      & \tm{\piNew{x}{\cpAbsurd{y}}}
+      & \Longrightarrow
+      & \tm{\cpAbsurd{y}}
+      \\
+      \hccpRedKappaMixTens
+      & \tm{(\piPar{\piBoundSend{y}{z}{P}}{R})}
+      & \Longrightarrow
+      & \tm{\piBoundSend{y}{z}{(\piPar{P}{R})}}
+      \\
+      \hccpRedKappaMixParr
+      & \tm{(\piPar{\piRecv{y}{z}{P}}{R})}
+      & \Longrightarrow
+      & \tm{\piRecv{y}{z}{(\piPar{P}{R})}}
+      \\
+      \hccpRedKappaMixOne
+      & \tm{(\piPar{\piBoundSend{y}{}{P}}{R})}
+      & \Longrightarrow
+      & \tm{\piBoundSend{y}{}{(\piPar{P}{R})}}
+      \\
+      \hccpRedKappaMixBot
+      & \tm{(\piPar{\piRecv{y}{}{P}}{R})}
+      & \Longrightarrow
+      & \tm{\piRecv{y}{}{(\piPar{P}{R})}}
+      \\
+      \hccpRedKappaMixPlus1
+      & \tm{(\piPar{\cpInl{y}{P}}{R})}
+      & \Longrightarrow
+      & \tm{\cpInl{y}{(\piPar{P}{R})}}
+      \\
+      \hccpRedKappaMixPlus2
+      & \tm{(\piPar{\cpInr{y}{P}}{R})}
+      & \Longrightarrow
+      & \tm{\cpInr{y}{(\piPar{P}{R})}}
+      \\
+      \hccpRedKappaMixWith
+      & \tm{(\piPar{\cpCase{y}{P}{Q}}{R})}
+      & \Longrightarrow
+      & \tm{\cpCase{y}{(\piPar{P}{R})}{(\piPar{Q}{R})}}
+      \\
+      \hccpRedKappaMixTop
+      & \tm{(\piPar{\cpAbsurd{y}}{R})}
+      & \Longrightarrow
+      & \tm{\cpAbsurd{y}}
     \end{array}
@@
   Logical Rules.
-
   \begin{center} \hccpInfBoundTens \hccpInfParr  \end{center}
@@
           \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
-          \NOM{H-Cycle}
+          \NOM{H-New}
           \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
@@
 
+\begin{definition}\label{def:hcp-kappa}
+  We define the relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ as the congruence
+  closure of the $\gamma$- and $\kappa$-rules for \hcp (see
+  \cref{def:hcp-reduction}).
+\end{definition}
+
+\begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
+  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp,
+  then there exist $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ in \cp,
+  such that
+  $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
+\end{lemma}
+\begin{proof}  
+  We repeatedly apply the $\kappa{\ppar}$-rules to move the applications of
+  \textsc{H-Mix} upwards. There are three cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item if an \textsc{H-Mix} gets stuck under an \textsc{H-New}, it forms a
+    \textsc{Cut};
+  \item if an \textsc{H-Mix} gets stuck under a $(\tens)$, it forms a \cp
+    $(\tens)$;
+  \item otherwise, it moves all the way to the top.
+  \end{enumerate*}
+  Since the only way to continue after a $(\one)$ is by using an \textsc{H-Mix},
+  all applications of $(\one)$ are now be followed by an application of
+  \textsc{H-Halt}, forming a \cp $(\one)$.
+\end{proof}
+
+We can interpret environments as types by collapsing them using a series of
+pars.
 \begin{definition}\label{def:bigparr}
-  We can interpret environments as types by collapsing them using a series
-  of pars.
-  \begin{gather*}
+  \(
   \begin{array}{lcl}
@@
   \end{array}
-  \end{gather*}
+  \)
 \end{definition}
@@
 
-\begin{definition}\label{def:bigtens}
 We can interpret hyper-environments as types by collapsing them using a series
@@
 $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
-  \begin{gather*}
+\begin{definition}\label{def:bigtens}
+  \(
   \begin{array}{lcl}
@@
   \end{array}
-  \end{gather*}
+  \)
 \end{definition}
-
-\begin{lemma}\label{lem:hcp2cp-split}
-  If $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp,
-  then there exist $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp.
-\end{lemma}
-\begin{proof}  
-  By induction on the structure of the derivation of
-  $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
-  taking care to remember the continuation of the derivation.
-  \begin{itemize}
-  \item 
-    Case \textsc{Cycle}. We know there \emph{must} be a corresponding
-    \textsc{H-Mix} deeper in the derivation. We have:
-    \[
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
-      \DisplayProof
-      \; \cdots f \cdots \;
-      \AXC{}\noLine
-      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, A \hsep \Delta, A^\bot}$}
-      \NOM{H-Cycle}
-      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, \Delta}$}
-      \DisplayProof
-      \; \cdots h \cdots \;
-      \AXC{}\noLine
-      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
-      \DisplayProof
-    \]
-    By induction, we obtain some number of proofs in \cp corresponding
-    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
-    Each rule in $f$ modifies only one of these proofs (or joins two).
-    Therefore we can split $f$, applying each rule to its corresponding proof
-    (joining proofs as necessary).
-    We now have several proofs, including two of $\seq{\Gamma, A}$ and
-    $\seq{\Delta, A^\bot}$, which we join using \textsc{Cut}.
-    Then we do the same for the rules in $h$.
-  \item
-    Case $(\tens)$. We know there \emph{must} be a corresponding
-    \textsc{H-Mix} deeper in the derivation. We have:
-    \[
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
-      \DisplayProof
-      \; \cdots f \cdots \;
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, A \hsep \Delta, B}$}
-      \SYM{\tens}
-      \UIC{$\seq{\mathcal{G}_3 \hsep \Gamma, \Delta, {A \tens B}}$}
-      \DisplayProof
-      \; \cdots h \cdots \;
-      \AXC{}\noLine\UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
-      \DisplayProof
-    \]
-    By induction, we obtain some number of proofs in \cp corresponding
-    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
-    Each rule in $f$ modifies only one of these proofs (or joins two).
-    Therefore we can split $f$, applying each rule to its corresponding proof
-    (joining proofs as necessary).
-    We now have several proofs, including two of $\seq{\Gamma, A}$ and
-    $\seq{\Delta, B}$, which we join using $(\tens)$.
-    Then we do the same for the rules in $h$.
-  \item
-    Case $(\one)$. We know there \emph{must} be a corresponding \textsc{H-Halt}
-    deeper in the derivation. There are two cases: either the corresponding
-    \textsc{H-Halt} follows immediately, in which case we rewrite the both rules
-    to an application of $(\one)$ in \cp, or it is deeper in the proof, in which
-    case it must be followed by an application of \textsc{Mix}. We have:
-    \[
-      \AXC{}
-      \NOM{H-Halt}
-      \UIC{\seq{\emptyhypercontext}}
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1}$}
-      \DisplayProof
-      \; \cdots f \cdots \;
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$} 
-      \SYM{\one}
-      \UIC{$\seq{\mathcal{G}_2 \hsep \one}$}
-      \DisplayProof
-      \; \cdots h \cdots \;
-      \AXC{}\noLine
-      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
-      \DisplayProof
-    \]
-    By induction, we obtain some number of proofs in \cp corresponding
-    to the sequents in $\ty{\mathcal{G}_1}$.
-    Each rule in $f$ modifies only one of these proofs (or joins two).
-    Therefore we can split $f$, applying each rule to its corresponding proof
-    (joining proofs as necessary).
-    We now have several proofs corresponding to the sequents in
-    $\ty{\mathcal{G}_2}$.
-    Then we do the same for the rules in $h$.
-  \item
-    Case \textsc{Mix}. We know that there is no application of \textsc{H-Cycle}
-    or $(\tens)$ which eliminates the hypersequent separator introduced by this
-    application of \textsc{Mix}. We have:
-    \[
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_1}$}
-      \AXC{}\noLine\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
-      \DisplayProof
-      \; \cdots f \cdots \;
-      \AXC{}\noLine
-      \UIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
-      \DisplayProof
-    \]
-    By induction, we obtain some number of proofs in \cp corresponding
-    to the sequents in $\ty{\mathcal{G}_1}$ and $\ty{\mathcal{G}_2}$.
-    Each rule in $f$ modifies only one of these proofs (or joins two).
-    Therefore we can split $f$, applying each rule to its corresponding proof
-    (joining proofs as necessary).
-  \end{itemize}
-\end{proof}
 

### 2018-04-23 doc/tlla2018/main.tex
Minor corrections

@@
   $\Longrightarrow$.
-  Reductions can be constructed as using the rules from \cref{def:cp-reduction},
-  with the following changes:
+  Reductions can only be constructed as follows:
   \begin{gather*}
@@
     If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
-    we apply \cref{lem:hcp2cp-split} to obtain proofs of $\seq{\Gamma_1}, \dots,
+    we apply \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots,
     \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of

### 2018-04-23 doc/tlla2018/main.tex
Minor corrections

@@
 \providecommand{\event}{Linearity and TLLA 2018}
-\usepackage{amsthm,amsmath}
+\usepackage[fleqn]{amsmath}
+\usepackage{amsthm}
 \usepackage{nameref,hyperref,cleveref}
@@
   \institute{University of Edinburgh\\ Edinburgh, Scotland}
-  \email{wen.kokke@ed.ac.uk}}
+  \email{wen.kokke@ed.ac.uk}
+  \and
+  Marco Peressotti
+  \institute{University of Southern Denmark\\ Odense, Denmark}
+  \email{peressotti@imada.sdu.dk}
+  \and
+  Fabrizio Montesi
+  \institute{University of Southern Denmark\\ Odense, Denmark}
+  \email{fmontesi@imada.sdu.dk}}
 \def\titlerunning{Taking Linear Logic Apart}
-\def\authorrunning{Wen Kokke}
+\def\authorrunning{W.\ Kokke, M.\ Peressotti, and F.\ Montesi}
 
@@
   terms which satisfies the following additional axioms:
-  \begin{gather*}
+  \[
     \setlength{\arraycolsep}{3pt}
@@
   Reductions can only be constructed as follows:
-  \begin{gather*}
+  \[
     \begin{array}{llcll}
@@
     \end{array}
-  \end{gather*}
+  \]
   \begin{center}
@@
 \begin{definition}[Types]\label{def:cp-types}
-  \begin{gather*}
+  \[
     \begin{array}{rclrcl}
@@
 \begin{definition}[Terms]\label{def:hcp-terms}
-  \begin{gather*}
+  \[
     \begin{array}{rllrll}
@@
       \hccpRedBetaTensParr
-      & \tm{\cpCut{x}{\piSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
+      & \tm{\cpCut{x}{\piBoundSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
       & \Longrightarrow
@@
       \hccpRedBetaOneBot
-      & \tm{\cpCut{x}{\piSend{x}{}{P}}{\piRecv{x}{}{P}}}
+      & \tm{\cpCut{x}{\piBoundSend{x}{}{P}}{\piRecv{x}{}{P}}}
       & \Longrightarrow
@@
 \begin{proof}
-  By induction on the structure of the derivation of $\seq[P]{\Gamma}$.
+  By induction on the derivation of $\seq[P]{\Gamma}$.
     \begin{itemize}
   \item 
-    Case \textsc{Cut}.
-    We rewrite to:
-    \[
+    Case \textsc{Cut}. We rewrite to:
+    \begin{gather*}
       \begin{array}{lcl}
@@
       \end{array}
-    \]
+    \end{gather*}
   \item
-    Case $(\tens)$.
-    We rewrite as follows:
-    \[
+    Case $(\tens)$. We rewrite as follows:
+    \begin{gather*}
       \begin{array}{lcl}
@@
       \end{array}
-    \]
+    \end{gather*}
   \item
-    Case $(\one)$.
-    We rewrite as follows:
-    \[
+    Case $(\one)$. We rewrite as follows:
+    \begin{flalign*}
       \begin{array}{lcl}
@@
       \end{array}      
-    \]
+    \end{flalign*}
   \end{itemize}
@@
 \begin{proof}
-  By induction on the structure of the derivation of $\tm{P}\equiv\tm{Q}$.
+  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
   \begin{itemize}
@@
     Case \cpEquivCutComm.
-    \[
+    \begin{gather*}
     \begin{array}{lcl}
@@
     \end{array}
-    \]
+    \end{gather*}
   \item
     Case \cpEquivCutAss1.
-    \[
+    \begin{gather*}
     \begin{array}{lcl}
       \tm{\piNew{x}{(\piPar{\mtf{P}}{\piNew{y}{(\piPar{\mtf{Q}}{\mtf{R}})}})}}
-        & \equiv & \text{by \hccpEquivScopeExt2}
-        \\
-        \tm{\piNew{x}{\piNew{y}{(\piPar{\mtf{P}}{(\piPar{\mtf{Q}}{\mtf{R}})})}}}
-        & \equiv & \text{by \hccpEquivNewComm}
-        \\
-        \tm{\piNew{y}{\piNew{x}{(\piPar{\mtf{P}}{(\piPar{\mtf{Q}}{\mtf{R}})})}}}
-        & \equiv & \text{by \hccpEquivMixAss1}
-        \\
-        \tm{\piNew{y}{\piNew{x}{(\piPar{(\piPar{\mtf{P}}{\mtf{Q}})}{\mtf{R}})}}}
-        & \equiv & \text{by \hccpEquivScopeExt1 and \hccpEquivMixComm}
+      & \equiv & \text{%
+                 by \hccpEquivNewComm, \hccpEquivMixAss1, \hccpEquivMixComm,
+                 and \hccpEquivScopeExt{}}
       \\
@@
     \end{array}
-    \]
+    \end{gather*}
   \end{itemize}
@@
 \begin{proof}
-  By induction on the structure of the derivation of $\reducesto{P}{Q}$.
+  By induction on the the derivation of $\reducesto{P}{Q}$.
   \begin{itemize}
@@
       \tm{\piNew{x}{\piNew{y}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
-        & \equiv & \text{by \hccpEquivNewComm}
-        \\
-        \tm{\piNew{y}{\piNew{x}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
-        & \equiv & \text{by \hccpEquivMixAss1}
-        \\
-        \tm{\piNew{y}{\piNew{x}{(\piPar{P}{(\piPar{Q}{\cpSub{y}{z}{R}})})}}}
-        & \equiv & \text{by \hccpEquivScopeExt1}
+      & \equiv & \text{%
+                 by \hccpEquivNewComm, \hccpEquivMixAss1, and \hccpEquivScopeExt1}
       \\
@@
 
-\begin{definition}\label{def:hcp-kappa}
+\begin{theorem}\label{hcp2cp-reduction}
+  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that
+  $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\reducesto{\mtf{P}}{R}$
+\end{proof}
+
+\begin{definition}\label{def:hcp-gammakappa}
   We define the relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ as the congruence
@@
   \begin{enumerate*}[label={\alph*)}]
-  \item if an \textsc{H-Mix} gets stuck under an \textsc{H-New}, it forms a
-    \textsc{Cut};
-  \item if an \textsc{H-Mix} gets stuck under a $(\tens)$, it forms a \cp
-    $(\tens)$;
-  \item otherwise, it moves all the way to the top.
+  \item
+    if an \textsc{H-Mix} gets stuck under an \textsc{H-New}, it forms a
+    \cp \textsc{Cut};
+  \item
+    if an \textsc{H-Mix} gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
+  \item
+    otherwise, it moves all the way to the top.
   \end{enumerate*}
@@
 \begin{definition}\label{def:bigparr}
-  \(
+  \begin{gather*}
   \begin{array}{lcl}
@@
   \end{array}
-  \)
+  \end{gather*}
 \end{definition}
@@
 \begin{proof}
-  By induction on the structure of $\Gamma$.
+  By induction on the structure of the environment $\Gamma$.
   \begin{itemize}
@@
 \begin{definition}\label{def:bigtens}
-  \(
+  \begin{gather*}
   \begin{array}{lcl}

### 2018-04-23 doc/tlla2018/main.tex
Added progress and preservation

@@
 
+\begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
+  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
+\end{lemma}
+\begin{proof}
+  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
+\end{proof}
+
+\begin{theorem}[Preservation]\label{thm:cp-preservation}
+  If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\reducesto{P}{Q}$.
+\end{proof}
+
+\begin{theorem}[Progress]\label{thm:cp-progress}
+  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that
+  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\seq[P]{\Gamma}$.
+  If the last rule is \textsc{Cut}, there are four cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item
+    if either side of the cut is an axiom, we apply \cpRedAxCut1;
+  \item
+    if either side of the cut is itself a cut, we recursively eliminate the cut;
+  \item
+    if both sides are logical rules acting on the cut formula, we apply
+    one of the $\beta$-rules;
+  \item
+    otherwise, at least one side is a logical rule acting on a formula other
+    than the cut formula, in which case we apply one of the $\kappa$-rules.
+  \end{enumerate*}
+\end{proof}
+
 \section{Hypersequent Classical Processes}
@@
       &  \mid& \tm{\piHalt}               &\text{terminated process}
-      \\ \mid& \tm{\piNew{x}{P}}          &\text{name restriction, ``new''}
+      \\ \mid& \tm{\piNew{x}{P}}          &\text{name restriction, ``cut''}
       &  \mid& \tm{( \piPar{P}{Q} )}      &\text{parallel composition, ``mix''}
@@
 
+\begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
+  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\Gamma}$.
+\end{lemma}
+\begin{proof}
+  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
+\end{proof}
+
+\begin{theorem}[Preservation]\label{thm:hcp-preservation}
+  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\reducesto{P}{Q}$.
+\end{proof}
+
+\begin{theorem}[Progress]\label{thm:hcp-progress}
+  If $\seq[P]{\mathcal{G}}$, then there exists a $\tm{Q}$ such that
+  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut or a mix.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\seq[P]{\mathcal{G}}$.
+  If the last rule is a cut, there are three cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item
+    if the rule under the cut is the corresponding mix, we eliminate both as in
+    \cref{thm:cp-progress};
+  \item
+    if the rule under the cut is an unrelated mix, we rewrite by
+    \hccpEquivScopeExt{}, and recursively eliminate the cut; 
+  \item
+    if the rule under the cut is a logical rule, we apply one of the
+    $\kappa\nu$-rules.
+  \end{enumerate*}
+  If the last rule is mix, there are two cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item
+    if the rule under the mix is a cut or another mix, we recursively eliminate it;
+  \item
+    if the rule under the mix is a logical rule, we apply one of the
+    $\kappa{\ppar}$-rules. 
+  \end{enumerate*}
+\end{proof}
+
 \section{Relation between \cp and \hcp}
@@
           \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
-          \NOM{H-New}
+          \NOM{H-Cut}
           \UIC{$\seq[\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
@@
 \begin{proof}  
-  We repeatedly apply the $\kappa{\ppar}$-rules to move the applications of
-  \textsc{H-Mix} upwards. There are three cases:
+  We repeatedly apply the $\kappa{\ppar}$-rules to move the mixes upwards.
+  There are three cases:
   \begin{enumerate*}[label={\alph*)}]
   \item
-    if an \textsc{H-Mix} gets stuck under an \textsc{H-New}, it forms a
-    \cp \textsc{Cut};
+    if a mix gets stuck under a cut, it forms a \cp cut;
   \item
-    if an \textsc{H-Mix} gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
+    if a mix gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
   \item
@@
   \end{enumerate*}
-  Since the only way to continue after a $(\one)$ is by using an \textsc{H-Mix},
-  all applications of $(\one)$ are now be followed by an application of
+  Since the only way to continue after a $(\one)$ is by using a mix, all
+  applications of $(\one)$ are now be followed by an application of
   \textsc{H-Halt}, forming a \cp $(\one)$.

### 2018-04-23 doc/tlla2018/main.tex
Finalising proofs

@@
 \begin{theorem}\label{thm:cp2hcp-equiv}
-  If $\tm{P}\equiv\tm{Q}$ in \cp, then $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
+  $\tm{P}\equiv\tm{Q}$ in \cp iff $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
 \end{theorem}
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-  \begin{itemize}
-  \item
-    Case \cpEquivCutComm.
-    \begin{gather*}
-    \begin{array}{lcl}
-      \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
-      & \equiv & \text{by \hccpEquivMixComm}
-      \\
-      \tm{\piNew{x}{(\piPar{\mtf{Q}}{\mtf{P}})}}
-    \end{array}
-    \end{gather*}
-  \item
-    Case \cpEquivCutAss1.
-    \begin{gather*}
-    \begin{array}{lcl}
-      \tm{\piNew{x}{(\piPar{\mtf{P}}{\piNew{y}{(\piPar{\mtf{Q}}{\mtf{R}})}})}}
-      & \equiv & \text{%
-                 by \hccpEquivNewComm, \hccpEquivMixAss1, \hccpEquivMixComm,
-                 and \hccpEquivScopeExt{}}
-      \\
-      \tm{\piNew{y}{(\piPar{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}{\mtf{R}})}}
-    \end{array}
-    \end{gather*}
-  \end{itemize}
-  The other cases are trivial.
+% \begin{itemize}
+% \item
+%   Case \cpEquivCutComm.
+%   \begin{gather*}
+%   \begin{array}{lcl}
+%     \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+%     & \equiv & \text{by \hccpEquivMixComm}
+%     \\
+%     \tm{\piNew{x}{(\piPar{\mtf{Q}}{\mtf{P}})}}
+%   \end{array}
+%   \end{gather*}
+% \item
+%   Case \cpEquivCutAss1.
+%   \begin{gather*}
+%   \begin{array}{lcl}
+%     \tm{\piNew{x}{(\piPar{\mtf{P}}{\piNew{y}{(\piPar{\mtf{Q}}{\mtf{R}})}})}}
+%     & \equiv & \text{%
+%                by \hccpEquivNewComm, \hccpEquivMixAss1, \hccpEquivMixComm,
+%                and \hccpEquivScopeExt{}}
+%     \\
+%     \tm{\piNew{y}{(\piPar{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}{\mtf{R}})}}
+%   \end{array}
+%   \end{gather*}
+% \end{itemize}
+% The other cases are trivial.
 \end{proof}
@@
   By induction on the the derivation of $\reducesto{P}{Q}$.
-  \begin{itemize}
-  \item
-    Case \cpRedBetaTensParr.
-    \begin{gather*}
-    \begin{array}{lcl}
-      \tm{\piNew{x}{(\piPar{\piBoundSend{x}{y}{(\piPar{P}{Q})}}{\piRecv{x}{z}{R}})}}
-      & \Longrightarrow & \text{by \hccpRedBetaTensParr}
-      \\
-      \tm{\piNew{x}{\piNew{y}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
-      & \equiv & \text{%
-                 by \hccpEquivNewComm, \hccpEquivMixAss1, and \hccpEquivScopeExt1}
-      \\
-      \tm{\piNew{y}{(\piPar{P}{\piNew{x}{(\piPar{Q}{\cpSub{y}{z}{R}})}})}}
-    \end{array}
-    \end{gather*}
-  \item
-    Case \cpRedBetaOneBot.
-    \begin{gather*}
-    \begin{array}{lcl}
-      \tm{\piNew{x}{(\piPar{\piBoundSend{x}{}{\piHalt}}{\piRecv{x}{}{\mtf{Q}}})}}
-      & \Longrightarrow & \text{by \hccpRedBetaOneBot}
-      \\
-      \tm{(\piPar{\piHalt}{\mtf{Q}})}
-      & \equiv & \text{by \hccpEquivMixHalt1}
-      \\
-      \tm{\mtf{Q}}
-    \end{array}
-    \end{gather*}
-  \end{itemize}
-  The other cases are trivial.
+% \begin{itemize}
+% \item
+%   Case \cpRedBetaTensParr.
+%   \begin{gather*}
+%   \begin{array}{lcl}
+%     \tm{\piNew{x}{(\piPar{\piBoundSend{x}{y}{(\piPar{P}{Q})}}{\piRecv{x}{z}{R}})}}
+%     & \Longrightarrow & \text{by \hccpRedBetaTensParr}
+%     \\
+%     \tm{\piNew{x}{\piNew{y}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
+%     & \equiv & \text{%
+%                by \hccpEquivNewComm, \hccpEquivMixAss1, and \hccpEquivScopeExt1}
+%     \\
+%     \tm{\piNew{y}{(\piPar{P}{\piNew{x}{(\piPar{Q}{\cpSub{y}{z}{R}})}})}}
+%   \end{array}
+%   \end{gather*}
+% \item
+%   Case \cpRedBetaOneBot.
+%   \begin{gather*}
+%   \begin{array}{lcl}
+%     \tm{\piNew{x}{(\piPar{\piBoundSend{x}{}{\piHalt}}{\piRecv{x}{}{\mtf{Q}}})}}
+%     & \Longrightarrow & \text{by \hccpRedBetaOneBot}
+%     \\
+%     \tm{(\piPar{\piHalt}{\mtf{Q}})}
+%     & \equiv & \text{by \hccpEquivMixHalt1}
+%     \\
+%     \tm{\mtf{Q}}
+%   \end{array}
+%   \end{gather*}
+% \end{itemize}
+% The other cases are trivial.
 \end{proof}
@@
 \begin{proof}
-  By induction on the derivation of $\reducesto{\mtf{P}}{R}$
+  By induction on the derivation of $\reducesto{\mtf{P}}{R}$.
+  The cases for \hccpRedAxCut1 and the $\beta$-rules are trivial.
+  For the $\kappa\nu$-rules, we rewrite by the appropriate $\kappa{\ppar}$ rule,
+  and vice versa.
 \end{proof}

### 2018-04-23 doc/tlla2018/main.tex
Minor corrections

@@
 \begin{definition}[Structural congruence]\label{def:cp-equiv}
-  We define the structural congruence $\equiv$ as the congruence closure over
-  terms which satisfies the following additional axioms:
+  The structural congruence $\equiv$ is the congruence closure over terms which
+  satisfies the following additional axioms:
   \[
@@
 \begin{definition}[Structural congruence]\label{def:hcp-equiv}
-  We define the structural congruence $\equiv$ as the congruence closure over
-  terms which satisfies the following additional axioms:
+  The structural congruence $\equiv$ is the congruence closure over terms which
+  satisfies the following additional axioms:
   \[
@@
 
+We define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp:
 \begin{definition}\label{def:cp2hcp-terms}
-  We define a translation from terms in \cp to terms in \hcp which breaks down
-  the term constructs in \cp into their more atomic constructs in \hcp.
   \[
@@
 
-\begin{definition}\label{def:hcp-gammakappa}
-  We define the relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ as the congruence
-  closure of the $\gamma$- and $\kappa$-rules for \hcp (see
-  \cref{def:hcp-reduction}).
+\begin{definition}\label{def:hcp-gk}
+  The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of
+  the $\gamma$- and $\kappa$-rules for \hcp (\cref{def:hcp-reduction}).
 \end{definition}

### 2018-04-23 doc/tlla2018/main.tex
A word

@@
   Since the only way to continue after a $(\one)$ is by using a mix, all
-  applications of $(\one)$ are now be followed by an application of
+  applications of $(\one)$ are now followed by an application of
   \textsc{H-Halt}, forming a \cp $(\one)$.

### 2018-04-24 doc/tlla2018/main.tex
Some related work

@@
-\documentclass[submission,copyright,creativecommons]{eptcs}
+\documentclass[draft,submission,copyright,creativecommons]{eptcs}
 \providecommand{\event}{Linearity and TLLA 2018}
+\usepackage[british]{babel}
+\usepackage[all]{foreign}
 \usepackage[fleqn]{amsmath}
 \usepackage{amsthm}
-\usepackage{nameref,hyperref,cleveref}
 \usepackage[inline]{enumitem}
@@
 \usepackage{textcomp,textgreek,upgreek}
+\usepackage[
+	sectionbib,
+	square,
+	numbers,
+	sort&compress
+	]{natbib} % \citet
+\usepackage{nameref,hyperref,cleveref}
+\hypersetup{
+	hidelinks,
+	final
+}
 \newtheorem{definition}{Definition}
@@
 \input{preamble-typing}
+
+\usepackage[
+%	disable,     % hide all todos
+	obeyDraft,   % show todos only in draft mode
+%	obeyFinal,   % hide todos if in final mode
+	textwidth=3cm,
+	textsize=small,
+]{todonotes}
 
@@
   \and
+  Fabrizio Montesi
+  \institute{University of Southern Denmark\\ Odense, Denmark}
+  \email{fmontesi@imada.sdu.dk}
+  \and
   Marco Peressotti
   \institute{University of Southern Denmark\\ Odense, Denmark}
-  \email{peressotti@imada.sdu.dk}
-  \and
-  Fabrizio Montesi
-  \institute{University of Southern Denmark\\ Odense, Denmark}
-  \email{fmontesi@imada.sdu.dk}}
+  \email{peressotti@imada.sdu.dk}}
 \def\titlerunning{Taking Linear Logic Apart}
-\def\authorrunning{W.\ Kokke, M.\ Peressotti, and F.\ Montesi}
+\def\authorrunning{W.\ Kokke, F.\ Montesi, and M.\ Peressotti}
 
@@
       &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
-      \\ \mid& \tm{\cpSend{x}{y}{P}{Q}} &\text{``output''}
-      &  \mid& \tm{\cpRecv{x}{y}{P}}    &\text{``input''}
+      \\ \mid& \tm{\cpSend{x}{y}{P}{Q}} &\text{output}
+      &  \mid& \tm{\cpRecv{x}{y}{P}}    &\text{input}
       \\ \mid& \tm{\cpHalt{x}}          &\text{halt}
@@
 
-\bibliographystyle{eptcs}
+\section{Related Work}
+
+Since its inception, linear logic was described as the logic of concurrency \citep{girard1987}.
+Correspondences between the proof theory of linear logic and variants of the $\pi$-calculus emerged soon afterwards \citep{abramsky1994,bellin1994}, by interpreting linear logic propositions as types for channels.
+Later, linearity inspired also the seminal theories of linear types for the $\pi$-calculus \cite{kobayashi1999} and session types \cite{honda1998}.
+Even though the two theories do not use exactly linear logic, the work by \citet{dardha2017} shows that the link is still strong enough that session types can be encoded into linear types.
+
+It took more than ten years for a formal correspondence between linear logic and (a variant of) session types to emerge, with the seminal paper by \citet{caires2010}.
+This then inspired the development of Classical Processes (CP) by \citet{wadler2014}.
+%, which we have already discussed in the Introduction.
+%\todo{mention this}
+
+The idea of extending linear logic to hypersequents for typing processes is not new.
+Specifically, in \cite{carbone18}, the multiplicative-additive fragment of Intuitionistic Linear Logic is extended with hypersequents to type choreographies (global descriptions of process communications).
+Differently, HCP is based on CLL, uses hypersequents to type processes.
+%, and deals also with exponentials and polymorphism. 
+The major difference is that the rules for manipulating hypersequents are different w.r.t.~\cite{carbone18}. In particular, hypersequents can be 
+formed in \cite{carbone18} only when sequents share resources (\cf our \NOM{H-Mix}), and resource sharing is then explicitly tracked using an additional connection modality (which is not present in \hcp).
+
+%As a consequence, the work in \cite{carbone18} does not support an LTS for the same reasons that we discussed for CP in the Introduction.
+Adding a connection modality to CT might be interesting for providing an LTS semantics to the choreographies studied in \cite{carbone18}.
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+%\bibliographystyle{eptcs}
+\bibliographystyle{abbrvnat}
 \bibliography{main}

### 2018-04-25 doc/tlla2018/main.tex
a bit of intro

@@
 \begin{abstract}
+We introduce the calculus of Hypersequent Classical Processes (\hcp), which extends the research line on the relationship between linear logic and bridges the gap between the structures of operators used as proof terms in previous work and those of the standard $\pi$-calculus (in particular parallel operator and restriction).
+The key twist from previous work is registering parallelism in typing judgements, by generalising linear logic judgements from one sequents to many (hypersequents).
 \end{abstract}
+
+\section{Introduction}
+\label{sec:introduction}
+
+Classical Processes (CP) \cite{wadler2014} is a process calculus inspired by the correspondence between the session-typed $\pi$-calculus and linear logic \cite{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
+Bridging process languages to linear logic paves the way to apply methods developed in one field to the other.
+This already worked for a few results, in both directions.
+For example, the proof theory of linear logic can be used to guarantee progress for processes \cite{caires2010,wadler2014}, and multiparty session types, originally developed for processes \cite{honda2016}, inspired a generalisation of the standard cut rule to the composition of an arbitrary number of proofs, allowing for safe circular dependencies among proofs \cite{carbone17}.
+
+The hallmark of CP is that the semantics of processes is given by sound proof transformations in Classical Linear Logic (CLL).
+While this permits reusing the metatheory of linear logic ``as is'' to reason about process behaviour (\eg, cut elimination yields communication progress), it also exhibits some fundamental discrepancies with the key operators of the $\pi$-calculus \cite{milner1992a,milner1992b}.
+
+Some discrepancies are syntactic.
+For example, the term for output of a linear name is $\cpSend{x}{y}{P}{Q}$, read ``send $y$ over $x$ and proceed as $P$ in parallel to $Q$''.
+Notice that the term constructor for output here actually
+takes $x$, $y$, $P$ and $Q$ as parameters at the same time. This discrepancy is caused by adopting processes as proof terms for CLL: the typing rule for 
+output (\ie, the $\tens$ rule of CLL) checks that the processes respectively implementing the behaviours of $y$ ($P$) and of $x$ ($Q$) share no resources, by taking two premises ($P$ and $Q$).
+In general, there is no independent parallel term $P \mid Q$ in the grammar of CP, and even if we added it as the $\NOM{Mix}$ rule suggested in the original presentation of CP \cite{wadler2014}, it would not allow $P$ and $Q$ to communicate as in standard $\pi$-calculus.
+Synchronisation is governed instead by the restriction operator $\piNew{x}{(\piPar{P}{Q})}$ (we use the latest syntax for CP, from \cite{carbone2016}), which links $x$ at $P$ with $y$ at $Q$ to enable communication.
+Again, parallel is mixed with another operator (restriction here), but in this case it means that $P$ and $Q$ will communicate
+
+The discrepancies carry over from syntax (and typing) to semantics.
+The rule for reducing an output with an input in CP is the following.
+\[
+	\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{y}{R}}
+  \Longrightarrow
+  \cpCut{y}{P}{\cpCut{x}{Q}{R}}
+\]
+Notice how the rule needs to inspect the structure of the continuation of the output term ($\piPar{P}{Q}$) to produce a typable structure for the resulting network, by nesting restrictions appropriately.
 

### 2018-04-25 doc/tlla2018/main.tex
Attempted to fix references; removed submodule preamble

--- 2018-04-23 doc/tlla2018/main.tex
@@
 \usepackage{textcomp,textgreek,upgreek}
+\usepackage{nameref,hyperref,cleveref}
+\hypersetup{hidelinks,final}
 \newtheorem{definition}{Definition}
@@
 \newtheorem{corollary}{Corollary}
+\newtheorem{example}{Example}
 \input{preamble-typing}
+\usepackage[sectionbib,square,numbers,sort&compress]{natbib}
 
@@
 \begin{abstract}
+  Process calculi based in logic, such as \piDILL and \cp, provide a foundation
+  for deadlock-free concurrent programming.
+  However, there is a mismatch between the structures of operators used as proof
+  terms in previous work, and the term constructs of the standard \textpi-calculus.
+  We introduce the Hypersequent Classical Processes (\hcp), which addresses this
+  mismatch.
+  The key insight is to register parallelism in the typing judgements using
+  hypersequents, a technique from logic which generalises judgements from one
+  sequent to many.
+  This allows us to take apart the term constructs used in Classical Processes
+  (\cp) to more closely match those of the standard $\pi$-calculus.
+  We prove that \hcp enjoys subject reduction and progress, and prove several
+  properties relating it back to \cp.
 \end{abstract}
+
+\section{Introduction}
+\label{sec:introduction}
+
+Classical Processes (\cp) \cite{wadler2012} is a process calculus inspired by the
+correspondence between the session-typed $\pi$-calculus and linear logic
+\cite{caires2010}, where processes correspond to proofs, session types
+(communication protocols) to propositions, and communication to cut elimination.
+Bridging process languages to linear logic paves the way for applying methods
+developed in one field to the other.
+For instance, the proof theory of linear logic can be used to guarantee progress
+for processes~\cite{caires2010,wadler2012}.
+
+The main attraction of \cp is that its semantics are \emph{prescribed} by the
+cut elimination procedure of Classical Linear Logic (CLL).
+This permits us to reuse the metatheory of linear logic ``as is'' to reason about
+the behaviour of processes.
+However, there is a mismatch between the structure of the proof terms of CLL and
+the term constructs of the standard \textpi-calculus~\cite{milner1992a,milner1992b}.
+For instance, the term for output of a linear name is
+$\tm{\cpSend{x}{y}{P}{Q}}$, which is read ``send $y$ over $x$ and proceed as $P$
+in parallel to $Q$''.
+Note that this is a single term constructor, which takes all four arguments at
+the same time.
+This is caused by directly adopting the $(\tens)$-rule from CLL as the process
+calculus construct for sending: the $(\tens)$-rule has two premises, and checks
+that they share no resources.
+
+There is no independent parallel term $\tm{(\piPar{P}{Q})}$ in the grammar of
+\cp terms.
+Instead, the parallel composition shows up in any term which corresponds to a
+binary rule.
+Even if we were to add an independent parallel composition via the
+\textsc{Mix}-rule, as suggested in the original presentation of
+\cp~\cite{wadler2012}, there would be no way to allow the composed process
+$\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as
+there is no independent name restriction either!
+Instead, synchronisation is governed by the ``cut'' operator
+$\tm{\piNew{x}{(\piPar{P}{Q})}}$, which composes $\tm{P}$ and $\tm{Q}$, enabling
+them to communicate along $\tm{x}$.
+Worse, if we naively added an independent parallel composition as well as an
+name restriction, using the rules shown below, we would lose cut elimination,
+and therefore deadlock-freedom!
+\begin{center}
+  \begin{prooftree*}
+    \AXC{$\seq[ P ]{ \Gamma }$}
+    \AXC{$\seq[ Q ]{ \Delta }$}
+    \NOM{Mix}
+    \BIC{$\seq[ \piPar{P}{Q} ]{ \Gamma , \Delta }$}
+  \end{prooftree*}
+  \begin{prooftree*}
+    \AXC{$\seq[ P ]{ \Gamma, \tmty{x}{A}, \tmty{y}{A^\bot} }$}
+    \NOM{``Cut''}
+    \UIC{$\seq[ \piNew{xy}{P} ]{ \Gamma }$}
+  \end{prooftree*}
+\end{center}
+
+This syntactic mismatch has an effect on the semantics as well.
+For instance, the $\beta$-reduction for output and input in \cp is
+\[
+	\reducesto
+  {\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{y}{R}}}
+  {\cpCut{y}{P}{\cpCut{x}{Q}{R}}}.
+\]
+Note that the parallel composition $\tm{(\piPar{P}{Q})}$ is of no relevance to
+the communication, yet the rule needs to inspect the structure of the
+continuation of the output to be able to nest the name restrictions
+appropriately in the resulting term.
 
@@
       \cpRedBetaTensParr
-      & \tm{\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{z}{R}}}
+      & \tm{\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{y}{R}}}
       & \Longrightarrow
-      & \tm{\cpCut{y}{P}{\cpCut{x}{Q}{\cpSub{y}{z}{R}}}}
+      & \tm{\cpCut{y}{P}{\cpCut{x}{Q}{R}}}
       \\
@@
 
+\begin{example}
+  \(
+  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
+    \Gamma, \Delta, \tmty{x}{A \with B}}
+  \)
+\end{example}
+
 \begin{definition}[Terms]\label{def:hcp-terms}
@@
       \hccpRedBetaTensParr
-      & \tm{\cpCut{x}{\piBoundSend{x}{y}{P}}{\piRecv{x}{z}{R}}}
+      & \tm{\cpCut{x}{\piBoundSend{x}{y}{P}}{\piRecv{x}{y}{R}}}
       & \Longrightarrow
-      & \tm{\piNew{x}{\piNew{y}{(\piPar{P}{\cpSub{y}{z}{R}})}}}
+      & \tm{\piNew{x}{\piNew{y}{(\piPar{P}{R})}}}
       \\
@@
 \section{Relation between \cp and \hcp}
+
+\begin{itemize}
+\item Every \cp process is an \hcp process.
+\item \hcp processes represent multiple entangled \cp processes.
+\item \hcp supports the same protocols as \cp.
+\end{itemize}
 
@@
 
+\section{Related Work}
+\label{sec:related-work}
+
+Since its inception, linear logic has been described as the logic of
+concurrency~\cite{girard1987}.
+Correspondences between the proof theory of linear logic and variants of the
+\textpi-calculus emerged soon afterwards \cite{abramsky1994,bellin1994}, by
+interpreting linear logic propositions as types for channels.
+Later, linearity inspired also the seminal theories of linear types for the
+\textpi-calculus \cite{kobayashi1999} and session types \cite{honda1998}.
+Even though the two theories do not have a direct correspondence with linear
+logic, the link is still strong enough that session types
+can be encoded into linear types \cite{dardha2017}.
+
+It took more than ten years for a formal correspondence between linear logic and
+(a variant of) session types to emerge, with the seminal paper by \citet{caires2010}.
+This inspired the development of Classical Processes by \citet{wadler2012},
+which we have discussed in great detail in this paper.
+
+The idea of extending linear logic to hypersequents for typing processes is not
+novel.
+For instance, \citet{carbone2018} extended the multiplicative-additive fragment
+of intuitionistic linear logic with hypersequents to type global descriptions of
+process communications known as choreographies.
+
+This work differs from our approach in that \hcp is based on \emph{classical}
+linear logic, and uses hypersequents to type processes.
+Furthermore, the rules for manipulating hypersequents are different.
+In \citet{carbone2018}, hypersequents can be formed only when sequents share
+resources (\cf \textsc{H-Mix}), and resource sharing is then explicitly tracked
+using an additional connection modality (which is not present in \hcp).
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+\clearpage
 \bibliographystyle{eptcs}

### 2018-04-25 doc/tlla2018/main.tex
Fixed bibliography; added parfill

@@
 \input{preamble-typing}
+\usepackage[parfill]{parskip}
 \usepackage[sectionbib,square,numbers,sort&compress]{natbib}
@@
 For instance, the $\beta$-reduction for output and input in \cp is
-\[
+\(
 \reducesto
 {\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{y}{R}}}
-  {\cpCut{y}{P}{\cpCut{x}{Q}{R}}}.
-\]
-Note that the parallel composition $\tm{(\piPar{P}{Q})}$ is of no relevance to
-the communication, yet the rule needs to inspect the structure of the
-continuation of the output to be able to nest the name restrictions
-appropriately in the resulting term.
+{\cpCut{y}{P}{\cpCut{x}{Q}{R}}}
+\).
+Here, the parallel composition $\tm{(\piPar{P}{Q})}$ is of no relevance to this
+communication, yet the rule needs to inspect it to be able to nest the name
+restrictions appropriately in the resulting term.
 
@@
 process communications known as choreographies.
-
-This work differs from our approach in that \hcp is based on \emph{classical}
-linear logic, and uses hypersequents to type processes.
+This work differs from our approach in that \hcp is based on classical linear
+logic, and uses hypersequents to type processes.
 Furthermore, the rules for manipulating hypersequents are different.
@@
 \clearpage
-\bibliographystyle{eptcs}
+\bibliographystyle{abbrvnat}
 \bibliography{main}

### 2018-04-25 doc/tlla2018/main.tex
Finished edits of introduction & related work

@@
 
+We proceed as follows.
+We introduce \cp and restate its proofs of subject reduction and progress
+(\cref{sec:cp}), then introduce \hcp and give its proofs of subject reduction
+and progress (\cref{sec:hcp}).
+We then prove several properties relating the two. Specifically, we prove that
+every \cp process is an \hcp process, that every \hcp process corresponds to
+several entangled \cp processes, and that \hcp supports the same communication
+protocols as \cp, and no more (\cref{sec:cp2hcp}).
+Finally, we discuss related work and conclude
+(\cref{sec:related-work,sec:conclusions}).
+
 \section{Classical Processes}
+\label{sec:cp}
 
@@
 \section{Hypersequent Classical Processes}
+\label{sec:hcp}
 
@@
 \section{Relation between \cp and \hcp}
+\label{sec:cp2hcp}
 

### 2018-04-26 doc/tlla2018/main.tex
A few fixes and related work updates

@@
 This is caused by directly adopting the $(\tens)$-rule from CLL as the process
-calculus construct for sending: the $(\tens)$-rule has two premises, and checks
-that they share no resources.
+calculus construct for sending: the $(\tens)$-rule has two premises (corresponding to $\tm P$ and $\tm Q$ in the output term), and checks
+that they share no resources (in the output term, $\tm x$ can be used only by $\tm P$, and $\tm y$ can be used only by $\tm Q$).
 
@@
 them to communicate along $\tm{x}$.
-Worse, if we naively added an independent parallel composition as well as an
+Worse, if we naively added an independent parallel composition as well as a
 name restriction, using the rules shown below, we would lose cut elimination,
@@
 \begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
-  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\Gamma}$.
+  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
 \end{lemma}
@@
 \begin{theorem}[Preservation]\label{thm:hcp-preservation}
-  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
+  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.
 \end{theorem}
@@
 Since its inception, linear logic has been described as the logic of
-concurrency~\cite{girard1987}.
+concurrency \cite{girard1987}.
 Correspondences between the proof theory of linear logic and variants of the
@@
 (a variant of) session types to emerge, with the seminal paper by \citet{caires2010}.
-This inspired the development of Classical Processes by \citet{wadler2012},
-which we have discussed in great detail in this paper.
+This inspired the development of Classical Processes by \citet{wadler2012}.
 
-The idea of extending linear logic to hypersequents for typing processes is not
-novel.
-For instance, \citet{carbone2018} extended the multiplicative-additive fragment
+The idea of using hypersequents to capture parallelism in linear logic judgements is not
+novel: \citet{carbone2018} extended the multiplicative-additive fragment
 of intuitionistic linear logic with hypersequents to type global descriptions of
 process communications known as choreographies.
-This work differs from our approach in that \hcp is based on classical linear
-logic, and uses hypersequents to type processes.
-Furthermore, the rules for manipulating hypersequents are different.
-In \citet{carbone2018}, hypersequents can be formed only when sequents share
+This work is distinct from our approach in that \hcp is based on classical linear
+logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share
 resources (\cf \textsc{H-Mix}), and resource sharing is then explicitly tracked

### 2018-04-26 doc/tlla2018/main.tex
Inserted basic explanation of CP (first bit)

@@
 
+In order to keep the discussion of \hcp in \cref{sec:hcp} simple, we restrict
+ourselves to the multiplicative-applicative subset of \cp.
+We foresee no problems in extending the proofs in \cref{sec:hcp} to cover the
+remaining features of \cp (polymophism and the exponentials).
+
+The term language of \cp is a variant of the \textpi-calculus.
 \begin{definition}[Terms]\label{def:cp-terms}
@@
 \end{definition}
+The variables $\tm{x}$, $\tm{y}$, and $\tm{z}$ range over channel names.
+The construct $\tm{\cpLink{x}{y}}$ links two
+channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on
+$\tm{x}$ to $\tm{y}$ and vice versa.
+The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes
+two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
+Therefore, in $\tm{\cpCut{x}{P}{Q}}$ the name $\tm{x}$ is bound in both $\tm{P}$
+and $\tm{Q}$.
+In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote
+input, square brackets denote output.
+We use bound output~\cite{sangiorgi1996}, meaning that both input and output
+bind a new name.
+In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
+In $\tm{\cpSend{x}{y}{P}{Q}}$, the new name $\tm{y}$ is only bound in $\tm{P}$,
+while $\tm{x}$ is only bound in $\tm{Q}$.
 
+Terms in \cp are identified up to structural congruence, which states that
+links are symmetric, and parallel compositions $\tm{\cpCut{x}{P}{Q}}$ are
+associative and commutative.
 \begin{definition}[Structural congruence]\label{def:cp-equiv}

### 2018-04-26 doc/tlla2018/main.tex
Finished section on CP; renamed preservation to subject reduction

@@
 
+In this paper, we introduce the Hypersequent Classical Processes (\hcp), which
+addresses this mismatch.
+The key insight is to register parallelism in the typing judgements using
+hypersequents, a technique from logic which generalises judgements from one
+sequent to many.
+This allows us to take apart the term constructs used in Classical Processes
+(\cp) to more closely match those of the standard $\pi$-calculus.
 We proceed as follows.
-We introduce \cp and restate its proofs of subject reduction and progress
-(\cref{sec:cp}), then introduce \hcp and give its proofs of subject reduction
-and progress (\cref{sec:hcp}).
-We then prove several properties relating the two. Specifically, we prove that
-every \cp process is an \hcp process, that every \hcp process corresponds to
-several entangled \cp processes, and that \hcp supports the same communication
-protocols as \cp, and no more (\cref{sec:cp2hcp}).
+We start by introducing \cp (\cref{sec:cp}).
+Then, we introduce \hcp and prove it enjoys subject reduction and progress
+(\cref{sec:hcp}).
+We prove several properties relating the two.
+Specifically, we prove that every \cp process is an \hcp process, that every
+\hcp process corresponds to several entangled \cp processes, and that \hcp
+supports the same communication protocols as \cp, and no more
+(\cref{sec:cp2hcp}).
 Finally, we discuss related work and conclude
@@
 The term language of \cp is a variant of the \textpi-calculus.
+The variables $\tm{x}$, $\tm{y}$, and $\tm{z}$ range over channel names.
+The construct $\tm{\cpLink{x}{y}}$ links two
+channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on
+$\tm{x}$ to $\tm{y}$ and vice versa.
+The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes
+two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
+Therefore, in $\tm{\cpCut{x}{P}{Q}}$ the name $\tm{x}$ is bound in both $\tm{P}$
+and $\tm{Q}$.
+In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote
+input, square brackets denote output.
+We use bound output~\cite{sangiorgi1996}, meaning that both input and output
+bind a new name.
+In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
+In $\tm{\cpSend{x}{y}{P}{Q}}$, the new name $\tm{y}$ is only bound in $\tm{P}$,
+while $\tm{x}$ is only bound in $\tm{Q}$.
 \begin{definition}[Terms]\label{def:cp-terms}
@@
 \end{definition}
-The variables $\tm{x}$, $\tm{y}$, and $\tm{z}$ range over channel names.
-The construct $\tm{\cpLink{x}{y}}$ links two
-channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on
-$\tm{x}$ to $\tm{y}$ and vice versa.
-The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes
-two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
-Therefore, in $\tm{\cpCut{x}{P}{Q}}$ the name $\tm{x}$ is bound in both $\tm{P}$
-and $\tm{Q}$.
-In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote
-input, square brackets denote output.
-We use bound output~\cite{sangiorgi1996}, meaning that both input and output
-bind a new name.
-In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
-In $\tm{\cpSend{x}{y}{P}{Q}}$, the new name $\tm{y}$ is only bound in $\tm{P}$,
-while $\tm{x}$ is only bound in $\tm{Q}$.
 
@@
 
+Reductions relate processes with their reduced forms.
 \begin{definition}[Reduction]\label{def:cp-reduction}
@@
 
+Channels in \cp are typed using a session type system which corresponds to
+classical linear logic.
+A process communicating over a channel of type \ty{A \tens B} must be ready to
+split into two independent processes (two processes which share no
+channels), ready to communicate over a channel of type \ty{A} and \ty{B},
+respectively, and process communicating over a channel of type \ty{A \parr B} is
+dual to this, and therefore must be ready to start communicating concurrently
+with two independent processes.
+A process communicating over a channel of type \ty{A \plus B} can choose to
+communicate either as \ty{A} or \ty{B}, and a process communicating over a
+channel of type \ty{A \with B} must be able to communicate either as \ty{A} or
+\ty{B}.
 \begin{definition}[Types]\label{def:cp-types}
@@
 \end{definition}
-
-\begin{figure*}[!htb]
+Duality plays a crucial role in both linear logic and session types.
+In \cp, the two endpoints of a channel are assigned dual types.
+This ensures that, for instance, whenever a process \emph{sends} across a
+channel, the process on the other end of that channel is waiting to
+\emph{receive}.
+Each type $\ty{A}$ has a dual, written $\ty{A^\bot}$.
+Duality is an involutive function.
+\begin{definition}[Duality]\label{def:cp-negation}
+  \[
+    \begin{array}{lcllcllcllcl}
+         \ty{(A \tens B)^\bot} &=& \ty{A^\bot \parr B^\bot}
+      &  \ty{\one^\bot}        &=& \ty{\bot}
+      &  \ty{(A \parr B)^\bot} &=& \ty{A^\bot \tens B^\bot}
+      &  \ty{\bot^\bot}        &=& \ty{\one}
+      \\ \ty{(A \plus B)^\bot} &=& \ty{A^\bot \with B^\bot}
+      &  \ty{\nil^\bot}        &=& \ty{\top}
+      &  \ty{(A \with B)^\bot} &=& \ty{A^\bot \plus B^\bot}
+      &  \ty{\top^\bot}        &=& \ty{\nil}
+    \end{array}
+  \]
+\end{definition}
+Environments associate channels with types.
+Names in environments must be unique, and environments $\ty{\Gamma}$ and
+$\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if
+$\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
+\begin{definition}[Environments]\label{def:cp-environments}
+  \(
+    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} := \tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}
+  \) 
+\end{definition}
+Typing judgements associate processes with collections of typed channels.
+\begin{definition}[Typing judgements]\label{def:cp}
+  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}}$ denotes
+  that the process \tm{P} communicates along channels $\tm{x_1}\dots\tm{x_n}$
+  following protocols $\ty{A_1}\dots\ty{A_n}$.
+  Typing judgements can be constructed using the following inference rules.
+  \\[0.5\baselineskip]
   Structural Rules.
-  \begin{center} \cpInfAx     \cpInfCut      \end{center}
+  \begin{center} \cpInfAx     \cpInfCut   \end{center}\vspace*{0.5\baselineskip}
 
   Logical Rules.
-  \begin{center} \cpInfTens   \cpInfParr     \end{center}
-  \begin{center} \cpInfOne    \cpInfBot      \end{center}
-  \begin{center} \cpInfPlus1  \cpInfPlus2    \end{center}
-  \begin{center} \cpInfWith                  \end{center}
-  \begin{center} \cpInfNil    \cpInfTop      \end{center}
-
-  \caption{Classical Processes (\cp)}
-  \label{fig:cp}
-\end{figure*}
-
-\begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
-  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
-\end{lemma}
-\begin{proof}
-  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}
-
-\begin{theorem}[Preservation]\label{thm:cp-preservation}
-  If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem}
-\begin{proof}
-  By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}
-
-\begin{theorem}[Progress]\label{thm:cp-progress}
-  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that
-  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem}
-\begin{proof}
-  By induction on the derivation of $\seq[P]{\Gamma}$.
-  If the last rule is \textsc{Cut}, there are four cases:
-  \begin{enumerate*}[label={\alph*)}]
-  \item
-    if either side of the cut is an axiom, we apply \cpRedAxCut1;
-  \item
-    if either side of the cut is itself a cut, we recursively eliminate the cut;
-  \item
-    if both sides are logical rules acting on the cut formula, we apply
-    one of the $\beta$-rules;
-  \item
-    otherwise, at least one side is a logical rule acting on a formula other
-    than the cut formula, in which case we apply one of the $\kappa$-rules.
-  \end{enumerate*}
-\end{proof}
+  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{0.5\baselineskip}
+  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{0.5\baselineskip}
+  \begin{center} \cpInfWith               \end{center}\vspace*{0.5\baselineskip}
+  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{0.5\baselineskip}
+\end{definition}
+\cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.
 
@@
 
-\begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
+\begin{lemma}[Type preservation for \equiv]\label{lem:hcp-preservation-equiv}
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
@@
 
-\begin{theorem}[Preservation]\label{thm:hcp-preservation}
+\begin{theorem}[Subject reduction]\label{thm:hcp-preservation}
   If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.

### 2018-04-26 doc/tlla2018/main.tex
Put proofs from CP back... because otherwise my HCP proof isnt complete

@@
 \cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.
+\begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
+  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
+\end{lemma}
+\begin{proof}
+  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
+\end{proof}
+\begin{theorem}[Preservation]\label{thm:cp-preservation}
+  If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\reducesto{P}{Q}$.
+\end{proof}
+\begin{theorem}[Progress]\label{thm:cp-progress}
+  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that
+  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
+\end{theorem}
+\begin{proof}
+  By induction on the derivation of $\seq[P]{\Gamma}$.
+  If the last rule is \textsc{Cut}, there are four cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item
+    if either side of the cut is an axiom, we apply \cpRedAxCut1;
+  \item
+    if either side of the cut is itself a cut, we recursively eliminate the cut;
+  \item
+    if both sides are logical rules acting on the cut formula, we apply
+    one of the $\beta$-rules;
+  \item
+    otherwise, at least one side is a logical rule acting on a formula other
+    than the cut formula, in which case we apply one of the $\kappa$-rules.
+  \end{enumerate*}
+\end{proof}
 
@@
 
-\begin{lemma}[Type preservation for \equiv]\label{lem:hcp-preservation-equiv}
+\begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
@@
 
-\begin{theorem}[Subject reduction]\label{thm:hcp-preservation}
+\begin{theorem}[Preservation]\label{thm:hcp-preservation}
   If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.

### 2018-04-26 doc/tlla2018/main.tex
Minor corrections

@@
   Structural Rules.
-  \begin{center} \cpInfAx     \cpInfCut   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfAx     \cpInfCut  \end{center}\vspace*{0.5\baselineskip}
 
   Logical Rules.
-  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfWith               \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfTens   \cpInfParr \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfOne    \cpInfBot  \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfPlus1  \cpInfPlus2\end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfWith              \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfNil    \cpInfTop  \end{center}\vspace*{0.5\baselineskip}
 \end{definition}
@@
 \label{sec:hcp}
-
-\begin{example}
-  \(
-  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
-    \Gamma, \Delta, \tmty{x}{A \with B}}
-  \)
-\end{example}
 
@@
 
-\begin{figure*}[!htb]
+\begin{definition}[Typing judgements]\label{def:hcp}
+  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes
+  that the process $\tm{P}$ consists of $n$ independent, but potentially
+  interleaved processes, each of which communicates according to its own
+  protocol $\Gamma_i$. 
+  Typing judgements can be constructed using the following inference rules.
+  \\[0.5\baselineskip]
   Structural Rules.
-  \begin{center} \hccpInfAx        \hccpInfCycle \end{center}
-  \begin{center} \hccpInfMix       \hccpInfHalt  \end{center}
+  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{0.5\baselineskip}
 
   Logical Rules.
-  \begin{center} \hccpInfBoundTens \hccpInfParr  \end{center}
-  \begin{center} \hccpInfOne       \hccpInfBot   \end{center}
-  \begin{center} \hccpInfPlus1     \hccpInfPlus2 \end{center}
-  \begin{center} \hccpInfWith                    \end{center}
-  \begin{center} \hccpInfNil       \hccpInfTop   \end{center}
+  \begin{center}\hccpInfBoundTens \hccpInfParr \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfOne       \hccpInfBot  \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfPlus1     \hccpInfPlus2\end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfWith                   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfNil       \hccpInfTop  \end{center}\vspace*{0.5\baselineskip}
 
-  \centering
-  (Where each logical rule has the side condition that $\tm{x} \not\in
-  \ty{\mathcal{G}}$.)
-
-  \caption{Hypersequent Classical Processes (\hcp)}
-  \label{fig:hccp}
-\end{figure*}
+  Where each logical rule has the side condition that $\tm{x} \not\in
+  \ty{\mathcal{G}}$.
+\end{definition}
 
@@
 \begin{itemize}
+\item Not every \hcp process is a \cp process.
 \item Every \cp process is an \hcp process.
@@
 \end{itemize}
+
+\begin{example}
+  \(
+  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
+    \Gamma, \Delta, \tmty{x}{A \with B}}
+  \)
+\end{example}
 

### 2018-04-26 doc/tlla2018/main.tex
minor changes

--- 2018-04-26 doc/tlla2018/main.tex
@@
 \usepackage{amsthm}
+\allowdisplaybreaks
 \usepackage[inline]{enumitem}
@@
 \input{preamble-typing}
-\usepackage[parfill]{parskip}
+%\usepackage[parfill]{parskip}
+\usepackage{more-space}
 \usepackage[sectionbib,square,numbers,sort&compress]{natbib}
@@
   This allows us to take apart the term constructs used in Classical Processes
-  (\cp) to more closely match those of the standard $\pi$-calculus.
+  (\cp) to more closely match those of the standard \textpi-calculus.
   We prove that \hcp enjoys subject reduction and progress, and prove several
@@
 Classical Processes (\cp) \cite{wadler2012} is a process calculus inspired by the
-correspondence between the session-typed $\pi$-calculus and linear logic
+correspondence between the session-typed \textpi-calculus and linear logic
 \cite{caires2010}, where processes correspond to proofs, session types
@@
 This allows us to take apart the term constructs used in Classical Processes
-(\cp) to more closely match those of the standard $\pi$-calculus.
+(\cp) to more closely match those of the standard \textpi-calculus.
 We proceed as follows.
@@
   Typing judgements can be constructed using the following inference rules.
-  \\[0.5\baselineskip]
+
   Structural Rules.
-  \begin{center} \cpInfAx     \cpInfCut   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center} \cpInfAx     \cpInfCut   \end{center}\vspace*{-.5\baselineskip}
 
   Logical Rules.
-  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfWith               \end{center}\vspace*{0.5\baselineskip}
-  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{-.5\baselineskip}
+  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{-.5\baselineskip}
+  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{-.5\baselineskip}
+  \begin{center} \cpInfWith               \end{center}\vspace*{-.5\baselineskip}
+  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{-.5\baselineskip}
 \end{definition}
@@
 \begin{definition}\label{def:bigparr}
-  \begin{gather*}
-  \begin{array}{lcl}
-    \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
-    & = & \ty{A_1 \parr \dots \parr A_n}
-  \end{array}
-  \end{gather*}
+$\ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} =  \ty{A_1 \parr \dots \parr A_n}$.
+%  \begin{gather*}
+%  \begin{array}{lcl}
+%    \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
+%    & = & \ty{A_1 \parr \dots \parr A_n}
+%  \end{array}
+%  \end{gather*}
 \end{definition}
@@
   By induction on the structure of the environment $\Gamma$.
-  \begin{itemize}
-  \item
+%  \begin{itemize}
+%  \item
     If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
-  \item
+%  \item
     If $\ty{\Gamma} = \ty{A, B, \Gamma'}$,
-    then we apply $(\parr)$ to get $\seq{A \parr B, \Gamma'}$,\\
-    and apply the induction hypothesis.
-  \end{itemize}
+    then we apply $(\parr)$ to get $\seq{A \parr B, \Gamma'}$, and apply the induction hypothesis.
+%  \end{itemize}
 \end{proof}
@@
 \begin{definition}\label{def:bigtens}
-  \begin{gather*}
-  \begin{array}{lcl}
-    \ty{\bigtens(\emptyhypercontext)}
-    & = & \ty{\one}
-    \\
-    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
-    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
-  \end{array}
-  \end{gather*}
+  $\ty{\bigtens(\emptyhypercontext)} = \ty{\one}$
+  and 
+  $\ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)} = \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}$.
+%  \begin{gather*}
+%  \begin{array}{lcl}
+%    \ty{\bigtens(\emptyhypercontext)}
+%    & = & \ty{\one}
+%    \\
+%    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
+%    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
+%  \end{array}
+%  \end{gather*}
 \end{definition}
@@
   By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
-  \begin{itemize}
-  \item
+%  \begin{itemize}
+%  \item
     If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
-  \item
+%  \item
     If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
@@
     proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
-  \end{itemize}
+%  \end{itemize}
 \end{proof}
@@
 
+\looseness=-1
 The idea of using hypersequents to capture parallelism in linear logic judgements is not

### 2018-04-26 doc/tlla2018/main.tex

@@
   Typing judgements can be constructed using the following inference rules.
-
+  \\[0.5\baselineskip]
   Structural Rules.
-  \begin{center} \cpInfAx     \cpInfCut   \end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\cpInfAx     \cpInfCut  \end{center}\vspace*{0.5\baselineskip}
 
   Logical Rules.
-  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{-.5\baselineskip}
-  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{-.5\baselineskip}
-  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{-.5\baselineskip}
-  \begin{center} \cpInfWith               \end{center}\vspace*{-.5\baselineskip}
-  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\cpInfTens   \cpInfParr \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfOne    \cpInfBot  \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfPlus1  \cpInfPlus2\end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfWith              \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\cpInfNil    \cpInfTop  \end{center}\vspace*{0.5\baselineskip}
 \end{definition}
@@
 
-\begin{figure*}[!htb]
+\begin{definition}[Typing judgements]\label{def:hcp}
+  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes
+  that the process $\tm{P}$ consists of $n$ independent, but potentially
+  interleaved processes, each of which communicates according to its own
+  protocol $\Gamma_i$. 
+  Typing judgements can be constructed using the following inference rules.
+  \\[0.5\baselineskip]
   Structural Rules.
-  \begin{center} \hccpInfAx        \hccpInfCycle \end{center}
-  \begin{center} \hccpInfMix       \hccpInfHalt  \end{center}
+  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{-.5\baselineskip}
 
   Logical Rules.
-  \begin{center} \hccpInfBoundTens \hccpInfParr  \end{center}
-  \begin{center} \hccpInfOne       \hccpInfBot   \end{center}
-  \begin{center} \hccpInfPlus1     \hccpInfPlus2 \end{center}
-  \begin{center} \hccpInfWith                    \end{center}
-  \begin{center} \hccpInfNil       \hccpInfTop   \end{center}
-
-  \centering
-  (Where each logical rule has the side condition that $\tm{x} \not\in
-  \ty{\mathcal{G}}$.)
-
-  \caption{Hypersequent Classical Processes (\hcp)}
-  \label{fig:hccp}
-\end{figure*}
+  \begin{center}\hccpInfBoundTens \hccpInfParr \end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfOne       \hccpInfBot  \end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfPlus1     \hccpInfPlus2\end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfWith                   \end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfNil       \hccpInfTop  \end{center}\vspace*{.5\baselineskip}
+
+  Where each logical rule has the side condition that $\tm{x} \not\in
+  \ty{\mathcal{G}}$.
+\end{definition}
 

### 2018-04-26 doc/tlla2018/main.tex
minor changes

@@
 \usepackage{textcomp,textgreek,upgreek}
-\usepackage{nameref,hyperref,cleveref}
+\usepackage{nameref,hyperref}
+\usepackage[capitalise,nameinlink,noabbrev]{cleveref}
 \hypersetup{hidelinks,final}
@@
 while $\tm{x}$ is only bound in $\tm{Q}$.
-\begin{definition}[Terms]\label{def:cp-terms}
+\begin{definition}[Terms]\label{def:cp-terms}  Process terms are given by the following grammar:
   \[
@@
 
-Reductions relate processes with their reduced forms.
-\begin{definition}[Reduction]\label{def:cp-reduction}
-  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
-  to the process $\tm{Q}$ in a single step.
-  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
-  $\Longrightarrow$.
-  Reductions can only be constructed as follows:
+\begin{figure}
  \[
@@
   \end{center}
+  \caption{Classical Processes, reduction relation.}
+  \label{fig:cp-reduction}
+\end{figure}
+
+Reductions relate processes with their reduced forms \eg, a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
+\begin{definition}[Reduction]\label{def:cp-reduction}
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:cp-reduction}.
+  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of 
+  $\Longrightarrow$.
 \end{definition}
@@
 \end{definition}
+\begin{figure}
+%  Structural Rules.
+  \begin{center}\cpInfAx     \cpInfCut  \end{center}\vspace*{-.5\baselineskip}
+%  Logical Rules.
+  \begin{center}\cpInfTens   \cpInfParr \cpInfOne    \end{center}\vspace*{-.5\baselineskip}
+%  \begin{center}\end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\cpInfBot  \cpInfPlus1  \cpInfPlus2\end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\cpInfWith               
+%  \end{center}\vspace*{-.5\baselineskip}\begin{center}
+  \cpInfNil    \cpInfTop  \end{center} %\vspace*{-.5\baselineskip}
+  \caption{Classical Processes, typing.}
+  \label{fig:cp}
+\end{figure}
+\noindent
 Typing judgements associate processes with collections of typed channels.
@@
   following protocols $\ty{A_1}\dots\ty{A_n}$.
-  Typing judgements can be constructed using the following inference rules.
-  \\[0.5\baselineskip]
-  Structural Rules.
-  \begin{center}\cpInfAx     \cpInfCut  \end{center}\vspace*{0.5\baselineskip}
-
-  Logical Rules.
-  \begin{center}\cpInfTens   \cpInfParr \end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\cpInfOne    \cpInfBot  \end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\cpInfPlus1  \cpInfPlus2\end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\cpInfWith              \end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\cpInfNil    \cpInfTop  \end{center}\vspace*{0.5\baselineskip}
+  Typing judgements are derived using rules in \cref{fig:cp}.
 \end{definition}
@@
 
-\begin{definition}[Reduction]\label{def:hcp-reduction}
-  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
-  to the process $\tm{Q}$ in a single step.
-  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
-  $\Longrightarrow$.
-  Reductions can only be constructed as follows:
+\begin{figure}[t]
   \[
@@
   \end{center}
-\end{definition}
+  \caption{Hypersequent Classical Processes, reduction relation.}
+  \label{fig:hcp-reduction}
+\end{figure}
+
+\begin{definition}[Reduction]\label{def:hcp-reduction}
+ Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:hcp-reduction}.
+%  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
+%  to the process $\tm{Q}$ in a single step.
+%  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
+%  $\Longrightarrow$.
+%  Reductions can only be constructed as follows:
+\end{definition}
+
+\begin{figure}[t]
+%  Structural Rules.
+  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{-.5\baselineskip}
+%  Logical Rules.
+  \begin{center}\hccpInfBoundTens \hccpInfParr \hccpInfOne \end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfBot \hccpInfPlus1 \hccpInfPlus2\end{center}\vspace*{-.5\baselineskip}
+  \begin{center}\hccpInfWith \quad \hccpInfNil \quad \hccpInfTop  \end{center} %\vspace*{.5\baselineskip}
+  \caption{Hypersequent Classical Processes, typing.}
+  \label{fig:hcp}
+\end{figure}
 
@@
   interleaved processes, each of which communicates according to its own
-  protocol $\Gamma_i$. 
-  Typing judgements can be constructed using the following inference rules.
-  \\[0.5\baselineskip]
-  Structural Rules.
-  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{-.5\baselineskip}
-
-  Logical Rules.
-  \begin{center}\hccpInfBoundTens \hccpInfParr \end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfOne       \hccpInfBot  \end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfPlus1     \hccpInfPlus2\end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfWith                   \end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfNil       \hccpInfTop  \end{center}\vspace*{.5\baselineskip}
-
-  Where each logical rule has the side condition that $\tm{x} \not\in
-  \ty{\mathcal{G}}$.
+  protocol $\Gamma_i$. Typing judgements are derived using rules in \cref{fig:hcp}---each rule has the side condition that $\tm{x} \not\in    \ty{\mathcal{G}}$.
 \end{definition}
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
+%\section{Conclusions}
+%\label{sec:conclusions}
 

### 2018-04-27 doc/tlla2018/main.tex
Minor corrections

@@
 
+In this section, we introduce \cp.
 In order to keep the discussion of \hcp in \cref{sec:hcp} simple, we restrict
@@
   \[
-    \begin{array}{lcllcllcllcl}
-         \ty{(A \tens B)^\bot} &=& \ty{A^\bot \parr B^\bot}
-      &  \ty{\one^\bot}        &=& \ty{\bot}
-      &  \ty{(A \parr B)^\bot} &=& \ty{A^\bot \tens B^\bot}
-      &  \ty{\bot^\bot}        &=& \ty{\one}
-      \\ \ty{(A \plus B)^\bot} &=& \ty{A^\bot \with B^\bot}
-      &  \ty{\nil^\bot}        &=& \ty{\top}
-      &  \ty{(A \with B)^\bot} &=& \ty{A^\bot \plus B^\bot}
-      &  \ty{\top^\bot}        &=& \ty{\nil}
+    \setlength{\arraycolsep}{3pt}
+    \begin{array}{lclclclclclclcl}
+               \ty{(A \tens B)^\bot} & = & \ty{A^\bot \parr B^\bot}
+      &\qquad& \ty{\one^\bot}        & = & \ty{\bot}
+      &\qquad& \ty{(A \parr B)^\bot} & = & \ty{A^\bot \tens B^\bot}
+      &\qquad& \ty{\bot^\bot}        & = & \ty{\one}
+      \\       \ty{(A \plus B)^\bot} & = & \ty{A^\bot \with B^\bot}
+      &\qquad& \ty{\nil^\bot}        & = & \ty{\top}
+      &\qquad& \ty{(A \with B)^\bot} & = & \ty{A^\bot \plus B^\bot}
+      &\qquad& \ty{\top^\bot}        & = & \ty{\nil}
     \end{array}
@@
 
+In this section, we introduce Hypersequent Classical Processes (\hcp), a variant
+of \cp which registers parallelism in the typing jugdgements using
+hypersequents, allowing us to take apart the monolithic term constructors of \cp
+(\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term
+constructs.
+As expected, the term language of \hcp is a variant of \cp, where the term
+constructs have been taken apart into \textpi-calculus primitives.
 \begin{definition}[Terms]\label{def:hcp-terms}
@@
 \end{definition}
-
+One side-effect of the changes on the term level is that our structural
+congruence is much more standard. It has associativity, commutativity, and a
+unit for parallel composition, commutativity of name restrictions, and scope
+extrusion.
 \begin{definition}[Structural congruence]\label{def:hcp-equiv}
@@
 \end{definition}
-
-\begin{figure}[t]
+There are two changes to the reduction system.
+First, because $\tm{\piBoundSend{x}{y}{P}}$ and $\tm{\piBoundSend{x}{}{P}}$ are
+now terms in their own right, the $\cpRedBetaTensParr$ and $\cpRedBetaOneBot$
+rules become simpler.
+Secondly, because we have decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent
+name restriction and parallel composition, the $\kappa$-rules and the relevant
+$\gamma$-rule all decompose as well.
+\begin{definition}[Reduction]\label{def:hcp-reduction}
+  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
+  to the process $\tm{Q}$ in a single step.
+  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
+  $\Longrightarrow$.
+  Reductions can only be constructed as follows:
   \[
@@
 
-\begin{figure}[t]
-%  Structural Rules.
-  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{-.5\baselineskip}
-%  Logical Rules.
-  \begin{center}\hccpInfBoundTens \hccpInfParr \hccpInfOne \end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfBot \hccpInfPlus1 \hccpInfPlus2\end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\hccpInfWith \quad \hccpInfNil \quad \hccpInfTop  \end{center} %\vspace*{.5\baselineskip}
-  \caption{Hypersequent Classical Processes, typing.}
-  \label{fig:hcp}
-\end{figure}
+\begin{definition}[Hyper-environment]\label{def:hcp-hyper-environment}
+  \(
+  \ty{\mathcal{G}}, \ty{\mathcal{H}} :=
+  \ty{\emptyhypercontext}
+  \; \mid \;
+  \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}
+  \)
+\end{definition}
 
@@
   that the process $\tm{P}$ consists of $n$ independent, but potentially
-  interleaved processes, each of which communicates according to its own
-  protocol $\Gamma_i$. Typing judgements are derived using rules in \cref{fig:hcp}---each rule has the side condition that $\tm{x} \not\in    \ty{\mathcal{G}}$.
+  entangled processes, each of which communicates according to its own
+  protocol $\Gamma_i$.
+  Typing judgements can be constructed using the following inference rules.
+  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}$.
+  \\[0.5\baselineskip]
+  Structural Rules.
+  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{0.5\baselineskip}
+
+  Logical Rules.
+  \begin{center}\hccpInfBoundTens \hccpInfParr \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfOne       \hccpInfBot  \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfPlus1     \hccpInfPlus2\end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfWith                   \end{center}\vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfNil       \hccpInfTop  \end{center}\vspace*{0.5\baselineskip}
+
 \end{definition}

### 2018-04-27 doc/tlla2018/main.tex
Fixed results of erroneous merge

@@
 \begin{definition}[Reduction]\label{def:hcp-reduction}
-  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
-  to the process $\tm{Q}$ in a single step.
-  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
-  $\Longrightarrow$.
-  Reductions can only be constructed as follows:
+  Reductions are described by the smallest relation $\Longrightarrow$ on process
+  terms closed under rules in \cref{fig:hcp-reduction}.
+\end{definition}
+\begin{figure}
   \[
@@
 
-\begin{definition}[Reduction]\label{def:hcp-reduction}
- Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:hcp-reduction}.
-%  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
-%  to the process $\tm{Q}$ in a single step.
-%  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
-%  $\Longrightarrow$.
-%  Reductions can only be constructed as follows:
-\end{definition}
-
 \begin{definition}[Hyper-environment]\label{def:hcp-hyper-environment}
@@
   Typing judgements can be constructed using the following inference rules.
-  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}$.
+  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
   \\[0.5\baselineskip]
@@
 \begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
-  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
+  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal{G}}$.
 \end{lemma}
@@
 \begin{theorem}[Preservation]\label{thm:hcp-preservation}
-  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.
+  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal{G}}$.
 \end{theorem}

### 2018-04-27 doc/tlla2018/main.tex
Minor fixes

@@
   \]
-\end{definition}
+\end{definition}\noindent
 
@@
   $\Longrightarrow$.
-\end{definition}
+\end{definition}\noindent
 
@@
   \]
-\end{definition}
+\end{definition}\noindent
 Duality plays a crucial role in both linear logic and session types.
@@
   \]
-\end{definition}
+\end{definition}\noindent
 Environments associate channels with types.
@@
   \) 
-\end{definition}
+\end{definition}\noindent
 \begin{figure}
@@
   Typing judgements are derived using rules in \cref{fig:cp}.
-\end{definition}
+\end{definition}\noindent
 \cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}
+\end{proof}\noindent
 \begin{theorem}[Preservation]\label{thm:cp-preservation}
@@
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}
+\end{proof}\noindent
 \begin{theorem}[Progress]\label{thm:cp-progress}
@@
   \end{enumerate*}
-\end{proof}
+\end{proof}\noindent
 
@@
   \]
-\end{definition}
+\end{definition}\noindent
 One side-effect of the changes on the term level is that our structural
@@
   \]
-\end{definition}
+\end{definition}\noindent
 There are two changes to the reduction system.
@@
   terms closed under rules in \cref{fig:hcp-reduction}.
-\end{definition}
+\end{definition}\noindent
 \begin{figure}
@@
   \)
-\end{definition}
+\end{definition}\noindent
 
@@
 
-\end{definition}
+\end{definition}\noindent
 
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}
+\end{proof}\noindent
 
@@
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}
+\end{proof}\noindent
 
@@
   By induction on the derivation of $\seq[P]{\Gamma}$.
+  We show the interesting cases:
   \begin{itemize}
@@
   \end{itemize}
-  The other cases are trivial.
-\end{proof}
+\end{proof}\noindent
 
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
+% We show the interesting cases:
 % \begin{itemize}
@@
 % \end{itemize}
-% The other cases are trivial.
-\end{proof}
+\end{proof}\noindent
 
@@
   By induction on the the derivation of $\reducesto{P}{Q}$.
+% We show the interesting cases:
 % \begin{itemize}
@@
   and vice versa.
-\end{proof}
+\end{proof}\noindent
 
@@
   The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of
-  the $\gamma$- and $\kappa$-rules for \hcp (\cref{def:hcp-reduction}).
-\end{definition}
+  the $\gamma$- and $\kappa$-rules for \hcp.
+\end{definition}\noindent
 
@@
   \textsc{H-Halt}, forming a \cp $(\one)$.
-\end{proof}
-
+\end{proof}\noindent
 We can interpret environments as types by collapsing them using a series of
@@
 \begin{definition}\label{def:bigparr}
-$\ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} =  \ty{A_1 \parr \dots \parr A_n}$.
-%  \begin{gather*}
-%  \begin{array}{lcl}
-%    \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})}
-%    & = & \ty{A_1 \parr \dots \parr A_n}
-%  \end{array}
-%  \end{gather*}
-\end{definition}
+  \(
+  \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} =
+  \ty{A_1 \parr \dots \parr A_n}
+  \)
+\end{definition}\noindent
 
@@
   By induction on the structure of the environment $\Gamma$.
-%  \begin{itemize}
-%  \item
   If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
-%  \item
-    If $\ty{\Gamma} = \ty{A, B, \Gamma'}$,
-    then we apply $(\parr)$ to get $\seq{A \parr B, \Gamma'}$, and apply the induction hypothesis.
-%  \end{itemize}
-\end{proof}
+  If $\ty{\Gamma} = \ty{A, B, \Gamma'}$, then we apply $(\parr)$ to get $\seq{A
+    \parr B, \Gamma'}$, and apply the induction hypothesis.
+\end{proof}\noindent
 
@@
 \begin{definition}\label{def:bigtens}
-  $\ty{\bigtens(\emptyhypercontext)} = \ty{\one}$
-  and 
-  $\ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)} = \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}$.
-%  \begin{gather*}
-%  \begin{array}{lcl}
-%    \ty{\bigtens(\emptyhypercontext)}
-%    & = & \ty{\one}
-%    \\
-%    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
-%    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
-%  \end{array}
-%  \end{gather*}
-\end{definition}
+  \(
+  \begin{array}{lcl}
+    \ty{\bigtens(\emptyhypercontext)}
+    & = & \ty{\one}
+    \\
+    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
+    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
+  \end{array}
+  \)
+\end{definition}\noindent
 
@@
   By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
-%  \begin{itemize}
-%  \item
   If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
-%  \item
-    If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$,
-    we apply \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots,
-    \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of
-    those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
+  If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$, we apply
+  \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots,
+  \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of those
+  proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
   \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single
   proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
-%  \end{itemize}
-\end{proof}
+\end{proof}\noindent
 

### 2018-04-27 doc/tlla2018/main.tex
More compression

@@
 (\cref{sec:cp2hcp}).
-Finally, we discuss related work and conclude
-(\cref{sec:related-work,sec:conclusions}).
+Finally, we discuss related work (\cref{sec:related-work}).
 
@@
 \begin{figure}
-%  Structural Rules.
-  \begin{center}\cpInfAx     \cpInfCut  \end{center}\vspace*{-.5\baselineskip}
-%  Logical Rules.
-  \begin{center}\cpInfTens   \cpInfParr \cpInfOne    \end{center}\vspace*{-.5\baselineskip}
-%  \begin{center}\end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\cpInfBot  \cpInfPlus1  \cpInfPlus2\end{center}\vspace*{-.5\baselineskip}
-  \begin{center}\cpInfWith               
-%  \end{center}\vspace*{-.5\baselineskip}\begin{center}
-  \cpInfNil    \cpInfTop  \end{center} %\vspace*{-.5\baselineskip}
+  \begin{center}\cpInfAx \cpInfCut \end{center}
+  \vspace*{-.5\baselineskip}
+  \begin{center}\cpInfTens \cpInfParr \cpInfOne \end{center}
+  \vspace*{-.5\baselineskip}
+  \begin{center}\cpInfBot \cpInfPlus1 \cpInfPlus2\end{center}
+  \vspace*{-.5\baselineskip}
+  \begin{center}\cpInfWith \cpInfNil \cpInfTop \end{center}
   \caption{Classical Processes, typing.}
@@
   protocol $\Gamma_i$.
-  Typing judgements can be constructed using the following inference rules.
+  Typing judgements can be constructed using the inference rules in \cref{fig:hcp}.
   Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-  \\[0.5\baselineskip]
-  Structural Rules.
-  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{0.5\baselineskip}
-
-  Logical Rules.
-  \begin{center}\hccpInfBoundTens \hccpInfParr \end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\hccpInfOne       \hccpInfBot  \end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\hccpInfPlus1     \hccpInfPlus2\end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\hccpInfWith                   \end{center}\vspace*{0.5\baselineskip}
-  \begin{center}\hccpInfNil       \hccpInfTop  \end{center}\vspace*{0.5\baselineskip}
-
-\end{definition}\noindent
+\end{definition}\noindent
+
+\begin{figure}
+  \begin{center}\hccpInfAx \hccpInfCycle\end{center}
+  \vspace*{-0.5\baselineskip}
+  \begin{center}\hccpInfMix \hccpInfHalt\end{center}
+  \vspace*{-0.5\baselineskip}
+  \begin{center}\hccpInfBoundTens \hccpInfParr \hccpInfOne\end{center}
+  \vspace*{-0.5\baselineskip}
+  \begin{center}\hccpInfBot \hccpInfPlus1 \hccpInfPlus2\end{center}
+  \vspace*{0.5\baselineskip}
+  \begin{center}\hccpInfWith \hccpInfNil \hccpInfTop\end{center}
+  \caption{Hypersequent Classical Processes, typing.}
+  \label{fig:hcp}
+\end{figure}
 
@@
   \)
-\end{example}
-
+\end{example}\noindent
 We define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp:

### 2018-04-27 doc/tlla2018/main.tex
Minor additions

@@
 \usepackage{nameref,hyperref}
-\usepackage[capitalise,nameinlink,noabbrev]{cleveref}
+\usepackage[nameinlink,noabbrev]{cleveref}
 \hypersetup{hidelinks,final}
@@
 \input{preamble-typing}
-%\usepackage[parfill]{parskip}
 \usepackage{more-space}
 \usepackage[sectionbib,square,numbers,sort&compress]{natbib}
+\renewcommand*{\eg}{e.g.\@\xspace}
+\renewcommand*{\ie}{i.e.\@\xspace}
 
@@
 
+\paragraph{Terms}
 The term language of \cp is a variant of the \textpi-calculus.
@@
 while $\tm{x}$ is only bound in $\tm{Q}$.
-\begin{definition}[Terms]\label{def:cp-terms}  Process terms are given by the following grammar:
+\begin{definition}[Terms]\label{def:cp-terms}
+  Process terms are given by the following grammar:
   \[
@@
 \end{definition}\noindent
-
 Terms in \cp are identified up to structural congruence, which states that
@@
 \end{definition}\noindent
-
 \begin{figure}
@@
 \end{figure}
-
-Reductions relate processes with their reduced forms \eg, a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
+Reductions relate processes with their reduced forms \eg, a reduction
+$\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process
+$\tm{Q}$ in a single step.
 \begin{definition}[Reduction]\label{def:cp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:cp-reduction}.
+  Reductions are described by the smallest relation $\Longrightarrow$ on process
+  terms closed under rules in \cref{fig:cp-reduction}.
   The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of 
@@
 
+\paragraph{Typing}
 Channels in \cp are typed using a session type system which corresponds to
@@
   \label{fig:cp}
-\end{figure}
-\noindent
+\end{figure}\noindent
 Typing judgements associate processes with collections of typed channels.
@@
 \end{definition}\noindent
+
+\paragraph{Metatheory}
 \cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.
@@
 \end{proof}\noindent
+\begin{theorem}[Termination]\label{thm:cp-termination}
+  If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction
+  sequences.
+\end{theorem}
+\begin{proof}
+  Every reduction reduces a single cut to zero, one or two cuts.
+  However, each of these cuts is smaller, in the sense that the type of the
+  channel on which the communication takes place is smaller.
+  Each reduction either eliminates a connective.
+  Furthermore, each instance of the structural congruence preserves the size of
+  the cut.
+  Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
+\end{proof}
 
@@
 constructs.
-As expected, the term language of \hcp is a variant of \cp, where the term
-constructs have been taken apart into \textpi-calculus primitives.
+
+\paragraph{Terms}
+The term language of \hcp is a variant of \cp where the term constructs have
+been taken apart into \textpi-calculus primitives.
 \begin{definition}[Terms]\label{def:hcp-terms}
@@
 
+\paragraph{Typing}
+We use the same definitions for types and environments for \hcp as we used for \cp.
+However, on top of this, we add the definition of a hyper-environment.
+Hyper-environments are either empty, or consist of a series of typing
+environments, separated by vertical bars.
+A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ can be used to
+type a series of $n$ entangled, but independent processes.
 \begin{definition}[Hyper-environment]\label{def:hcp-hyper-environment}
@@
 \end{definition}\noindent
-
+Typing judgements in \hcp associate processes with hyper-environments.
+\textsc{H-Mix} composes two processes in parallel, but remembers that they are
+independent on in the sequent.
+\textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of
+at least two unconnected processes, and connects them, eliminating the vertical
+bar.
+Note that each logical rule has the side condition that $\tm{x} \not\in
+\mathcal{G}$, which can be read as ``you cannot act on one end-point of $x$ if
+you are also holding its other end-point''.
+This prevents self-locking processes, \eg
+$\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}
@@
   Typing judgements can be constructed using the inference rules in \cref{fig:hcp}.
-  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-\end{definition}\noindent
-
+  Furthermore, each logical rule has the side condition that $\tm{x} \not\in
+  \ty{\mathcal{G}}$.
+\end{definition}\noindent
 \begin{figure}
@@
 
+\paragraph{Metatheory}
+Much like \cp, \hcp enjoys subject reduction, progress, and termination.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
@@
 \end{proof}\noindent
-
 \begin{theorem}[Preservation]\label{thm:hcp-preservation}
@@
 \end{proof}\noindent
-
 \begin{theorem}[Progress]\label{thm:hcp-progress}
@@
 \end{proof}\noindent
+\begin{theorem}[Termination]\label{thm:hcp-termination}
+  If $\seq[P]{\mathcal{G}}$, then there are no infinite
+  $\Longrightarrow$-reduction sequences.
+\end{theorem}
+\begin{proof}
+  As \cref{thm:cp-termination}.
+\end{proof}
 
@@
 \end{definition}\noindent
-
 \begin{theorem}\label{thm:cp2hcp-typing}
@@
     Case $(\one)$. We rewrite as follows:
-    \begin{flalign*}
+    \begin{gather*}
       \begin{array}{lcl}
@@
       \end{array}
-    \end{flalign*}
+    \end{gather*}
   \end{itemize}
 \end{proof}\noindent
-
 \begin{theorem}\label{thm:cp2hcp-equiv}
@@
 \end{proof}\noindent
-
 \begin{theorem}\label{thm:cp2hcp-reduction}
@@
 \end{definition}\noindent
-
 \begin{lemma}\label{lem:cp-bigparr}
@@
 \end{proof}\noindent
-
 We can interpret hyper-environments as types by collapsing them using a series

### 2018-04-27 doc/tlla2018/main.tex
Draft version; needs a conclusion and also needs to be shorter

@@
 \paragraph{Metatheory}
-Much like \cp, \hcp enjoys subject reduction, progress, and termination.
+\hcp enjoys subject reduction, progress, and termination.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
@@
 
-\begin{itemize}
-\item Not every \hcp process is a \cp process.
-\item Every \cp process is an \hcp process.
-\item \hcp processes represent multiple entangled \cp processes.
+In this section, we discuss the relation between \cp and \hcp.
+We will prove three important theorems:
+\begin{enumerate*}[label={\alph*)}]
+\item every \cp process is an \hcp process;
+\item \hcp processes represent multiple entangled \cp processes; and
 \item \hcp supports the same protocols as \cp.
-\end{itemize}
-
-\begin{example}
-  \(
-  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
-    \Gamma, \Delta, \tmty{x}{A \with B}}
-  \)
-\end{example}\noindent
-We define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp:
+\end{enumerate*}
+To facilitate this, we define a translation from terms in \cp to terms in \hcp
+which breaks down the term constructs in \cp into their more atomic constructs
+in \hcp.
 \begin{definition}\label{def:cp2hcp-terms}
@@
 \end{definition}\noindent
+First, we prove that each \cp process can be translated by this trivial
+translation to an \hcp process, and that this translation respects structural
+congruence and reduction.
+Reductions from \cp can be trivially translated to reductions in \hcp.
+However, as we took apart each $\kappa$-rule into two separate rules, the
+reduction relation of \hcp is a slight refinement over that of \cp.
 \begin{theorem}\label{thm:cp2hcp-typing}
@@
 \end{proof}\noindent
-
 \begin{theorem}\label{hcp2cp-reduction}
@@
 
+It would be wonderful if each \hcp process could be translated back into a
+series of \cp processes.
+However, \hcp exhibits some behaviours which are impossible to directly
+translate back into \cp.
+For instance, in the process below, the choice sent on $\tm{x}$ will affect the
+choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the
+channel $\tm{x}$.
+\begin{example}
+  \(
+  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
+    \Gamma, \Delta, \tmty{x}{A \with B}}
+  \)
+\end{example}\noindent
+Instead, we will define a new relation to characterise the relation between \hcp
+and \cp processes.
 \begin{definition}\label{def:hcp-gk}
@@
 \end{definition}\noindent
-
+This relation allows us to apply $\kappa$-rules under arbitrary prefixes.
+We can show that, if we allow ourselves to do this, we can rewrite any process
+to a form in which all mixes are either attached to their respective cuts or
+tensors, or at the top-level.
 \begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
@@
 \end{proof}\noindent
-We can interpret environments as types by collapsing them using a series of
-pars.
+
+Finally, we will prove that \hcp supports the same communication protocols as
+\cp.
+This is the same as saying that it inhabits the same session types, or that the
+associated logical systems derive the same theorems.
+We show this by proving that we can interpret the hyper-environments as formulas
+in the logic.
+This is a standard method for proving the soundness of a hypersequent calculus.
+
+We start out by showing that we can interpret environments as types by
+collapsing them using a series of pars.
 \begin{definition}\label{def:bigparr}
@@
 \end{proof}\noindent
-We can interpret hyper-environments as types by collapsing them using a series
-of tensors. In the case of the empty hyper-environment
-$\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
+Then, using \cref{lem:hcp-disentangle}, we can show that we can interpret
+hyper-environments as types by collapsing them using a series of tensors.
+In the case of the empty hyper-environment $\ty{\emptyhypercontext}$, we
+interpret this as the unit of tensor.
 \begin{definition}\label{def:bigtens}

### 2018-04-28 doc/tlla2018/main.tex
Draft version

@@
 
-\paragraph{Typing}
+\paragraph{Types}
 Channels in \cp are typed using a session type system which corresponds to
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
-\end{lemma}
+\end{lemma}\vspace*{-0.75\baselineskip}%
 \begin{proof}
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Preservation]\label{thm:cp-preservation}
   If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Progress]\label{thm:cp-progress}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   \end{enumerate*}
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Termination]\label{thm:cp-termination}
@@
   sequences.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
 
-\paragraph{Typing}
+\paragraph{Types}
 We use the same definitions for types and environments for \hcp as we used for \cp.
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal{G}}$.
-\end{lemma}
+\end{lemma}\vspace*{-0.75\baselineskip}%
 \begin{proof}
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Preservation]\label{thm:hcp-preservation}
   If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal{G}}$.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Progress]\label{thm:hcp-progress}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut or a mix.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   \end{enumerate*}
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Termination]\label{thm:hcp-termination}
@@
   $\Longrightarrow$-reduction sequences.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq[P]{\Gamma}$ in \cp, then $\seq[\mtf{P}]{\Gamma}$ in \hcp.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   \item
-    Case \textsc{Cut}. We rewrite to:
+    Case \textsc{Cut}. We rewrite as follows:
     \begin{gather*}
@@
   \end{itemize}
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}\label{thm:cp2hcp-equiv}
   $\tm{P}\equiv\tm{Q}$ in \cp iff $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
 % \end{itemize}
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}\label{thm:cp2hcp-reduction}
   If $\reducesto{P}{Q}$ in \cp, then $\reducesto{\mtf{P}}{\mtf{Q}}$ in \hcp.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
 % \end{itemize}
-\end{proof}\noindent
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}\label{hcp2cp-reduction}
@@
   $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
-\end{lemma}
+\end{lemma}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
-\end{lemma}
+\end{lemma}\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
-\end{theorem}
+\end{theorem}\vspace*{-0.75\baselineskip}%
 \begin{proof}

### 2018-04-28 doc/tlla2018/main.tex
Minor changes

@@
 \input{preamble-typing}
-\usepackage{more-space}
 \usepackage[sectionbib,square,numbers,sort&compress]{natbib}
@@
 \renewcommand*{\ie}{i.e.\@\xspace}
+\usepackage{more-space}
+\usepackage{setspace}
+\renewcommand{\baselinestretch}{0.925}
 
@@
 The key insight is to register parallelism in the typing judgements using
-hypersequents, a technique from logic which generalises judgements from one
-sequent to many.
+hypersequents~\cite{avron1991}, a technique from logic which generalises
+judgements from one sequent to many.
 This allows us to take apart the term constructs used in Classical Processes
@@
 \end{definition}\noindent
-\begin{figure}
+\begin{figure}[htb]
  \[
@@
   $\Longrightarrow$.
-\end{definition}\noindent
+\end{definition}
 
@@
 \end{definition}\noindent
-\begin{figure}
+\begin{figure}[htb]
   \begin{center}\cpInfAx \cpInfCut \end{center}
@@
 \end{definition}\noindent
-\begin{figure}
+\begin{figure}[htb]
   \[
@@
 We use the same definitions for types and environments for \hcp as we used for \cp.
-However, on top of this, we add the definition of a hyper-environment.
+However, we introduce a new layer on top of sequents: hypersequents.
+As \cp is a one-sided logic, and it uses the left-hand side of the
+turnstile to write the process, the traditional hypersequent notation can look
+confusing: ``$\seq[P]{\Gamma_1}\hsep\dots\hsep\seq{\Gamma_n}$'' seems to claim
+that $\tm{P}$ acts according to protocol $\ty{\Gamma_1}$.
+What are all the other $\Gamma$s doing there? Are they typing empty processes?
+Therefore, we opt to leave out the repeated turnstile, and instead work with the
+notion of ``hyper-environments''. However, we will still refer to our system as a
+hypersequent system.
 Hyper-environments are either empty, or consist of a series of typing
 environments, separated by vertical bars.
-A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ can be used to
-type a series of $n$ entangled, but independent processes.
+A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of
+$n$ entangled, but independent processes.
 \begin{definition}[Hyper-environment]\label{def:hcp-hyper-environment}
@@
 \end{definition}\noindent
-\begin{figure}
+\begin{figure}[htb]
   \begin{center}\hccpInfAx \hccpInfCycle\end{center}
@@
   \end{itemize}
+  \vspace*{-\baselineskip}%
 \end{proof}\vspace*{-0.75\baselineskip}%
@@
   \(
-  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
+  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q''})}]{
     \Gamma, \Delta, \tmty{x}{A \with B}}

### 2018-04-28 doc/tlla2018/main.tex
Minor fixes
minor changes

@@
 \usepackage[british]{babel}
-\usepackage[all]{foreign}
+%\usepackage[all]{foreign}
 \usepackage[fleqn]{amsmath}
@@
 \usepackage[sectionbib,square,numbers,sort&compress]{natbib}
-\renewcommand*{\eg}{e.g.\@\xspace}
-\renewcommand*{\ie}{i.e.\@\xspace}
+%\renewcommand*{\eg}{e.g.\@\xspace}
+%\renewcommand*{\ie}{i.e.\@\xspace}
 \usepackage{more-space}
@@
 \end{figure}
-Reductions relate processes with their reduced forms \eg, a reduction
+Reductions relate processes with their reduced forms e.g., a reduction
 $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process
@@
 \end{definition}\noindent
-\begin{figure}[htb]
+%\begin{figure}[htb]
+%  \begin{center}\cpInfAx \cpInfCut \end{center}
+%  \vspace*{-.5\baselineskip}
+%  \begin{center}\cpInfTens \cpInfParr \cpInfOne \end{center}
+%  \vspace*{-.5\baselineskip}
+%  \begin{center}\cpInfBot \cpInfPlus1 \cpInfPlus2\end{center}
+%  \vspace*{-.5\baselineskip}
+%  \begin{center}\cpInfWith \cpInfNil \cpInfTop \end{center}
+%  \caption{Classical Processes, typing.}
+%  \label{fig:cp}
+%\end{figure}\noindent
+Typing judgements associate processes with collections of typed channels.
+\begin{definition}[Typing judgements]\label{def:cp}
+  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}}$ denotes
+  that the process \tm{P} communicates along channels $\tm{x_1}\dots\tm{x_n}$
+  following protocols $\ty{A_1}\dots\ty{A_n}$.
+  Typing judgements are derived using the rules below.%rules in \cref{fig:cp}.
   \begin{center}\cpInfAx \cpInfCut \end{center}
@@
   \begin{center}\cpInfWith \cpInfNil \cpInfTop \end{center}
-  \caption{Classical Processes, typing.}
-  \label{fig:cp}
-\end{figure}\noindent
-Typing judgements associate processes with collections of typed channels.
-\begin{definition}[Typing judgements]\label{def:cp}
-  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}}$ denotes
-  that the process \tm{P} communicates along channels $\tm{x_1}\dots\tm{x_n}$
-  following protocols $\ty{A_1}\dots\ty{A_n}$.
-  Typing judgements are derived using rules in \cref{fig:cp}.
 \end{definition}\noindent
@@
 hypersequents, allowing us to take apart the monolithic term constructors of \cp
-(\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term
+(e.g.~$\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term
 constructs.
@@
 you are also holding its other end-point''.
-This prevents self-locking processes, \eg
-$\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
+This prevents self-locking processes, e.g.~$\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}
@@
   \begin{center}\hccpInfBot \hccpInfPlus1 \hccpInfPlus2\end{center}
-  \vspace*{0.5\baselineskip}
+  \vspace*{-0.5\baselineskip}
   \begin{center}\hccpInfWith \hccpInfNil \hccpInfTop\end{center}
@@
 
-We start out by showing that we can interpret environments as types by
-collapsing them using a series of pars.
+Environments can be interpreted as types by
+collapsing them as series of pars.
 \begin{definition}\label{def:bigparr}
@@
 \end{proof}\noindent
-Then, using \cref{lem:hcp-disentangle}, we can show that we can interpret
-hyper-environments as types by collapsing them using a series of tensors.
-In the case of the empty hyper-environment $\ty{\emptyhypercontext}$, we
-interpret this as the unit of tensor.
+Furthermore, hyper-environments can be interpreted as types by collapsing them as series of tensors where environments are handled using \cref{lem:hcp-disentangle}.
+The empty hyper-environment $\ty{\emptyhypercontext}$ (that is the unit of $\hsep$) is interpreted as the unit of tensor.
 \begin{definition}\label{def:bigtens}
@@
 \looseness=-1
-The idea of using hypersequents to capture parallelism in linear logic judgements is not
-novel: \citet{carbone2018} extended the multiplicative-additive fragment
-of intuitionistic linear logic with hypersequents to type global descriptions of
-process communications known as choreographies.
-This work is distinct from our approach in that \hcp is based on classical linear
-logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share
-resources (\cf \textsc{H-Mix}), and resource sharing is then explicitly tracked
+The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: \citet{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies.
+This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share resources (cf.~\textsc{H-Mix}), and resource sharing is explicitly tracked
 using an additional connection modality (which is not present in \hcp).

### 2018-04-28 doc/tlla2018/main.tex
Added hyper-environment to (T) rule; Minor fixes

--- 2018-04-28 doc/tlla2018/main.tex
@@
 \usepackage{setspace}
-\renewcommand{\baselinestretch}{0.925}
+\everypar{\looseness=-1}
+\renewcommand{\baselinestretch}{0.975}
 
@@
 This is caused by directly adopting the $(\tens)$-rule from CLL as the process
-calculus construct for sending: the $(\tens)$-rule has two premises (corresponding to $\tm P$ and $\tm Q$ in the output term), and checks
-that they share no resources (in the output term, $\tm x$ can be used only by $\tm P$, and $\tm y$ can be used only by $\tm Q$).
+calculus construct for sending: the $(\tens)$-rule has two premises
+(corresponding to $\tm P$ and $\tm Q$ in the output term), and checks that they
+share no resources (in the output term, $\tm x$ can be used only by $\tm P$, and
+$\tm y$ can be used only by $\tm Q$).
 
@@
 \textsc{H-Mix} composes two processes in parallel, but remembers that they are
-independent on in the sequent.
+independent in the sequent.
 \textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of
-at least two unconnected processes, and connects them, eliminating the vertical
+at least two independent processes, and connects them, eliminating the vertical
 bar.
 Note that each logical rule has the side condition that $\tm{x} \not\in
-\mathcal{G}$, which can be read as ``you cannot act on one end-point of $x$ if
-you are also holding its other end-point''.
+\ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$
+if you are also holding its other end-point''.
 This prevents self-locking processes, \eg
@@
 
-\looseness=-1
-The idea of using hypersequents to capture parallelism in linear logic judgements is not
-novel: \citet{carbone2018} extended the multiplicative-additive fragment
-of intuitionistic linear logic with hypersequents to type global descriptions of
-process communications known as choreographies.
-This work is distinct from our approach in that \hcp is based on classical linear
-logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share
-resources (\cf \textsc{H-Mix}), and resource sharing is then explicitly tracked
-using an additional connection modality (which is not present in \hcp).
-
-%\section{Conclusions}
-%\label{sec:conclusions}
+The idea of using hypersequents to capture parallelism in linear logic
+judgements is not novel: \citet{carbone2018} extended the
+multiplicative-additive fragment of intuitionistic linear logic with
+hypersequents to type global descriptions of process communications known as
+choreographies.
+This work is distinct from our approach in that \hcp is based on classical
+linear logic and manipulates hypersequents differently: in \citet{carbone2018},
+hypersequents can be formed only when sequents share resources (\cf
+\textsc{H-Mix}), and resource sharing is then explicitly tracked using an
+additional connection modality (which is not present in \hcp).
+
+\section{Conclusions}
+\label{sec:conclusions}
 

### 2018-04-28 doc/tlla2018/main.tex
new convention: one line per paragraph

@@
 \usepackage[sectionbib,square,numbers,sort&compress]{natbib}
-\renewcommand*{\eg}{e.g.\@\xspace}
-\renewcommand*{\ie}{i.e.\@\xspace}
 \usepackage{more-space}
@@
 
-Classical Processes (\cp) \cite{wadler2012} is a process calculus inspired by the
-correspondence between the session-typed \textpi-calculus and linear logic
-\cite{caires2010}, where processes correspond to proofs, session types
-(communication protocols) to propositions, and communication to cut elimination.
-Bridging process languages to linear logic paves the way for applying methods
-developed in one field to the other.
-For instance, the proof theory of linear logic can be used to guarantee progress
-for processes~\cite{caires2010,wadler2012}.
-
-The main attraction of \cp is that its semantics are \emph{prescribed} by the
-cut elimination procedure of Classical Linear Logic (CLL).
-This permits us to reuse the metatheory of linear logic ``as is'' to reason about
-the behaviour of processes.
-However, there is a mismatch between the structure of the proof terms of CLL and
-the term constructs of the standard \textpi-calculus~\cite{milner1992a,milner1992b}.
-For instance, the term for output of a linear name is
-$\tm{\cpSend{x}{y}{P}{Q}}$, which is read ``send $y$ over $x$ and proceed as $P$
-in parallel to $Q$''.
-Note that this is a single term constructor, which takes all four arguments at
-the same time.
-This is caused by directly adopting the $(\tens)$-rule from CLL as the process
-calculus construct for sending: the $(\tens)$-rule has two premises
-(corresponding to $\tm P$ and $\tm Q$ in the output term), and checks that they
-share no resources (in the output term, $\tm x$ can be used only by $\tm P$, and
-$\tm y$ can be used only by $\tm Q$).
-
-There is no independent parallel term $\tm{(\piPar{P}{Q})}$ in the grammar of
-\cp terms.
-Instead, the parallel composition shows up in any term which corresponds to a
-binary rule.
-Even if we were to add an independent parallel composition via the
-\textsc{Mix}-rule, as suggested in the original presentation of
-\cp~\cite{wadler2012}, there would be no way to allow the composed process
-$\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as
-there is no independent name restriction either!
-Instead, synchronisation is governed by the ``cut'' operator
-$\tm{\piNew{x}{(\piPar{P}{Q})}}$, which composes $\tm{P}$ and $\tm{Q}$, enabling
-them to communicate along $\tm{x}$.
-Worse, if we naively added an independent parallel composition as well as a
-name restriction, using the rules shown below, we would lose cut elimination,
-and therefore deadlock-freedom!
+Classical Processes (\cp) \cite{wadler2012} is a process calculus inspired by the correspondence between the session-typed \textpi-calculus and linear logic \cite{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
+Bridging process languages to linear logic paves the way for applying methods developed in one field to the other.
+For instance, the proof theory of linear logic can be used to guarantee progress for processes~\cite{caires2010,wadler2012}.
+
+The main attraction of \cp is that its semantics are \emph{prescribed} by the cut elimination procedure of Classical Linear Logic (CLL).
+This permits us to reuse the metatheory of linear logic ``as is'' to reason about the behaviour of processes.
+However, there is a mismatch between the structure of the proof terms of CLL and the term constructs of the standard \textpi-calculus~\cite{milner1992a,milner1992b}.
+For instance, the term for output of a linear name is $\tm{\cpSend{x}{y}{P}{Q}}$, which is read ``send $y$ over $x$ and proceed as $P$ in parallel to $Q$''.
+Note that this is a single term constructor, which takes all four arguments at the same time.
+This is caused by directly adopting the $(\tens)$-rule from CLL as the process calculus construct for sending: the $(\tens)$-rule has two premises (corresponding to $\tm P$ and $\tm Q$ in the output term), and checks that they share no resources (in the output term, $\tm x$ can be used only by $\tm P$, and $\tm y$ can be used only by $\tm Q$).
+
+There is no independent parallel term $\tm{(\piPar{P}{Q})}$ in the grammar of \cp terms.
+Instead, the parallel composition shows up in any term which corresponds to a binary rule.
+Even if we were to add an independent parallel composition via the \textsc{Mix}-rule, as suggested in the original presentation of \cp~\cite{wadler2012}, there would be no way to allow the composed process $\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as there is no independent name restriction either!
+Instead, synchronisation is governed by the ``cut'' operator $\tm{\piNew{x}{(\piPar{P}{Q})}}$, which composes $\tm{P}$ and $\tm{Q}$, enabling them to communicate along $\tm{x}$.
+Worse, if we naively added an independent parallel composition as well as a name restriction, using the rules shown below, we would lose cut elimination, and therefore deadlock-freedom!
 \begin{center}
@@
 This syntactic mismatch has an effect on the semantics as well.
-For instance, the $\beta$-reduction for output and input in \cp is
-\(
-\reducesto
-{\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{y}{R}}}
-{\cpCut{y}{P}{\cpCut{x}{Q}{R}}}
-\).
-Here, the parallel composition $\tm{(\piPar{P}{Q})}$ is of no relevance to this
-communication, yet the rule needs to inspect it to be able to nest the name
-restrictions appropriately in the resulting term.
-
-In this paper, we introduce the Hypersequent Classical Processes (\hcp), which
-addresses this mismatch.
-The key insight is to register parallelism in the typing judgements using
-hypersequents~\cite{avron1991}, a technique from logic which generalises
-judgements from one sequent to many.
-This allows us to take apart the term constructs used in Classical Processes
-(\cp) to more closely match those of the standard \textpi-calculus.
+For instance, the $\beta$-reduction for output and input in \cp is \(\reducesto {\cpCut{x}{\cpSend{x}{y}{P}{Q}}{\cpRecv{x}{y}{R}}} {\cpCut{y}{P}{\cpCut{x}{Q}{R}}}\).
+Here, the parallel composition $\tm{(\piPar{P}{Q})}$ is of no relevance to this communication, yet the rule needs to inspect it to be able to nest the name restrictions appropriately in the resulting term.
+
+In this paper, we introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch.
+The key insight is to register parallelism in the typing judgements using hypersequents~\cite{avron1991}, a technique from logic which generalises judgements from one sequent to many.
+This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
 We proceed as follows.
 We start by introducing \cp (\cref{sec:cp}).
-Then, we introduce \hcp and prove it enjoys subject reduction and progress
-(\cref{sec:hcp}).
+Then, we introduce \hcp and prove it enjoys subject reduction and progress (\cref{sec:hcp}).
 We prove several properties relating the two.
-Specifically, we prove that every \cp process is an \hcp process, that every
-\hcp process corresponds to several entangled \cp processes, and that \hcp
-supports the same communication protocols as \cp, and no more
-(\cref{sec:cp2hcp}).
+Specifically, we prove that every \cp process is an \hcp process, that every \hcp process corresponds to several entangled \cp processes, and that \hcp supports the same communication protocols as \cp, and no more (\cref{sec:cp2hcp}).
 Finally, we discuss related work (\cref{sec:related-work}).
@@
 In this section, we introduce \cp.
-In order to keep the discussion of \hcp in \cref{sec:hcp} simple, we restrict
-ourselves to the multiplicative-applicative subset of \cp.
-We foresee no problems in extending the proofs in \cref{sec:hcp} to cover the
-remaining features of \cp (polymophism and the exponentials).
+In order to keep the discussion of \hcp in \cref{sec:hcp} simple, we restrict ourselves to the multiplicative-applicative subset of \cp.
+We foresee no problems in extending the proofs in \cref{sec:hcp} to cover the remaining features of \cp (polymophism and the exponentials).
 
@@
 The variables $\tm{x}$, $\tm{y}$, and $\tm{z}$ range over channel names.
-The construct $\tm{\cpLink{x}{y}}$ links two
-channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on
-$\tm{x}$ to $\tm{y}$ and vice versa.
-The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes
-two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
-Therefore, in $\tm{\cpCut{x}{P}{Q}}$ the name $\tm{x}$ is bound in both $\tm{P}$
-and $\tm{Q}$.
-In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote
-input, square brackets denote output.
-We use bound output~\cite{sangiorgi1996}, meaning that both input and output
-bind a new name.
+The construct $\tm{\cpLink{x}{y}}$ links two channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on $\tm{x}$ to $\tm{y}$ and vice versa.
+The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
+Therefore, in $\tm{\cpCut{x}{P}{Q}}$ the name $\tm{x}$ is bound in both $\tm{P}$ and $\tm{Q}$.
+In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote input, square brackets denote output.
+We use bound output~\cite{sangiorgi1996}, meaning that both input and output bind a new name.
 In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
-In $\tm{\cpSend{x}{y}{P}{Q}}$, the new name $\tm{y}$ is only bound in $\tm{P}$,
-while $\tm{x}$ is only bound in $\tm{Q}$.
+In $\tm{\cpSend{x}{y}{P}{Q}}$, the new name $\tm{y}$ is only bound in $\tm{P}$, while $\tm{x}$ is only bound in $\tm{Q}$.
 \begin{definition}[Terms]\label{def:cp-terms}
@@
 \end{definition}\noindent
-Terms in \cp are identified up to structural congruence, which states that
-links are symmetric, and parallel compositions $\tm{\cpCut{x}{P}{Q}}$ are
-associative and commutative.
+Terms in \cp are identified up to structural congruence, which states that links are symmetric, and parallel compositions $\tm{\cpCut{x}{P}{Q}}$ are associative and commutative.
 \begin{definition}[Structural congruence]\label{def:cp-equiv}
@@
 \end{figure}
-Reductions relate processes with their reduced forms \eg, a reduction
-$\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process
-$\tm{Q}$ in a single step.
+Reductions relate processes with their reduced forms \eg a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
 \begin{definition}[Reduction]\label{def:cp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process
-  terms closed under rules in \cref{fig:cp-reduction}.
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:cp-reduction}.
 The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
@@
 \paragraph{Types}
-Channels in \cp are typed using a session type system which corresponds to
-classical linear logic.
-A process communicating over a channel of type \ty{A \tens B} must be ready to
-split into two independent processes (two processes which share no
-channels), ready to communicate over a channel of type \ty{A} and \ty{B},
-respectively, and process communicating over a channel of type \ty{A \parr B} is
-dual to this, and therefore must be ready to start communicating concurrently
-with two independent processes.
-A process communicating over a channel of type \ty{A \plus B} can choose to
-communicate either as \ty{A} or \ty{B}, and a process communicating over a
-channel of type \ty{A \with B} must be able to communicate either as \ty{A} or
-\ty{B}.
+Channels in \cp are typed using a session type system which corresponds to classical linear logic.
+A process communicating over a channel of type \ty{A \tens B} must be ready to split into two independent processes (two processes which share no channels), ready to communicate over a channel of type \ty{A} and \ty{B}, respectively, and process communicating over a channel of type \ty{A \parr B} is dual to this, and therefore must be ready to start communicating concurrently with two independent processes.
+A process communicating over a channel of type \ty{A \plus B} can choose to communicate either as \ty{A} or \ty{B}, and a process communicating over a channel of type \ty{A \with B} must be able to communicate either as \ty{A} or \ty{B}.
 \begin{definition}[Types]\label{def:cp-types}
@@
 In \cp, the two endpoints of a channel are assigned dual types.
-This ensures that, for instance, whenever a process \emph{sends} across a
-channel, the process on the other end of that channel is waiting to
-\emph{receive}.
+This ensures that, for instance, whenever a process \emph{sends} across a channel, the process on the other end of that channel is waiting to \emph{receive}.
 Each type $\ty{A}$ has a dual, written $\ty{A^\bot}$.
@@
 Environments associate channels with types.
-Names in environments must be unique, and environments $\ty{\Gamma}$ and
-$\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if
-$\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
+Names in environments must be unique, and environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
 \begin{definition}[Environments]\label{def:cp-environments}
@@
 \begin{proof}
-  By induction on the derivation of $\seq[P]{\Gamma}$.
-  If the last rule is \textsc{Cut}, there are four cases:
+  By induction on the derivation of $\seq[P]{\Gamma}$. If the last rule is \textsc{Cut}, there are four cases:
   \begin{enumerate*}[label={\alph*)}]
@@
 \begin{theorem}[Termination]\label{thm:cp-termination}
-  If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction
-  sequences.
+  If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
 \end{theorem}\vspace*{-0.75\baselineskip}%
@@
   Every reduction reduces a single cut to zero, one or two cuts.
-  However, each of these cuts is smaller, in the sense that the type of the
-  channel on which the communication takes place is smaller.
+However, each of these cuts is smaller, in the sense that the type of the channel on which the communication takes place is smaller.
 Each reduction either eliminates a connective.
-  Furthermore, each instance of the structural congruence preserves the size of
-  the cut.
+Furthermore, each instance of the structural congruence preserves the size of the cut.
 Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
@@
 
-In this section, we introduce Hypersequent Classical Processes (\hcp), a variant
-of \cp which registers parallelism in the typing jugdgements using
-hypersequents, allowing us to take apart the monolithic term constructors of \cp
-(\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term
-constructs.
+In this section, we introduce Hypersequent Classical Processes (\hcp), a variant of \cp which registers parallelism in the typing judgements using hypersequents, allowing us to take apart the monolithic term constructors of \cp (\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term constructs.
 
 \paragraph{Terms}
-The term language of \hcp is a variant of \cp where the term constructs have
-been taken apart into \textpi-calculus primitives.
+The term language of \hcp is a variant of \cp where the term constructs have been taken apart into \textpi-calculus primitives.
 \begin{definition}[Terms]\label{def:hcp-terms}
@@
 \end{definition}\noindent
-One side-effect of the changes on the term level is that our structural
-congruence is much more standard. It has associativity, commutativity, and a
-unit for parallel composition, commutativity of name restrictions, and scope
-extrusion.
+One side-effect of the changes on the term level is that our structural congruence is much more standard.
+It has associativity, commutativity, and a unit for parallel composition, commutativity of name restrictions, and scope extrusion.
 \begin{definition}[Structural congruence]\label{def:hcp-equiv}
-  The structural congruence $\equiv$ is the congruence closure over terms which
-  satisfies the following additional axioms:
+  The structural congruence $\equiv$ is the congruence closure over terms which satisfies the following additional axioms:
   \[
@@
 There are two changes to the reduction system.
-First, because $\tm{\piBoundSend{x}{y}{P}}$ and $\tm{\piBoundSend{x}{}{P}}$ are
-now terms in their own right, the $\cpRedBetaTensParr$ and $\cpRedBetaOneBot$
-rules become simpler.
-Secondly, because we have decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent
-name restriction and parallel composition, the $\kappa$-rules and the relevant
-$\gamma$-rule all decompose as well.
+First, because $\tm{\piBoundSend{x}{y}{P}}$ and $\tm{\piBoundSend{x}{}{P}}$ are now terms in their own right, the $\cpRedBetaTensParr$ and $\cpRedBetaOneBot$ rules become simpler.
+Secondly, because we have decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent name restriction and parallel composition, the $\kappa$-rules and the relevant $\gamma$-rule all decompose as well.
 \begin{definition}[Reduction]\label{def:hcp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process
-  terms closed under rules in \cref{fig:hcp-reduction}.
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:hcp-reduction}.
 \end{definition}\noindent
@@
 However, we introduce a new layer on top of sequents: hypersequents.
-As \cp is a one-sided logic, and it uses the left-hand side of the
-turnstile to write the process, the traditional hypersequent notation can look
-confusing: ``$\seq[P]{\Gamma_1}\hsep\dots\hsep\seq{\Gamma_n}$'' seems to claim
-that $\tm{P}$ acts according to protocol $\ty{\Gamma_1}$.
-What are all the other $\Gamma$s doing there? Are they typing empty processes?
-Therefore, we opt to leave out the repeated turnstile, and instead work with the
-notion of ``hyper-environments''. However, we will still refer to our system as a
-hypersequent system.
-Hyper-environments are either empty, or consist of a series of typing
-environments, separated by vertical bars.
-A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of
-$n$ entangled, but independent processes.
+As \cp is a one-sided logic, and it uses the left-hand side of the turnstile to write the process, the traditional hypersequent notation can look confusing: ``$\seq[P]{\Gamma_1}\hsep\dots\hsep\seq{\Gamma_n}$'' seems to claim that $\tm{P}$ acts according to protocol $\ty{\Gamma_1}$.
+What are all the other $\Gamma$s doing there?
+Are they typing empty processes?
+Therefore, we opt to leave out the repeated turnstile, and instead work with the notion of ``hyper-environments''.
+However, we will still refer to our system as a hypersequent system.
+Hyper-environments are either empty, or consist of a series of typing environments, separated by vertical bars.
+A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of $n$ entangled, but independent processes.
 \begin{definition}[Hyper-environment]\label{def:hcp-hyper-environment}
-  \(
-  \ty{\mathcal{G}}, \ty{\mathcal{H}} :=
-  \ty{\emptyhypercontext}
-  \; \mid \;
-  \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}
-  \)
+  $\ty{\mathcal{G}}, \ty{\mathcal{H}} := \ty{\emptyhypercontext} \; \mid \; \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$
 \end{definition}\noindent
 Typing judgements in \hcp associate processes with hyper-environments.
-\textsc{H-Mix} composes two processes in parallel, but remembers that they are
-independent in the sequent.
-\textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of
-at least two independent processes, and connects them, eliminating the vertical
-bar.
-Note that each logical rule has the side condition that $\tm{x} \not\in
-\ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$
-if you are also holding its other end-point''.
-This prevents self-locking processes, \eg
-$\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
+\textsc{H-Mix} composes two processes in parallel, but remembers that they are independent in the sequent.
+\textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar.
+Note that each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''.
+This prevents self-locking processes \eg $\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}
-  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes
-  that the process $\tm{P}$ consists of $n$ independent, but potentially
-  entangled processes, each of which communicates according to its own
-  protocol $\Gamma_i$.
+  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
 Typing judgements can be constructed using the inference rules in \cref{fig:hcp}.
-  Furthermore, each logical rule has the side condition that $\tm{x} \not\in
-  \ty{\mathcal{G}}$.
+Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
 \end{definition}\noindent
@@
 \begin{proof}
-  By induction on the derivation of $\seq[P]{\mathcal{G}}$.
-  If the last rule is a cut, there are three cases:
+  By induction on the derivation of $\seq[P]{\mathcal{G}}$. If the last rule is a cut, there are three cases:
   \begin{enumerate*}[label={\alph*)}]
@@
   \item
-    if the rule under the cut is an unrelated mix, we rewrite by
-    \hccpEquivScopeExt{}, and recursively eliminate the cut;
-  \item
-    if the rule under the cut is a logical rule, we apply one of the
-    $\kappa\nu$-rules.
+    if the rule under the cut is an unrelated mix, we rewrite by \hccpEquivScopeExt{}, and recursively eliminate the cut;
+  \item
+    if the rule under the cut is a logical rule, we apply one of the $\kappa\nu$-rules.
   \end{enumerate*}
@@
 \begin{theorem}[Termination]\label{thm:hcp-termination}
-  If $\seq[P]{\mathcal{G}}$, then there are no infinite
-  $\Longrightarrow$-reduction sequences.
+  If $\seq[P]{\mathcal{G}}$, then there are no infinite $\Longrightarrow$-reduction sequences.
 \end{theorem}\vspace*{-0.75\baselineskip}%
@@
 
-In this section, we discuss the relation between \cp and \hcp.
-We will prove three important theorems:
+In this section, we discuss the relation between \cp and \hcp. We will prove three important theorems:
 \begin{enumerate*}[label={\alph*)}]
@@
 \end{enumerate*}
-To facilitate this, we define a translation from terms in \cp to terms in \hcp
-which breaks down the term constructs in \cp into their more atomic constructs
-in \hcp.
+To facilitate this, we define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp.
 \begin{definition}\label{def:cp2hcp-terms}
@@
 \end{definition}\noindent
-First, we prove that each \cp process can be translated by this trivial
-translation to an \hcp process, and that this translation respects structural
-congruence and reduction.
+First, we prove that each \cp process can be translated by this trivial translation to an \hcp process, and that this translation respects structural congruence and reduction.
 Reductions from \cp can be trivially translated to reductions in \hcp.
-However, as we took apart each $\kappa$-rule into two separate rules, the
-reduction relation of \hcp is a slight refinement over that of \cp.
+However, as we took apart each $\kappa$-rule into two separate rules, the reduction relation of \hcp is a slight refinement over that of \cp.
 \begin{theorem}\label{thm:cp2hcp-typing}
@@
 \begin{proof}
-  By induction on the derivation of $\seq[P]{\Gamma}$.
-  We show the interesting cases:
+  By induction on the derivation of $\seq[P]{\Gamma}$. We show the interesting cases:
   \begin{itemize}
@@
 \begin{theorem}\label{hcp2cp-reduction}
-  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that
-  $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
+  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
 \end{theorem}\vspace*{-0.75\baselineskip}%
@@
 The cases for \hccpRedAxCut1 and the $\beta$-rules are trivial.
-  For the $\kappa\nu$-rules, we rewrite by the appropriate $\kappa{\ppar}$ rule,
-  and vice versa.
+For the $\kappa\nu$-rules, we rewrite by the appropriate $\kappa{\ppar}$ rule, and vice versa.
 \end{proof}\noindent
 
-It would be wonderful if each \hcp process could be translated back into a
-series of \cp processes.
-However, \hcp exhibits some behaviours which are impossible to directly
-translate back into \cp.
-For instance, in the process below, the choice sent on $\tm{x}$ will affect the
-choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the
-channel $\tm{x}$.
+It would be wonderful if each \hcp process could be translated back into a series of \cp processes.
+However, \hcp exhibits some behaviours which are impossible to directly translate back into \cp.
+For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
 \begin{example}
@@
 \end{example}\noindent
-Instead, we will define a new relation to characterise the relation between \hcp
-and \cp processes.
+Instead, we will define a new relation to characterise the relation between \hcp and \cp processes.
 \begin{definition}\label{def:hcp-gk}
-  The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of
-  the $\gamma$- and $\kappa$-rules for \hcp.
+  The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of the $\gamma$- and $\kappa$-rules for \hcp.
 \end{definition}\noindent
 This relation allows us to apply $\kappa$-rules under arbitrary prefixes.
-We can show that, if we allow ourselves to do this, we can rewrite any process
-to a form in which all mixes are either attached to their respective cuts or
-tensors, or at the top-level.
+We can show that, if we allow ourselves to do this, we can rewrite any process to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
 \begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
-  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp,
-  then there exist $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ in \cp,
-  such that
-  $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
+  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ in \cp, such that $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
 \end{lemma}\vspace*{-0.75\baselineskip}%
 \begin{proof}
-  We repeatedly apply the $\kappa{\ppar}$-rules to move the mixes upwards.
-  There are three cases:
+  We repeatedly apply the $\kappa{\ppar}$-rules to move the mixes upwards. There are three cases:
   \begin{enumerate*}[label={\alph*)}]
@@
   \end{enumerate*}
-  Since the only way to continue after a $(\one)$ is by using a mix, all
-  applications of $(\one)$ are now followed by an application of
-  \textsc{H-Halt}, forming a \cp $(\one)$.
+  Since the only way to continue after a $(\one)$ is by using a mix, all applications of $(\one)$ are now followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
 \end{proof}\noindent
 
-Finally, we will prove that \hcp supports the same communication protocols as
-\cp.
-This is the same as saying that it inhabits the same session types, or that the
-associated logical systems derive the same theorems.
-We show this by proving that we can interpret the hyper-environments as formulas
-in the logic.
+Finally, we will prove that \hcp supports the same communication protocols as \cp.
+This is the same as saying that it inhabits the same session types, or that the associated logical systems derive the same theorems.
+We show this by proving that we can interpret the hyper-environments as formulas in the logic.
 This is a standard method for proving the soundness of a hypersequent calculus.
 
-We start out by showing that we can interpret environments as types by
-collapsing them using a series of pars.
+We start out by showing that we can interpret environments as types by collapsing them using a series of pars.
 \begin{definition}\label{def:bigparr}
@@
 \end{proof}\noindent
-Then, using \cref{lem:hcp-disentangle}, we can show that we can interpret
-hyper-environments as types by collapsing them using a series of tensors.
-In the case of the empty hyper-environment $\ty{\emptyhypercontext}$, we
-interpret this as the unit of tensor.
+Then, using \cref{lem:hcp-disentangle}, we can show that we can interpret hyper-environments as types by collapsing them using a series of tensors.
+In the case of the empty hyper-environment $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
 \begin{definition}\label{def:bigtens}
@@
   If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
-  If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$, we apply
-  \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots,
-  \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of those
-  proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots,
-  \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single
-  proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
+  If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$, we apply \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots, \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
 \end{proof}\noindent
@@
 
-Since its inception, linear logic has been described as the logic of
-concurrency \cite{girard1987}.
-Correspondences between the proof theory of linear logic and variants of the
-\textpi-calculus emerged soon afterwards \cite{abramsky1994,bellin1994}, by
-interpreting linear logic propositions as types for channels.
-Later, linearity inspired also the seminal theories of linear types for the
-\textpi-calculus \cite{kobayashi1999} and session types \cite{honda1998}.
-Even though the two theories do not have a direct correspondence with linear
-logic, the link is still strong enough that session types
-can be encoded into linear types \cite{dardha2017}.
-
-It took more than ten years for a formal correspondence between linear logic and
-(a variant of) session types to emerge, with the seminal paper by \citet{caires2010}.
+Since its inception, linear logic has been described as the logic of concurrency \cite{girard1987}.
+Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \cite{abramsky1994,bellin1994}, by interpreting linear logic propositions as types for channels.
+Later, linearity inspired also the seminal theories of linear types for the \textpi-calculus \cite{kobayashi1999} and session types \cite{honda1998}.
+Even though the two theories do not have a direct correspondence with linear logic, the link is still strong enough that session types can be encoded into linear types \cite{dardha2017}.
+
+It took more than ten years for a formal correspondence between linear logic and (a variant of) session types to emerge, with the seminal paper by \citet{caires2010}.
 This inspired the development of Classical Processes by \citet{wadler2012}.
 
-The idea of using hypersequents to capture parallelism in linear logic
-judgements is not novel: \citet{carbone2018} extended the
-multiplicative-additive fragment of intuitionistic linear logic with
-hypersequents to type global descriptions of process communications known as
-choreographies.
-This work is distinct from our approach in that \hcp is based on classical
-linear logic and manipulates hypersequents differently: in \citet{carbone2018},
-hypersequents can be formed only when sequents share resources (\cf
-\textsc{H-Mix}), and resource sharing is then explicitly tracked using an
-additional connection modality (which is not present in \hcp).
+The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: \citet{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies.
+This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then explicitly tracked using an additional connection modality (which is not present in \hcp).
 

### 2018-04-28 doc/tlla2018/main.tex
wrote bit of a conclusion
omitted a phrase

@@
 Then, we introduce \hcp and prove it enjoys subject reduction and progress (\cref{sec:hcp}).
-We prove several properties relating the two.
-Specifically, we prove that every \cp process is an \hcp process, that every \hcp process corresponds to several entangled \cp processes, and that \hcp supports the same communication protocols as \cp, and no more (\cref{sec:cp2hcp}).
+We prove that every \cp process is an \hcp process, that every \hcp process corresponds to several entangled \cp processes, and that \hcp supports the same communication protocols as \cp, and no more (\cref{sec:cp2hcp}).
 Finally, we discuss related work (\cref{sec:related-work}).
@@
 
+We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\cite{wadler2012}.
+We showed that \hcp enjoys preservation, progress and termination, and described its relation to \cp.
+
 \clearpage

### 2018-04-28 doc/tlla2018/main.tex
Changed bibstyle and minor changes

@@
 \input{preamble-typing}
-\usepackage[sectionbib,square,numbers,sort&compress]{natbib}
+\usepackage[sectionbib,authordate,sort&compress]{natbib}
 \usepackage{more-space}
@@
   for deadlock-free concurrent programming.
-  However, there is a mismatch between the structures of operators used as proof
-  terms in previous work, and the term constructs of the standard \textpi-calculus.
-  We introduce the Hypersequent Classical Processes (\hcp), which addresses this
-  mismatch.
-  The key insight is to register parallelism in the typing judgements using
-  hypersequents, a technique from logic which generalises judgements from one
-  sequent to many.
-  This allows us to take apart the term constructs used in Classical Processes
-  (\cp) to more closely match those of the standard \textpi-calculus.
-  We prove that \hcp enjoys subject reduction and progress, and prove several
-  properties relating it back to \cp.
+However, there is a mismatch between the structures of operators used as proof terms in previous work, and the term constructs of the standard \textpi-calculus.
+We introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch.
+The key insight is to register parallelism in the typing judgements using hypersequents, a technique from logic which generalises judgements from one sequent to many.
+This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
+We prove that \hcp enjoys subject reduction and progress, and prove several properties relating it back to \cp.
 \end{abstract}
@@
 
-Classical Processes (\cp) \cite{wadler2012} is a process calculus inspired by the correspondence between the session-typed \textpi-calculus and linear logic \cite{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
+Classical Processes (\cp) \citep{wadler2012} is a process calculus inspired by the correspondence between the session-typed \textpi-calculus and linear logic \citep{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
 Bridging process languages to linear logic paves the way for applying methods developed in one field to the other.
-For instance, the proof theory of linear logic can be used to guarantee progress for processes~\cite{caires2010,wadler2012}.
+For instance, the proof theory of linear logic can be used to guarantee progress for processes~\citep{caires2010,wadler2012}.
 
@@
 This permits us to reuse the metatheory of linear logic ``as is'' to reason about the behaviour of processes.
-However, there is a mismatch between the structure of the proof terms of CLL and the term constructs of the standard \textpi-calculus~\cite{milner1992a,milner1992b}.
+However, there is a mismatch between the structure of the proof terms of CLL and the term constructs of the standard \textpi-calculus~\citep{milner1992a,milner1992b}.
 For instance, the term for output of a linear name is $\tm{\cpSend{x}{y}{P}{Q}}$, which is read ``send $y$ over $x$ and proceed as $P$ in parallel to $Q$''.
@@
 Instead, the parallel composition shows up in any term which corresponds to a binary rule.
-Even if we were to add an independent parallel composition via the \textsc{Mix}-rule, as suggested in the original presentation of \cp~\cite{wadler2012}, there would be no way to allow the composed process $\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as there is no independent name restriction either!
+Even if we were to add an independent parallel composition via the \textsc{Mix}-rule, as suggested in the original presentation of \cp~\citep{wadler2012}, there would be no way to allow the composed process $\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as there is no independent name restriction either!
 Instead, synchronisation is governed by the ``cut'' operator $\tm{\piNew{x}{(\piPar{P}{Q})}}$, which composes $\tm{P}$ and $\tm{Q}$, enabling them to communicate along $\tm{x}$.
@@
 In this paper, we introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch.
-The key insight is to register parallelism in the typing judgements using hypersequents~\cite{avron1991}, a technique from logic which generalises judgements from one sequent to many.
+The key insight is to register parallelism in the typing judgements using hypersequents~\citep{avron1991}, a technique from logic which generalises judgements from one sequent to many.
 This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
@@
 The variables $\tm{x}$, $\tm{y}$, and $\tm{z}$ range over channel names.
-The construct $\tm{\cpLink{x}{y}}$ links two channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on $\tm{x}$ to $\tm{y}$ and vice versa.
+The construct $\tm{\cpLink{x}{y}}$ links two channels~\citep{sangiorgi1996,boreale1998}, forwarding messages received on $\tm{x}$ to $\tm{y}$ and vice versa.
 The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
@@
 In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote input, square brackets denote output.
-We use bound output~\cite{sangiorgi1996}, meaning that both input and output bind a new name.
+We use bound output~\citep{sangiorgi1996}, meaning that both input and output bind a new name.
 In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
@@
 \paragraph{Metatheory}
-\cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.
+\cp enjoys subject reduction, progress, and termination~\citep{wadler2012}.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
@@
 
-Since its inception, linear logic has been described as the logic of concurrency \cite{girard1987}.
-Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \cite{abramsky1994,bellin1994}, by interpreting linear logic propositions as types for channels.
-Later, linearity inspired also the seminal theories of linear types for the \textpi-calculus \cite{kobayashi1999} and session types \cite{honda1998}.
-Even though the two theories do not have a direct correspondence with linear logic, the link is still strong enough that session types can be encoded into linear types \cite{dardha2017}.
+Since its inception, linear logic has been described as the logic of concurrency \citep{girard1987}.
+Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \citep{abramsky1994,bellin1994}, by interpreting linear logic propositions as types for channels.
+Later, linearity inspired also the seminal theories of linear types for the \textpi-calculus \citep{kobayashi1999} and session types \citep{honda1998}.
+Even though the two theories do not have a direct correspondence with linear logic, the link is still strong enough that session types can be encoded into linear types \citep{dardha2017}.
 
@@
 
-We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\cite{wadler2012}.
+We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\citep{wadler2012}.
 We showed that \hcp enjoys preservation, progress and termination, and described its relation to \cp.
@@
 \clearpage
-\bibliographystyle{abbrvnat}
+\bibliographystyle{apalike}
 \bibliography{main}

### 2018-04-30 doc/tlla2018/main.tex
Minor fix
Abstract

@@
 \input{preamble-typing}
-\usepackage[sectionbib,authordate,sort&compress]{natbib}
+\usepackage[sectionbib,sort&compress]{natbib}
 \usepackage{more-space}
@@
   for deadlock-free concurrent programming.
-However, there is a mismatch between the structures of operators used as proof terms in previous work, and the term constructs of the standard \textpi-calculus.
-We introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch.
-The key insight is to register parallelism in the typing judgements using hypersequents, a technique from logic which generalises judgements from one sequent to many.
-This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
-We prove that \hcp enjoys subject reduction and progress, and prove several properties relating it back to \cp.
+However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus.
+We introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch by using hypersequents (collections of sequents) to register parallelism in the typing judgements.
+	% This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the \textpi-calculus.
+	We prove that \hcp enjoys deadlock-freedom and a series of properties that relate it back to \cp.
 \end{abstract}

### 2018-04-30 doc/tlla2018/main.tex
Cuts cuts cuts

@@
 Classical Processes (\cp) \citep{wadler2012} is a process calculus inspired by the correspondence between the session-typed \textpi-calculus and linear logic \citep{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
-Bridging process languages to linear logic paves the way for applying methods developed in one field to the other.
-For instance, the proof theory of linear logic can be used to guarantee progress for processes~\citep{caires2010,wadler2012}.
+This correspondence allows for exchanging methods between the two fields.
+For example, the proof theory of linear logic can be used to guarantee progress for processes \citep{caires2010,wadler2012}.
 
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
-\end{lemma}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{lemma}%\vspace*{-0.75\baselineskip}%
+% \begin{proof}
+%   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
+% \end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Preservation]\label{thm:cp-preservation}
   If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{theorem}%\vspace*{-0.75\baselineskip}%
+% \begin{proof}
+%   By induction on the derivation of $\reducesto{P}{Q}$.
+% \end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Progress]\label{thm:cp-progress}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  By induction on the derivation of $\seq[P]{\Gamma}$. If the last rule is \textsc{Cut}, there are four cases:
-  \begin{enumerate*}[label={\alph*)}]
-  \item
-    if either side of the cut is an axiom, we apply \cpRedAxCut1;
-  \item
-    if either side of the cut is itself a cut, we recursively eliminate the cut;
-  \item
-    if both sides are logical rules acting on the cut formula, we apply
-    one of the $\beta$-rules;
-  \item
-    otherwise, at least one side is a logical rule acting on a formula other
-    than the cut formula, in which case we apply one of the $\kappa$-rules.
-  \end{enumerate*}
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{theorem}%\vspace*{-0.75\baselineskip}%
+% \begin{proof}
+%   By induction on the derivation of $\seq[P]{\Gamma}$. If the last rule is \textsc{Cut}, there are four cases:
+%   \begin{enumerate*}[label={\alph*)}]
+%   \item
+%     if either side of the cut is an axiom, we apply \cpRedAxCut1;
+%   \item
+%     if either side of the cut is itself a cut, we recursively eliminate the cut;
+%   \item
+%     if both sides are logical rules acting on the cut formula, we apply
+%     one of the $\beta$-rules;
+%   \item
+%     otherwise, at least one side is a logical rule acting on a formula other
+%     than the cut formula, in which case we apply one of the $\kappa$-rules.
+%   \end{enumerate*}
+% \end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Termination]\label{thm:cp-termination}
   If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  Every reduction reduces a single cut to zero, one or two cuts.
+\end{theorem}%\vspace*{-0.75\baselineskip}%
+% \begin{proof}
+%   Every reduction reduces a single cut to zero, one or two cuts.
 However, each of these cuts is smaller, in the sense that the type of the channel on which the communication takes place is smaller.
@@
 Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
-\end{proof}
+% \end{proof}
 
@@
 \end{definition}\noindent
-One side-effect of the changes on the term level is that our structural congruence is much more standard.
-It has associativity, commutativity, and a unit for parallel composition, commutativity of name restrictions, and scope extrusion.
+A pleasant effect of our updated syntax is that it makes our structural congruence much more standard: it has associativity, commutativity, and a unit for parallel composition, commutativity of name restrictions, and scope extrusion.
 \begin{definition}[Structural congruence]\label{def:hcp-equiv}
@@
 There are two changes to the reduction system.
-First, because $\tm{\piBoundSend{x}{y}{P}}$ and $\tm{\piBoundSend{x}{}{P}}$ are now terms in their own right, the $\cpRedBetaTensParr$ and $\cpRedBetaOneBot$ rules become simpler.
-Secondly, because we have decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent name restriction and parallel composition, the $\kappa$-rules and the relevant $\gamma$-rule all decompose as well.
+First, since $\tm{\piBoundSend{x}{y}{P}}$ and $\tm{\piBoundSend{x}{}{P}}$ are now terms in their own right, the $\cpRedBetaTensParr$ and $\cpRedBetaOneBot$ rules are simpler.
+Second, since we decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent name restriction and parallel composition, the $\kappa$-rules and the relevant $\gamma$-rule all decompose as well.
 \begin{definition}[Reduction]\label{def:hcp-reduction}
@@
 A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of $n$ entangled, but independent processes.
-\begin{definition}[Hyper-environment]\label{def:hcp-hyper-environment}
-  $\ty{\mathcal{G}}, \ty{\mathcal{H}} := \ty{\emptyhypercontext} \; \mid \; \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$
+\begin{definition}[Hyper-environments]\label{def:hcp-hyper-environment}
+  $\ty{\mathcal{G}}, \ty{\mathcal{H}} := \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$
 \end{definition}\noindent
+We write $\ty{\emptyhypercontext}$ for the empty hyper-environment.
 Typing judgements in \hcp associate processes with hyper-environments.
@@
 Note that each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''.
-This prevents self-locking processes \eg $\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
+This prevents self-locking processes, \eg $\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}
@@
 This relation allows us to apply $\kappa$-rules under arbitrary prefixes.
-We can show that, if we allow ourselves to do this, we can rewrite any process to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
+We can use this relation to rewrite any process to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
 \begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
@@
 Since its inception, linear logic has been described as the logic of concurrency \citep{girard1987}.
-Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \citep{abramsky1994,bellin1994}, by interpreting linear logic propositions as types for channels.
-Later, linearity inspired also the seminal theories of linear types for the \textpi-calculus \citep{kobayashi1999} and session types \citep{honda1998}.
+Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \citep{abramsky1994,bellin1994}, by interpreting linear propositions as types for channels.
+Linearity inspired also the seminal theories of linear types for the \textpi-calculus \citep{kobayashi1999} and session types \citep{honda1998}.
 Even though the two theories do not have a direct correspondence with linear logic, the link is still strong enough that session types can be encoded into linear types \citep{dardha2017}.
@@
 The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: \citet{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies.
-This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then explicitly tracked using an additional connection modality (which is not present in \hcp).
+This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
 

### 2018-04-30 doc/tlla2018/main.tex
feedback; put proofs from cp back

@@
 \begin{abstract}
-  Process calculi based in logic, such as \piDILL and \cp, provide a foundation
-  for deadlock-free concurrent programming.
+  Process calculi based in logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
 However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus.
 We introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch by using hypersequents (collections of sequents) to register parallelism in the typing judgements.
-	% This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the \textpi-calculus.
 We prove that \hcp enjoys deadlock-freedom and a series of properties that relate it back to \cp.
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
-\end{lemma}%\vspace*{-0.75\baselineskip}%
-% \begin{proof}
-%   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-% \end{proof}\vspace*{-0.75\baselineskip}%
+\end{lemma}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Preservation]\label{thm:cp-preservation}
   If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem}%\vspace*{-0.75\baselineskip}%
-% \begin{proof}
-%   By induction on the derivation of $\reducesto{P}{Q}$.
-% \end{proof}\vspace*{-0.75\baselineskip}%
+\end{theorem}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  By induction on the derivation of $\reducesto{P}{Q}$.
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Progress]\label{thm:cp-progress}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem}%\vspace*{-0.75\baselineskip}%
-% \begin{proof}
-%   By induction on the derivation of $\seq[P]{\Gamma}$. If the last rule is \textsc{Cut}, there are four cases:
-%   \begin{enumerate*}[label={\alph*)}]
-%   \item
-%     if either side of the cut is an axiom, we apply \cpRedAxCut1;
-%   \item
-%     if either side of the cut is itself a cut, we recursively eliminate the cut;
-%   \item
-%     if both sides are logical rules acting on the cut formula, we apply
-%     one of the $\beta$-rules;
-%   \item
-%     otherwise, at least one side is a logical rule acting on a formula other
-%     than the cut formula, in which case we apply one of the $\kappa$-rules.
-%   \end{enumerate*}
-% \end{proof}\vspace*{-0.75\baselineskip}%
+\end{theorem}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  By induction on the derivation of $\seq[P]{\Gamma}$. If the last rule is \textsc{Cut}, there are four cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item
+    if either side of the cut is an axiom, we apply \cpRedAxCut1;
+  \item
+    if either side of the cut is itself a cut, we recursively eliminate the cut;
+  \item
+    if both sides are logical rules acting on the cut formula, we apply
+    one of the $\beta$-rules;
+  \item
+    otherwise, at least one side is a logical rule acting on a formula other
+    than the cut formula, in which case we apply one of the $\kappa$-rules.
+  \end{enumerate*}
+\end{proof}\vspace*{-0.75\baselineskip}%
 \begin{theorem}[Termination]\label{thm:cp-termination}
   If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem}%\vspace*{-0.75\baselineskip}%
-% \begin{proof}
-%   Every reduction reduces a single cut to zero, one or two cuts.
+\end{theorem}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  Every reduction reduces a single cut to zero, one or two cuts.
 However, each of these cuts is smaller, in the sense that the type of the channel on which the communication takes place is smaller.
@@
 Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
-% \end{proof}
+\end{proof}
 
@@
 
-It would be wonderful if each \hcp process could be translated back into a series of \cp processes.
-However, \hcp exhibits some behaviours which are impossible to directly translate back into \cp.
+\hcp exhibits some behaviours which are impossible to directly translate back into \cp.
 For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
-\begin{example}
-  \(
+\[
   \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q''})}]{
     \Gamma, \Delta, \tmty{x}{A \with B}}
-  \)
-\end{example}\noindent
-Instead, we will define a new relation to characterise the relation between \hcp and \cp processes.
+\]
+Instead, we define a new relation to characterise the relation between \hcp and \cp processes.
 \begin{definition}\label{def:hcp-gk}
@@
 \begin{proof}
-  By induction on the structure of the environment $\Gamma$.
-  If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
-  If $\ty{\Gamma} = \ty{A, B, \Gamma'}$, then we apply $(\parr)$ to get $\seq{A
-    \parr B, \Gamma'}$, and apply the induction hypothesis.
+  By repeated application of $(\parr)$.
+% By induction on the structure of the environment $\Gamma$.
+% If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
+% If $\ty{\Gamma} = \ty{A, B, \Gamma'}$, then we apply $(\parr)$ to get $\seq{A
+%   \parr B, \Gamma'}$, and apply the induction hypothesis.
 \end{proof}\noindent

### 2018-04-30 doc/tlla2018/main.tex
Removed some space hacks
Minor fix
minor changes

@@
 \usepackage{more-space}
-\usepackage{setspace}
-\everypar{\looseness=-1}
-\renewcommand{\baselinestretch}{0.975}
 
@@
 \begin{definition}[Reduction]\label{def:hcp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:hcp-reduction}.
-\end{definition}\noindent
-\begin{figure}[htb]
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under the rules below. %rules in \cref{fig:hcp-reduction}.
+%\end{definition}\noindent
+%\begin{figure}[htb]
   \[
@@
   \end{center}
-  \caption{Hypersequent Classical Processes, reduction relation.}
-  \label{fig:hcp-reduction}
-\end{figure}
+\end{definition}
+%  \caption{Hypersequent Classical Processes, reduction relation.}
+%  \label{fig:hcp-reduction}
+%\end{figure}
 
@@
   A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
-Typing judgements can be constructed using the inference rules in \cref{fig:hcp}.
-Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-\end{definition}\noindent
-\begin{figure}[htb]
+  Typing judgements can be constructed using the inference rules below.
+%  in \cref{fig:hcp}. Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
+%\end{definition}\noindent
+%\begin{figure}[htb]
   \begin{center}\hccpInfAx \hccpInfCycle\end{center}
@@
   \begin{center}\hccpInfBot \hccpInfPlus1 \hccpInfPlus2\end{center}
-  \vspace*{0.5\baselineskip}
+  \vspace*{-0.5\baselineskip}
   \begin{center}\hccpInfWith \hccpInfNil \hccpInfTop\end{center}
-  \caption{Hypersequent Classical Processes, typing.}
-  \label{fig:hcp}
-\end{figure}
+%  \caption{Hypersequent Classical Processes, typing.}
+%  \label{fig:hcp}
+%\end{figure}
+Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
+\end{definition}
 
@@
 \[
-  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q''})}]{
+  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
     \Gamma, \Delta, \tmty{x}{A \with B}}
@@
 
-We start out by showing that we can interpret environments as types by collapsing them using a series of pars.
+Environments can be interpreted as types by collapsing them as series of pars.
 \begin{definition}\label{def:bigparr}
@@
 \end{proof}\noindent
-Then, using \cref{lem:hcp-disentangle}, we can show that we can interpret hyper-environments as types by collapsing them using a series of tensors.
-In the case of the empty hyper-environment $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
+Furthermore, hyper-environments can be interpreted as types by collapsing them as series of tensors where environments are handled using \cref{lem:hcp-disentangle}.
+The empty hyper-environment $\ty{\emptyhypercontext}$ (that is the unit of $\hsep$) is interpreted as the unit of tensor.
 \begin{definition}\label{def:bigtens}

### 2018-05-01 doc/tlla2018/main.tex
added notation for empty environment & definition of bigparr
Removed draft option; minor fixes

@@
-\documentclass[draft,submission,copyright,creativecommons]{eptcs}
+\documentclass[submission,copyright,creativecommons]{eptcs}
 \providecommand{\event}{Linearity and TLLA 2018}
@@
 Names in environments must be unique, and environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
+We write $\ty{\cdot}$ for the empty environment.
 \begin{definition}[Environments]\label{def:cp-environments}
@@
   \label{fig:cp}
-\end{figure}\noindent
+\end{figure}
+
 Typing judgements associate processes with collections of typed channels.
@@
 A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of $n$ entangled, but independent processes.
+We write $\ty{\emptyhypercontext}$ for the empty hyper-environment.
 \begin{definition}[Hyper-environments]\label{def:hcp-hyper-environment}
@@
 \end{definition}\noindent
-We write $\ty{\emptyhypercontext}$ for the empty hyper-environment.
 Typing judgements in \hcp associate processes with hyper-environments.
@@
   \(
-  \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} =
-  \ty{A_1 \parr \dots \parr A_n}
+  \begin{array}{lcll}
+    \ty{\bigparr(\emptycontext)}
+    & = & \ty{\bot}
+    \\
+    \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} 
+     & = & \ty{A_1 \parr \dots \parr A_n}
+     & \text{ if } n \geq 1
+    \\
+  \end{array}
   \)
@@
   \(
-  \begin{array}{lcl}
+  \begin{array}{lcll}
     \ty{\bigtens(\emptyhypercontext)}
@@
     & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
+    & \text{ if } n \geq 1
   \end{array}

### 2018-05-01 doc/tlla2018/main.tex
minor fix
commented out conclusions

@@
   \label{fig:cp}
-\end{figure}
-
+\end{figure}\noindent
 Typing judgements associate processes with collections of typed channels.
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
-
-We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\citep{wadler2012}.
+%\section{Conclusions}
+%\label{sec:conclusions}
+%
+%We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\citep{wadler2012}.
 We showed that \hcp enjoys preservation, progress and termination, and described its relation to \cp.

### 2018-05-13 doc/tlla2018/main.tex
Fixed typing rules, removed possibility to continue after a (1) rule.

@@
   \end{enumerate*}
-  Since the only way to continue after a $(\one)$ is by using a mix, all applications of $(\one)$ are now followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
+  All applications of $(\one)$ are followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
 \end{proof}\noindent
@@
 
-%\section{Conclusions}
-%\label{sec:conclusions}
-%
-%We introduced Hypersequent Classical Processes, a process calculus which addresses the mismatch between proof terms and \textpi-calculus terms which exists in Classical Processes~\citep{wadler2012}.
-We showed that \hcp enjoys preservation, progress and termination, and described its relation to \cp.
-
 \clearpage

### 2018-05-21 doc/abstract/main.tex
Renamed tlla2018/ to abstract/
Removed the space hackery.

--- 2018-05-13 doc/tlla2018/main.tex
@@
 \usepackage[sectionbib,sort&compress]{natbib}
-\usepackage{more-space}
 
@@
   \begin{center}\cpInfAx    \cpInfCut   \end{center}
-  \vspace*{-.5\baselineskip}
-  \begin{center}\cpInfTens \cpInfParr \cpInfOne \end{center}
-  \vspace*{-.5\baselineskip}
-  \begin{center}\cpInfBot \cpInfPlus1 \cpInfPlus2\end{center}
-  \vspace*{-.5\baselineskip}
-  \begin{center}\cpInfWith \cpInfNil \cpInfTop \end{center}
+  \begin{center}\cpInfTens  \cpInfParr  \end{center}
+  \begin{center}\cpInfBot   \cpInfOne   \end{center}
+  \begin{center}\cpInfPlus1 \cpInfPlus2 \end{center}
+  \begin{center}\cpInfWith              \end{center}
+  \begin{center}\cpInfNil   \cpInfTop   \end{center}
   \caption{Classical Processes, typing.}
@@
 However, each of these cuts is smaller, in the sense that the type of the channel on which the communication takes place is smaller.
-Each reduction either eliminates a connective.
+Each reduction eliminates a connective.
 Furthermore, each instance of the structural congruence preserves the size of the cut.
@@
   A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
-  Typing judgements can be constructed using the inference rules below.
-%  in \cref{fig:hcp}. Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-%\end{definition}\noindent
-%\begin{figure}[htb]
-  \begin{center}\hccpInfAx \hccpInfCycle\end{center}
-  \vspace*{-0.5\baselineskip}
-  \begin{center}\hccpInfMix \hccpInfHalt\end{center}
-  \vspace*{-0.5\baselineskip}
-  \begin{center}\hccpInfBoundTens \hccpInfParr \hccpInfOne\end{center}
-  \vspace*{-0.5\baselineskip}
-  \begin{center}\hccpInfBot \hccpInfPlus1 \hccpInfPlus2\end{center}
-  \vspace*{-0.5\baselineskip}
-  \begin{center}\hccpInfWith \hccpInfNil \hccpInfTop\end{center}
-%  \caption{Hypersequent Classical Processes, typing.}
-%  \label{fig:hcp}
-%\end{figure}
-Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-\end{definition}
+  Typing judgements can be constructed using the inference rules in
+  \cref{fig:hcp}.
+  Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
+\end{definition}\noindent
+\begin{figure}[htb]
+  \begin{center}\hccpInfAx        \hccpInfCycle \end{center}
+  \begin{center}\hccpInfMix       \hccpInfHalt  \end{center}
+  \begin{center}\hccpInfBoundTens \hccpInfParr  \end{center}
+  \begin{center}\hccpInfOne       \hccpInfBot   \end{center}
+  \begin{center}\hccpInfPlus1     \hccpInfPlus2 \end{center}
+  \begin{center}\hccpInfWith                    \end{center}
+  \begin{center}\hccpInfNil       \hccpInfTop   \end{center}
+  \caption{Hypersequent Classical Processes, typing.}
+  \label{fig:hcp}
+\end{figure}
 

### 2018-05-21 doc/abstract/main.tex
Readded parskip; removed more space hacking; rewrite disentanglement to avoid mentioning processes.

@@
 \usepackage{underscore} % Only needed if you use pdflatex.
+\usepackage{parskip}
 \usepackage{textcomp,textgreek,upgreek}
@@
 \hypersetup{hidelinks,final}
-\newtheorem{definition}{Definition}
 \newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{example}{Example}
+\newtheorem{theorem}[lemma]{Theorem}
+\newtheorem{corollary}[lemma]{Corollary}
+\newtheorem{definition}[lemma]{Definition}
 \input{preamble-typing}
@@
 
-\paragraph{Terms}
+\subsection{Terms}
 The term language of \cp is a variant of the \textpi-calculus.
@@
 
-\paragraph{Types}
+\subsection{Types}
 Channels in \cp are typed using a session type system which corresponds to classical linear logic.
@@
 
-\paragraph{Metatheory}
+\subsection{Metatheory}
 \cp enjoys subject reduction, progress, and termination~\citep{wadler2012}.
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}
 \begin{theorem}[Preservation]\label{thm:cp-preservation}
@@
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}[Progress]\label{thm:cp-progress}
@@
   \end{enumerate*}
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}[Termination]\label{thm:cp-termination}
@@
 
-\paragraph{Terms}
+\subsection{Terms}
 The term language of \hcp is a variant of \cp where the term constructs have been taken apart into \textpi-calculus primitives.
@@
 \begin{definition}[Reduction]\label{def:hcp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under the rules below. %rules in \cref{fig:hcp-reduction}.
-%\end{definition}\noindent
-%\begin{figure}[htb]
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under the rules in \cref{fig:hcp-reduction}.
+The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of $\Longrightarrow$.
+\end{definition}
+\begin{figure}[htb]
   \[
@@
       \hccpRedBetaOneBot
-      & \tm{\cpCut{x}{\piBoundSend{x}{}{P}}{\piRecv{x}{}{P}}}
+      & \tm{\cpCut{x}{\piBoundSend{x}{}{P}}{\piRecv{x}{}{Q}}}
       & \Longrightarrow
@@
   \end{center}
-\end{definition}
-%  \caption{Hypersequent Classical Processes, reduction relation.}
-%  \label{fig:hcp-reduction}
-%\end{figure}
+  \label{fig:hcp-reduction}
+  \caption{Hypersequent Classical Processes, reduction relation.}
+\end{figure}
 
-\paragraph{Types}
+\subsection{Types}
 We use the same definitions for types and environments for \hcp as we used for \cp.
@@
 
-\paragraph{Metatheory}
+\subsection{Metatheory}
 \hcp enjoys subject reduction, progress, and termination.
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}[Preservation]\label{thm:hcp-preservation}
@@
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}[Progress]\label{thm:hcp-progress}
@@
   \end{enumerate*}
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}[Termination]\label{thm:hcp-termination}
@@
   \vspace*{-\baselineskip}%
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}\label{thm:cp2hcp-equiv}
@@
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-% We show the interesting cases:
-% \begin{itemize}
-% \item
-%   Case \cpEquivCutComm.
-%   \begin{gather*}
-%   \begin{array}{lcl}
-%     \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
-%     & \equiv & \text{by \hccpEquivMixComm}
-%     \\
-%     \tm{\piNew{x}{(\piPar{\mtf{Q}}{\mtf{P}})}}
-%   \end{array}
-%   \end{gather*}
-% \item
-%   Case \cpEquivCutAss1.
-%   \begin{gather*}
-%   \begin{array}{lcl}
-%     \tm{\piNew{x}{(\piPar{\mtf{P}}{\piNew{y}{(\piPar{\mtf{Q}}{\mtf{R}})}})}}
-%     & \equiv & \text{%
-%                by \hccpEquivNewComm, \hccpEquivMixAss1, \hccpEquivMixComm,
-%                and \hccpEquivScopeExt{}}
-%     \\
-%     \tm{\piNew{y}{(\piPar{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}{\mtf{R}})}}
-%   \end{array}
-%   \end{gather*}
-% \end{itemize}
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}\label{thm:cp2hcp-reduction}
-  If $\reducesto{P}{Q}$ in \cp, then $\reducesto{\mtf{P}}{\mtf{Q}}$ in \hcp.
+  If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
 \end{theorem}\vspace*{-0.75\baselineskip}%
@@
   By induction on the the derivation of $\reducesto{P}{Q}$.
-% We show the interesting cases:
-% \begin{itemize}
-% \item
-%   Case \cpRedBetaTensParr.
-%   \begin{gather*}
-%   \begin{array}{lcl}
-%     \tm{\piNew{x}{(\piPar{\piBoundSend{x}{y}{(\piPar{P}{Q})}}{\piRecv{x}{z}{R}})}}
-%     & \Longrightarrow & \text{by \hccpRedBetaTensParr}
-%     \\
-%     \tm{\piNew{x}{\piNew{y}{(\piPar{(\piPar{P}{Q})}{\cpSub{y}{z}{R}})}}}
-%     & \equiv & \text{%
-%                by \hccpEquivNewComm, \hccpEquivMixAss1, and \hccpEquivScopeExt1}
-%     \\
-%     \tm{\piNew{y}{(\piPar{P}{\piNew{x}{(\piPar{Q}{\cpSub{y}{z}{R}})}})}}
-%   \end{array}
-%   \end{gather*}
-% \item
-%   Case \cpRedBetaOneBot.
-%   \begin{gather*}
-%   \begin{array}{lcl}
-%     \tm{\piNew{x}{(\piPar{\piBoundSend{x}{}{\piHalt}}{\piRecv{x}{}{\mtf{Q}}})}}
-%     & \Longrightarrow & \text{by \hccpRedBetaOneBot}
-%     \\
-%     \tm{(\piPar{\piHalt}{\mtf{Q}})}
-%     & \equiv & \text{by \hccpEquivMixHalt1}
-%     \\
-%     \tm{\mtf{Q}}
-%   \end{array}
-%   \end{gather*}
-% \end{itemize}
-\end{proof}\vspace*{-0.75\baselineskip}%
+\end{proof}%
 \begin{theorem}\label{hcp2cp-reduction}
@@
 \]
-Instead, we define a new relation to characterise the relation between \hcp and \cp processes.
+Instead, we define a new relation to characterise the relation between proofs in \hcp and \cp.
 \begin{definition}\label{def:hcp-gk}
-  The relation $\tm{P}\equiv_{\gamma\kappa}\tm{Q}$ is the congruence closure of the $\gamma$- and $\kappa$-rules for \hcp.
+  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules below.
+  The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
+  \begin{center}
+    \resizebox{\textwidth}{!}{
+    \(
+    \begin{array}{lcr}
+      \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
+      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
+      \NOM{H-Cut}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+      \DisplayProof
+      & \moveMixDown
+      & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+        \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
+        \NOM{H-Cut}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+        \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+        \NOM{H-Mix}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+        \DisplayProof
+      \\\\
+      \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
+      \SYM{\tens}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
+      \hsep {A \tens B}, \Gamma, \Delta}$}
+      \DisplayProof
+      & \moveMixDown
+      & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+        \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
+        \SYM{\tens}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \tens B},
+        \Gamma, \Delta}$}
+        \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+        \NOM{H-Mix}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
+        \hsep {A \tens B}, \Gamma, \Delta}$} 
+        \DisplayProof
+      \\\\
+      \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
+      \SYM{\parr}
+      \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
+      \DisplayProof
+      & \moveMixDown
+      & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
+        \SYM{\parr}
+        \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
+        \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+        \NOM{H-Mix}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
+        \DisplayProof
+      \\\\
+      \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
+      \SYM{\bot}
+      \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {\bot}, \Gamma}$}
+      \DisplayProof
+      & \moveMixDown
+      & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
+        \SYM{\bot}
+        \UIC{$\seq{\mathcal{G}_1 \hsep {\bot}, \Gamma}$}
+        \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+        \NOM{H-Mix}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
+        \DisplayProof
+      \\\\
+      \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+      \SYM{\plus_1}
+      \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
+      \DisplayProof
+      & \moveMixDown
+      & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+        \SYM{\plus_1}
+        \UIC{$\seq{\mathcal{G}_1 \hsep {A \plus B}, \Gamma}$}
+        \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+        \NOM{H-Mix}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
+        \DisplayProof
+      \\\\
+      \multicolumn{3}{l}{%
+      \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
+      \pvar{$\rho_4$}\UIC{$\seq{\mathcal{G}_2}$} 
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {B}, \Gamma}$}
+      \SYM{\with}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
+      \DisplayProof
+      }
+      \\\\
+      & \moveMixDown
+      & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+        \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
+        \SYM{\with}
+        \BIC{$\seq{\mathcal{G}_1 \hsep {A \with B}, \Gamma}$}
+        \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+        \NOM{H-Mix}
+        \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
+        \DisplayProof
+    \end{array}
+    \)}
+  \end{center}
 \end{definition}\noindent
-This relation allows us to apply $\kappa$-rules under arbitrary prefixes.
-We can use this relation to rewrite any process to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
+This relation allows us to move applications of $\textsc{H-Mix}$ downwards in the proof tree.
+We can use this relation to rewrite any derivation to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
 \begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
-  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ in \cp, such that $\tm{P}\equiv_{\gamma\kappa}\tm{(\mtf{P_1}\ppar\dots\ppar\mtf{P_n})}$.
+  If there exists a derivation $\rho$ of $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist derivations $\rho_1, \dots, \rho_n$ of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp such that
+  \[
+  \rho
+  \moveMixDown^\star
+  \begin{prooftree*}
+    \AXC{}\noLine\UIC{$\rho_1$}
+    \AXC{}\noLine\UIC{$\dots$}
+    \AXC{}\noLine\UIC{$\rho_n$}
+    \NOM{H-Mix}
+    \TIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+  \end{prooftree*}
+  \]
 \end{lemma}\vspace*{-0.75\baselineskip}%
 \begin{proof}
-  We repeatedly apply the $\kappa{\ppar}$-rules to move the mixes upwards. There are three cases:
+  We repeatedly apply the $\moveMixDown$-rules to the derivation $\rho$ to move the mixes downwards.
+  There are three cases:
   \begin{enumerate*}[label={\alph*)}]
@@
 \begin{definition}\label{def:bigparr}
-  \(
+  \[
   \begin{array}{lcll}
@@
   \end{array}
-  \)
+  \]
 \end{definition}\noindent
@@
   By repeated application of $(\parr)$.
-% By induction on the structure of the environment $\Gamma$.
-% If $\ty{\Gamma} = \ty{A}$, then the statement is trivially true.
-% If $\ty{\Gamma} = \ty{A, B, \Gamma'}$, then we apply $(\parr)$ to get $\seq{A
-%   \parr B, \Gamma'}$, and apply the induction hypothesis.
 \end{proof}\noindent
@@
 \begin{definition}\label{def:bigtens}
-  \(
+  \[
   \begin{array}{lcll}

### 2018-05-21 doc/abstract/main.tex
Finished first rewrite
Minor changes

@@
 \usepackage{underscore} % Only needed if you use pdflatex.
-\usepackage{parskip}
+%\usepackage{parskip}
 \usepackage{textcomp,textgreek,upgreek}
@@
 Then, we introduce \hcp and prove it enjoys subject reduction and progress (\cref{sec:hcp}).
-We prove that every \cp process is an \hcp process, that every \hcp process corresponds to several entangled \cp processes, and that \hcp supports the same communication protocols as \cp, and no more (\cref{sec:cp2hcp}).
+We prove that every \cp process is an \hcp process, and that \hcp supports the same communication protocols as \cp, and no more (\cref{sec:cp2hcp}).
 Finally, we discuss related work (\cref{sec:related-work}).
@@
 
-In this section, we discuss the relation between \cp and \hcp. We will prove three important theorems:
-\begin{enumerate*}[label={\alph*)}]
-\item every \cp process is an \hcp process;
-\item \hcp processes represent multiple entangled \cp processes; and
-\item \hcp supports the same protocols as \cp.
-\end{enumerate*}
+In this section, we discuss the relation between \cp and \hcp.
+We will prove two important theorems: every \cp process is an \hcp process; and \hcp supports the same protocols as \cp.
 To facilitate this, we define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp.
@@
 \end{definition}\noindent
+We will use this relation in the first proof, and its analogue for derivations in the second.
+
+\subsection{Every \cp process is an \hcp process}
 First, we prove that each \cp process can be translated by this trivial translation to an \hcp process, and that this translation respects structural congruence and reduction.
@@
 
+\subsection{\hcp supports the same communication protocols as \cp}
 \hcp exhibits some behaviours which are impossible to directly translate back into \cp.
@@
 \]
-Instead, we define a new relation to characterise the relation between proofs in \hcp and \cp.
+
+Instead, we will prove that \hcp supports the same communication protocols as \cp.
+This is the same as saying that it inhabits the same session types, or that the associated logical systems derive the same theorems.
+We show this by proving that we can interpret the hyper-environments as formulas in the logic.
+This is a standard method for proving the soundness of a hypersequent calculus.
+We start off by defining a relation on derivations of \hcp.
 \begin{definition}\label{def:hcp-gk}
-  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules below.
+  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules below, plus the associativity and commutativity of mixes.
 The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
@@
     \(
+    \setlength{\arraycolsep}{2pt}
     \begin{array}{lcr}
@@
       \\\\
-      \multicolumn{3}{l}{%
       \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
@@
       \DisplayProof
-      }
-      \\\\
       & \moveMixDown
@@
   \begin{prooftree*}
-    \AXC{}\noLine\UIC{$\rho_1$}
+    \AXC{}\noLine\UIC{$\mtf{\rho_1}$}
     \AXC{}\noLine\UIC{$\dots$}
-    \AXC{}\noLine\UIC{$\rho_n$}
+    \AXC{}\noLine\UIC{$\mtf{\rho_n}$}
     \NOM{H-Mix}
@@
 \end{proof}\noindent
-
-Finally, we will prove that \hcp supports the same communication protocols as \cp.
-This is the same as saying that it inhabits the same session types, or that the associated logical systems derive the same theorems.
-We show this by proving that we can interpret the hyper-environments as formulas in the logic.
-This is a standard method for proving the soundness of a hypersequent calculus.
-
 Environments can be interpreted as types by collapsing them as series of pars.

### 2018-05-23 doc/abstract/main.tex
minor changes
Rewrote figure & text around disentanglement; text around hyper-environments.

@@
 \hypersetup{hidelinks,final}
-\newtheorem{lemma}{Lemma}
+\newtheorem{lemma}{Lemma}[section]
 \newtheorem{theorem}[lemma]{Theorem}
@@
 Names in environments must be unique, and environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
-We write $\ty{\cdot}$ for the empty environment.
 \begin{definition}[Environments]\label{def:cp-environments}
   \(
-    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} := \tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}
+    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} := \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
   \)
@@
 A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of $n$ entangled, but independent processes.
-We write $\ty{\emptyhypercontext}$ for the empty hyper-environment.
 \begin{definition}[Hyper-environments]\label{def:hcp-hyper-environment}
-  $\ty{\mathcal{G}}, \ty{\mathcal{H}} := \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$
-\end{definition}\noindent
+  $\ty{\mathcal{G}}, \ty{\mathcal{H}} := \ty{\emptyhypercontext} \, \mid \, \ty{\mathcal{G} \hsep \Gamma}$
+\end{definition}\noindent
+Hyper-environments are multisets of environments.
+While names within environments must be unique, names may be shared between multiple environments in a hyper-environment.
+We write $\ty{\mathcal{G} \hsep \mathcal{H}}$ to combine two hyper-environments.
+
 Typing judgements in \hcp associate processes with hyper-environments.
@@
 \]
-
 Instead, we will prove that \hcp supports the same communication protocols as \cp.
@@
 This is a standard method for proving the soundness of a hypersequent calculus.
-We start off by defining a relation on derivations of \hcp.
+
+We start off by defining a relation on derivations of \hcp, which we call ``disentanglement''.
+This relation allows us to move applications of $\textsc{H-Mix}$ downwards in the proof tree.
+We can use this relation to rewrite any derivation to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
 \begin{definition}\label{def:hcp-gk}
-  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules below, plus the associativity and commutativity of mixes.
+  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules in \cref{fig:disentangle}, plus the associativity and commutativity of mixes.
 The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
-  \begin{center}
-    \resizebox{\textwidth}{!}{
+\end{definition}\noindent
+We named this relation ``disentanglement'' to reflect the intuition that proof in \hcp represent multiple entangled \cp proofs, which we can disentangle.
+However, this is not entirely accurate.
+The proof structure of \hcp is slightly richer than that of \cp.
+This can be seen in the example process above.
+In this case, when disentangling, we are forced to forget some of the proof structure.
+This can be seen in the last rule in \cref{fig:disentangle}.
+Nonetheless, the relation is type preserving, and so it suffices for showing that \hcp supports the same communication protocols as \cp.
+\begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
+  If there exists a derivation $\rho$ of $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist derivations $\rho_1, \dots, \rho_n$ of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp such that
+  \[
+  \rho
+  \moveMixDown^\star
+  \begin{prooftree*}
+    \AXC{}\noLine\UIC{$\mtf{\rho_1}$}
+    \AXC{}\noLine\UIC{$\dots$}
+    \AXC{}\noLine\UIC{$\mtf{\rho_n}$}
+    \NOM{H-Mix}
+    \TIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+  \end{prooftree*}
+  \]
+\end{lemma}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  We repeatedly apply the $\moveMixDown$-rules to the derivation $\rho$ to move the mixes downwards.
+  There are three cases:
+  \begin{enumerate*}[label={\alph*)}]
+  \item
+    if a mix gets stuck under a cut, it forms a \cp cut;
+  \item
+    if a mix gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
+  \item
+    otherwise, it moves all the way to the top.
+  \end{enumerate*}
+  All applications of $(\one)$ are followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
+\end{proof}\noindent
+Environments can be interpreted as types by collapsing them as series of pars.
+\begin{definition}\label{def:bigparr}
+  \[
+  \begin{array}{lcll}
+    \ty{\bigparr(\emptycontext)}
+    & = & \ty{\bot}
+    \\
+    \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} 
+     & = & \ty{A_1 \parr \dots \parr A_n}
+     & \text{ if } n \geq 1
+    \\
+  \end{array}
+  \]
+\end{definition}\noindent
+\begin{lemma}\label{lem:cp-bigparr}
+  If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
+\end{lemma}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  By repeated application of $(\parr)$.
+\end{proof}\noindent
+Furthermore, hyper-environments can be interpreted as types by collapsing them as series of tensors where environments are handled using \cref{lem:hcp-disentangle}.
+The empty hyper-environment $\ty{\emptyhypercontext}$ is interpreted as the unit of tensor.
+\begin{definition}\label{def:bigtens}
+  \[
+  \begin{array}{lcll}
+    \ty{\bigtens(\emptyhypercontext)}
+    & = & \ty{\one}
+    \\
+    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
+    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
+    & \text{ if } n \geq 1
+  \end{array}
+  \]
+\end{definition}\noindent
+
+\begin{theorem}\label{thm:hcp2cp-bigtens}
+  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
+\end{theorem}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
+  If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
+  If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$, we apply \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots, \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
+\end{proof}\noindent
+
+\begin{sidewaysfigure}[htb]
   \(
-    \setlength{\arraycolsep}{2pt}
   \begin{array}{lcr}
@@
   \end{array}
-    \)}
-  \end{center}
-\end{definition}\noindent
-This relation allows us to move applications of $\textsc{H-Mix}$ downwards in the proof tree.
-We can use this relation to rewrite any derivation to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
-\begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
-  If there exists a derivation $\rho$ of $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist derivations $\rho_1, \dots, \rho_n$ of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp such that
-  \[
-  \rho
-  \moveMixDown^\star
-  \begin{prooftree*}
-    \AXC{}\noLine\UIC{$\mtf{\rho_1}$}
-    \AXC{}\noLine\UIC{$\dots$}
-    \AXC{}\noLine\UIC{$\mtf{\rho_n}$}
-    \NOM{H-Mix}
-    \TIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
-  \end{prooftree*}
-  \]
-\end{lemma}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  We repeatedly apply the $\moveMixDown$-rules to the derivation $\rho$ to move the mixes downwards.
-  There are three cases:
-  \begin{enumerate*}[label={\alph*)}]
-  \item
-    if a mix gets stuck under a cut, it forms a \cp cut;
-  \item
-    if a mix gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
-  \item
-    otherwise, it moves all the way to the top.
-  \end{enumerate*}
-  All applications of $(\one)$ are followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
-\end{proof}\noindent
-Environments can be interpreted as types by collapsing them as series of pars.
-\begin{definition}\label{def:bigparr}
-  \[
-  \begin{array}{lcll}
-    \ty{\bigparr(\emptycontext)}
-    & = & \ty{\bot}
-    \\
-    \ty{\bigparr(\tmty{x_1}{A_1} , \dots , \tmty{x_n}{A_n})} 
-     & = & \ty{A_1 \parr \dots \parr A_n}
-     & \text{ if } n \geq 1
-    \\
-  \end{array}
-  \]
-\end{definition}\noindent
-\begin{lemma}\label{lem:cp-bigparr}
-  If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
-\end{lemma}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  By repeated application of $(\parr)$.
-\end{proof}\noindent
-Furthermore, hyper-environments can be interpreted as types by collapsing them as series of tensors where environments are handled using \cref{lem:hcp-disentangle}.
-The empty hyper-environment $\ty{\emptyhypercontext}$ (that is the unit of $\hsep$) is interpreted as the unit of tensor.
-\begin{definition}\label{def:bigtens}
-  \[
-  \begin{array}{lcll}
-    \ty{\bigtens(\emptyhypercontext)}
-    & = & \ty{\one}
-    \\
-    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
-    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
-    & \text{ if } n \geq 1
-  \end{array}
-  \]
-\end{definition}\noindent
-
-\begin{theorem}\label{thm:hcp2cp-bigtens}
-  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
-\end{theorem}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  By case analysis on the structure of the hyper-environment $\ty{\mathcal{G}}$.
-  If $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$, we apply $(\one)$.
-  If $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$, we apply \cref{lem:hcp-disentangle} to obtain proofs of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp, then we apply \cref{lem:cp-bigparr} to each of those proofs to obtain proofs of $\seq{\bigparr\Gamma_1}, \dots, \seq{\bigparr\Gamma_n}$, and join them using $(\tens)$ to obtain a single proof of $\seq{\bigtens\mathcal{G}}$ in \cp.
-\end{proof}\noindent
+  \)
+  \caption{The disentanglement relation for \hcp.}
+  \label{fig:disentangle}
+\end{sidewaysfigure}
 
@@
 
-\clearpage
+%\clearpage
 \bibliographystyle{apalike}

### 2018-05-23 doc/abstract/main.tex
Put the \clearpage back in front of the bibliography
rewrite based on feedback

@@
 \usepackage[inline]{enumitem}
-\usepackage{breakurl} % Not needed if you use pdflatex only.
-\usepackage{underscore} % Only needed if you use pdflatex.
+%\usepackage{breakurl} % Not needed if you use pdflatex only.
+%\usepackage{underscore} % Only needed if you use pdflatex.
 %\usepackage{parskip}
@@
 \usepackage{nameref,hyperref}
-\usepackage[nameinlink,noabbrev]{cleveref}
+\usepackage[nameinlink,noabbrev,capitalize]{cleveref}
 \hypersetup{hidelinks,final}
@@
 \begin{abstract}
-  Process calculi based in logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
+  Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
 However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus.
-We introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch by using hypersequents (collections of sequents) to register parallelism in the typing judgements.
+We introduce Hypersequent Classical Processes (\hcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
 We prove that \hcp enjoys deadlock-freedom and a series of properties that relate it back to \cp.
@@
 There is no independent parallel term $\tm{(\piPar{P}{Q})}$ in the grammar of \cp terms.
-Instead, the parallel composition shows up in any term which corresponds to a binary rule.
+Instead, parallel composition shows up in any term which corresponds to a typing rule which splits the context.
 Even if we were to add an independent parallel composition via the \textsc{Mix}-rule, as suggested in the original presentation of \cp~\citep{wadler2012}, there would be no way to allow the composed process $\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as there is no independent name restriction either!
 Instead, synchronisation is governed by the ``cut'' operator $\tm{\piNew{x}{(\piPar{P}{Q})}}$, which composes $\tm{P}$ and $\tm{Q}$, enabling them to communicate along $\tm{x}$.
-Worse, if we naively added an independent parallel composition as well as a name restriction, using the rules shown below, we would lose cut elimination, and therefore deadlock-freedom!
+Worse, if we naively add an independent parallel composition as well as a name restriction, using the rules shown below, we lose cut elimination, and therefore deadlock-freedom!
 \begin{center}
@@
 
-In this paper, we introduce the Hypersequent Classical Processes (\hcp), which addresses this mismatch.
+In this paper, we introduce Hypersequent Classical Processes (\hcp), which addresses this mismatch.
 The key insight is to register parallelism in the typing judgements using hypersequents~\citep{avron1991}, a technique from logic which generalises judgements from one sequent to many.
@@
 In this section, we introduce \cp.
-In order to keep the discussion of \hcp in \cref{sec:hcp} simple, we restrict ourselves to the multiplicative-applicative subset of \cp.
+In order to keep the discussion of \hcp in \cref{sec:hcp} simple, we restrict ourselves to the multiplicative-additive subset of \cp.
 We foresee no problems in extending the proofs in \cref{sec:hcp} to cover the remaining features of \cp (polymophism and the exponentials).
@@
 In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote input, square brackets denote output.
-We use bound output~\citep{sangiorgi1996}, meaning that both input and output bind a new name.
+\cp uses bound output~\citep{sangiorgi1996}, meaning that both input and output bind a new name.
 In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
@@
   Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:cp-reduction}.
-The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
-  $\Longrightarrow$.
+The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of $\Longrightarrow$.
+The relation $\Longrightarrow^{+}$ is the transitive closure of $\Longrightarrow$.
 \end{definition}
@@
 Channels in \cp are typed using a session type system which corresponds to classical linear logic.
-A process communicating over a channel of type \ty{A \tens B} must be ready to split into two independent processes (two processes which share no channels), ready to communicate over a channel of type \ty{A} and \ty{B}, respectively, and process communicating over a channel of type \ty{A \parr B} is dual to this, and therefore must be ready to start communicating concurrently with two independent processes.
-A process communicating over a channel of type \ty{A \plus B} can choose to communicate either as \ty{A} or \ty{B}, and a process communicating over a channel of type \ty{A \with B} must be able to communicate either as \ty{A} or \ty{B}.
 \begin{definition}[Types]\label{def:cp-types}
@@
 \end{definition}\noindent
+
+A channel of type \ty{A \tens B} represents a pair of channels, which communicate with two independent processes---that is to say, two processes who share no channels.
+A process acting on a channel of type \ty{A \tens B} will send one endpoint of a fresh channel, and then split into a pair of independent processes.
+One of these processes will be responsible for an interaction of type \ty{A} over the fresh channel, while the other process continues to interact as \ty{B}.
+
+A channel of type \ty{A \parr B} represents a pair of interdependent channels, which are used within a single process.
+A process acting on a channel of type \ty{A \parr B} will receive a channel to act on, and communicate on its channels in whatever order it pleases.
+This means that the usage of one channel can depend on that of another---\eg the interaction of type \ty{B} could depend on the result of the interaction of type \ty{A}, or vise versa, and if \ty{A} and \ty{B} are complex types, their interactions could likewise interweave in complex ways.
+
+A process acting on a channel of type \ty{A \plus B} either sends the value \tm{\text{inl}} to select an interaction of type \ty{A} or the value \tm{\text{inr}} to select one of type \ty{B}. 
+A process acting on a channel of type \ty{A \with B} receives such a value, and then offers an interaction of either type \ty{A} or \ty{B}, correspondingly.
+
 Duality plays a crucial role in both linear logic and session types.
@@
 Each type $\ty{A}$ has a dual, written $\ty{A^\bot}$.
-Duality is an involutive function.
+Duality is an involutive function \ie $\ty{(A^\bot)^\bot} = \ty{A}$.
 \begin{definition}[Duality]\label{def:cp-negation}
@@
 Environments associate channels with types.
-Names in environments must be unique, and environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
+Names in environments must be unique, and environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma, \Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
 \begin{definition}[Environments]\label{def:cp-environments}
@@
 \begin{figure}[htb]
+  \paragraph*{Structural rules}
   \begin{center}\cpInfAx    \cpInfCut   \end{center}
+  \paragraph*{Logical rules}
   \begin{center}\cpInfTens  \cpInfParr  \end{center}
@@
 \begin{definition}[Typing judgements]\label{def:cp}
-  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}}$ denotes
-  that the process \tm{P} communicates along channels $\tm{x_1}\dots\tm{x_n}$
-  following protocols $\ty{A_1}\dots\ty{A_n}$.
+  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n}}$ denotes that the process \tm{P} communicates along channels $\tm{x_1}$, \dots, $\tm{x_n}$ following protocols $\ty{A_1}$, \dots, $\ty{A_n}$.
 Typing judgements are derived using rules in \cref{fig:cp}.
@@
 \subsection{Metatheory}
-\cp enjoys subject reduction, progress, and termination~\citep{wadler2012}.
+\cp enjoys subject reduction, termination, and progress~\citep{wadler2012}.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
@@
 \end{proof}%
+\begin{theorem}[Termination]\label{thm:cp-termination}
+  If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
+\end{theorem}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  Every reduction reduces a single cut to zero, one or two cuts.
+However, each of these cuts is smaller, measured in the size of the cut term.
+Furthermore, each instance of the structural congruence preserves the size of the cut.
+Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
+\end{proof}
 \begin{theorem}[Progress]\label{thm:cp-progress}
@@
 \end{proof}%
-\begin{theorem}[Termination]\label{thm:cp-termination}
-  If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  Every reduction reduces a single cut to zero, one or two cuts.
-However, each of these cuts is smaller, in the sense that the type of the channel on which the communication takes place is smaller.
-Each reduction eliminates a connective.
-Furthermore, each instance of the structural congruence preserves the size of the cut.
-Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
-\end{proof}
 
@@
 \subsection{Terms}
-The term language of \hcp is a variant of \cp where the term constructs have been taken apart into \textpi-calculus primitives.
+The term language of \hcp is a variant of \cp where the term constructs have been taken apart into primitives which more closely resemble the \textpi-calculus primitives.
 \begin{definition}[Terms]\label{def:hcp-terms}
@@
 The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of $\Longrightarrow$.
+The relation $\Longrightarrow^{+}$ is the transitive closure of $\Longrightarrow$.
 \end{definition}
@@
   \end{center}
+  \caption{Hypersequent Classical Processes, reduction relation.}
   \label{fig:hcp-reduction}
-  \caption{Hypersequent Classical Processes, reduction relation.}
 \end{figure}
@@
 \textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar.
-Note that each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''.
+Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''.
 This prevents self-locking processes, \eg $\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
@@
 \begin{figure}[htb]
+  \paragraph*{Structural rules}
   \begin{center}\hccpInfAx        \hccpInfCycle \end{center}
   \begin{center}\hccpInfMix       \hccpInfHalt  \end{center}
+  \paragraph*{Logical rules}
   \begin{center}\hccpInfBoundTens \hccpInfParr  \end{center}
@@
   \begin{center}\hccpInfNil       \hccpInfTop   \end{center}
+  \centering
+  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
   \caption{Hypersequent Classical Processes, typing.}
@@
 \subsection{Metatheory}
-\hcp enjoys subject reduction, progress, and termination.
+\hcp enjoys subject reduction, termination, and progress.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
@@
 \end{proof}%
+\begin{theorem}[Termination]\label{thm:hcp-termination}
+  If $\seq[P]{\mathcal{G}}$, then there are no infinite $\Longrightarrow$-reduction sequences.
+\end{theorem}\vspace*{-0.75\baselineskip}%
+\begin{proof}
+  As \cref{thm:cp-termination}.
+\end{proof}
 \begin{theorem}[Progress]\label{thm:hcp-progress}
@@
 \end{proof}%
-\begin{theorem}[Termination]\label{thm:hcp-termination}
-  If $\seq[P]{\mathcal{G}}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem}\vspace*{-0.75\baselineskip}%
-\begin{proof}
-  As \cref{thm:cp-termination}.
-\end{proof}
 
@@
 
-In this section, we discuss the relation between \cp and \hcp.
+In this section, we discuss the relationship between \cp and \hcp.
 We will prove two important theorems: every \cp process is an \hcp process; and \hcp supports the same protocols as \cp.
-To facilitate this, we define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp.
+We define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp.
 \begin{definition}\label{def:cp2hcp-terms}
@@
 \begin{theorem}\label{thm:cp2hcp-reduction}
-  If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
+  If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
 \end{theorem}\vspace*{-0.75\baselineskip}%
@@
 \begin{theorem}\label{hcp2cp-reduction}
-  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^\star\tm{\mtf{Q}}$ in \hcp.
+  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
 \end{theorem}\vspace*{-0.75\baselineskip}%
@@
 For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
-\[
-  \seq[\cpCase{x}{(\piPar{P}{Q})}{(\piPar{P'}{Q'})}]{
-    \Gamma, \Delta, \tmty{x}{A \with B}}
-\]
+\begin{prooftree}
+  \AXC{}\noLine\UIC{$\seq[P]{ \Gamma }$}
+  \AXC{}\noLine\UIC{$\seq[Q]{ \Delta, \tmty{x}{A} }$}
+  \NOM{H-Mix}
+  \BIC{$\seq[\piPar{P}{Q}]{ \Gamma \hsep \Delta, \tmty{x}{A} }$}
+  \AXC{}\noLine\UIC{$\seq[P']{ \Gamma }$}
+  \AXC{}\noLine\UIC{$\seq[Q']{ \Delta, \tmty{x}{B} }$}
+  \NOM{H-Mix}
+  \BIC{$\seq[\piPar{P'}{Q'}]{ \Gamma \hsep \Delta, \tmty{x}{B} }$}
+  \SYM{\with}
+  \BIC{$\seq[\cpCase{x}{\piPar{P}{Q}}{\piPar{P'}{Q'}}]{ \Gamma \hsep \Delta, \tmty{x}{A \with B}}$}
+\end{prooftree}
 Instead, we will prove that \hcp supports the same communication protocols as \cp.
@@
 We can use this relation to rewrite any derivation to a form in which all mixes are either attached to their respective cuts or tensors, or at the top-level.
-\begin{definition}\label{def:hcp-gk}
-  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules in \cref{fig:disentangle}, plus the associativity and commutativity of mixes.
+\begin{definition}\label{def:hcp-disentangle}
+  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules in \cref{fig:hcp-disentangle}, plus the associativity and commutativity of mixes.
 The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
@@
 In this case, when disentangling, we are forced to forget some of the proof structure.
-This can be seen in the last rule in \cref{fig:disentangle}.
+This can be seen in the last rule in \cref{fig:hcp-disentangle}.
 Nonetheless, the relation is type preserving, and so it suffices for showing that \hcp supports the same communication protocols as \cp.
@@
   \caption{The disentanglement relation for \hcp.}
-  \label{fig:disentangle}
+  \label{fig:hcp-disentangle}
 \end{sidewaysfigure}
@@
 
-%\clearpage
+\clearpage
 \bibliographystyle{apalike}

### 2018-05-23 doc/abstract/main.tex
Minor changes

@@
 \end{definition}\noindent
-Environments associate channels with types.
-Names in environments must be unique, and environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma, \Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
+An environments associates channels with types.
+Names in environments must be unique, and two environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma, \Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
 \begin{definition}[Environments]\label{def:cp-environments}
@@
 \end{figure}\noindent
-Typing judgements associate processes with collections of typed channels.
+A typing judgement associates a process with collections of typed channels.
 \begin{definition}[Typing judgements]\label{def:cp}
@@
 However, we will still refer to our system as a hypersequent system.
-Hyper-environments are either empty, or consist of a series of typing environments, separated by vertical bars.
+A hyper-environment is either empty, or consist of a series of typing environments, separated by vertical bars.
 A hyper-environment $\ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ types a series of $n$ entangled, but independent processes.
@@
 \end{definition}\noindent
-Hyper-environments are multisets of environments.
+A hyper-environment is a multiset of environments.
 While names within environments must be unique, names may be shared between multiple environments in a hyper-environment.
@@
 Nonetheless, the relation is type preserving, and so it suffices for showing that \hcp supports the same communication protocols as \cp.
+
+Disentanglement is terminating, and confluent up to the associativity and commutativity of mixes.
 \begin{lemma}[Disentangle]\label{lem:hcp-disentangle}

### 2018-05-24 doc/abstract/main.tex
One more interpreted -> internalised

@@
 This is the same as saying that it inhabits the same session types, or that the associated logical systems derive the same theorems.
-We show this by proving that we can interpret the hyper-environments as formulas in the logic.
+We show this by proving that we can internalise the hyper-environments as formulas in the logic.
 This is a standard method for proving the soundness of a hypersequent calculus.
@@
 \end{proof}\noindent
-Environments can be interpreted as types by collapsing them as series of pars.
+An environment can be internalised as a type by collapsing it as a series of pars.
+We give the case for the empty environment $\ty{\emptycontext}$ for completeness' sake, though there are no proofs of $\seq{\emptycontext}$ in \hcp.
 \begin{definition}\label{def:bigparr}
@@
 \end{proof}\noindent
-Furthermore, hyper-environments can be interpreted as types by collapsing them as series of tensors where environments are handled using \cref{lem:hcp-disentangle}.
-The empty hyper-environment $\ty{\emptyhypercontext}$ is interpreted as the unit of tensor.
+Furthermore, a hyper-environment can be internalised as a type by collapsing it as series a of tensors, where each constituent environment is internalised using $\ty{\bigparr}$.
+The empty hyper-environment $\ty{\emptyhypercontext}$ is internalised as the unit of tensor.
 \begin{definition}\label{def:bigtens}

### 2018-05-24 doc/abstract/main.tex

--- 2018-05-23 doc/abstract/main.tex
@@
 \usepackage[all]{foreign}
-\usepackage[fleqn]{amsmath}
+\usepackage[]{amsmath}
+\allowdisplaybreaks
 \usepackage{amsthm}
-\allowdisplaybreaks
+\usepackage{amssymb}
+\usepackage{mathtools}
+\def\defeq{\coloneqq} %\triangleq
 \usepackage[inline]{enumitem}
@@
 Worse, if we naively add an independent parallel composition as well as a name restriction, using the rules shown below, we lose cut elimination, and therefore deadlock-freedom!
-\begin{center}
+\[
   \begin{prooftree*}
@@
   \end{prooftree*}
+  \qquad
   \begin{prooftree*}
@@
   \end{prooftree*}
-\end{center}
+\]
 
@@
       \tm{P}, \tm{Q}, \tm{R}
-           :=& \tm{\cpLink{x}{y}}       &\text{link}
+           \Coloneqq& \tm{\cpLink{x}{y}}       &\text{link}
       &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
@@
 \end{definition}\noindent
-\begin{figure}[htb]
- \[
+%\begin{figure}[htb]
+% 
+%  \caption{Classical Processes, reduction relation.}
+%  \label{fig:cp-reduction}
+%\end{figure}
+Reductions relate processes with their reduced forms \eg a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
+\begin{definition}[Reduction]\label{def:cp-reduction}
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules below.%in \cref{fig:cp-reduction}. 
+  \begin{gather*}
       \begin{array}{llcll}
@@
       \end{array}
-  \]
-  \begin{center}
+    \\
       \begin{prooftree*}
@@
       \end{prooftree*}
+      \qquad
       \begin{prooftree*}
@@
       \end{prooftree*}
-  \end{center}
-  \caption{Classical Processes, reduction relation.}
-  \label{fig:cp-reduction}
-\end{figure}
-Reductions relate processes with their reduced forms \eg a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
-\begin{definition}[Reduction]\label{def:cp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:cp-reduction}.
-The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of $\Longrightarrow$.
-The relation $\Longrightarrow^{+}$ is the transitive closure of $\Longrightarrow$.
+    \end{gather*}
+  Relations $\Longrightarrow^{+}$ and $\Longrightarrow^\star$ are the transitive, and the reflexive, transitive closures of $\Longrightarrow$, respectively.
 \end{definition}
@@
       \ty{A}, \ty{B}, \ty{C}
-           :=& \ty{A \tens B} &\text{pair of independent processes}
+           \Coloneqq & \ty{A \tens B} &\text{pair of independent processes}
       &  \mid& \ty{\one}      &\text{unit for} \; {\tens}
@@
   \(
-    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} := \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
+    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} \coloneqq \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
   \)
 \end{definition}\noindent
-\begin{figure}[htb]
-  \paragraph*{Structural rules}
-  \begin{center}\cpInfAx    \cpInfCut   \end{center}
-  \paragraph*{Logical rules}
-  \begin{center}\cpInfTens  \cpInfParr  \end{center}
-  \begin{center}\cpInfBot   \cpInfOne   \end{center}
-  \begin{center}\cpInfPlus1 \cpInfPlus2 \end{center}
-  \begin{center}\cpInfWith              \end{center}
-  \begin{center}\cpInfNil   \cpInfTop   \end{center}
-  \caption{Classical Processes, typing.}
-  \label{fig:cp}
-\end{figure}\noindent
+%\begin{figure}[htb]
+%  \paragraph*{Structural rules}
+%  \begin{center}\cpInfAx    \cpInfCut   \end{center}
+%  \paragraph*{Logical rules}
+%  \begin{center}\cpInfTens  \cpInfParr  \end{center}
+%  \begin{center}\cpInfBot   \cpInfOne   \end{center}
+%  \begin{center}\cpInfPlus1 \cpInfPlus2 \end{center}
+%  \begin{center}\cpInfWith              \end{center}
+%  \begin{center}\cpInfNil   \cpInfTop   \end{center}
+%  \caption{Classical Processes, typing.}
+%  \label{fig:cp}
+%\end{figure}\noindent
 A typing judgement associates a process with collections of typed channels.
@@
   A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n}}$ denotes that the process \tm{P} communicates along channels $\tm{x_1}$, \dots, $\tm{x_n}$ following protocols $\ty{A_1}$, \dots, $\ty{A_n}$.
-Typing judgements are derived using rules in \cref{fig:cp}.
-\end{definition}\noindent
+Typing judgements are derived using rules below.
+%in \cref{fig:cp}.
+  \begin{description}
+	  \item[Structural rules]
+  		\begin{gather*}\cpInfAx  \qquad  \cpInfCut   \end{gather*}
+	  \item[Logical rules]
+		  \begin{gather*}
+				\cpInfTens \qquad 
+				\cpInfParr \\
+				\cpInfBot \qquad 
+				\cpInfOne \\
+				\cpInfPlus1 \qquad 
+				\cpInfPlus2 \\
+				\cpInfWith \qquad
+				\cpInfNil \qquad 
+				\cpInfTop   
+			\end{gather*}
+	\end{description}
+\end{definition}
 
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
-\end{lemma}\vspace*{-0.75\baselineskip}%
+\end{lemma} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
       \tm{P}, \tm{Q}, \tm{R}
-           :=& \tm{\cpLink{x}{y}}         &\text{link}
+           \Coloneqq & \tm{\cpLink{x}{y}}         &\text{link}
       &  \mid& \tm{\piHalt}               &\text{terminated process}
@@
       &  \mid& \tm{( \piPar{P}{Q} )}      &\text{parallel composition, ``mix''}
-      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{``output''}
-      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{``input''}
-      \\ \mid& \tm{\piBoundSend{x}{}{P}}  &\text{``halt''}
+      \\ \mid& \tm{\piBoundSend{x}{y}{P}} &\text{output}
+      &  \mid& \tm{\piRecv{x}{y}{P}}      &\text{input}
+      \\ \mid& \tm{\piBoundSend{x}{}{P}}  &\text{halt}
       &  \mid& \tm{\cpWait{x}{}{P}}       &\text{wait}
@@
   Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under the rules in \cref{fig:hcp-reduction}. 
-The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of $\Longrightarrow$.
-The relation $\Longrightarrow^{+}$ is the transitive closure of $\Longrightarrow$.
+  Relations $\Longrightarrow^{+}$ and $\Longrightarrow^\star$ are the transitive, and the reflexive, transitive closures of $\Longrightarrow$, respectively.
 \end{definition}
 \begin{figure}[htb]
-  \[
+  \begin{gather*}
     \begin{array}{llcll}
@@
     \end{array}
-  \]
-  \begin{center}
+    \\
       \begin{prooftree*}
@@
       \end{prooftree*}
-  \end{center}
+  \end{gather*}  
   \caption{Hypersequent Classical Processes, reduction relation.}
@@
 \begin{definition}[Hyper-environments]\label{def:hcp-hyper-environment}
-  $\ty{\mathcal{G}}, \ty{\mathcal{H}} := \ty{\emptyhypercontext} \, \mid \, \ty{\mathcal{G} \hsep \Gamma}$
+  $\ty{\mathcal{G}}, \ty{\mathcal{H}} \Coloneqq \ty{\emptyhypercontext} \, \mid \, \ty{\mathcal{G} \hsep \Gamma}$
 \end{definition}\noindent
@@
   A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
-  Typing judgements can be constructed using the inference rules in
-  \cref{fig:hcp}.
+  Typing judgements can be constructed using the inference rules below. %in  \cref{fig:hcp}.
+  \begin{description}
+    \item[Structural rules]
+    \begin{gather*}
+			\hccpInfAx \qquad
+			\hccpInfCycle \\
+	    \hccpInfMix  \qquad
+	    \hccpInfHalt
+    \end{gather*}
+    \item[Logical rules]
+    \begin{gather*}
+    	\hccpInfBoundTens \qquad \hccpInfParr \\
+			\hccpInfOne  \qquad    \hccpInfBot \\  
+			\hccpInfPlus1 \qquad    \hccpInfPlus2 \\
+			\hccpInfWith \\    
+			\hccpInfNil   \qquad    \hccpInfTop
+    \end{gather*}
+  \end{description}
   Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
 \end{definition}\noindent
-\begin{figure}[htb]
-  \paragraph*{Structural rules}
-  \begin{center}\hccpInfAx        \hccpInfCycle \end{center}
-  \begin{center}\hccpInfMix       \hccpInfHalt  \end{center}
-  \paragraph*{Logical rules}
-  \begin{center}\hccpInfBoundTens \hccpInfParr  \end{center}
-  \begin{center}\hccpInfOne       \hccpInfBot   \end{center}
-  \begin{center}\hccpInfPlus1     \hccpInfPlus2 \end{center}
-  \begin{center}\hccpInfWith                    \end{center}
-  \begin{center}\hccpInfNil       \hccpInfTop   \end{center}
-  \centering
-  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-  \caption{Hypersequent Classical Processes, typing.}
-  \label{fig:hcp}
-\end{figure}
+%\begin{figure}[htb]
+%  \centering  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
+%  \caption{Hypersequent Classical Processes, typing.}
+%  \label{fig:hcp}
+%\end{figure}
 
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal{G}}$.
-\end{lemma}\vspace*{-0.75\baselineskip}%
+\end{lemma} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal{G}}$.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq[P]{\mathcal{G}}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut or a mix.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
          \tm{\mtf{\cpLink{x}{y}}}
-      &  := & \tm{\cpLink{x}{y}}
+      &  \defeq & \tm{\cpLink{x}{y}}
       &  \tm{\mtf{\cpCut{x}{P}{Q}}}
-      &  := & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  \defeq & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
       \\ \tm{\mtf{\cpSend{x}{y}{P}{Q}}}
-      &  := & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  \defeq & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
       &  \tm{\mtf{\cpRecv{x}{y}{P}}}
-      &  := & \tm{\piRecv{x}{y}{\mtf{P}}}
+      &  \defeq & \tm{\piRecv{x}{y}{\mtf{P}}}
       \\ \tm{\mtf{\cpHalt{x}}}
-      &  := & \tm{\piBoundSend{x}{}{\piHalt}}
+      &  \defeq & \tm{\piBoundSend{x}{}{\piHalt}}
       &  \tm{\mtf{\cpWait{x}{P}}}
-      &  := & \tm{\piRecv{x}{}{\mtf{P}}}
+      &  \defeq & \tm{\piRecv{x}{}{\mtf{P}}}
       \\ \tm{\mtf{\cpInl{x}{P}}}
-      &  := & \tm{\cpInl{x}{\mtf{P}}}
+      &  \defeq & \tm{\cpInl{x}{\mtf{P}}}
       &  \tm{\mtf{\cpInr{x}{P}}}
-      &  := & \tm{\cpInr{x}{\mtf{P}}}
+      &  \defeq & \tm{\cpInr{x}{\mtf{P}}}
       \\ \tm{\mtf{\cpCase{x}{P}{Q}}}
-      &  := & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
+      &  \defeq & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
       &  \tm{\mtf{\cpAbsurd{x}}}
-      &  := & \tm{\cpAbsurd{x}}
+      &  \defeq & \tm{\cpAbsurd{x}}
     \end{array}
@@
   If $\seq[P]{\Gamma}$ in \cp, then $\seq[\mtf{P}]{\Gamma}$ in \hcp.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   $\tm{P}\equiv\tm{Q}$ in \cp iff $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
 For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
-\begin{prooftree}
+%
+\[
+\begin{prooftree*}%
   \AXC{}\noLine\UIC{$\seq[P]{ \Gamma }$}
@@
   \BIC{$\seq[\cpCase{x}{\piPar{P}{Q}}{\piPar{P'}{Q'}}]{ \Gamma \hsep \Delta, \tmty{x}{A \with B}}$}
-\end{prooftree}
+\end{prooftree*}
+\]
 Instead, we will prove that \hcp supports the same communication protocols as \cp.
@@
 \end{definition}\noindent
+\begin{sidewaysfigure} %[htb]
+  \(
+  \begin{array}{lcr}
+    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
+    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
+    \NOM{H-Cut}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+    \DisplayProof
+    & \moveMixDown
+    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
+      \NOM{H-Cut}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+      \DisplayProof
+    \\\\
+    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
+    \SYM{\tens}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
+    \hsep {A \tens B}, \Gamma, \Delta}$}
+    \DisplayProof
+    & \moveMixDown
+    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
+      \SYM{\tens}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \tens B},
+      \Gamma, \Delta}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
+      \hsep {A \tens B}, \Gamma, \Delta}$}
+      \DisplayProof
+    \\\\
+    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
+    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
+    \SYM{\parr}
+    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
+    \DisplayProof
+    & \moveMixDown
+    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
+      \SYM{\parr}
+      \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
+      \DisplayProof
+    \\\\
+    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
+    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
+    \SYM{\bot}
+    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {\bot}, \Gamma}$}
+    \DisplayProof
+    & \moveMixDown
+    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
+      \SYM{\bot}
+      \UIC{$\seq{\mathcal{G}_1 \hsep {\bot}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
+      \DisplayProof
+    \\\\
+    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+    \SYM{\plus_1}
+    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
+    \DisplayProof
+    & \moveMixDown
+    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \SYM{\plus_1}
+      \UIC{$\seq{\mathcal{G}_1 \hsep {A \plus B}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
+      \DisplayProof
+    \\\\
+    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
+    \pvar{$\rho_4$}\UIC{$\seq{\mathcal{G}_2}$}
+    \NOM{H-Mix}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {B}, \Gamma}$}
+    \SYM{\with}
+    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
+    \DisplayProof
+    & \moveMixDown
+    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
+      \SYM{\with}
+      \BIC{$\seq{\mathcal{G}_1 \hsep {A \with B}, \Gamma}$}
+      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \NOM{H-Mix}
+      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
+      \DisplayProof
+  \end{array}
+  \)
+  \caption{The disentanglement relation for \hcp.}
+  \label{fig:hcp-disentangle}
+\end{sidewaysfigure}
+\noindent
 We named this relation ``disentanglement'' to reflect the intuition that proof in \hcp represent multiple entangled \cp proofs, which we can disentangle.
@@
   \]
-\end{lemma}\vspace*{-0.75\baselineskip}%
+\end{lemma} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   All applications of $(\one)$ are followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
-\end{proof}\noindent
+\end{proof}
+
 Environments can be interpreted as types by collapsing them as series of pars.
@@
   If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
-\end{lemma}\vspace*{-0.75\baselineskip}%
+\end{lemma} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
   If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
-\end{theorem}\vspace*{-0.75\baselineskip}%
+\end{theorem} %\vspace*{-0.75\baselineskip}%
 \begin{proof}
@@
 \end{proof}\noindent
-
-\begin{sidewaysfigure}[htb]
-  \(
-  \begin{array}{lcr}
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
-    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
-    \NOM{H-Cut}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
-      \NOM{H-Cut}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
-      \DisplayProof
-    \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
-    \SYM{\tens}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
-    \hsep {A \tens B}, \Gamma, \Delta}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
-      \SYM{\tens}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \tens B},
-      \Gamma, \Delta}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
-      \hsep {A \tens B}, \Gamma, \Delta}$}
-      \DisplayProof
-    \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
-    \SYM{\parr}
-    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
-      \SYM{\parr}
-      \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
-      \DisplayProof
-    \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
-    \SYM{\bot}
-    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {\bot}, \Gamma}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
-      \SYM{\bot}
-      \UIC{$\seq{\mathcal{G}_1 \hsep {\bot}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
-      \DisplayProof
-    \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
-    \SYM{\plus_1}
-    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \SYM{\plus_1}
-      \UIC{$\seq{\mathcal{G}_1 \hsep {A \plus B}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
-      \DisplayProof
-    \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
-    \pvar{$\rho_4$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {B}, \Gamma}$}
-    \SYM{\with}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
-      \SYM{\with}
-      \BIC{$\seq{\mathcal{G}_1 \hsep {A \with B}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
-      \DisplayProof
-  \end{array}
-  \)
-  \caption{The disentanglement relation for \hcp.}
-  \label{fig:hcp-disentangle}
-\end{sidewaysfigure}
 

### 2018-05-24 doc/abstract/main.tex
Reapplied changes

@@
 \usepackage[all]{foreign}
-\usepackage[]{amsmath}
+\usepackage{amsmath}
 \allowdisplaybreaks
@@
 \usepackage{mathtools}
-\def\defeq{\coloneqq} %\triangleq
 \usepackage[inline]{enumitem}
-%\usepackage{breakurl} % Not needed if you use pdflatex only.
-%\usepackage{underscore} % Only needed if you use pdflatex.
-%\usepackage{parskip}
+\usepackage{breakurl} % Not needed if you use pdflatex only.
+\usepackage{underscore} % Only needed if you use pdflatex.
 \usepackage{textcomp,textgreek,upgreek}
@@
 \end{definition}\noindent
-%\begin{figure}[htb]
-% 
-%  \caption{Classical Processes, reduction relation.}
-%  \label{fig:cp-reduction}
-%\end{figure}
 Reductions relate processes with their reduced forms \eg a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
 \begin{definition}[Reduction]\label{def:cp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules below.%in \cref{fig:cp-reduction}. 
+  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules below.
   \begin{gather*}
@@
 \end{definition}\noindent
-An environments associates channels with types.
+An environment associates channels with types.
 Names in environments must be unique, and two environments $\ty{\Gamma}$ and $\ty{\Delta}$ can only be combined as $\ty{\Gamma, \Delta}$ if $\ty{\fv{\Gamma}} \cap \ty{\fv{\Delta}} = \varnothing$.
@@
 \end{definition}\noindent
-%\begin{figure}[htb]
-%  \paragraph*{Structural rules}
-%  \begin{center}\cpInfAx    \cpInfCut   \end{center}
-%  \paragraph*{Logical rules}
-%  \begin{center}\cpInfTens  \cpInfParr  \end{center}
-%  \begin{center}\cpInfBot   \cpInfOne   \end{center}
-%  \begin{center}\cpInfPlus1 \cpInfPlus2 \end{center}
-%  \begin{center}\cpInfWith              \end{center}
-%  \begin{center}\cpInfNil   \cpInfTop   \end{center}
-%  \caption{Classical Processes, typing.}
-%  \label{fig:cp}
-%\end{figure}\noindent
 A typing judgement associates a process with collections of typed channels.
@@
 Typing judgements are derived using rules below.
-%in \cref{fig:cp}.
   \begin{description}
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
-\end{lemma} %\vspace*{-0.75\baselineskip}%
+\end{lemma} 
 \begin{proof}
@@
   If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}%
+\end{proof}
 \begin{theorem}[Termination]\label{thm:cp-termination}
   If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   \end{enumerate*}
-\end{proof}%
+\end{proof}
 
@@
   A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
-  Typing judgements can be constructed using the inference rules below. %in  \cref{fig:hcp}.
+  Typing judgements can be constructed using the inference rules below. 
   \begin{description}
@@
 \end{definition}\noindent
-%\begin{figure}[htb]
-%  \centering  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
-%  \caption{Hypersequent Classical Processes, typing.}
-%  \label{fig:hcp}
-%\end{figure}
 
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal{G}}$.
-\end{lemma} %\vspace*{-0.75\baselineskip}%
+\end{lemma} 
 \begin{proof}
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}%
+\end{proof}
 \begin{theorem}[Preservation]\label{thm:hcp-preservation}
   If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal{G}}$.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
   By induction on the derivation of $\reducesto{P}{Q}$.
-\end{proof}%
+\end{proof}
 \begin{theorem}[Termination]\label{thm:hcp-termination}
   If $\seq[P]{\mathcal{G}}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut or a mix.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
          \tm{\mtf{\cpLink{x}{y}}}
-      &  \defeq & \tm{\cpLink{x}{y}}
+      &  \coloneqq & \tm{\cpLink{x}{y}}
       &  \tm{\mtf{\cpCut{x}{P}{Q}}}
-      &  \defeq & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  \coloneqq & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
       \\ \tm{\mtf{\cpSend{x}{y}{P}{Q}}}
-      &  \defeq & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  \coloneqq & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
       &  \tm{\mtf{\cpRecv{x}{y}{P}}}
-      &  \defeq & \tm{\piRecv{x}{y}{\mtf{P}}}
+      &  \coloneqq & \tm{\piRecv{x}{y}{\mtf{P}}}
       \\ \tm{\mtf{\cpHalt{x}}}
-      &  \defeq & \tm{\piBoundSend{x}{}{\piHalt}}
+      &  \coloneqq & \tm{\piBoundSend{x}{}{\piHalt}}
       &  \tm{\mtf{\cpWait{x}{P}}}
-      &  \defeq & \tm{\piRecv{x}{}{\mtf{P}}}
+      &  \coloneqq & \tm{\piRecv{x}{}{\mtf{P}}}
       \\ \tm{\mtf{\cpInl{x}{P}}}
-      &  \defeq & \tm{\cpInl{x}{\mtf{P}}}
+      &  \coloneqq & \tm{\cpInl{x}{\mtf{P}}}
       &  \tm{\mtf{\cpInr{x}{P}}}
-      &  \defeq & \tm{\cpInr{x}{\mtf{P}}}
+      &  \coloneqq & \tm{\cpInr{x}{\mtf{P}}}
       \\ \tm{\mtf{\cpCase{x}{P}{Q}}}
-      &  \defeq & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
+      &  \coloneqq & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
       &  \tm{\mtf{\cpAbsurd{x}}}
-      &  \defeq & \tm{\cpAbsurd{x}}
+      &  \coloneqq & \tm{\cpAbsurd{x}}
     \end{array}
@@
   If $\seq[P]{\Gamma}$ in \cp, then $\seq[\mtf{P}]{\Gamma}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   \end{itemize}
-  \vspace*{-\baselineskip}%
-\end{proof}%
+  \vspace*{-\baselineskip}
+\end{proof}
 \begin{theorem}\label{thm:cp2hcp-equiv}
   $\tm{P}\equiv\tm{Q}$ in \cp iff $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
   By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
-\end{proof}%
+\end{proof}
 \begin{theorem}\label{thm:cp2hcp-reduction}
   If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
   By induction on the the derivation of $\reducesto{P}{Q}$.
-\end{proof}%
+\end{proof}
 \begin{theorem}\label{hcp2cp-reduction}
   If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
 For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
-%
-\[
-\begin{prooftree*}%
+\[
+\begin{prooftree*}
   \AXC{}\noLine\UIC{$\seq[P]{ \Gamma }$}
@@
 \end{definition}\noindent
-\begin{sidewaysfigure} %[htb]
+\begin{sidewaysfigure} 
   \(
@@
   \]
-\end{lemma} %\vspace*{-0.75\baselineskip}%
+\end{lemma} 
 \begin{proof}
@@
 \end{proof}
-
-Environments can be interpreted as types by collapsing them as series of pars.
+An environment can be internalised as a type by collapsing it as a series of pars.
 \begin{definition}\label{def:bigparr}
@@
   If $\seq{\Gamma}$ in \cp, then $\seq{\bigparr\Gamma}$ in \cp.
-\end{lemma} %\vspace*{-0.75\baselineskip}%
+\end{lemma} 
 \begin{proof}
@@
 \end{proof}\noindent
-Furthermore, hyper-environments can be interpreted as types by collapsing them as series of tensors where environments are handled using \cref{lem:hcp-disentangle}.
-The empty hyper-environment $\ty{\emptyhypercontext}$ is interpreted as the unit of tensor.
+Furthermore, a hyper-environment can be internalised as a type by collapsing it as a series of tensors, where each constituent environment is internalised using $\ty{\bigparr}$.
+The empty hyper-environment $\ty{\emptyhypercontext}$ is internalised as the unit of tensor.
 \begin{definition}\label{def:bigtens}
@@
   If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}

### 2018-05-24 doc/abstract/main.tex
dropped mathtools

--- 2018-05-24 doc/abstract/main.tex
@@
 \usepackage{mathtools}
-\def\defeq{\coloneqq} %\triangleq
 \usepackage[inline]{enumitem}
@@
       \tm{P}, \tm{Q}, \tm{R}
-           \Coloneqq& \tm{\cpLink{x}{y}}       &\text{link}
+           ::= & \tm{\cpLink{x}{y}}       &\text{link}
       &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
@@
       \ty{A}, \ty{B}, \ty{C}
-           \Coloneqq & \ty{A \tens B} &\text{pair of independent processes}
+           ::= & \ty{A \tens B} &\text{pair of independent processes}
       &  \mid& \ty{\one}      &\text{unit for} \; {\tens}
@@
   \(
-    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} \coloneqq \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
+    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} ::= \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
   \)
 \end{definition}\noindent
-%\begin{figure}[htb]
-%  \paragraph*{Structural rules}
-%  \begin{center}\cpInfAx    \cpInfCut   \end{center}
-%  \paragraph*{Logical rules}
-%  \begin{center}\cpInfTens  \cpInfParr  \end{center}
-%  \begin{center}\cpInfBot   \cpInfOne   \end{center}
-%  \begin{center}\cpInfPlus1 \cpInfPlus2 \end{center}
-%  \begin{center}\cpInfWith              \end{center}
-%  \begin{center}\cpInfNil   \cpInfTop   \end{center}
-%  \caption{Classical Processes, typing.}
-%  \label{fig:cp}
-%\end{figure}\noindent
 A typing judgement associates a process with collections of typed channels.
@@
   If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   If $\seq[P]{\Gamma}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
       \tm{P}, \tm{Q}, \tm{R}
-           \Coloneqq & \tm{\cpLink{x}{y}}         &\text{link}
+           ::= & \tm{\cpLink{x}{y}}         &\text{link}
       &  \mid& \tm{\piHalt}               &\text{terminated process}
@@
 \begin{definition}[Hyper-environments]\label{def:hcp-hyper-environment}
-  $\ty{\mathcal{G}}, \ty{\mathcal{H}} \Coloneqq \ty{\emptyhypercontext} \, \mid \, \ty{\mathcal{G} \hsep \Gamma}$
+  $\ty{\mathcal{G}}, \ty{\mathcal{H}} ::= \ty{\emptyhypercontext} \, \mid \, \ty{\mathcal{G} \hsep \Gamma}$
 \end{definition}\noindent
@@
   A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
-  Typing judgements can be constructed using the inference rules below. %in  \cref{fig:hcp}.
+  Typing judgements can be constructed using the inference rules below.
   \begin{description}
@@
   If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal{G}}$.
-\end{lemma} %\vspace*{-0.75\baselineskip}%
+\end{lemma} 
 \begin{proof}
@@
   If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal{G}}$.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   If $\seq[P]{\mathcal{G}}$, then there are no infinite $\Longrightarrow$-reduction sequences.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
          \tm{\mtf{\cpLink{x}{y}}}
-      &  \defeq & \tm{\cpLink{x}{y}}
+      &  := & \tm{\cpLink{x}{y}}
       &  \tm{\mtf{\cpCut{x}{P}{Q}}}
-      &  \defeq & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  := & \tm{\piNew{x}{(\piPar{\mtf{P}}{\mtf{Q}})}}
       \\ \tm{\mtf{\cpSend{x}{y}{P}{Q}}}
-      &  \defeq & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
+      &  := & \tm{\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}}
       &  \tm{\mtf{\cpRecv{x}{y}{P}}}
-      &  \defeq & \tm{\piRecv{x}{y}{\mtf{P}}}
+      &  := & \tm{\piRecv{x}{y}{\mtf{P}}}
       \\ \tm{\mtf{\cpHalt{x}}}
-      &  \defeq & \tm{\piBoundSend{x}{}{\piHalt}}
+      &  := & \tm{\piBoundSend{x}{}{\piHalt}}
       &  \tm{\mtf{\cpWait{x}{P}}}
-      &  \defeq & \tm{\piRecv{x}{}{\mtf{P}}}
+      &  := & \tm{\piRecv{x}{}{\mtf{P}}}
       \\ \tm{\mtf{\cpInl{x}{P}}}
-      &  \defeq & \tm{\cpInl{x}{\mtf{P}}}
+      &  := & \tm{\cpInl{x}{\mtf{P}}}
       &  \tm{\mtf{\cpInr{x}{P}}}
-      &  \defeq & \tm{\cpInr{x}{\mtf{P}}}
+      &  := & \tm{\cpInr{x}{\mtf{P}}}
       \\ \tm{\mtf{\cpCase{x}{P}{Q}}}
-      &  \defeq & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
+      &  := & \tm{\cpCase{x}{\mtf{P}}{\mtf{Q}}}
       &  \tm{\mtf{\cpAbsurd{x}}}
-      &  \defeq & \tm{\cpAbsurd{x}}
+      &  := & \tm{\cpAbsurd{x}}
     \end{array}
@@
   $\tm{P}\equiv\tm{Q}$ in \cp iff $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}
@@
   If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
-\end{theorem} %\vspace*{-0.75\baselineskip}%
+\end{theorem} 
 \begin{proof}

### 2018-10-04 doc/notes/def-cp-action.tex
merged notes and old slides

\begin{definition}[Action]\label{def:cp-action}
  A process $\tm{P}$ \emph{acts on} a channel $\tm{x}$ if it is in one of the
  following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\cpLink{x}{y}}$
    \item $\tm{\cpLink{y}{x}}$
    \item $\tm{\cpSend{x}{y}{P'}{Q'}}$
    \item $\tm{\cpRecv{x}{y}{P'}}$
    \item $\tm{\cpHalt{x}}$
    \item $\tm{\cpWait{x}{P'}}$
    \item $\tm{\cpInl{x}{P'}}$
    \item $\tm{\cpInr{x}{P'}}$
    \item $\tm{\cpCase{x}{P'}{Q'}}$
    \item $\tm{\cpAbsurd{x}}$
    \end{itemize}
  \end{multicols}
  We say a process $\tm{P}$ is an \emph{action} if it acts on some channel $\tm{x}$.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-cp-canonical-forms.tex
merged notes and old slides

\begin{definition}[Canonical forms]\label{def:cp-canonical-forms}
  A process $\tm{P}$ is in canonical form if it is an action, or if it is of the
  form
  \[
    \tm{\cpCut{x_1}{P_1}{\dots \cpCut{x_n}{P_n}{P_{n+1}}\dots}},
  \]
  where each $\tm{P_i}$ is an action, no $\tm{P_i}$ is a link acting on a bound
  channel, and no two actions $\tm{P_i}$ and $\tm{P_j}$ act on the same bound
  channel.

  An immediate consequence of this definition is that if a process is in
  canonical form, then at least one of the actions $\tm{P_i}$ is acting on an
  free channel.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-cp-envs.tex
merged notes and old slides

\begin{definition}[Environments]\label{def:cp-envs}
  We define environments as follows:
  \begin{gather*}
    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} ::=
    \tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}
  \end{gather*}
  The empty environment is denoted $\emptycontext$.

  Names in environments must be unique, and environments $\ty{\Gamma}$ and
  $\ty{\Delta}$ can only be combined as $\ty{\Gamma}, \ty{\Delta}$ if
  $\text{fv}(\ty{\Gamma}) \cap \text{fv}(\ty{\Delta}) = \varnothing$.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-cp-equiv.tex
merged notes and old slides

\begin{definition}[Structural congruence]\label{def:cp-equiv}
  We define the structural congruence $\equiv$ as the congruence closure over
  terms which satisfies the following additional axioms:
  \begin{gather*}
    \begin{array}{llcll}
      \cpEquivLinkComm
      & \tm{\cpLink{x}{y}}
      & \equiv
      & \tm{\cpLink{y}{x}}
      \\
      \cpEquivCutComm
      & \tm{\cpCut{x}{P}{Q}}
      & \equiv
      & \tm{\cpCut{x}{Q}{P}}
      \\
      \cpEquivCutAss1
      & \tm{\cpCut{x}{P}{\cpCut{y}{Q}{R}}}
      & \equiv
      & \tm{\cpCut{y}{\cpCut{x}{P}{Q}}{R}}
      & \text{if }\notFreeIn{x}{R}\text{ and }\notFreeIn{y}{P}
    \end{array}
  \end{gather*}
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-cp-evaluation-contexts.tex
merged notes and old slides

\begin{definition}[Evaluation contexts]\label{def:cp-evaluation-contexts}
  We define evaluation contexts as:
  \begin{gather*}
    \tm{E} := \tm{\hole} \mid \tm{\cpCut{x}{E}{P}} \mid \tm{\cpCut{x}{P}{E}}
  \end{gather*}
\end{definition}
\begin{definition}[Plugging]\label{def:cp-evaluation-context-plugging}
  We define plugging for evaluation contexts as:
  \begin{gather*}
    \begin{array}{ll}
      \tm{\cpPlug{\hole}{R}}            
      & := \; \tm{R}
      \\
      \tm{\cpPlug{\cpCut{x}{E}{P}}{R}}
      & := \; \tm{\cpCut{x}{\cpPlug{E}{R}}{P}}
      \\
      \tm{\cpPlug{\cpCut{x}{P}{E}}{R}}
      & := \; \tm{\cpCut{x}{P}{\cpPlug{E}{R}}}
    \end{array}
  \end{gather*}
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-cp-evaluation-prefixes.tex
merged notes and old slides

\begin{definition}[Evaluation prefixes]\label{def:cp-evaluation-prefixes}
  We define evaluation prefixes as:
  \begin{align*}
    \tm{G}, \tm{H} := \tm{\hole} \mid \tm{\cpCut{x}{G}{H}}
  \end{align*}
  The $\tm{\hole}$ construct represents a hole.
\end{definition}
\begin{definition}[Plugging]\label{def:cp-evaluation-prefix-plugging}
  We define plugging for an evaluation prefix with $n$ holes as:
  \begin{gather*}
    \begin{array}{ll}
      \tm{\cpPlug{\hole}{R}} & := \; \tm{R} \\
      \tm{\cpPlug{\cpCut{x}{G}{H}}{R_1 \dots R_m, R_{m+1} \dots R_{n}}}
                            & := \; \tm{\cpCut{x}{\cpPlug{G}{R_1 \dots R_m}}{\cpPlug{H}{R_{m+1} \dots R_n}}}
    \end{array}
  \end{gather*}
  Note that in the second case, $\tm{G}$ is an evaluation prefix with $m$ holes,
  and $\tm{H}$ is an evaluation prefix with $(n-m)$ holes.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hccp-canonical-forms.tex
merged notes and old slides

\begin{definition}[Canonical forms]\label{def:hccp-canonical-forms}
  A process $\tm{P}$ is in canonical form if it is an action, or if it is of the
  form
  \[
    \tm{\piNew{x_1\dots x_n}{(P_1\ppar\dots\ppar P_{m+n+1})}}
  \]
  where each $\tm{P_i}$ is an action, no $\tm{P_i}$ is a link acting on a bound
  channel, and no two actions $\tm{P_i}$ and $\tm{P_j}$ act on the same bound
  channel.

  An immediate consequence of this definition is that if a process is in
  canonical form, then at least $m+1$ of the actions $\tm{P_i}$ are blocked on
  free channels.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hccp-evaluation-prefixes.tex
merged notes and old slides

\begin{definition}[Evaluation prefixes]\label{def:hccp-evaluation-prefixes}
  We define evaluation prefixes as:
  \begin{align*}
    \tm{G}, \tm{H} := \tm{\hole} \mid \tm{\piNew{x}{G}} \mid \tm{(\piPar{G}{H})}
  \end{align*}
  The $\tm{\hole}$ construct represents a hole.
\end{definition}
\begin{definition}[Plugging]\label{def:hccp-evaluation-prefix-plugging}
  We define plugging for an evaluation prefix with $n$ holes as:
  \begin{gather*}
    \begin{array}{ll}
      \tm{\cpPlug{\hole}{R}} & := \; \tm{R} \\
      \tm{\cpPlug{\piNew{x}{G}}{R_1 \dots R_n}}
                            & := \; \tm{\piPar{x}{\cpPlug{G}{R_1 \dots R_m}}} \\
      \tm{\cpPlug{(\piPar{G}{H})}{R_1 \dots R_m, R_{m+1} \dots R_{n}}}
                            & := \; \tm{(\piPar{\cpPlug{G}{R_1 \dots R_m}}{\cpPlug{H}{R_{m+1} \dots R_n}})}
    \end{array}
  \end{gather*}
  Note that in the third case, $\tm{G}$ is an evaluation prefix with $m$ holes,
  and $\tm{H}$ is an evaluation prefix with $(n-m)$ holes. 
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hccp-typing.tex
merged notes and old slides

\begin{definition}[Typing judgements]\label{def:hccp-typing}
  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes
  that the process $\tm{P}$ consists of $n$ independent, but potentially
  interleaved processes, each of which communicates according to its own
  protocol $\Gamma_i$. 
  Typing judgements can be constructed using the inference rules in
  \cref{fig:hccp}.
\end{definition}
\begin{figure*}[!htb]
  Structural Rules.
  \begin{center} \hccpInfAx        \hccpInfCycle \end{center}\vspace*{1\baselineskip}
  \begin{center} \hccpInfMix       \hccpInfHalt  \end{center}\vspace*{1\baselineskip}

  Logical Rules.
  \begin{center} \hccpInfBoundTens \hccpInfParr  \end{center}\vspace*{1\baselineskip}
  \begin{center} \hccpInfOne       \hccpInfBot   \end{center}\vspace*{1\baselineskip}
  \begin{center} \hccpInfPlus1     \hccpInfPlus2 \end{center}\vspace*{1\baselineskip}
  \begin{center} \hccpInfWith                    \end{center}\vspace*{1\baselineskip}
  \begin{center} \hccpInfNil       \hccpInfTop   \end{center}\vspace*{1\baselineskip}

  \centering
  (Where each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.)

  \caption{Hypersequent Cyclic Classical Processes with \textsc{H-Mix}}
  \label{fig:hccp}
\end{figure*}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hcp-canonical-forms.tex
merged notes and old slides

\begin{definition}[Canonical forms]\label{def:hcp-canonical-forms}
  A process $\tm{P}$ is in canonical form if it is an action, or if it is of the
  form
  \[
    \tm{(\piPar{
        \piNew{x_1}{(\piPar{P_1}{\dots \piNew{x_n}{(\piPar{P_n}{P_{n+1}})} \dots})}
      }{
        Q_1 \ppar \dots \ppar Q_m
      })},
  \]
  where each $\tm{P_i}$ and each $\tm{Q_i}$ is an action, no $\tm{P_i}$ is a
  link acting on a bound channel, and no two actions $\tm{P_i}$ and $\tm{P_j}$
  act on the same bound channel.

  An immediate consequence of this definition is that if a process is in
  canonical form, then at least one of the actions $\tm{P_i}$ and all of the
  actions $\tm{Q_i}$ are acting on free channels.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hcp-evaluation-contexts.tex
merged notes and old slides

\begin{definition}[Evaluation contexts]\label{def:hcp-evaluation-contexts}
  We extend \cref{def:cp-evaluation-contexts} with the following constructs:
  \begin{align*}
    \tm{E} := \dots \mid \tm{( \piPar{E}{P} )} \mid \tm{( \piPar{P}{E} )}
  \end{align*}
\end{definition}
\begin{definition}[Plugging]\label{def:hcp-evaluation-context-plugging}
  We extend \cref{def:cp-evaluation-context-plugging} with the following cases:
  \begin{gather*}
    \begin{array}{lcl}
      \tm{\cpPlug{( \piPar{E}{P} )}{R}}
      & := & \tm{\piPar{( \cpPlug{E}{R} )}{P}}
      \\
      \tm{\cpPlug{( \piPar{P}{E} )}{R}}
      & := & \tm{\piPar{P}{( \cpPlug{E}{R} )}}
    \end{array}
  \end{gather*}
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hcp-evaluation-prefixes.tex
merged notes and old slides

\begin{definition}[Evaluation prefixes]\label{def:hcp-evaluation-prefixes}
  We extend \cref{def:cp-evaluation-prefixes} with the following constructs:
  \begin{align*}
    \tm{G}, \tm{H} := \dots \mid \tm{(\piPar{G}{H})}
  \end{align*}
\end{definition}
\begin{definition}[Plugging]\label{def:hcp-evaluation-prefix-plugging}
  We define plugging for an evaluation prefix with $n$ holes as:
  \begin{gather*}
    \begin{array}{l}
      \tm{\cpPlug{(\piPar{G}{H})}{R_1 \dots R_m, R_{m+1} \dots R_{n}}}
      := \; \tm{(\piPar{\cpPlug{G}{R_1 \dots R_m}}{\cpPlug{H}{R_{m+1} \dots R_n}})}
    \end{array}
  \end{gather*}
  Note that in this case, $\tm{G}$ is an evaluation prefix with $m$ holes,
  and $\tm{H}$ is an evaluation prefix with $(n-m)$ holes.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hcp-hyperenvs.tex
merged notes and old slides

\begin{definition}[Hyper-environments]\label{def:hcp-hyperenvs}
  We define hyper-environments as follows:
  \begin{gather*}
    \ty{\mathcal{G}}, \ty{\mathcal{H}}
    ::= \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}
  \end{gather*}
  The empty hyper-environment is denoted $\ty{\emptyhypercontext}$.

  Note that variable names may occur multiple times in a hyper-environment, as
  long as names within each environment are still unique.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-hcp-reduction.tex
merged notes and old slides

\begin{definition}[Reduction]\label{def:hcp-reduction}
  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
  to the process $\tm{Q}$ in a single step. Reductions can only be constructed
  using the rules in \cref{def:cp-reduction} and the following addition
  congruence rule:
  \begin{prooftree}
    \AXC{$\reducesto{P}{P^\prime}$}
    \SYM{\hcpRedGammaMix}
    \UIC{$\reducesto{\piPar{P}{Q}}{\piPar{P^\prime}{Q}}$}
  \end{prooftree}
  The relations $\Longrightarrow^{?}$, $\Longrightarrow^{+}$, and
  $\Longrightarrow^\star$ are the reflexive, transitive and reflexive,
  transitive closures of $\Longrightarrow$.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-safeap-equiv.tex
merged notes and old slides

\begin{definition}[Structural congruence]\label{def:safeap-equiv}
  We define the structural congruence $\equiv$ as the congruence closure over
  terms which satisfies the axioms in \cref{def:ccp-equiv} and the following
  additional axioms:
  \begin{gather*}
    \begin{array}{llcll}
      \apEquivGCNew
      & \tm{\piNew{xy}{P}}
      & \equiv
      & \tm{P}
      & \text{if }\tm{x},\tm{y}\not\in\tm{P}
    \end{array}
  \end{gather*}
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-safeap-reduction.tex
merged notes and old slides

\begin{definition}[Reduction]\label{def:safeap-reduction}
  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
  to the process $\tm{Q}$ in a single step. Reductions can only be constructed
  using the rules in \cref{def:cccp-reduction} and the following addition
  congruence rule:
  \begin{gather*}
    \begin{array}{llcll}
      \apRedSessInit
      & \tm{\piNew{xy}{(\piPar{\piPar{\apSend{x}{z}{P}}{\apRecv{y}{w}{Q}}}{R})}}
      & \Longrightarrow
      & \tm{\piNew{xy}{\piNew{zw}{(\piPar{\piPar{P}{Q}}{R})}}}
      \\
    \end{array}
  \end{gather*}
  The relations $\Longrightarrow^{?}$, $\Longrightarrow^{+}$, and
  $\Longrightarrow^\star$ are the reflexive, the transitive, and the reflexive,
  transitive closures of $\Longrightarrow$.
\end{definition}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/def-safeap-typing.tex
merged notes and old slides

\begin{definition}[Typing judgements]\label{def:ap-typing}
  A typing judgement
  $\cseq[P]{\tmty{x_1}{A_1}\dots\tmty{x_n}{A_n}}{\mathcal{C}}$ denotes that the
  process $\tm{P}$ communicates along channels $\tm{x_1}\dots\tm{x_n}$ following
  protocols $\ty{A_1}\dots\ty{A_n}$, and that $\tm{P}$ is free from deadlocks if
  the constraint set $\cs{\mathcal{C}}$ is satisfiable.
  Typing judgements can be constructed using the inference rules in
  \cref{fig:cccp} and those in \cref{fig:safe-ap}.
\end{definition}
\begin{figure*}[!htb]
  Logical Rules.
  \begin{center} \apInfApBang  \apInfApYnot  \end{center}\vspace*{1\baselineskip}
  \begin{center} \apInfApBangC               \end{center}\vspace*{1\baselineskip}
  \begin{center} \apInfApYnotC               \end{center}\vspace*{1\baselineskip}
  \begin{center} \apInfApBangW \apInfApYnotW \end{center}

  \caption{Safe Access Points}
  \label{fig:safe-ap}
\end{figure*}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/lem-cp-progress-beta.tex
merged notes and old slides

\begin{lemma}\label{lem:cp-progress-beta}
  If $\seq[{ \cpPlug{G}{P_1 \dots P_n} }]{ \Gamma }$, and some $\tm{P_i}$ and
  $\tm{P_j}$, on different sides of at least one cut, act on the same bound
  channel $\tm{x}$, then there exist $\tm{E}$, $\tm{E_i}$ and $\tm{E_j}$ such that 
  \(
  \tm{\cpPlug{G}{P_1 \dots P_n}} =
  \tm{\cpPlug{E}{\cpCut{x}{\cpPlug{E_i}{P_i}}{\cpPlug{E_j}{P_j}}}}
  \).
\end{lemma}
\begin{proof}
  By induction on the structure of $\tm{G}$.
  \begin{itemize}
  \item
    Case $\tm{\cpCut{x}{\cpPlug{G'}{P_1\dots P_i\dots P_m}}{\cpPlug{G''}{P_{m+1}\dots P_j\dots P_n}}}$. 
    \\
    \(
    \arraycolsep=4pt
    \begin{array}[t]{lll}
      \text{Let}& \tm{E}   &:= \tm{\hole}, \\
                & \tm{E_i} &:= \tm{\cpPlug{G'}{P_1\dots P_{i-1},\hole,P_{i+1}\dots P_m}}, \\
                & \tm{E_j} &:= \tm{\cpPlug{G''}{P_{m+1}\dots P_{j-1},\hole,P_{j+1}\dots P_n}}.
    \end{array}
    \)
    \\[1ex]
    By reflexivity.
  \item
    Case $\tm{\cpCut{x}{\cpPlug{G'}{P_1\dots P_j\dots P_m}}{\cpPlug{G''}{P_{m+1}\dots P_i\dots P_n}}}$.
    \\
    As above.
  \item
    Case $\tm{\cpCut{y}{\cpPlug{G'}{P_1\dots P_i\dots P_j\dots P_m}}{\cpPlug{G''}{P_{m+1}\dots P_n}}}$. \\
    Case $\tm{\cpCut{y}{\cpPlug{G'}{P_1\dots P_m}}{\cpPlug{G''}{P_{m+1}\dots P_i\dots P_j\dots P_n}}}$.
    \\
    We obtain $\tm{E}$, $\tm{E_1}$ and $\tm{E_2}$ from the induction hypothesis and
    \cref{thm:cp-preservation-equiv}, and then prepend either
    $\tm{\cpCut{y}{\hole}{\cpPlug{G''}{P_{m+1}\dots P_n}}}$ or
    $\tm{\cpCut{y}{\cpPlug{G'}{P_1\dots P_m}}{\hole}}$ to $\tm{E}$.
    The desired equality follows by congruence.
  \end{itemize}
  The case for $\tm{\hole}$ is excluded because $n > 1$.
  The cases in which $\tm{P_i}$ and $\tm{P_j}$ are on the \emph{same} side of the
  cut, but the cut binds $\tm{x}$, and the cases in which $\tm{P_i}$ and $\tm{P_j}$
  are on different sides of the cut, but the cut binds some other channel
  $\tm{y}$, are excluded by the type system.
\end{proof}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/lem-hcp-progress-beta.tex
merged notes and old slides

\begin{lemma}\label{lem:hcp-progress-beta}
  If $\seq[{ \cpPlug{G}{P_1 \dots P_n} }]{ \Gamma }$, and some $\tm{P_i}$ and
  $\tm{P_j}$, on different sides of at least one cut, act on the same bound
  channel $\tm{x}$, then there exist $\tm{E}$, $\tm{E_i}$ and $\tm{E_j}$ such
  that 
  \begin{gather*}
    \tm{\cpPlug{G}{P_1 \dots P_n}} =
    \tm{\cpPlug{E}{\cpCut{x}{\cpPlug{E_i}{P_i}}{\cpPlug{E_j}{P_j}}}}.
  \end{gather*}
\end{lemma}
\begin{proof}
  As \cref{lem:cp-progress-link}.
  The two cases for
  \begin{gather*}
    \tm{\piPar{\cpPlug{G'}{P_1 \dots P_i \dots P_j \dots P_m}}{\cpPlug{G''}{P_{m+1} \dots P_n}}}\\
    \text{and}\\
    \tm{\piPar{\cpPlug{G'}{P_1 \dots P_m}}{\cpPlug{G''}{P_{m+1} \dots P_i \dots P_j \dots P_n}}}
  \end{gather*}
  are handled exactly as the cases for cuts which do not bind $\tm{x}$.
  The case where $\tm{P_i}$ and $\tm{P_j}$ are on different sides of a mix is
  excluded by the type system.
\end{proof}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/lem-hcp-progress-link.tex
merged notes and old slides

\begin{lemma}\label{lem:hcp-progress-link}
  If $\seq[{ \cpPlug{G}{P_1 \dots P_n} }]{ \Gamma }$, and some $\tm{P_i}$ is a
  link $\tm{\cpLink{x}{y}}$, then either $\tm{x}$ and $\tm{y}$ are not bound by
  $\tm{G}$, or there exist $\tm{E}$, $\tm{E'}$ and $\tm{Q}$ such that
  \begin{gather*}
    \tm{\cpPlug{G}{P_1 \dots P_n}} \equiv
    \tm{\cpPlug{E}{\cpCut{x}{\cpPlug{E'}{\cpLink{x}{y}}}{Q}}}.
  \end{gather*}
\end{lemma}
\begin{proof}
  As \cref{lem:cp-progress-link}. The two cases for
  \begin{gather*}
    \tm{\piPar{\cpPlug{G'}{P_1 \dots P_i \dots P_m}}{\cpPlug{G''}{P_{m+1} \dots P_n}}}\\
    \text{and}\\
    \tm{\piPar{\cpPlug{G'}{P_1 \dots P_m}}{\cpPlug{G''}{P_{m+1} \dots P_i \dots P_n}}}
  \end{gather*}
  are handled exactly as the cases for cuts which do not bind $\tm{x}$ or $\tm{y}$.
\end{proof}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/main.tex
merged notes and old slides

\documentclass{article}
\input{preamble}
\input{preamble-biblatex}
\input{preamble-theorems}
\input{preamble-typing}
\input{preamble-emoji}
\pagenumbering{gobble}
\usepackage[section]{placeins}
\usepackage[parfill]{parskip}
\usepackage{titlesec}
\newcommand{\sectionbreak}{\ifnum\value{section}>1\clearpage\fi}
\addbibresource{main.bib}
\author{Wen Kokke}
\title{Hypersequent Classical Processes}
\begin{document}

\section{Classical Processes}\label{sec:cp}
In this section, we will introduce a variant of \cp which removes the
commutative conversions from the reductions.
\cp was introduced by \textcite{wadler2012}, based on work by \textcite{caires2010}
and \textcite{gay2009}.

\subsection{Terms}\label{sec:cp-terms}
\input{def-cp-terms}
\input{def-cp-equiv}
\input{def-cp-reduction}

\subsection{Types}\label{sec:cp-types}
\input{def-cp-types}
\input{def-cp-negation}
\input{lem-cp-negation-involutive}
\input{def-cp-envs}
\input{def-cp-typing}

\subsection{Properties}\label{sec:cp-properties}

\subsubsection{Preservation}\label{sec:cp-preservation}
\input{lem-cp-preservation-equiv}
\input{lem-cp-preservation-subst}
\input{thm-cp-preservation}

\subsubsection{Canonical Forms and Progress}\label{sec:cp-canonical-forms-and-progress}

\paragraph{Canonical Forms}\label{sec:cp-canonical-forms}
\input{def-cp-action}

\paragraph{Evaluation Contexts}\label{sec:cp-evaluation-contexts}
\input{def-cp-evaluation-contexts}
\input{def-cp-evaluation-prefixes}
\input{def-cp-maximum-evaluation-prefixes}
\input{lem-cp-maximum-evaluation-prefixes}

\paragraph{Progress}\label{sec:cp-progress}
\input{thm-cp-progress}

\section{Hypersequent Classical Processes}\label{sec:hcp}
In this section, we will introduce a variant of \cp based on hypersequent
calculi.
Hypersequent calculi were introduced independently by \textcite{avron1987} and
\textcite{pottinger1983}.

\subsection{Terms}\label{sec:hcp-terms}
\input{def-hcp-terms}
\input{def-hcp-equiv}
\input{def-hcp-reduction}

\subsection{Types}\label{sec:hcp-types}
We keep the types and environments from \cp, see \cref{def:cp-types} and
\cref{def:cp-envs}.
We introduce a new layer on top of sequents: hypersequents.
However, as \cp is a one-sided logic, and it uses the left-hand side of the
turnstile to write the process, the traditional hypersequent notation can look
awkward:
\[
  \seq[P]{\Gamma_1}\hsep\dots\hsep\seq{\Gamma_n}.
\]
The above may be confusing. It seems to claim that $\tm{P}$ acts according to
protocol $\ty{\Gamma_1}$. What are all the other $\Gamma$s doing there?
Are they typing empty processes?
Therefore, we opt to leave out the repeated turnstile, and instead work with the
notion of ``hyper-environments''. However, we will still refer to our system as a
hypersequent system.
\input{def-hcp-hyperenvs}
\input{def-hcp-typing}

\subsection{Properties}\label{sec:hcp-properties}

\subsubsection{Preservation}\label{sec:hcp-preservation}
\input{lem-hcp-preservation-equiv}
\input{lem-hcp-preservation-subst}
\input{thm-hcp-preservation}

\subsubsection{Canonical Forms and Progress}\label{sec:hcp-canonical-forms-and-progress}

\paragraph{Canonical Forms}\label{sec:hcp-canonical-forms}
\input{def-hcp-canonical-forms}

\paragraph{Evaluation contexts}
\input{def-hcp-evaluation-contexts}
\input{def-hcp-evaluation-prefixes}

\paragraph{Progress}
\input{thm-hcp-progress}

\subsection{Relation to \cp}\label{sec:hcp2cp}

\subsubsection{\hcp shares \textsc{Mix}-free processes with \cp}
First off, we have the following theorems, relating terms with a singleton
hypersequent, i.e.\ \textsc{Mix}-free terms, in \hcp to terms in \cp and vice
versa.
\input{thm-cp2hcp-typing}
\input{thm-cp2hcp-equiv}
\input{thm-cp2hcp-reduction}
\input{thm-hcp2cp-typing}
\input{thm-hcp2cp-equiv}
\input{thm-hcp2cp-reduction}

\subsubsection{\hcp supports the same protocols as \cp}
In \hcp, we can use \textsc{H-Mix} to compose two independent processes, but
once composed, we cannot form any direct connections between the two.
Unconnected process can block on each other's communications, and behave
differently due to each other's choices.
Therefore, processes in \hcp are strictly more expressive than processes in \cp
and parallel compositions of processes in \cp.
One example of a process which is expressible in \hcp, but not in \cp, is
$$
\seq[{
  \cpCase{x}{\piPar{P}{Q}}{\piPar{P'}{Q'}}
}]{
  \Gamma \hsep \tmty{x}{A \with B}, \Delta
}
$$
where $\seq[P]{\Gamma}$, $\seq[P']{\Gamma}$, $\seq[Q]{\tmty{x}{A}, \Delta}$ and
$\seq[Q]{\tmty{x}{B}, \Delta}$.

However, we can prove that \hcp inhabits the same types as \cp. This is a
property of the logic, and we will present it as such, omitting the process
terms. We prove this by showing that the hypersequent separator can be
interpreted as a tensor.\footnote{%
  In most hypersequent systems, the hypersequent separator is interpreted as a
  disjunctive connective. However, here we interpret it as a conjunctive
  connective.}
First, however, we prove a lemma showing that we can interpret the structural
comma as a par.
\input{lem-hcp-bigparr}
\input{thm-hcp-bigtens}
As a corollary, we now know that \hcp inhabits the same types as \cp.
\input{fig-hcp-cc-hmix}

\section{Hypersequent Cyclic Classical Processes}\label{sec:hccp}

\subsection{Terms}\label{sec:hccp-term}
\input{def-hccp-terms}
\input{def-hccp-equiv}
\input{def-hccp-reduction}

\subsection{Types}\label{sec:hccp-types}
We keep the types, environments, and hyper-environments from \hcp, see
\cref{def:cp-types,def:cp-envs,def:hcp-hyperenvs}.
\input{def-hccp-typing}

\subsection{Properties}\label{sec:hccp-properties}

\subsubsection{Preservation}\label{sec:hccp-preservation}
\input{lem-hccp-preservation-equiv}
\input{lem-hccp-preservation-subst}
\input{thm-hccp-preservation}

\subsubsection{Canonical Forms and Progress}\label{sec:hccp-canonical-forms-and-progress}

\paragraph{Canonical Forms}\label{sec:hccp-canonical-forms}
\input{def-hccp-canonical-forms}

\paragraph{Evaluation Contexts}\label{sec:hccp-evaluation-contexts}
\input{def-hccp-evaluation-contexts}
\input{def-hccp-evaluation-prefixes}
\input{def-hccp-maximum-evaluation-prefixes}
\input{lem-hccp-maximum-evaluation-prefixes}

\paragraph{Progress}\label{sec:hccp-progress}
\input{thm-hccp-progress}

\subsection{Relation to \hcp}\label{sec:hcp2hccp}
\subsubsection{\hcp processes can be translated to \hccp}
The relation between \hccp and \hcp is slightly more complex than that between
\hcp and \cp.
In \cref{sec:hcp2cp}, we could simply insert terms in \cp into \hcp, as the term
language of \hcp is a simple extension of that of \cp.
In this case, however, we will have to start by defining a translation between
the two term languages.
\input{def-hcp2hccp-terms}
In the cases for $\tm{\cpCut{x}{P}{Q}}$, $\tm{\cpSend{x}{y}{P}{Q}}$ and
$\tm{\cpHalt{x}}$, while it does not look like much is happening, it is
important to realise that the constructs on the left-hand side are atomic,
whereas those on the right-hand side are complex.

We can show that this translation respects typing.
\input{thm-hcp2hccp-typing}

We can show that this translation respects the structural congruence---that is
to say, if two terms are equivalent in \hcp, then their translations are
equivalent in \hccp.
\input{thm-hcp2hccp-equiv}

Furthermore, we can show that this translation respects reductions.
\input{thm-hcp2hccp-reduction}
\input{thm-hcp2hccp-reduction-inv}

\subsubsection{\hccp supports the same protocols as \hcp}\label{sec:hccp2hcp}
There is no neat translation from \hccp to \hcp, as there is no way to translate
processes of the form $\tm{\piSend{x}{}{P}}$ in \hcp---though there is probably
a way to simulate them.
Instead, similarly to \cref{sec:hcp2cp}, we will prove that \hccp inhabits the
same sequents as \hcp.
We prove this by showing that each proof in \hccp can be transformed into a
proof in \hcp.
The reduction behaviour between the two processes associated with these proofs,
however, may differ.
Therefore, we will present this as a property of the logic, and we will present
it as such, omitting the process terms.
\input{thm-hccp2hcp}
As a corollary, we now have that \hccp inhabits the same types as \cp.

\section{Priority-based Classical Processes}\label{sec:ccp}
The type system for \cp with cyclic communication structures (\ccp) is described
by \textcite{dardha2018}.
It is strictly more expressive than \cp and \hccp, as it allows cyclic
communication structures to be formed.
It enforces deadlock freedom by checking that the communication graph is
acyclic.
It uses the same definitions for terms as \hccp, and the following definitions
for structural congruence and term reduction. 
\input{def-ccp-equiv}
\input{def-ccp-reduction}
It uses the same types and environments as \hccp, though it annotates the
connectives of types with \emph{priorities}, e.g.\ as $\ty{A \tens^{\cs{o}} B}$.
A priority can be thought of as a label for an action.
Priorities form a partial order, where $\cs{o}<\cs{o'}$ means that the action
labeled with $\cs{o}$ must happen before the action labeled with $\cs{o'}$.
In \textcite{dardha2018}, priorities are natural numbers.
\input{def-ccp-pr}
\input{def-ccp-typing}

In this section, we will explore a revision of \ccp which has two benefits:
\begin{itemize}
\item
  we allow our priorities to be any partial order, instead of requiring them to
  be natural numbers;
\item
  and we generate a set of priority constraints during type checking, and return 
  this set as a result of type checking, instead of interleaving type and
  priority checking.
\end{itemize}
Why are these benefits?

The priority constraints are an encoding of (a sub-graph\footnote{%
  It is a sub-graph because some of the edges are enforced by the term syntax,
  and as such these are not checked by the priority constraints.
  For instance, in
  $\tm{\piBoundSend{x^{\cs{o}}}{y}{\piRecv{x^{\cs{o'}}}{z}{P}}}$,
  there is no reason to check that $\cs{o < o'}$, as there is no way for the
  receive action to take place before the send action.
} of) the communication graph, where $\cs{o < o'}$ means that the action
associated with $\cs{o}$ must happen before the action associated with
$\cs{o'}$.
In the case of parallel actions, we will have $\cs{o \parallel o'}$---i.e.\ %
there is \emph{no relation} between $\cs{o}$ and $\cs{o'}$. 
Natural numbers, however, are a total order, meaning that we will have to choose
either $\cs{o < o'}$, $\cs{o' < o}$, or $\cs{o = o'}$.
Therefore, by using priorities which have more structure than is required, we
lose some precision.

Gathering all priority constraints, instead of checking them during type
checking, makes it convenient to talk about
\begin{itemize}
\item 
  programs which are well-typed but (potentially) contain deadlocks;
\item
  programs which are deadlock free but also obey additional constraints on the
  ordering of actions, such as those that may arise from global types; 
\item
  translations between \ccp and other systems, such as \cp, because it separates
  the proofs of type preservation and that of constraint satisfaction.
\end{itemize}
We define two functions on priority-annotated types, in addition to the function
$\pr{\ty{A}}$ given in \cref{def:ccp-pr}:
\input{def-cccp-fg}
\input{def-cccp-un}
\input{def-cccp-typing}

\section{Safe Access Points}
\input{def-safeap-terms}
\input{def-safeap-equiv}
\input{def-safeap-reduction}
\input{def-safeap-types}
\input{def-safeap-typing}

\section{Global Types for Binary Sessions}\label{sec:globaltypes}
The work by \textcite{carbone2016} introduced globally-governed \cp (\gcp).
This work introduces a multiparty extension of \cp.
Processes in \gcp are ``typed'' by global types.
This is a bit of a misnomer, as global types are a whole host of things, but
types is not one of them, and it is probably best to see global types as the
arbiter processes to which they are compiled, together with some proof of
coherence.
With the addition of global types, \gcp adds several new---and in my eyes
orthogonal---features to \cp.

\begin{itemize}
\item
  \textbf{Global types stratify the global communication order}\\
  What do we mean by this? If there are two independent communications which can
  happen, say we have
  $\tm{({\piBoundSend{x}{y}{P}}\ppar{\piBoundSend{z}{w}{Q}}\ppar\dots)}$ and
  both $\tm{\piBoundSend{x}{y}{}}$ and $\tm{\piBoundSend{z}{w}{}}$ can happen,
  then we can use global types to stratify these communications. How? The
  potential for stratification in global types arises from the fact that we are
  basically writing an arbiter process. We are writing down who sends what to
  who when. For instance, for the example above, we could imagine some global
  type written as $\tm{{x}\to{\co{x}}.{z}\to{\co{z}}.\dots}$, where
  $\tm{\co{x}}$ and $\tm{\co{z}}$ are the endpoints on the other side of
  $\tm{x}$ and $\tm{z}$. This would require that the communication on $\tm{x}$
  happens before the communication on $\tm{z}$.
\item
  \textbf{Global types allow for broadcasting}\\
  There are two kinds of broadcasting in \gcp. First, the rules for $\tens\parr$
  and $\one\bot$ give the language some sort of ``gather'' operation and a
  wait-for-all operation. However, it is a well-known fact that the the
  constructs associated with the multiplicative connectives only perform
  ``plumbing''. Therefore, the gather construct that is implemented is not
  really gathering any information. Rather, it allows for some measure of
  abstraction in putting together sessions in which one process communicates
  with multiple other processes.

  The \emph{real} broadcasting operation is implemented by the $\plus\with$
  rule, which facilitates a single process sending one bit of information,
  identical in each case, to multiple recipients.

  The coherence rules presented by \textcite{carbone2016} are all asymmetric. In
  each case, \emph{one} process on the one side is communicating with multiple
  processes on the other. In each case, the side with \emph{one} process happens
  to be the ``strong'' side---the side which decides in which order
  communications happen $(\parr)$, and the side which makes the choice
  $(\plus)$. This, of course, is no coincidence. Instead, it has a much deeper
  connection to the logic. In each case, these stronger connectives are
  associated with \emph{unary} instead of binary rules. This makes it easy to
  expand a ``gather'' into a series of receive actions, and a choice into a
  series of choices.\footnote{This means that it should be possible to define a
    globally-governed variant of, say, \hccp or \ccp, in which both the plumbing
    and the choice are taken care of by broadcasting operations.}
\item
  \textbf{Global types allow for \emph{some} measure of non-determinism}\\
  If we see a broadcast operation as a series of binary sending operations, then
  we wouldn't expect those to be ordered among one another. The semantics for
  \gcp treat broadcast and gather as a \emph{single} operation, which only takes
  place when all intended recipients are ready. The semantics for \gcp, when
  compiled to \cp, however, imposes an ordering on the broadcasting (or
  gathering) process, by compiling the single action down to a series of
  actions. This is a bit odd.
\end{itemize}
We can easily model stratification of the global communication order in \cccp,
by simply making more demands of the final constraint set.
For instance, if we have a global type which requires
$\tm{{x}\to{\co{x}}.{z}\to{\co{z}}.\dots}$, i.e. that the first action on
$\tm{x}$ happens before the first action on $\tm{z}$, we can simply grab the
priorities associated with those actions---say $\cs{o}$ and $\cs{o'}$---and
require that the constraint $\cs{o} < \cs{o'}$ is present in the final
constraint set.

The broadcasting behaviours added by \gcp are\dots

\begin{definition}[Global types]\label{def:globaltypes}
  We define global types following \textcite{carbone2016}:
  \begin{gather*}
    \begin{array}{lcll}
      \tm{G}, \tm{H}
      & :=   & \gtyAx{x}{A}{y}                                         & \text{link} \\
      & \mid & \gtyTensParr{x}{y}{G}{H}                                & \text{multiparty gather} \\
      & \mid & \gtyOneBot{x}{y}                                        & \text{multiparty halt} \\
      & \mid & \gtyPlusWith{x}{y}{G}{H}                                & \text{multiparty choice} \\
      & \mid & \gtyNilTop{x}{y}                                        & \text{multiparty absurd}
    \end{array}
  \end{gather*}
\end{definition}

\begin{definition}[Coherence]\label{def:globaltypes-coherence}
  We define coherence following \textcite{carbone2016}:
  \begin{center} \gcpInfAx                     \end{center}\vspace{1\baselineskip}
  \begin{center} \gcpInfTensParr \gcpInfOneBot \end{center}
\end{definition}

\printbibliography

\end{document}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/thm-cp-progress.tex
merged notes and old slides

\begin{theorem}[Progress]\label{thm:cp-progress}
  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that either
  $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form, or $\reducesto{P}{Q}$.
\end{theorem}
\begin{proof}
  By induction on the structure of derivation for $\seq[P]{\Gamma}$.
  The only interesting case is when the last rule of the derivation is
  \textsc{Cut}---in every other case, the typing rule constructs a term which is
  in canonical form.
  \\
  We consider the maximum evaluation prefix $\tm{G}$ of $\tm{P}$, such that $\tm{P}
  = \tm{\cpPlug{G}{P_1 \dots P_{n+1}}}$ and each $\tm{P_i}$ is an action.
  The prefix $\tm{G}$ consists of $n$ cuts, and introduces $n$ channels, but
  composes $n+1$ actions. Therefore, one of the following must be true:
  \begin{itemize}
  \item
    One of the actions composed by $\tm{G}$ is a link $\tm{\cpLink{x}{y}}$
    acting on a bound channel.
    Suppose that $\tm{x}$ is the bound channel.
    There exist evaluation contexts $\tm{E}$ and $\tm{E'}$ such that
    \[
      \tm{P} =
      \tm{\cpPlug{E}{\cpCut{x}{\cpPlug{E'}{\cpLink{x}{y}}}{R}}}.
    \]
    We rewrite by $\equiv$ to obtain
    \[
      \tm{P} =
      \tm{\cpPlug{E}{\cpPlug{E'}{\cpCut{x}{\cpLink{x}{y}}{R}}}}.
    \]
    We then reduce by applying \cpRedAxCut1.
    Similarly if $\tm{y}$ is the bound channel.
  \item
    Two of the actions composed by $\tm{G}$ are acting on the \emph{same} bound
    channel.
    Let the two actions be $\tm{P_i}$ and $\tm{P_j}$, and the bound channel
    $\tm{x}$.
    There exist evaluation contexts $\tm{E}$, $\tm{E_i}$, and $\tm{E_j}$ such
    that
    \[
      \tm{P} =
      \tm{\cpPlug{E}{\cpCut{x}{\cpPlug{E_i}{P_i}}{\cpPlug{E_j}{P_j}}}}
    \]
    We rewrite by $\equiv$ to obtain
    \[
      \tm{P} \equiv
      \tm{\cpPlug{E}{\cpPlug{E_i}{\cpPlug{E_j}{\cpCut{x}{P_i}{P_j}}}}}
    \]
    We then reduce by applying the appropriate \textbeta-reduction.
  \item
    Otherwise (at least) one of the actions composed by $\tm{G}$ must be acting
    on a free channel.
    None of the actions composed by $\tm{G}$ is a link.
    No two actions composed by $\tm{G}$ are acting on the same channel $\tm{x}$.
    Therefore, $\tm{P}$ is equivalent to a process in canonical form.
  \end{itemize}
\end{proof}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/thm-hccp-progress.tex
merged notes and old slides

\begin{theorem}[Progress]\label{thm:hccp-progress}
  If $\seq[P]{\mathcal{G}}$, then there exists a $\tm{Q}$ such that either
  $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form, or $\reducesto{P}{Q}$.
\end{theorem}
\begin{proof}
  By induction on the structure of the derivation for $\seq[P]{\mathcal{G}}$.
  The only interesting cases are when the last rule of the derivation is
  \textsc{H-Cycle} or \textsc{H-Mix}. In every other case, the typing rule
  constructs a term which is in canonical form.

  If the last rule in the derivation is \textsc{H-Cycle} or \textsc{H-Mix}, we
  consider the maximum evaluation prefix $\tm{G}$ of $\tm{P}$.
  Let the prefix $\tm{G}$ consist of $n$ cycles, and $m$ mixes, which introduces
  $n$ channels, and composes $m+1$ actions.
  Furthermore, let $o$ denote the number of environments in the
  hyper-environment $\ty{\mathcal{G}}$.

  Actions are introduced by the logical rules, each of which is annotated with
  the side condition that to act on one end-point of a channel, the other
  end-point may not be in scope.
  Let us call a channel ``locked'' if both its end-points are in scope.
  In this sense, a mix can unlock \emph{one} channel introduced by a cycle,
  and $m$ mixes can unlock $m$ channels.
  As the hyper-environment $\ty{\mathcal{G}}$ consists of $o$ environments,
  there are $o - 1$ possible applications of \textsc{Mix} which do not unlock
  one of the $n$ channels introduced in $\tm{G}$.
  Let $n'$ refer to the number of unlocked channels.
  We have $m - (o - 1) \le n' \le m$.
  Therefore, one of the following must be true:
  \begin{itemize}
  \item
    One of the actions composed by $\tm{G}$ is a link $\tm{\cpLink{x}{y}}$
    acting on a bound channel.
    Suppose that $\tm{x}$ is the bound channel.
    There exist evaluation contexts $\tm{E}$, $\tm{E'}$, and $\tm{E''}$ such that
    \[
      \tm{P} =
      \tm{\cpPlug{E}{\piNew{x}{\cpPlug{E'}{\piPar{\cpPlug{E''}{\cpLink{x}{y}}}{R}}}}}.
    \]
    We rewrite by $\equiv$ to obtain
    \[
      \tm{P} \equiv
      \tm{\cpPlug{E}{\cpPlug{E'}{\cpPlug{E''}{\piNew{x}{( \piPar{\cpLink{x}{y}}{R} )}}}}}.
    \]
    We then reduce by applying \hccpRedAxCut1.
    Similarly if $\tm{y}$ is the bound channel.
  \item
    Two of the actions composed by $\tm{G}$ are acting on the \emph{same}
    bound channel.
    Let the two actions be $\tm{P_i}$ and $\tm{P_i}$, and the bound channel
    $\tm{x}$.
    There exist evaluation contexts $\tm{E}$, $\tm{E'}$, $\tm{E_i}$, and
    $\tm{E_j}$ such that
    \[
      \tm{P} =
      \tm{\cpPlug{E}{
          \piNew{x}{\cpPlug{E'}{
              \piPar{
                \cpPlug{E_i}{P_i}
              }{
                \cpPlug{E_j}{P_j}
              }}}}}
    \]
    We rewrite by $\equiv$ to obtain
    \[
      \tm{P} \equiv
      \tm{\cpPlug{E}{
          \cpPlug{E'}{
            \cpPlug{E_i}{
              \cpPlug{E_j}{
                \piNew{x}{(\piPar{P_i}{P_j})}
              }}}}}
    \]
    We then reduce by applying the appropriate \textbeta-reduction.
  \item
    Otherwise, (at least) one of the actions composed by $\tm{G}$ must be acting
    on a free channel.
    None of the actions composed by $\tm{G}$ is a link acting on a bound channel.
    No two actions composed by $\tm{G}$ are acting on the same bound channel.
    Therefore, $\tm{P}$ is equivalent to a process in canonical form.
  \end{itemize}
\end{proof}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/thm-hcp-bigtens.tex
merged notes and old slides

\begin{definition}\label{def:hcp-bigtens}
  We can interpret hyper-environments as types by collapsing them using a series
  of tensors. In the case of the empty hyper-environment
  $\ty{\emptyhypercontext}$, we interpret this as the unit of tensor.
  \begin{gather*}
    \begin{array}{lcl}
      \ty{\bigtens\emptyhypercontext}
      & = & \ty{\one}
      \\
      \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
      & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
    \end{array}
  \end{gather*}
\end{definition}
\begin{theorem}\label{thm:hcp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \hcp.
\end{theorem}
\begin{proof}
  By case analysis on the structure of $\ty{\mathcal{G}}$.
  \begin{itemize}
  \item
    Case $\ty{\mathcal{G}} = \ty{\emptyhypercontext}$.\\
    By inversion on the derivation of $\seq{\emptyhypercontext}$.
    The only typing derivation ends in \textsc{H-Halt}.\\
    We rewrite as follows:
    \[
      \begin{array}{lcl}
        \AXC{}\NOM{H-Halt}\UIC{$\seq{\emptyhypercontext}$}
        \DisplayProof
        & \Rightarrow
        & \AXC{}\SYM{\one}\UIC{$\seq{\one}$}
          \DisplayProof
      \end{array}
    \] 
  \item
    Case $\ty{\mathcal{G}} = \ty{\Gamma_1 \hsep \dots \hsep \Gamma_n}$.\\
    By induction on the derivation of $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$.
    \begin{itemize}
    \item
      We remove any application of \textsc{H-Mix} where either premise is \textsc{H-Halt}.
    \item
      We propagate the applications of \textsc{H-Mix} downwards to the root of the
      proof, using the rewrite rules in \cref{fig:cc-hmix}, and obtain a
      derivation of the following form:
      \begin{prooftree}
        \pvar{$\rho_1$}\UIC{$\seq{\Gamma_1}$}
        \AXC{$\dots$}
        \pvar{$\rho_n$}\UIC{$\seq{\Gamma_n}$}
        \NOM{H-Mix}
        \TIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
      \end{prooftree}
    \item
      We apply \cref{lem:hcp-bigparr} to each sub-proof $\rho_i$ to obtain a
      series of single-formula sequents, joined by applications of \textsc{H-Mix}.
    \item
      We replace the applications of \textsc{H-Mix} with applications of $(\tens)$.
    \end{itemize}
  \end{itemize}
\end{proof}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

### 2018-10-04 doc/notes/thm-hcp-progress.tex
merged notes and old slides

--- 2018-10-04 doc/notes/thm-cp-progress.tex
@@
-\begin{theorem}[Progress]\label{thm:cp-progress}
-  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that either
+\begin{theorem}[Progress]\label{thm:hcp-progress}
+  If $\seq[P]{\mathcal{G}}$, then there exists a $\tm{Q}$ such that either
   $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form, or $\reducesto{P}{Q}$.
@@
 \begin{proof}
-  By induction on the structure of derivation for $\seq[P]{\Gamma}$.
-  The only interesting case is when the last rule of the derivation is
-  \textsc{Cut}---in every other case, the typing rule constructs a term which is
-  in canonical form.
+  By induction on the structure of derivation for $\seq[{ P }]{ \mathcal{G} }$.
+  The only interesting cases are when the last rule of the derivation is
+  \textsc{Cut} or \textsc{H-Mix}. In every other case, the typing rule
+  constructs a term which is in canonical form. 
   \\
-  We consider the maximum evaluation prefix $\tm{G}$ of $\tm{P}$, such that $\tm{P}
-  = \tm{\cpPlug{G}{P_1 \dots P_{n+1}}}$ and each $\tm{P_i}$ is an action.
-  The prefix $\tm{G}$ consists of $n$ cuts, and introduces $n$ channels, but
-  composes $n+1$ actions. Therefore, one of the following must be true:
+  If the last rule in the derivation is \textsc{Cut} or \textsc{H-Mix}, we
+  consider the maximum evaluation prefix $\tm{G}$ of $\tm{P}$, such that $\tm{P}
+  = \tm{\cpPlug{G}{P_1 \dots P_{m+n+1}}}$ and each $\tm{P_i}$ is an action.
+  The prefix $\tm{G}$ consists of $m$ mixes, $n$ cuts, and introduces $n$
+  channels, but composes $m+n+1$ actions, at most $m+1$ of which are on the same
+  side of all cuts.
   \begin{itemize}
@@
   \item
-    Otherwise (at least) one of the actions composed by $\tm{G}$ must be acting
-    on a free channel.
-    None of the actions composed by $\tm{G}$ is a link.
-    No two actions composed by $\tm{G}$ are acting on the same channel $\tm{x}$.
+    Otherwise (at least) one of the processes acts on an external channel.
+    No process $\tm{P_i}$ is a link acting on a bound channel.
+    No two processes $\tm{P_i}$ and $\tm{P_j}$ act on the same channel $\tm{x}$.
     Therefore, $\tm{P}$ is equivalent to a process in canonical form.

### 2018-10-26 doc/paper/main.tex
copied abstract source for paper
Rewrote proofs and theory of TLLA 2018

--- 2018-05-24 doc/abstract/main.tex
@@
 \usepackage{amssymb}
-\usepackage{mathtools}
+\def\Coloneqq{\mathbin{::=}}
+\def\coloneqq{\mathbin{:=}}
 \usepackage[inline]{enumitem}
@@
       \tm{P}, \tm{Q}, \tm{R}
-           \Coloneqq& \tm{\cpLink{x}{y}}       &\text{link}
+           \Coloneqq & \tm{\cpLink{x}{y}}       &\text{link}
       &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
@@
         & \tm{\cpCut{x}{P}{R}}
-        \\
-        \cpRedKappaTens1
-        & \tm{\cpCut{x}{\cpSend{y}{z}{P}{Q}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpSend{y}{z}{\cpCut{x}{P}{R}}{Q}}
-          \quad \text{if} \; \notFreeIn{x}{Q}
-        \\
-        \cpRedKappaTens2
-        & \tm{\cpCut{x}{\cpSend{y}{z}{P}{Q}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpSend{y}{z}{P}{\cpCut{x}{Q}{R}}}
-          \quad \text{if} \; \notFreeIn{x}{P}
-        \\
-        \cpRedKappaParr
-        & \tm{\cpCut{x}{\cpRecv{y}{z}{P}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpRecv{y}{z}{\cpCut{x}{P}{R}}}
-        \\
-        \cpRedKappaBot
-        & \tm{\cpCut{x}{\cpWait{y}{P}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpWait{y}{\cpCut{x}{P}{R}}}
-        \\
-        \cpRedKappaPlus1
-        & \tm{\cpCut{x}{\cpInl{y}{P}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpInl{y}{\cpCut{x}{P}{R}}}
-        \\
-        \cpRedKappaPlus2
-        &\tm{\cpCut{x}{\cpInr{y}{P}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpInr{y}{\cpCut{x}{P}{R}}}
-        \\
-        \cpRedKappaWith
-        & \tm{\cpCut{x}{\cpCase{y}{P}{Q}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpCase{y}{\cpCut{x}{P}{R}}{\cpCut{x}{Q}{R}}}
-        \\
-        \cpRedKappaTop
-        & \tm{\cpCut{x}{\cpAbsurd{y}}{R}}
-        & \Longrightarrow \;
-        & \tm{\cpAbsurd{y}}
       \end{array}
@@
   \(
-    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} \coloneqq \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
+    \ty{\Gamma}, \ty{\Delta}, \ty{\Theta} \Coloneqq \ty{\emptycontext} \mid \ty{\Gamma}, \tmty{x}{A}
   \)
@@
 \begin{definition}[Typing judgements]\label{def:cp}
-  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n}}$ denotes that the process \tm{P} communicates along channels $\tm{x_1}$, \dots, $\tm{x_n}$ following protocols $\ty{A_1}$, \dots, $\ty{A_n}$.
-Typing judgements are derived using rules below.
-  \begin{description}
-	  \item[Structural rules]
-  		\begin{gather*}\cpInfAx  \qquad  \cpInfCut   \end{gather*}
-	  \item[Logical rules]
-		  \begin{gather*}
-				\cpInfTens \qquad 
-				\cpInfParr \\
-				\cpInfBot \qquad 
-				\cpInfOne \\
-				\cpInfPlus1 \qquad 
-				\cpInfPlus2 \\
-				\cpInfWith \qquad
-				\cpInfNil \qquad 
+  A typing judgement $\seq[{ P }]{\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n}}$
+  denotes that the process \tm{P} communicates along channels $\tm{x_1}$, \dots,
+  $\tm{x_n}$ following protocols $\ty{A_1}$, \dots, $\ty{A_n}$. Typing
+  judgements are derived using rules below.
+  \\
+  {Structural rules}
+  \begin{center}
+    \cpInfAx
+    \cpInfCut
+  \end{center}
+	{Logical rules}
+  \begin{center}
+    \cpInfTens
+    \cpInfParr
+  \end{center}
+  \begin{center}
+    \cpInfBot
+    \cpInfOne
+  \end{center}
+  \begin{center}
+    \cpInfPlus1
+    \cpInfPlus2
+  \end{center}
+  \begin{center}
+    \cpInfWith
+  \end{center}
+  \begin{center}
+    \cpInfNil
     \cpInfTop   
-			\end{gather*}
-	\end{description}
+  \end{center}
 \end{definition}
@@
 \end{proof}
+\begin{definition}[Canonical forms]
+  A process $\tm{P}$ is in canonical form if
+  \(
+    \tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}},
+  \)
+  such that: no process $\tm{P_i}$ is a cut; no process $\tm{P_i}$ is a link acting on a bound channel $\tm{x_i}$; and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel $\tm{x_i}$.
+\end{definition}
+\begin{corollary}
+  If a process $\tm{P}$ is in canonical form, then it is blocked on an external communication.
+\end{corollary}
+\begin{proof}
+  We have $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
+The prefix of cuts introduces $n$ channels, and $n+1$ processes.
+Therefore, at least \emph{one} of the processes $\tm{P_i}$ must be acting on a free channel, i.e., blocked on an external communication.
+\end{proof}
+\begin{theorem}[Progress]\label{thm:cp-progress}
+  If $\seq[P]{\Gamma}$, then either $\tm{P}$ is in canonical form, or there exists a process $\tm{Q}$ such that $\tm{P}\Longrightarrow\tm{Q}$.
+\end{theorem} 
+\begin{proof}
+  We consider the maximum prefix of cuts of $\tm{P}$ such that $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ and no $\tm{P_i}$ is a cut.
+If any process $\tm{P_i}$ is a link, we reduce by $(\cpLink{}{})$.
+If any two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same channel $\tm{x_i}$, we rewrite by $\equiv$ and reduce by the appropriate $\beta$-rule.
+Otherwise, $\tm{P}$ is in canonical form.
+\end{proof}
 \begin{theorem}[Termination]\label{thm:cp-termination}
@@
 Therefore, there cannot be an infinite $\Longrightarrow$-reduction sequence.
-\end{proof}
-\begin{theorem}[Progress]\label{thm:cp-progress}
-  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that
-  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
-\end{theorem} 
-\begin{proof}
-  By induction on the derivation of $\seq[P]{\Gamma}$. If the last rule is \textsc{Cut}, there are four cases:
-  \begin{enumerate*}[label={\alph*)}]
-  \item
-    if either side of the cut is an axiom, we apply \cpRedAxCut1;
-  \item
-    if either side of the cut is itself a cut, we recursively eliminate the cut;
-  \item
-    if both sides are logical rules acting on the cut formula, we apply
-    one of the $\beta$-rules;
-  \item
-    otherwise, at least one side is a logical rule acting on a formula other
-    than the cut formula, in which case we apply one of the $\kappa$-rules.
-  \end{enumerate*}
 \end{proof}
@@
       &
-        \hccpEquivMixHalt1
+        \hcpEquivMixHalt1
       & \tm{\piPar{P}{\piHalt}}
@@
       \\
-        \hccpEquivMixComm
+        \hcpEquivMixComm
       & \tm{\piPar{P}{Q}}
@@
       &
-        \hccpEquivMixAss1
+        \hcpEquivMixAss1
       & \tm{\piPar{P}{( \piPar{Q}{R} )}}
@@
       \\
-        \hccpEquivNewComm
+        \hcpEquivNewComm
       & \tm{\piNew{x}{\piNew{y}{P}}}
@@
       &
-        \hccpEquivScopeExt1
+        \hcpEquivScopeExt1
       & \tm{\piNew{x}{( \piPar{P}{Q} )}}
@@
     \begin{array}{llcll}
-      \hccpRedAxCut1
+      \hcpRedAxCut1
       & \tm{\cpCut{x}{\cpLink{w}{x}}{P}}
@@
       \\
-      \hccpRedBetaTensParr
+      \hcpRedBetaTensParr
       & \tm{\cpCut{x}{\piBoundSend{x}{y}{P}}{\piRecv{x}{y}{R}}}
@@
       \\
-      \hccpRedBetaOneBot
+      \hcpRedBetaOneBot
       & \tm{\cpCut{x}{\piBoundSend{x}{}{P}}{\piRecv{x}{}{Q}}}
@@
       \\
-      \hccpRedBetaPlusWith1
+      \hcpRedBetaPlusWith1
       & \tm{\cpCut{x}{\cpInl{x}{P}}{\cpCase{x}{Q}{R}}}
@@
       \\
-      \hccpRedBetaPlusWith2
+      \hcpRedBetaPlusWith2
       & \tm{\cpCut{x}{\cpInr{x}{P}}{\cpCase{x}{Q}{R}}}
@@
       & \tm{\cpCut{x}{P}{R}}
-      \\
-      \hccpRedKappaNuTens
-      & \tm{\piNew{x}{\piBoundSend{y}{z}{P}}}
-      & \Longrightarrow
-      & \tm{\piBoundSend{y}{z}{\piNew{x}{P}}}
-      \\
-      \hccpRedKappaNuParr
-      & \tm{\piNew{x}{\piRecv{y}{z}{P}}}
-      & \Longrightarrow
-      & \tm{\piRecv{y}{z}{\piNew{x}{P}}}
-      \\
-      \hccpRedKappaNuOne
-      & \tm{\piNew{x}{\piBoundSend{y}{}{P}}}
-      & \Longrightarrow
-      & \tm{\piBoundSend{y}{}{\piNew{x}{P}}}
-      \\
-      \hccpRedKappaNuBot
-      & \tm{\piNew{x}{\piRecv{y}{}{P}}}
-      & \Longrightarrow
-      & \tm{\piRecv{y}{}{\piNew{x}{P}}}
-      \\
-      \hccpRedKappaNuPlus1
-      & \tm{\piNew{x}{\cpInl{y}{P}}}
-      & \Longrightarrow
-      & \tm{\cpInl{y}{\piNew{x}{P}}}
-      \\
-      \hccpRedKappaNuPlus2
-      & \tm{\piNew{x}{\cpInr{y}{P}}}
-      & \Longrightarrow
-      & \tm{\cpInr{y}{\piNew{x}{P}}}
-      \\
-      \hccpRedKappaNuWith
-      & \tm{\piNew{x}{\cpCase{y}{P}{Q}}}
-      & \Longrightarrow
-      & \tm{\cpCase{y}{\piNew{x}{P}}{\piNew{x}{Q}}}
-      \\
-      \hccpRedKappaNuTop
-      & \tm{\piNew{x}{\cpAbsurd{y}}}
-      & \Longrightarrow
-      & \tm{\cpAbsurd{y}}
-      \\
-      \hccpRedKappaMixTens
-      & \tm{(\piPar{\piBoundSend{y}{z}{P}}{R})}
-      & \Longrightarrow
-      & \tm{\piBoundSend{y}{z}{(\piPar{P}{R})}}
-      \\
-      \hccpRedKappaMixParr
-      & \tm{(\piPar{\piRecv{y}{z}{P}}{R})}
-      & \Longrightarrow
-      & \tm{\piRecv{y}{z}{(\piPar{P}{R})}}
-      \\
-      \hccpRedKappaMixOne
-      & \tm{(\piPar{\piBoundSend{y}{}{P}}{R})}
-      & \Longrightarrow
-      & \tm{\piBoundSend{y}{}{(\piPar{P}{R})}}
-      \\
-      \hccpRedKappaMixBot
-      & \tm{(\piPar{\piRecv{y}{}{P}}{R})}
-      & \Longrightarrow
-      & \tm{\piRecv{y}{}{(\piPar{P}{R})}}
-      \\
-      \hccpRedKappaMixPlus1
-      & \tm{(\piPar{\cpInl{y}{P}}{R})}
-      & \Longrightarrow
-      & \tm{\cpInl{y}{(\piPar{P}{R})}}
-      \\
-      \hccpRedKappaMixPlus2
-      & \tm{(\piPar{\cpInr{y}{P}}{R})}
-      & \Longrightarrow
-      & \tm{\cpInr{y}{(\piPar{P}{R})}}
-      \\
-      \hccpRedKappaMixWith
-      & \tm{(\piPar{\cpCase{y}{P}{Q}}{R})}
-      & \Longrightarrow
-      & \tm{\cpCase{y}{(\piPar{P}{R})}{(\piPar{Q}{R})}}
-      \\
-      \hccpRedKappaMixTop
-      & \tm{(\piPar{\cpAbsurd{y}}{R})}
-      & \Longrightarrow
-      & \tm{\cpAbsurd{y}}
     \end{array}
@@
         \AXC{$\reducesto{P}{P^\prime}$}
-        \SYM{\hccpRedGammaNew}
+        \SYM{\hcpRedGammaNew}
         \UIC{$\reducesto{\piNew{x}{P}}{\piNew{x}{P^\prime}}$}
@@
         \AXC{$\reducesto{P}{P^\prime}$}
-        \SYM{\hccpRedGammaMix}
+        \SYM{\hcpRedGammaMix}
         \UIC{$\reducesto{\piPar{P}{Q}}{\piPar{P^\prime}{Q}}$}
@@
         \AXC{$\tm{Q^\prime}\equiv\tm{P^\prime}$}
-        \SYM{\hccpRedGammaEquiv}
+        \SYM{\hcpRedGammaEquiv}
         \TIC{$\reducesto{P}{P^\prime}$}
@@
   Typing judgements can be constructed using the inference rules below. 
-  \begin{description}
-    \item[Structural rules]
-    \begin{gather*}
-			\hccpInfAx \qquad
-			\hccpInfCycle \\
-	    \hccpInfMix  \qquad
-	    \hccpInfHalt
-    \end{gather*}
-    \item[Logical rules]
-    \begin{gather*}
-    	\hccpInfBoundTens \qquad \hccpInfParr \\
-			\hccpInfOne  \qquad    \hccpInfBot \\  
-			\hccpInfPlus1 \qquad    \hccpInfPlus2 \\
-			\hccpInfWith \\    
-			\hccpInfNil   \qquad    \hccpInfTop
-    \end{gather*}
-  \end{description}
+  \\
+  {Structural rules}
+  \begin{center}
+    \hcpInfAx
+    \hcpInfCut
+  \end{center}
+  \begin{center}
+    \hcpInfMix
+    \hcpInfHalt
+  \end{center}
+  {Logical rules}
+  \begin{center}
+    \hcpInfBoundTens
+    \hcpInfParr
+  \end{center}
+  \begin{center}
+    \hcpInfOne
+    \hcpInfBot
+  \end{center}
+  \begin{center}
+    \hcpInfPlus1
+    \hcpInfPlus2
+  \end{center}
+  \begin{center}
+    \hcpInfWith
+  \end{center}
+  \begin{center}
+    \hcpInfNil
+    \hcpInfTop
+  \end{center}
   Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
@@
 \end{proof}
+\begin{definition}[Canonical forms]
+  A process $\tm{P}$ is in canonical form if
+  \(
+    \tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}},
+  \)
+  such that: no process $\tm{P_i}$ is a cut or a mix; no process $\tm{P_i}$ is a link acting on a bound channel $\tm{x_i}$; and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel $\tm{x_i}$.
+\end{definition}
+\begin{corollary}
+  If a process $\tm{P}$ is in canonical form, then it is blocked on an external communication.
+\end{corollary}
+\begin{proof}
+  We have $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
+The prefix of cuts and mixes introduces $n$ channels.
+Each application of cut requires an application of mix, so the prefix introduces $n+m+1$ processes.
+Therefore, at least $\tm{m+1}$ of the processes $\tm{P_i}$ must be acting on a free channel, i.e., blocked on an external communication.
+\end{proof}
+\begin{theorem}[Progress]\label{thm:hcp-progress}
+  If $\seq[P]{\Gamma}$, then either $\tm{P}$ is in canonical form, or there exists a process $\tm{Q}$ such that $\tm{P}\Longrightarrow\tm{Q}$.
+\end{theorem} 
+\begin{proof}
+  We consider the maximum prefix of cuts of $\tm{P}$ such that $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ and no $\tm{P_i}$ is a cut.
+If any process $\tm{P_i}$ is a link, we reduce by $(\cpLink{}{})$.
+If any two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same channel $\tm{x_i}$, we rewrite by $\equiv$ and reduce by the appropriate $\beta$-rule.
+Otherwise, $\tm{P}$ is in canonical form.
+\end{proof}
 \begin{theorem}[Termination]\label{thm:hcp-termination}
@@
   As \cref{thm:cp-termination}.
-\end{proof}
-\begin{theorem}[Progress]\label{thm:hcp-progress}
-  If $\seq[P]{\mathcal{G}}$, then there exists a $\tm{Q}$ such that
-  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut or a mix.
-\end{theorem} 
-\begin{proof}
-  By induction on the derivation of $\seq[P]{\mathcal{G}}$. If the last rule is a cut, there are three cases:
-  \begin{enumerate*}[label={\alph*)}]
-  \item
-    if the rule under the cut is the corresponding mix, we eliminate both as in
-    \cref{thm:cp-progress};
-  \item
-    if the rule under the cut is an unrelated mix, we rewrite by \hccpEquivScopeExt{}, and recursively eliminate the cut;
-  \item
-    if the rule under the cut is a logical rule, we apply one of the $\kappa\nu$-rules.
-  \end{enumerate*}
-  If the last rule is mix, there are two cases:
-  \begin{enumerate*}[label={\alph*)}]
-  \item
-    if the rule under the mix is a cut or another mix, we recursively eliminate it;
-  \item
-    if the rule under the mix is a logical rule, we apply one of the
-    $\kappa{\ppar}$-rules.
-  \end{enumerate*}
 \end{proof}
@@
         & \AXC{}
-          \NOM{H-Halt}
+          \NOM{H-Mix$_0$}
           \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
@@
   By induction on the derivation of $\reducesto{\mtf{P}}{R}$.
-The cases for \hccpRedAxCut1 and the $\beta$-rules are trivial.
+The cases for \hcpRedAxCut1 and the $\beta$-rules are trivial.
 For the $\kappa\nu$-rules, we rewrite by the appropriate $\kappa{\ppar}$ rule, and vice versa.
@@
       \DisplayProof
-    \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
-    \pvar{$\rho_4$}\UIC{$\seq{\mathcal{G}_2}$}
-    \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {B}, \Gamma}$}
-    \SYM{\with}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
-    \DisplayProof
-    & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_1 \hsep {B}, \Gamma}$}
-      \SYM{\with}
-      \BIC{$\seq{\mathcal{G}_1 \hsep {A \with B}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
-      \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \with B}, \Gamma}$}
-      \DisplayProof
   \end{array}
@@
   \end{enumerate*}
-  All applications of $(\one)$ are followed by an application of \textsc{H-Halt}, forming a \cp $(\one)$.
+  All applications of $(\one)$ are followed by an application of \textsc{H-Mix$_0$}, forming a \cp $(\one)$.
 \end{proof}

### 2018-10-28 doc/paper/main.tex
final version

@@
 \begin{abstract}
-  Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
+% Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
 However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus.
@@
 
-In this paper, we introduce Hypersequent Classical Processes (\hcp), which addresses this mismatch.
+\citet{kokke2019} introduced Hypersequent Classical Processes (\hcp), which addresses this mismatch.
 The key insight is to register parallelism in the typing judgements using hypersequents~\citep{avron1991}, a technique from logic which generalises judgements from one sequent to many.
 This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
+\hcp has labelled transition semantics with delayed actions~\citep{merro2004} and a full abstraction result: bisimilarity, denotational equivalence, and barbed congruence coincide.
+
+However, the step from \cp to \hcp is a big one.
+As of yet, \hcp does not have reduction semantics, and the addition of delayed actions means that \cp processes interpreted as \hcp processes do not behave as they would in \cp.
+
+In this paper, we address these issues by introducing a variant of \hcp with reduction semantics and without delayed actions.
 We proceed as follows.
 We start by introducing \cp (\cref{sec:cp}).
-Then, we introduce \hcp and prove it enjoys subject reduction and progress (\cref{sec:hcp}).
-We prove that every \cp process is an \hcp process, and that \hcp supports the same communication protocols as \cp, and no more (\cref{sec:cp2hcp}).
+Then, we introduce our variant of \hcp and prove it enjoys subject reduction and progress (\cref{sec:hcp}).
+We prove that every \cp process is an \hcp process, relate processes in \hcp back to \cp, and restate the result that \hcp supports the same communication protocols as \cp (\cref{sec:cp2hcp}).
 Finally, we discuss related work (\cref{sec:related-work}).
@@
 \end{definition}\noindent
+The reduction semantics presented here are a variant of those presented by \citet{lindley2015}, who showed that reduction in \cp can be decomposed in two phases: one in which all \textbeta-reduction happens, and one in which an arbitrary action, blocked on an external communication, is moved to the top of the term using commuting conversions.
+We choose to stop after the first phase, and do away with the commuting conversions.
+
 Reductions relate processes with their reduced forms \eg a reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce to the process $\tm{Q}$ in a single step.
@@
   judgements are derived using rules below.
-  \\
+  \\[1\baselineskip]
   {Structural rules}
   \begin{center}
-    \cpInfAx
-    \cpInfCut
+    \cpInfAx \cpInfCut
   \end{center}
@@
   \begin{center}
-    \cpInfTens
-    \cpInfParr
+    \cpInfTens \cpInfParr
   \end{center}
@@
 
-In this section, we introduce Hypersequent Classical Processes (\hcp), a variant of \cp which registers parallelism in the typing judgements using hypersequents, allowing us to take apart the monolithic term constructors of \cp (\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term constructs.
+In this section, we introduce our variant of Hypersequent Classical Processes (\hcp), itself a variant of \cp which registers parallelism in the typing judgements using hypersequents, allowing us to take apart the monolithic term constructors of \cp (\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term constructs.
+
+The crucial difference between \hcp as described here and \hcp as described by \citet{kokke2019} is in the absence of delayed actions.
+However, removing delayed actions introduces self-locking processes, which we rule out using an extra restriction in the type system (see \cref{sec:hcp-types}).
+Furthermore, we follow \cp in using the same name for both endpoints of a channel, writing, \eg $\tm{\cpCut{x}{\cpHalt{x}}{\cpWait{x}{P}}}$ as opposed to $\tm{\cpCut{xy}{\cpHalt{x}}{\cpWait{y}{P}}}$.
 
@@
 
-\subsection{Types}
+\subsection{Types}\label{sec:hcp-types}
 We use the same definitions for types and environments for \hcp as we used for \cp.
@@
   Typing judgements can be constructed using the inference rules below. 
-  \\
+  \\[1\baselineskip]
   {Structural rules}
@@
 In this section, we discuss the relationship between \cp and \hcp.
-We will prove two important theorems: every \cp process is an \hcp process; and \hcp supports the same protocols as \cp.
+We prove two important theorems: every \cp process is an \hcp process; and \hcp supports the same protocols as \cp.
 We define a translation from terms in \cp to terms in \hcp which breaks down the term constructs in \cp into their more atomic constructs in \hcp.
@@
 \end{definition}\noindent
-We will use this relation in the first proof, and its analogue for derivations in the second.
+We use this relation in the first proof, and its analogue for derivations in the second.
 
@@
 \subsection{\hcp supports the same communication protocols as \cp}
-\hcp exhibits some behaviours which are impossible to directly translate back into \cp.
-For instance, in the process below, the choice sent on $\tm{x}$ will affect the choice between $\tm{P}$ and $\tm{P'}$, even though neither has access to the channel $\tm{x}$.
-\[
-\begin{prooftree*}
-  \AXC{}\noLine\UIC{$\seq[P]{ \Gamma }$}
-  \AXC{}\noLine\UIC{$\seq[Q]{ \Delta, \tmty{x}{A} }$}
-  \NOM{H-Mix}
-  \BIC{$\seq[\piPar{P}{Q}]{ \Gamma \hsep \Delta, \tmty{x}{A} }$}
-  \AXC{}\noLine\UIC{$\seq[P']{ \Gamma }$}
-  \AXC{}\noLine\UIC{$\seq[Q']{ \Delta, \tmty{x}{B} }$}
-  \NOM{H-Mix}
-  \BIC{$\seq[\piPar{P'}{Q'}]{ \Gamma \hsep \Delta, \tmty{x}{B} }$}
-  \SYM{\with}
-  \BIC{$\seq[\cpCase{x}{\piPar{P}{Q}}{\piPar{P'}{Q'}}]{ \Gamma \hsep \Delta, \tmty{x}{A \with B}}$}
-\end{prooftree*}
-\]
-Instead, we will prove that \hcp supports the same communication protocols as \cp.
+In this section, we prove that \hcp supports the same communication protocols as \cp.
 This is the same as saying that it inhabits the same session types, or that the associated logical systems derive the same theorems.
@@
 \begin{definition}\label{def:hcp-disentangle}
-  Disentanglement is described by the smallest relation $\moveMixDown$ on proof derivations closed under the rules in \cref{fig:hcp-disentangle}, plus the associativity and commutativity of mixes.
+  Disentanglement is described by the smallest relation $\moveMixDown$ on processes closed under the rules in \cref{fig:hcp-disentangle}, plus the associativity and commutativity of mixes.
 The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
@@
 \begin{sidewaysfigure} 
-  \(
+  \[
   \begin{array}{lcr}
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
+    \AXC{$\seq[Q]{\mathcal{H}}$}
     \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2}$}
-    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
+    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
     \NOM{H-Cut}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+    \UIC{$\seq[\piNew{x}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
     \DisplayProof
     & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {A^\bot}, \Delta}$}
+    & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
       \NOM{H-Cut}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \UIC{$\seq[\piNew{x}{P}]{\mathcal{G} \hsep \Gamma, \Delta}$}
+      \AXC{$\seq[Q]{\mathcal{H}}$}
       \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3 \hsep \Gamma, \Delta}$}
+      \BIC{$\seq[(\piNew{x}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
       \DisplayProof
     \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
+    \AXC{$\seq[Q]{\mathcal{H}}$}
     \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
+    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
     \SYM{\tens}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
-    \hsep {A \tens B}, \Gamma, \Delta}$}
+    \UIC{$\seq[\piBoundSend{x}{y}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta, \tmty{x}{A \tens B}}$}
     \DisplayProof
     & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-      \pvar{$\rho_3$}\UIC{$\seq{\mathcal{G}_3 \hsep {B}, \Delta}$}
+    & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
       \SYM{\tens}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \tens B},
-      \Gamma, \Delta}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \UIC{$\seq[\piBoundSend{x}{y}{P}]{\mathcal{G} \hsep \Gamma, \Delta}$}
+      \AXC{$\seq[Q]{\mathcal{H}}$}
       \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \mathcal{G}_3
-      \hsep {A \tens B}, \Gamma, \Delta}$}
+      \BIC{$\seq[(\piBoundSend{x}{y}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta, \tmty{x}{A \tens B}}$}
       \DisplayProof
     \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{y}{A}, \tmty{x}{B}}$}
+    \AXC{$\seq[Q]{\mathcal{H}}$}
     \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
+    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{y}{A}, \tmty{x}{B}}$}
     \SYM{\parr}
-    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
+    \UIC{$\seq[(\piRecv{x}{y}{(P \ppar Q)})]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma \tmty{x}{A \parr B}}$}
     \DisplayProof
     & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, {B}, \Gamma}$}
+    & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{y}{A}, \tmty{x}{B}}$}
       \SYM{\parr}
-      \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, {B}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \UIC{$\seq[\piRecv{x}{y}{P}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \parr B}}$}
+      \AXC{$\seq[Q]{\mathcal{H}}$}
       \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \parr B}, \Gamma}$}
+      \BIC{$\seq[(\piRecv{x}{y}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \parr B}}$}
       \DisplayProof
     \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma}$}
+    \AXC{$\seq[Q]{\mathcal{H}}$}
     \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
+    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma}$}
     \SYM{\bot}
-    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {\bot}, \Gamma}$}
+    \UIC{$\seq[\piRecv{x}{}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{\bot}}$}
     \DisplayProof
     & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep \Gamma}$}
+    & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma}$}
       \SYM{\bot}
-      \UIC{$\seq{\mathcal{G}_1 \hsep {\bot}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \UIC{$\seq[\piRecv{x}{}{P}]{\mathcal{G} \hsep \Gamma, \tmty{x}{\bot}}$}
+      \AXC{$\seq[Q]{\mathcal{H}}$}
       \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep \Gamma}$}
+      \BIC{$\seq[(\piRecv{x}{}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{\bot}}$}
       \DisplayProof
     \\\\
-    \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
-    \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+    \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A}}$}
+    \AXC{$\seq[Q]{\mathcal{H}}$}
     \NOM{H-Mix}
-    \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A}, \Gamma}$}
+    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A}}$}
     \SYM{\plus_1}
-    \UIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
+    \UIC{$\seq[\cpInl{x}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \plus B}}$}
     \DisplayProof
     & \moveMixDown
-    & \pvar{$\rho_1$}\UIC{$\seq{\mathcal{G}_1 \hsep {A}, \Gamma}$}
+    & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A}}$}
       \SYM{\plus_1}
-      \UIC{$\seq{\mathcal{G}_1 \hsep {A \plus B}, \Gamma}$}
-      \pvar{$\rho_2$}\UIC{$\seq{\mathcal{G}_2}$}
+      \UIC{$\seq[\cpInl{x}{P}]{\mathcal{G} \hsep \Gamma, \tmty{x}{A \plus B}}$}
+      \AXC{$\seq[Q]{\mathcal{H}}$}
       \NOM{H-Mix}
-      \BIC{$\seq{\mathcal{G}_1 \hsep \mathcal{G}_2 \hsep {A \plus B}, \Gamma}$}
+      \BIC{$\seq[(\cpInl{x}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \plus B}}$}
       \DisplayProof
   \end{array}
-  \)
+  \]
   \caption{The disentanglement relation for \hcp.}
@@
 \begin{lemma}[Disentangle]\label{lem:hcp-disentangle}
-  If there exists a derivation $\rho$ of $\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist derivations $\rho_1, \dots, \rho_n$ of $\seq{\Gamma_1}, \dots, \seq{\Gamma_n}$ in \cp such that
+  If $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ in \hcp, then there exist processes $\tm{P_1}, \dots, \tm{P_n}$ in \cp such that $\seq[P_1]{\Gamma_1}, \dots, \seq[P_n]{\Gamma_n}$ and
   \[
-  \rho
+    \begin{prooftree*}
+      \AXC{\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}}
+    \end{prooftree*}
     \moveMixDown^\star
     \begin{prooftree*}
-    \AXC{}\noLine\UIC{$\mtf{\rho_1}$}
-    \AXC{}\noLine\UIC{$\dots$}
-    \AXC{}\noLine\UIC{$\mtf{\rho_n}$}
-    \NOM{H-Mix}
-    \TIC{$\seq{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+      \AXC{$\seq[\mtf{P_1}]{\Gamma_1}$}
+      \AXC{$\dots$}
+      \AXC{$\seq[\mtf{P_n}]{\Gamma_n}$}
+      \NOM{H-Mix$^\star$}
+      \TIC{$\seq[(P_1 \ppar \dots \ppar P_n)]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
     \end{prooftree*}
@@
 %%% End:
+
+% LocalWords:  labelled

### 2018-12-19 doc/paper/main.tex
First pass after reviews

@@
   Every reduction reduces a single cut to zero, one or two cuts.
-However, each of these cuts is smaller, measured in the size of the cut term.
+However, each of these cuts is smaller, measured in the size of the cut formula.
 Furthermore, each instance of the structural congruence preserves the size of the cut.
@@
 First, since $\tm{\piBoundSend{x}{y}{P}}$ and $\tm{\piBoundSend{x}{}{P}}$ are now terms in their own right, the $\cpRedBetaTensParr$ and $\cpRedBetaOneBot$ rules are simpler.
-Second, since we decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent name restriction and parallel composition, the $\kappa$-rules and the relevant $\gamma$-rule all decompose as well.
+Second, since we decomposed $\tm{\cpCut{x}{P}{Q}}$ into an independent name restriction and parallel composition, the relevant $\gamma$-rule all decompose as well.
 \begin{definition}[Reduction]\label{def:hcp-reduction}
@@
   \(
-    \tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}},
+  \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \mid \dots \mid P_{n+m+1})}}},
   \)
@@
 \begin{proof}
-  We have $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
+  We have
+  \(
+  \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}},
+  \)
+  such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
 The prefix of cuts and mixes introduces $n$ channels.
 Each application of cut requires an application of mix, so the prefix introduces $n+m+1$ processes.
-Therefore, at least $\tm{m+1}$ of the processes $\tm{P_i}$ must be acting on a free channel, i.e., blocked on an external communication.
+Therefore, at least $m+1$ of the processes $\tm{P_i}$ must be acting on a free channel, i.e., blocked on an external communication.
 \end{proof}
@@
 Reductions from \cp can be trivially translated to reductions in \hcp.
-However, as we took apart each $\kappa$-rule into two separate rules, the reduction relation of \hcp is a slight refinement over that of \cp.
 \begin{theorem}\label{thm:cp2hcp-typing}
@@
 \begin{theorem}\label{thm:cp2hcp-reduction}
-  If $\reducesto{P}{Q}$ in \cp, then $\tm{\mtf{P}}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
+  If $\reducesto{P}{Q}$ in \cp, then $\reducesto{\mtf{P}}{\mtf{Q}}$ in \hcp.
 \end{theorem} 
@@
 \begin{theorem}\label{hcp2cp-reduction}
-  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\Longrightarrow^{+}\tm{\mtf{Q}}$ in \hcp.
+  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\reducesto{R}{\mtf{Q}}$ or $\tm{R}\equiv\tm{\mtf{Q}}$ in \hcp.
 \end{theorem} 
@@
   By induction on the derivation of $\reducesto{\mtf{P}}{R}$.
-The cases for \hcpRedAxCut1 and the $\beta$-rules are trivial.
-For the $\kappa\nu$-rules, we rewrite by the appropriate $\kappa{\ppar}$ rule, and vice versa.
 \end{proof}\noindent
@@
 \begin{definition}\label{def:hcp-disentangle}
-  Disentanglement is described by the smallest relation $\moveMixDown$ on processes closed under the rules in \cref{fig:hcp-disentangle}, plus the associativity and commutativity of mixes.
+  Disentanglement is described by the smallest relation $\moveMixDown$ on processes closed under the rules in \cref{fig:hcp-disentangle}, plus the structural congruence $\equiv$.
 The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
@@
       \SYM{\tens}
-      \UIC{$\seq[\piBoundSend{x}{y}{P}]{\mathcal{G} \hsep \Gamma, \Delta}$}
+      \UIC{$\seq[\piBoundSend{x}{y}{P}]{\mathcal{G} \hsep \Gamma, \Delta, \tmty{x}{A \tens B}}$}
       \AXC{$\seq[Q]{\mathcal{H}}$}
@@
     \SYM{\parr}
-    \UIC{$\seq[(\piRecv{x}{y}{(P \ppar Q)})]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma \tmty{x}{A \parr B}}$}
+    \UIC{$\seq[(\piRecv{x}{y}{(P \ppar Q)})]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \parr B}}$}
     \DisplayProof
@@
 We named this relation ``disentanglement'' to reflect the intuition that proof in \hcp represent multiple entangled \cp proofs, which we can disentangle.
-However, this is not entirely accurate.
-The proof structure of \hcp is slightly richer than that of \cp.
-This can be seen in the example process above.
-In this case, when disentangling, we are forced to forget some of the proof structure.
-This can be seen in the last rule in \cref{fig:hcp-disentangle}.
-Nonetheless, the relation is type preserving, and so it suffices for showing that \hcp supports the same communication protocols as \cp.
 
@@
       \NOM{H-Mix$^\star$}
-      \TIC{$\seq[(P_1 \ppar \dots \ppar P_n)]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
+      \TIC{$\seq[(\mtf{P_1} \ppar \dots \ppar \mtf{P_n})]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}
     \end{prooftree*}
@@
   \item
-    if a mix gets stuck under a cut, it forms a \cp cut;
+    if a mix gets stuck above a cut, it forms a \cp cut;
   \item
-    if a mix gets stuck under a $(\tens)$, it forms a \cp $(\tens)$;
+    if a mix gets stuck above a $(\tens)$, it forms a \cp $(\tens)$;
   \item
-    otherwise, it moves all the way to the top.
+    otherwise, it moves all the way to the bottom.
   \end{enumerate*}

### 2018-12-23 doc/paper/main.tex
Weakened correspondence
More changes

@@
 \begin{abstract}
-% Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
-However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus.
+Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
+However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus: the fundamental operator for parallel composition does not correspond to any rule of linear logic.
 We introduce Hypersequent Classical Processes (\hcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
@@
 \end{definition}
+Note that we do not need to add a side condition to $\cpRedBetaTensParr$ to restrict its usage to the case where $\tm{y}$ is bound in $\tm{P}$ and $\tm{x}$ is bound in $\tm{Q}$, as this is true by definition of the send construct $\tm{\cpSend{x}{y}{P}{Q}}$.
 
@@
 \end{definition}
+Note that we have added the restriction ``acting on a bound channel'' to the case for links.
+This was not necessary for \cp, as all links in \cp act on at least one bound channel.
+Consequently, processes such as $\tm{\cpLink{x}{y}}$ and $\tm{(\piPar{\cpLink{x}{y}}{\cpLink{z}{w}})}$ are considered to be in canonical form.
+If this is objectionable, the reduction system can be extended with identity expansion, expanding, \eg the process $\tm{\cpLink{x^{\ty{\bot}}}{y}}$ to $\tm{\cpWait{x}{\cpHalt{y}}}$.
 \begin{corollary}
@@
   \)
-  such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
+  such that no $\tm{P_i}$ is a cut or a link acting on a bound channel, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
 The prefix of cuts and mixes introduces $n$ channels.
@@
 \begin{proof}
-  We consider the maximum prefix of cuts of $\tm{P}$ such that $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ and no $\tm{P_i}$ is a cut.
+  We consider the maximum prefix of cuts and mixes of $\tm{P}$ such that
+  \(
+  \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}},
+  \)
+  and no $\tm{P_i}$ is a cut.
 If any process $\tm{P_i}$ is a link, we reduce by $(\cpLink{}{})$.
@@
 \begin{theorem}\label{thm:cp2hcp-equiv}
-  $\tm{P}\equiv\tm{Q}$ in \cp iff $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
+  If $\tm{P}\equiv\tm{Q}$ in \cp, then $\tm{\mtf{P}}\equiv\tm{\mtf{Q}}$ in \hcp.
 \end{theorem} 

### 2018-12-25 doc/paper/main.tex
More rewrites

@@
 \begin{abstract}
-Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
-However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus: the fundamental operator for parallel composition does not correspond to any rule of linear logic.
-We introduce Hypersequent Classical Processes (\hcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
-We prove that \hcp enjoys deadlock-freedom and a series of properties that relate it back to \cp.
 \end{abstract}
@@
 
-\citet{kokke2019} introduced Hypersequent Classical Processes (\hcp), which addresses this mismatch.
+\citet{kokke2019} introduced Hypersequent Classical Processes (\dhcp), which addresses this mismatch.
 The key insight is to register parallelism in the typing judgements using hypersequents~\citep{avron1991}, a technique from logic which generalises judgements from one sequent to many.
 This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
-\hcp has labelled transition semantics with delayed actions~\citep{merro2004} and a full abstraction result: bisimilarity, denotational equivalence, and barbed congruence coincide.
+\dhcp has labelled transition semantics with delayed actions~\citep{merro2004} and a full abstraction result: bisimilarity, denotational equivalence, and barbed congruence coincide.
 
-However, the step from \cp to \hcp is a big one.
-As of yet, \hcp does not have reduction semantics, and the addition of delayed actions means that \cp processes interpreted as \hcp processes do not behave as they would in \cp.
+However, the step from \cp to \dhcp is a big one.
+As of yet, \dhcp does not have reduction semantics, and the addition of delayed actions means that \cp processes interpreted as \dhcp processes do not behave as they would in \cp.
 
-In this paper, we address these issues by introducing a variant of \hcp with reduction semantics and without delayed actions.
+In this paper, we address these issues by introducing \hcp, a variant of \dhcp with reduction semantics and without delayed actions.
 We proceed as follows.
@@
 Then, we introduce our variant of \hcp and prove it enjoys subject reduction and progress (\cref{sec:hcp}).
-We prove that every \cp process is an \hcp process, relate processes in \hcp back to \cp, and restate the result that \hcp supports the same communication protocols as \cp (\cref{sec:cp2hcp}).
+We prove that every \cp process is an \hcp process, relate processes in \hcp back to \cp, and prove that \hcp supports the same communication protocols as \cp (\cref{sec:cp2hcp}).
 Finally, we discuss related work (\cref{sec:related-work}).
@@
   Relations $\Longrightarrow^{+}$ and $\Longrightarrow^\star$ are the transitive, and the reflexive, transitive closures of $\Longrightarrow$, respectively.
-\end{definition}
-Note that we do not need to add a side condition to $\cpRedBetaTensParr$ to restrict its usage to the case where $\tm{y}$ is bound in $\tm{P}$ and $\tm{x}$ is bound in $\tm{Q}$, as this is true by definition of the send construct $\tm{\cpSend{x}{y}{P}{Q}}$.
+\end{definition}\noindent
+
+Note that we do not need to add a side condition to $\cpRedBetaTensParr$ to restrict its usage to the case where $\tm{y}$ is bound in $\tm{P}$ and $\tm{x}$ is bound in $\tm{Q}$, as this is required by the definition of the send construct $\tm{\cpSend{x}{y}{P}{Q}}$.
 
@@
 
-The crucial difference between \hcp as described here and \hcp as described by \citet{kokke2019} is in the absence of delayed actions.
+The crucial difference between \hcp as described here and \dhcp as described by \citet{kokke2019} is in the absence of delayed actions.
 However, removing delayed actions introduces self-locking processes, which we rule out using an extra restriction in the type system (see \cref{sec:hcp-types}).
@@
 Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''.
-This prevents self-locking processes, \eg $\tm{\piBoundSend{x}{}{\piRecv{x}{}{\piHalt}}}$.
+This prevents self-locking processes, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}
@@
 
+Note that the rules $(\with)$ and $(\top)$ disallow hyperenvironments.
+Allowing hyperenvironments in $(\with)$ would allow us to derive processes which are struck.
+For instance, the following process would be well-typed, but is stuck---even in the presence of delayed actions:
+\[
+\seq[{
+  \tm{\piNew{x^{\ty{\one \with \one}}}{\piNew{y^{\ty{\bot \plus \bot}}}{\left(
+          \begin{array}{l}
+            x \triangleright
+            \left\{
+            \begin{array}{l}
+              \texttt{inl}: (\cpInl{y}{\cpWait{y}{\cpHalt{z}}} \ppar \cpHalt{x});
+              \\
+              \texttt{inr}: (\cpInr{y}{\cpWait{y}{\cpHalt{z}}} \ppar \cpHalt{x})
+            \end{array}
+            \right\}
+            \ppar
+            \\
+            y \triangleright
+            \left\{
+            \begin{array}{l}
+              \texttt{inl}: (\cpInl{x}{\cpWait{x}{\cpHalt{w}}} \ppar \cpHalt{y});
+              \\
+              \texttt{inr}: (\cpInr{x}{\cpWait{x}{\cpHalt{w}}} \ppar \cpHalt{y})
+            \end{array}
+            \right\}
+          \end{array}
+        \right)}}}
+}]{
+  \tmty{z}{\one} \hsep \tmty{w}{\one}
+}
+\]
+Allowing hypersequents in $(\top)$ would lead to problems with \cref{lem:hcp-disentangle}.
+Intuitively, if we allowed the derivation $\seq[\cpAbsurd{x}]{\mathcal{G} \hsep \Gamma, \tmty{x}{\top}}$, we would claim that $\tm{\cpAbsurd{x}}$ ``consistst of $n$ independent, but potentially entangled processes'', which is clearly false.
+
 \subsection{Metatheory}
@@
 Consequently, processes such as $\tm{\cpLink{x}{y}}$ and $\tm{(\piPar{\cpLink{x}{y}}{\cpLink{z}{w}})}$ are considered to be in canonical form.
+This is a generalisation of \cp, where $\tm{\cpLink{x}{y}}$ is considered to be in canonical form.
 If this is objectionable, the reduction system can be extended with identity expansion, expanding, \eg the process $\tm{\cpLink{x^{\ty{\bot}}}{y}}$ to $\tm{\cpWait{x}{\cpHalt{y}}}$.
@@
 \begin{theorem}\label{hcp2cp-reduction}
-  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\reducesto{R}{\mtf{Q}}$ or $\tm{R}\equiv\tm{\mtf{Q}}$ in \hcp.
+  If $\reducesto{\mtf{P}}{R}$ in \hcp, then there is a $\tm{Q}$ such that $\reducesto{P}{Q}$ in \cp and $\tm{R}\equiv\tm{\mtf{Q}}$ in \hcp.
+
 \end{theorem} 
@@
       \BIC{$\seq[(\piRecv{x}{y}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \parr B}}$}
+      \DisplayProof
+    \\\\
+    \AXC{$\seq[P]{\mathcal{G}}$}
+    \AXC{$\seq[Q]{\mathcal{H}}$}
+    \NOM{H-Mix}
+    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H}}$}
+    \SYM{\one}
+    \UIC{$\seq[\piBoundSend{x}{}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \tmty{x}{\one}}$}
+    \DisplayProof
+    & \moveMixDown
+    & \AXC{$\seq[P]{\mathcal{G}}$}
+      \SYM{\one}
+      \UIC{$\seq[\piBoundSend{x}{}{P}]{\mathcal{G} \hsep \tmty{x}{\one}}$}
+      \AXC{$\seq[Q]{\mathcal{H}}$}
+      \NOM{H-Mix}
+      \BIC{$\seq[(\piBoundSend{x}{}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{\one}}$}
       \DisplayProof

### 2018-12-25 doc/paper/main.tex
Added abstract

@@
 \begin{abstract}
+  Process calculi based on logic, such as \piDILL and \cp, provide a foundation for deadlock-free concurrent programming.
+However, in previous work, there is a mismatch between the rules for constructing proofs and the term constructors of the \textpi-calculus: the fundamental operator for parallel composition does not correspond to any rule of linear logic.
+
+  \citet{kokke2019} introduced Hypersequent Classical Processes (\hcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
+  However, the step from \cp to \dhcp is a big one.
+As of yet, \dhcp does not have reduction semantics, and the addition of delayed actions means that \cp processes interpreted as \dhcp processes do not behave as they would in \cp.
+
+  We introduce \hcp, a variant of \dhcp with reduction semantics and without delayed actions.
+We prove progress, preservation, and termination, and show that \hcp supports the same communication protocols as \cp.
 \end{abstract}

### 2018-12-25 doc/paper/main.tex
Fix abstract

@@
 
-  \citet{kokke2019} introduced Hypersequent Classical Processes (\hcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
+  \citet{kokke2019} introduced Hypersequent Classical Processes (\dhcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
   However, the step from \cp to \dhcp is a big one.

### 2018-12-29 doc/paper/main.tex
Wrote draft conclusion

@@
 
+\section{Conclusions and Future Work}
+\label{sec:conclusion}
+In this paper, we introduced \hcp, a variant of \dhcp which sits in between \cp and \dhcp.
+It has reduction semantics, and does not allow for delayed actions, like \cp, but registers parallelism using hypersequents, like \dhcp.
+This results in a calculus which structurally resembles \dhcp, but which is behaviourally much more like \cp: all \cp processes can be translated to \hcp processes, and this translation preserves the reduction behaviour of the process.
+The key insight to making this calculus work is to add a side condition to the logical rules in the type system which rules out self-locking processes---processes which act on both endpoints of a channel, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
+
+\hcp focuses on the basic features of \cp, corresponding to multiplicative applicative linear logic.
+In the future, we intend to study the full version of \hcp, which includes exponentials and quantifiers.
+Furthermore, we intend to study extensions to \hcp which capture more behaviours, such as recursive types~\citep{lindley2016} and access points~\citep{gay2009}.
+Separately, we would like to extend the reduction semantics of \hcp to cover all of \dhcp by adding delayed actions.
+
 \clearpage

### 2019-02-01 doc/paper/main.tex
Minor changes
Fixed disentanglement relation
Added definition for "actions"

@@
 Note that this is a single term constructor, which takes all four arguments at the same time.
-This is caused by directly adopting the $(\tens)$-rule from CLL as the process calculus construct for sending: the $(\tens)$-rule has two premises (corresponding to $\tm P$ and $\tm Q$ in the output term), and checks that they share no resources (in the output term, $\tm x$ can be used only by $\tm P$, and $\tm y$ can be used only by $\tm Q$).
+This is caused by directly adopting the $(\tens)$-rule from CLL as the process calculus construct for sending: the $(\tens)$-rule has two premises (corresponding to $\tm P$ and $\tm Q$ in the output term), and checks that they share no resources (in the output term, $\tm y$ can be used only by $\tm P$, and $\tm x$ can be used only by $\tm Q$).
 
@@
 \end{proof}
+\begin{definition}[Actions]
+  A process $\tm{P}$ acts on $\tm{x}$ whenever $\tm{x}$ is free in the outermost
+  term constructor of $\tm{P}$, \eg $\tm{\cpSend{x}{y}{P}{Q}}$ acts on $\tm{x}$
+  but not on $\tm{y}$, and $\tm{\cpLink{x}{y}}$ acts on both $\tm{x}$ and $\tm{y}$.
+  A process $\tm{P}$ is an action if it acts on some channel $\tm{x}$.
+\end{definition}
 \begin{definition}[Canonical forms]
@@
 Note that the rules $(\with)$ and $(\top)$ disallow hyperenvironments.
-Allowing hyperenvironments in $(\with)$ would allow us to derive processes which are struck.
+Allowing hyperenvironments in $(\with)$ would allow us to derive processes which are stuck.
 For instance, the following process would be well-typed, but is stuck---even in the presence of delayed actions:
@@
     \AXC{$\seq[P]{\mathcal{G}}$}
-    \AXC{$\seq[Q]{\mathcal{H}}$}
-    \NOM{H-Mix}
-    \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H}}$}
     \SYM{\one}
-    \UIC{$\seq[\piBoundSend{x}{}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \tmty{x}{\one}}$}
+    \UIC{$\seq[\piBoundSend{x}{}{P}]{\mathcal{G} \hsep \tmty{x}{\one}}$}
     \DisplayProof
     & \moveMixDown
-    & \AXC{$\seq[P]{\mathcal{G}}$}
+    & \AXC{}
+      \NOM{H-Mix$_0$}
+      \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
       \SYM{\one}
-      \UIC{$\seq[\piBoundSend{x}{}{P}]{\mathcal{G} \hsep \tmty{x}{\one}}$}
-      \AXC{$\seq[Q]{\mathcal{H}}$}
+      \UIC{$\seq[\piBoundSend{x}{}{0}]{\tmty{x}{\one}}$}
+      \AXC{$\seq[P]{\mathcal{G}}$}
       \NOM{H-Mix}
-      \BIC{$\seq[(\piBoundSend{x}{}{P} \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{\one}}$}
+      \BIC{$\seq[(\piBoundSend{x}{}{\piHalt} \ppar P)]{\mathcal{G} \hsep \tmty{x}{\one}}$}
       \DisplayProof
@@
 
-\clearpage
 \bibliographystyle{apalike}
@@
 %%% End:
-
-% LocalWords:  labelled

### 2019-02-10 doc/paper/main.tex
Final version

@@
 \usepackage[all]{foreign}
-\usepackage{amsmath}
+\usepackage{amsmath,amsthm,amssymb}
 \allowdisplaybreaks
-\usepackage{amsthm}
-\usepackage{amssymb}
 \def\Coloneqq{\mathbin{::=}}
@@
 \usepackage{breakurl} % Not needed if you use pdflatex only.
-\usepackage{underscore} % Only needed if you use pdflatex.
-\usepackage{textcomp,textgreek,upgreek}
+\usepackage{textcomp,textgreek,upgreek,stmaryrd}
 \usepackage{nameref,hyperref}
+\usepackage[dvipsnames,table]{xcolor}
+\usepackage{scalerel}
+\usepackage{rotating}
+\usepackage{centernot}
+\usepackage{xspace}
+\xspaceaddexceptions{]\}}
 \usepackage[nameinlink,noabbrev,capitalize]{cleveref}
@@
       \end{array}
-    \\
+      \\[1\baselineskip]
       \begin{prooftree*}
@@
   A process $\tm{P}$ is in canonical form if
-  \(
+  \[
     \tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}},
-  \)
+  \]
   such that: no process $\tm{P_i}$ is a cut; no process $\tm{P_i}$ is a link acting on a bound channel $\tm{x_i}$; and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel $\tm{x_i}$.
@@
 \begin{proof}
-  We have $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$ such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
+  We have
+  \[
+  \tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}
+  \]
+  such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
 The prefix of cuts introduces $n$ channels, and $n+1$ processes.
@@
 \begin{definition}[Reduction]\label{def:hcp-reduction}
-  Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under the rules in \cref{fig:hcp-reduction}. 
-  Relations $\Longrightarrow^{+}$ and $\Longrightarrow^\star$ are the transitive, and the reflexive, transitive closures of $\Longrightarrow$, respectively.
-\end{definition}
-\begin{figure}[htb]
+  Reductions are described by the smallest relation $\Longrightarrow$ on process
+  terms closed under the rules below:
   \begin{gather*}
@@
     \end{array}
-    \\
+    \\[1\baselineskip]
     \begin{prooftree*}
@@
   \end{gather*}  
-  \caption{Hypersequent Classical Processes, reduction relation.}
-  \label{fig:hcp-reduction}
-\end{figure}
+  Relations $\Longrightarrow^{+}$ and $\Longrightarrow^\star$ are the transitive, and the reflexive, transitive closures of $\Longrightarrow$, respectively.
+\end{definition}
 
@@
   A process $\tm{P}$ is in canonical form if
-  \(
+  \[
   \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \mid \dots \mid P_{n+m+1})}}},
-  \)
+  \]
   such that: no process $\tm{P_i}$ is a cut or a mix; no process $\tm{P_i}$ is a link acting on a bound channel $\tm{x_i}$; and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel $\tm{x_i}$.
@@
   We have
-  \(
+  \[
   \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}},
-  \)
+  \]
   such that no $\tm{P_i}$ is a cut or a link acting on a bound channel, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
@@
   We consider the maximum prefix of cuts and mixes of $\tm{P}$ such that
-  \(
+  \[
   \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}},
-  \)
+  \]
   and no $\tm{P_i}$ is a cut.

### 2019-02-11 doc/paper/main.tex
Switch to EPTCS style in progress
Inserted author names verbatim because sigh

@@
 \providecommand{\event}{Linearity and TLLA 2018}
+\usepackage{url,doi}
 \usepackage[british]{babel}
@@
 \def\coloneqq{\mathbin{:=}}
-\usepackage[inline]{enumitem}
+\usepackage[inline]{enumitem}%
 \usepackage{breakurl} % Not needed if you use pdflatex only.
@@
 \input{preamble-typing}
-\usepackage[sectionbib,sort&compress]{natbib}
+\usepackage[sectionbib,sort&compress,numbers]{natbib}
 
@@
 
-  \citet{kokke2019} introduced Hypersequent Classical Processes (\dhcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
+  Kokke \etal~\cite{kokke2019} introduced Hypersequent Classical Processes (\dhcp), which addresses this mismatch using hypersequents (collections of sequents) to register parallelism in the typing judgements.
   However, the step from \cp to \dhcp is a big one.
@@
 
-Classical Processes (\cp) \citep{wadler2012} is a process calculus inspired by the correspondence between the session-typed \textpi-calculus and linear logic \citep{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
+Classical Processes (\cp) \cite{wadler2012} is a process calculus inspired by the correspondence between the session-typed \textpi-calculus and linear logic \cite{caires2010}, where processes correspond to proofs, session types (communication protocols) to propositions, and communication to cut elimination.
 This correspondence allows for exchanging methods between the two fields.
-For example, the proof theory of linear logic can be used to guarantee progress for processes \citep{caires2010,wadler2012}.
+For example, the proof theory of linear logic can be used to guarantee progress for processes \cite{caires2010,wadler2012}.
 
@@
 This permits us to reuse the metatheory of linear logic ``as is'' to reason about the behaviour of processes.
-However, there is a mismatch between the structure of the proof terms of CLL and the term constructs of the standard \textpi-calculus~\citep{milner1992a,milner1992b}.
+However, there is a mismatch between the structure of the proof terms of CLL and the term constructs of the standard \textpi-calculus~\cite{milner1992a,milner1992b}.
 For instance, the term for output of a linear name is $\tm{\cpSend{x}{y}{P}{Q}}$, which is read ``send $y$ over $x$ and proceed as $P$ in parallel to $Q$''.
@@
 Instead, parallel composition shows up in any term which corresponds to a typing rule which splits the context.
-Even if we were to add an independent parallel composition via the \textsc{Mix}-rule, as suggested in the original presentation of \cp~\citep{wadler2012}, there would be no way to allow the composed process $\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as there is no independent name restriction either!
+Even if we were to add an independent parallel composition via the \textsc{Mix}-rule, as suggested in the original presentation of \cp~\cite{wadler2012}, there would be no way to allow the composed process $\tm{P}$ and $\tm{Q}$ to communicate as in the standard \textpi-calculus, as there is no independent name restriction either!
 Instead, synchronisation is governed by the ``cut'' operator $\tm{\piNew{x}{(\piPar{P}{Q})}}$, which composes $\tm{P}$ and $\tm{Q}$, enabling them to communicate along $\tm{x}$.
@@
 
-\citet{kokke2019} introduced Hypersequent Classical Processes (\dhcp), which addresses this mismatch.
-The key insight is to register parallelism in the typing judgements using hypersequents~\citep{avron1991}, a technique from logic which generalises judgements from one sequent to many.
+Kokke \etal~\cite{kokke2019} introduced Hypersequent Classical Processes (\dhcp), which addresses this mismatch.
+The key insight is to register parallelism in the typing judgements using hypersequents~\cite{avron1991}, a technique from logic which generalises judgements from one sequent to many.
 This allows us to take apart the term constructs used in Classical Processes (\cp) to more closely match those of the standard \textpi-calculus.
-\dhcp has labelled transition semantics with delayed actions~\citep{merro2004} and a full abstraction result: bisimilarity, denotational equivalence, and barbed congruence coincide.
+\dhcp has labelled transition semantics with delayed actions~\cite{merro2004} and a full abstraction result: bisimilarity, denotational equivalence, and barbed congruence coincide.
 
@@
 The variables $\tm{x}$, $\tm{y}$, and $\tm{z}$ range over channel names.
-The construct $\tm{\cpLink{x}{y}}$ links two channels~\citep{sangiorgi1996,boreale1998}, forwarding messages received on $\tm{x}$ to $\tm{y}$ and vice versa.
+The construct $\tm{\cpLink{x}{y}}$ links two channels~\cite{sangiorgi1996,boreale1998}, forwarding messages received on $\tm{x}$ to $\tm{y}$ and vice versa.
 The construct $\tm{\cpCut{x}{P}{Q}}$ creates a new channel $\tm{x}$, and composes two processes, $\tm{P}$ and $\tm{Q}$, which communicate on $\tm{x}$, in parallel.
@@
 In $\tm{\cpRecv{x}{y}{P}}$ and $\tm{\cpSend{x}{y}{P}{Q}}$, round brackets denote input, square brackets denote output.
-\cp uses bound output~\citep{sangiorgi1996}, meaning that both input and output bind a new name.
+\cp uses bound output~\cite{sangiorgi1996}, meaning that both input and output bind a new name.
 In $\tm{\cpRecv{x}{y}{P}}$ the new name $\tm{y}$ is bound in $\tm{P}$.
@@
 \end{definition}\noindent
-The reduction semantics presented here are a variant of those presented by \citet{lindley2015}, who showed that reduction in \cp can be decomposed in two phases: one in which all \textbeta-reduction happens, and one in which an arbitrary action, blocked on an external communication, is moved to the top of the term using commuting conversions.
+The reduction semantics presented here are a variant of those presented by
+Lindley and Morris~\cite{lindley2015}, who showed that reduction in \cp can be decomposed in two phases: one in which all \textbeta-reduction happens, and one in which an arbitrary action, blocked on an external communication, is moved to the top of the term using commuting conversions.
 We choose to stop after the first phase, and do away with the commuting conversions.
@@
 \subsection{Metatheory}
-\cp enjoys subject reduction, termination, and progress~\citep{wadler2012}.
+\cp enjoys subject reduction, termination, and progress~\cite{wadler2012}.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
@@
 
-The crucial difference between \hcp as described here and \dhcp as described by \citet{kokke2019} is in the absence of delayed actions.
+The crucial difference between \hcp as described here and \dhcp as described by Kokke \etal~\cite{kokke2019} is in the absence of delayed actions.
 However, removing delayed actions introduces self-locking processes, which we rule out using an extra restriction in the type system (see \cref{sec:hcp-types}).
@@
 
-Since its inception, linear logic has been described as the logic of concurrency \citep{girard1987}.
-Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \citep{abramsky1994,bellin1994}, by interpreting linear propositions as types for channels.
-Linearity inspired also the seminal theories of linear types for the \textpi-calculus \citep{kobayashi1999} and session types \citep{honda1998}.
-Even though the two theories do not have a direct correspondence with linear logic, the link is still strong enough that session types can be encoded into linear types \citep{dardha2017}.
-
-It took more than ten years for a formal correspondence between linear logic and (a variant of) session types to emerge, with the seminal paper by \citet{caires2010}.
-This inspired the development of Classical Processes by \citet{wadler2012}.
-
-The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: \citet{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies.
-This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in \citet{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
+Since its inception, linear logic has been described as the logic of concurrency \cite{girard1987}.
+Correspondences between the proof theory of linear logic and variants of the \textpi-calculus emerged soon afterwards \cite{abramsky1994,bellin1994}, by interpreting linear propositions as types for channels.
+Linearity inspired also the seminal theories of linear types for the \textpi-calculus \cite{kobayashi1999} and session types \cite{honda1998}.
+Even though the two theories do not have a direct correspondence with linear logic, the link is still strong enough that session types can be encoded into linear types \cite{dardha2017}.
+
+It took more than ten years for a formal correspondence between linear logic and (a variant of) session types to emerge, with the seminal paper by Caires and Pfenning~\cite{caires2010}.
+This inspired the development of Classical Processes by Wadler~\cite{wadler2012}.
+
+The idea of using hypersequents to capture parallelism in linear logic judgements is not novel: Carbone \etal~\cite{carbone2018} extended the multiplicative-additive fragment of intuitionistic linear logic with hypersequents to type global descriptions of process communications known as choreographies.
+This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in Carbone \etal~\cite{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
 
@@
 In the future, we intend to study the full version of \hcp, which includes exponentials and quantifiers.
-Furthermore, we intend to study extensions to \hcp which capture more behaviours, such as recursive types~\citep{lindley2016} and access points~\citep{gay2009}.
+Furthermore, we intend to study extensions to \hcp which capture more behaviours, such as recursive types~\cite{lindley2016} and access points~\cite{gay2009}.
 Separately, we would like to extend the reduction semantics of \hcp to cover all of \dhcp by adding delayed actions.
 
-\bibliographystyle{apalike}
+\bibliographystyle{eptcs}
 \bibliography{main}

### 2019-06-03 doc/paper/main.tex
Fixed proof rules and rule names

@@
 \subsection{Metatheory}
-\cp enjoys subject reduction, termination, and progress~\cite{wadler2012}.
+\cp enjoys subject reduction, termination, and progress~\cite{wadler2012,lindley2015}.
 \begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
@@
   \end{center}
-  Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
 \end{definition}\noindent
 
-Note that the rules $(\with)$ and $(\top)$ disallow hyperenvironments.
-Allowing hyperenvironments in $(\with)$ would allow us to derive processes which are stuck.
-For instance, the following process would be well-typed, but is stuck---even in the presence of delayed actions:
-\[
-\seq[{
-  \tm{\piNew{x^{\ty{\one \with \one}}}{\piNew{y^{\ty{\bot \plus \bot}}}{\left(
-          \begin{array}{l}
-            x \triangleright
-            \left\{
-            \begin{array}{l}
-              \texttt{inl}: (\cpInl{y}{\cpWait{y}{\cpHalt{z}}} \ppar \cpHalt{x});
-              \\
-              \texttt{inr}: (\cpInr{y}{\cpWait{y}{\cpHalt{z}}} \ppar \cpHalt{x})
-            \end{array}
-            \right\}
-            \ppar
-            \\
-            y \triangleright
-            \left\{
-            \begin{array}{l}
-              \texttt{inl}: (\cpInl{x}{\cpWait{x}{\cpHalt{w}}} \ppar \cpHalt{y});
-              \\
-              \texttt{inr}: (\cpInr{x}{\cpWait{x}{\cpHalt{w}}} \ppar \cpHalt{y})
-            \end{array}
-            \right\}
-          \end{array}
-        \right)}}}
-}]{
-  \tmty{z}{\one} \hsep \tmty{w}{\one}
-}
-\]
-Allowing hypersequents in $(\top)$ would lead to problems with \cref{lem:hcp-disentangle}.
-Intuitively, if we allowed the derivation $\seq[\cpAbsurd{x}]{\mathcal{G} \hsep \Gamma, \tmty{x}{\top}}$, we would claim that $\tm{\cpAbsurd{x}}$ ``consistst of $n$ independent, but potentially entangled processes'', which is clearly false.
+Note that the logical rules disallow hyperenvironments.
 
@@
         \AXC{$\seq[Q]{\Delta, \tmty{x}{B}}$}
-        \SYM{\tens}
+        \SYM{(\tens)}
         \BIC{$\seq[\cpSend{x}{y}{P}{Q}]{\Gamma, \Delta, \tmty{x}{A \tens B}}$}
@@
           \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
-          \SYM{\tens}
+          \SYM{(\tens)}
           \UIC{$\seq[\piBoundSend{x}{y}{(\piPar{\mtf{P}}{\mtf{Q}})}]{
@@
       \begin{array}{lcl}
-        \AXC{}\SYM{\one}
+        \AXC{}\SYM{(\one)}
         \UIC{$\seq[\cpHalt{x}]{\tmty{x}{\one}}$}
@@
           \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
-          \SYM{\one}
+          \SYM{(\one)}
           \UIC{$\seq[\piBoundSend{x}{}{\piHalt}]{\tmty{x}{\one}}$}
@@
     \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
-    \SYM{\tens}
+    \SYM{(\tens)}
     \UIC{$\seq[\piBoundSend{x}{y}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta, \tmty{x}{A \tens B}}$}
@@
     & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{y}{A} \hsep \Delta, \tmty{x}{B}}$}
-      \SYM{\tens}
+      \SYM{(\tens)}
       \UIC{$\seq[\piBoundSend{x}{y}{P}]{\mathcal{G} \hsep \Gamma, \Delta, \tmty{x}{A \tens B}}$}
@@
     \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{y}{A}, \tmty{x}{B}}$}
-    \SYM{\parr}
+    \SYM{(\parr)}
     \UIC{$\seq[(\piRecv{x}{y}{(P \ppar Q)})]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \parr B}}$}
@@
     & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{y}{A}, \tmty{x}{B}}$}
-      \SYM{\parr}
+      \SYM{(\parr)}
       \UIC{$\seq[\piRecv{x}{y}{P}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \parr B}}$}
@@
     \AXC{$\seq[P]{\mathcal{G}}$}
-    \SYM{\one}
+    \SYM{(\one)}
     \UIC{$\seq[\piBoundSend{x}{}{P}]{\mathcal{G} \hsep \tmty{x}{\one}}$}
@@
       \UIC{$\seq[\piHalt]{\emptyhypercontext}$}
-      \SYM{\one}
+      \SYM{(\one)}
       \UIC{$\seq[\piBoundSend{x}{}{0}]{\tmty{x}{\one}}$}
@@
     \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma}$}
-    \SYM{\bot}
+    \SYM{(\bot)}
     \UIC{$\seq[\piRecv{x}{}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{\bot}}$}
@@
     & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma}$}
-      \SYM{\bot}
+      \SYM{(\bot)}
       \UIC{$\seq[\piRecv{x}{}{P}]{\mathcal{G} \hsep \Gamma, \tmty{x}{\bot}}$}
@@
     \BIC{$\seq[(P \ppar Q)]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A}}$}
-    \SYM{\plus_1}
+    \SYM{(\plus_1)}
     \UIC{$\seq[\cpInl{x}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \tmty{x}{A \plus B}}$}
@@
     & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A}}$}
-      \SYM{\plus_1}
+      \SYM{(\plus_1)}
       \UIC{$\seq[\cpInl{x}{P}]{\mathcal{G} \hsep \Gamma, \tmty{x}{A \plus B}}$}

### 2019-06-03 doc/paper/main.tex
Rewrote section explaining why no hyperenvironments for logical rules

@@
   \end{center}
-\end{definition}\noindent
-
-Note that the logical rules disallow hyperenvironments.
+\end{definition}
+Note that the logical rules disallow hyperenvironments. If they did not, the following processes would be well-typed, even though they are stuck:
+\begin{center}
+  \begin{prooftree*}
+    \noLine\AXC{$\vphantom{\Gamma}$}\UIC{$\vphantom{\Gamma}$}
+    \NOM{H-Mix$_0$}
+    \UIC{$\seq
+      [\piHalt]
+      {\emptyhypercontext}$}
+    \SYM{(\one)}
+    \UIC{$\seq
+      [\piBoundSend{z}{}{\piHalt}]
+      {\tmty{z}{\one}}$}
+    \SYM{(\one)}
+    \UIC{$\seq
+      [\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}]
+      {\tmty{x}{\one} \hsep \tmty{z}{\one}}$}
+    \SYM{(\bot)}
+    \UIC{$\seq
+      [\piRecv{x}{}{\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}}]
+      {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
+    \NOM{Cut}
+    \UIC{$\seq
+      [\piNew{x}{(\piRecv{x}{}{\piBoundSend{x}{}{\piBoundSend{z}{}{\piHalt}}})}]
+      {\tmty{z}{\one}}$}
+  \end{prooftree*}\hspace*{-1.75em}%
+  \begin{prooftree*}
+    \AXC{}
+    \NOM{H-Mix$_0$}
+    \UIC{$\seq
+      [{\piHalt}]
+      {\emptyhypercontext}$}
+    \SYM{(\one)}
+    \UIC{$\seq
+      [\piBoundSend{y}{}{\piHalt}]
+      {\tmty{y}{\one}}$}
+    \SYM{(\one)}
+    \UIC{$\seq
+      [\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}]
+      {\tmty{x}{\one} \hsep \tmty{y}{\one}}$}
+    \AXC{}
+    \NOM{Ax}
+    \UIC{$\seq
+      [\cpLink{x}{z}]
+      {\tmty{x}{\bot}, \tmty{z}{\one}}$}
+    \SYM{(\bot)}
+    \UIC{$\seq
+      [\piRecv{y}{}{\cpLink{x}{z}}]
+      {\tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
+    \NOM{H-Mix}
+    \BIC{$\seq
+      [(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})]
+      {\tmty{x}{\one} \hsep \tmty{y}{\one} \hsep \tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
+    \NOM{Cut}
+    \UIC{$\seq
+      [\piNew{y}{(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})}]
+      {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
+    \NOM{Cut}
+    \UIC{$\seq
+      [\piNew{x}{\piNew{y}{(\piPar{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}{\piRecv{y}{}{\cpLink{x}{z}}})}}]
+      {\tmty{z}{\one}}$}
+  \end{prooftree*}
+\end{center}
+The first process is self-locking, in that it holds both endpoints of a channel in the same process, and hence communication can never happen.
+Self-locking processes can be ruled out by requiring that the two endpoints of a channel are held in different processes.
+
+The second term is more complicated: it is not a self-lock, and not a traditional deadlock, where two processes are waiting on each other.
+However, it is definitely stuck.
+The problem lies with readiness: a process typed under a hyperenvironment $\ty{\Gamma_1}\hsep\dots\hsep\ty{\Gamma_n}$, it promises to act as, essentially, $n$ independent processes, each of which ready to act on a channel from $\ty{\Gamma_i}$.
+However, the process $\tm{\piBoundSend{x}{}{\piBoundSend{y}{}{\piHalt}}}$, a single process, can be typed under the hyperenvironment $\ty{\tmty{x}{\one} \hsep \tmty{y}{\one}}$, which consists of \emph{two} environments.
+We can abuse this failure of readiness by asking the process to communicate on $\tm{y}$, which it is incapable of doing immediately.
+This is not a property of the $(\one)$ rule allowing hyperenvironments.
+For instance, a similar example can be constructed using the $(\tens)$ rule.
 

### 2019-06-04 doc/paper/main.tex
Rewrote paper to fix error
ref to classical transitions

@@
 
-In this section, we introduce our variant of Hypersequent Classical Processes (\hcp), itself a variant of \cp which registers parallelism in the typing judgements using hypersequents, allowing us to take apart the monolithic term constructors of \cp (\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term constructs.
+We introduce our variant of Hypersequent Classical Processes (\hcp), itself a variant of \cp which registers parallelism in the typing judgements using hypersequents, allowing us to take apart the monolithic term constructors of \cp (\eg $\tm{\cpSend{x}{y}{P}{Q}}$) into the corresponding \textpi-calculus term constructs.
 
 The crucial difference between \hcp as described here and \dhcp as described by Kokke \etal~\cite{kokke2019} is in the absence of delayed actions.
-However, removing delayed actions introduces self-locking processes, which we rule out using an extra restriction in the type system (see \cref{sec:hcp-types}).
-Furthermore, we follow \cp in using the same name for both endpoints of a channel, writing, \eg $\tm{\cpCut{x}{\cpHalt{x}}{\cpWait{x}{P}}}$ as opposed to $\tm{\cpCut{xy}{\cpHalt{x}}{\cpWait{y}{P}}}$.
+However, removing delayed actions from \dhcp introduces self-locking processes, which we rule out by adopting (with minor changes) the type system first introduced by Montesi and Peressotti in \cite{montesi2018} (see \cref{sec:hcp-types}).
+Differently from \loccit, we follow \cp in using the same name for both endpoints of a channel, writing, \eg $\tm{\cpCut{x}{\cpHalt{x}}{\cpWait{x}{P}}}$ as opposed to $\tm{\cpCut{xy}{\cpHalt{x}}{\cpWait{y}{P}}}$.
 
@@
   \\[1\baselineskip]
-  {Structural rules}
+  {Structural rules} %\vspace{-3ex}
   \begin{center}
@@
   \end{center}
-  {Logical rules}
+%  \vspace{.3ex}
+  {Logical rules} %\vspace{-3ex}
   \begin{center}
@@
 \end{definition}
-Note that the logical rules disallow hyperenvironments. If they did not, the following processes would be well-typed, even though they are stuck:
+Note that the logical rules disallow hyperenvironments. If they did not, the following processes would be well-typed, even though they are stuck (unless we allow delayed actions as in \dhcp):
 \begin{center}
@@
   \end{prooftree*}
-\end{center}
-The first process is self-locking, in that it holds both endpoints of a channel in the same process, and hence communication can never happen.
-Self-locking processes can be ruled out by requiring that the two endpoints of a channel are held in different processes.
-
-The second term is more complicated: it is not a self-lock, and not a traditional deadlock, where two processes are waiting on each other.
+\end{center}\vspace{.5\belowdisplayskip}
+
+The first process is self-locking, in that it holds both endpoints of a channel in the same process, and hence communication can never happen in a semantic without delayed and self-synchronising actions.
+Self-locking processes can be ruled out by requiring that the two endpoints of a channel are held in different processes \ie appear in distinct hypersequents.
+
+The second term is not self-locked, nor a deadlock where two processes are waiting on each other.
 However, it is definitely stuck.
@@
 This is not a property of the $(\one)$ rule allowing hyperenvironments.
-For instance, a similar example can be constructed using the $(\tens)$ rule.
+Similar examples can be constructed using the $(\tens)$ rule.
 
@@
   A process $\tm{P}$ is in canonical form if
-  \[
+ $
   \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \mid \dots \mid P_{n+m+1})}}},
-  \]
+  $
   such that: no process $\tm{P_i}$ is a cut or a mix; no process $\tm{P_i}$ is a link acting on a bound channel $\tm{x_i}$; and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel $\tm{x_i}$.
@@
   We have
-  \[
+  $
   \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}},
-  \]
+  $
   such that no $\tm{P_i}$ is a cut or a link acting on a bound channel, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
@@
 \begin{definition}\label{def:hcp-disentangle}
-  Disentanglement is described by the smallest relation $\moveMixDown$ on processes closed under the rules in \cref{fig:hcp-disentangle}, plus the structural congruence $\equiv$.
+  Disentanglement is the smallest relation $\moveMixDown$ on processes closed under the rules in \cref{fig:hcp-disentangle}, plus the structural congruence $\equiv$.
 The relation $\moveMixDown^\star$ is the reflexive, transitive closure of $\moveMixDown$.
@@
 This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in Carbone \etal~\cite{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
+Montesi and Peressotti \cite{montesi2018} revisited \cp in the light of hypersequents to derive the first correspondence between the labelled transition system semantics on proof transformations, later refined in \cite{kokke2019}.
+The type system of \hcp is that of \cite{montesi2018} save for rule \textsc{H-Mix\textsubscript{0}} which is from \cite{kokke2019}.
+This is difference means that \cite{montesi2018} does not enjoy the translation to CLL that \hcp and \dhcp enjoy.
 

### 2019-06-14 doc/paper/main.tex
small fix to H-Cut

@@
-\documentclass[submission,copyright,creativecommons]{eptcs}
+\documentclass[copyright,creativecommons]{eptcs}
 \providecommand{\event}{Linearity and TLLA 2018}
@@
 
+\usepackage[framemethod=tikz]{mdframed}
+\newenvironment{changed}
+	{\mdframed[hidealllines=true,backgroundcolor=black!20]}
+	{\endmdframed}
+
 \title{Taking Linear Logic Apart}
@@
 \textsc{H-Mix} composes two processes in parallel, but remembers that they are independent in the sequent.
-\textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar.
-Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$, which can be read as ``you cannot act on one end-point of $x$ if you are also holding its other end-point''.
-This prevents self-locking processes, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
+\textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar (the side condition $\tm{x} \not\in \ty{\mathcal{G}}$ ensures that sessions are binary).
+%This prevents self-locking processes, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}

### 2019-07-13 doc/paper/main.tex
minor fixes

@@
 \begin{proof}
-  We have
-  \[
-  \tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}
-  \]
+  We have $\tm{P} \equiv \tm{\cpCut{x_1}{P_1}{\dots\cpCut{x_n}{P_n}{P_{n+1}}\dots}}$
   such that no $\tm{P_i}$ is a cut or a link, and no two processes $\tm{P_i}$ and $\tm{P_j}$ are acting on the same bound channel.
@@
 \textsc{H-Cut} and $(\tens)$ take as their premise a process which consists of at least two independent processes, and connects them, eliminating the vertical bar (the side condition $\tm{x} \not\in \ty{\mathcal{G}}$ ensures that sessions are binary).
-%This prevents self-locking processes, \eg $\tm{\piRecv{x}{}{\piBoundSend{x}{}{\piHalt}}}$.
 \begin{definition}[Typing judgements]\label{def:hcp}
@@
   \end{center}
+We shall omit the side condition $\tm{x} \not\in \ty{\mathcal{G}}$ in applications of rule \textsc{H-Cut} whenever $\ty{\mathcal{G}}$ is empty.
 \end{definition}
@@
       {\tmty{x}{\one} \hsep \tmty{x}{\bot}, \tmty{z}{\one}}$}
-    \NOM{Cut}
+    \NOM{H-Cut}
     \UIC{$\seq
@@
       {\tmty{z}{\one}}$}
-  \end{prooftree*}\hspace*{-1.75em}%
+  \end{prooftree*}\hspace*{-1.85em}%
   \begin{prooftree*}
@@
       {\tmty{x}{\one} \hsep \tmty{y}{\one} \hsep \tmty{x}{\bot}, \tmty{y}{\bot}, \tmty{z}{\one}}$}
-    \NOM{Cut}
+    \NOM{H-Cut}
     \UIC{$\seq
@@
   We consider the maximum prefix of cuts and mixes of $\tm{P}$ such that
-  \[
-  \tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}},
-  \]
+  $\tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}}$,
   and no $\tm{P_i}$ is a cut.
@@
   \begin{array}{lcr}
+    \AXC{$\tm{x} \not\in \ty{(\mathcal{G} \hsep \mathcal{H})}$}
     \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
@@
     \NOM{H-Cut}
-    \UIC{$\seq[\piNew{x}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
+    \BIC{$\seq[\piNew{x}{(P \ppar Q)}]{\mathcal{G} \hsep \mathcal{H} \hsep \Gamma, \Delta}$}
     \DisplayProof
@@
     & \AXC{$\seq[P]{\mathcal{G} \hsep \Gamma, \tmty{x}{A} \hsep \Delta, \tmty{x}{A^\bot}}$}
+      \AXC{$\tm{x} \not\in \ty{\mathcal{G}}$}
       \NOM{H-Cut}
-      \UIC{$\seq[\piNew{x}{P}]{\mathcal{G} \hsep \Gamma, \Delta}$}
+      \BIC{$\seq[\piNew{x}{P}]{\mathcal{G} \hsep \Gamma, \Delta}$}
       \AXC{$\seq[Q]{\mathcal{H}}$}
@@
       \AXC{$\seq[\mtf{P_n}]{\Gamma_n}$}
-      \NOM{H-Mix$^\star$}
+      \doubleLine
+      \NOM{H-Mix}
       \TIC{$\seq[(\mtf{P_1} \ppar \dots \ppar \mtf{P_n})]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$}

### 2019-07-13 doc/paper/eptcsdata.tex
EPTCS metadata & "revised version" subtitle

\providecommand{\firstpage}{90}
\providecommand{\publicationstatus}{T. Ehrhard, M. Fern\'andez, V. de Paiva, L. Tortora de Falco (Eds.):\\ Linearity-TLLA 2018\\
EPTCS 292, 2019, pp.\ \pageref*{FirstPage}--\pageref{LastPage},
doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}}

### 2019-07-17 doc/paper/main.tex
EPTCS metadata & "revised version" subtitle
minor changes
erratum

@@
 \usepackage{xspace}
+\usepackage[normalem]{ulem}
 \xspaceaddexceptions{]\}}
@@
 
-\usepackage[framemethod=tikz]{mdframed}
-\newenvironment{changed}
-	{\mdframed[hidealllines=true,backgroundcolor=black!20]}
-	{\endmdframed}
-
-\title{Taking Linear Logic Apart}
+\title{Taking Linear Logic Apart\\{\large Post-publication version: 2019-07-17}}
 \author{%
@@
   \end{center}
-We shall omit the side condition $\tm{x} \not\in \ty{\mathcal{G}}$ in applications of rule \textsc{H-Cut} whenever $\ty{\mathcal{G}}$ is empty.
+%We shall omit the side condition $\tm{x} \not\in \ty{\mathcal{G}}$ in applications of rule \textsc{H-Cut} whenever $\ty{\mathcal{G}}$ is empty.
 \end{definition}
@@
   We consider the maximum prefix of cuts and mixes of $\tm{P}$ such that
-  $\tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}}$,
+  \[\tm{P} \equiv \tm{\piNew{x_1}{\dots\piNew{x_n}{(P_1 \ppar \dots \ppar P_{n+m+1})}}}\text{,}\]
   and no $\tm{P_i}$ is a cut.
@@
 \bibliography{main}
+
+\appendix
+\clearpage
+\pagenumbering{Roman} 
+\setcounter{page}{1}
+
+\section*{Erratum}
+
+\makeatletter
+\def\cb#1#2#3{{\fboxsep=0pt\colorbox{#1}{\vphantom{\uline{#3}}#2{#3}}}}
+\def\defann#1#2{%
+	\expandafter\def\csname#1\endcsname{%
+		\def\ann@####1{\hbox{#2{\ensuremath{####1}}}}%
+		\def\ann@@####1{#2{####1}}%
+		\@ifstar{\ann@}{\ann@@}%
+	}}
+\defann{added}{\cb{green!20}\uline}
+\defann{removed}{\cb{red!20}\sout}
+\makeatother
+
+Since publishing this paper we discovered that \cref{thm:hcp-progress,thm:hcp-termination} do not hold for the version of \hcp in the published version of this paper.
+There are two solutions to this problem: 
+\begin{enumerate*}[label={\alph*)}]
+	\item introduce delayed actions as in \cite{kokke2019};
+	\item remove hypersequents from all logical rules as in \cite{montesi2018}.
+\end{enumerate*}
+For this revision, we opted for the second solution as it only required minimal changes to \cref{def:hcp} (all other definitions and theorems in the paper are unchanged).
+Below we include the published version of the type system of \hcp highlighting \added{additions} and \removed{deletions} introduced by this revision.
+{\renewcommand\thelemma{\ref{def:hcp}}
+\begin{definition}[Typing judgements]
+  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes that the process $\tm{P}$ consists of $n$ independent, but potentially entangled processes, each of which communicates according to its own protocol $\Gamma_i$.
+  Typing judgements can be constructed using the inference rules below. 
+  \\[1\baselineskip]
+  {Structural rules} %\vspace{-3ex}
+  \begin{center}
+    \hcpInfAx
+    %
+    \begin{prooftree*}
+        \AXC{$\seq[{ P }]{
+            \mathcal{G}\hsep
+            \Gamma, \tmty{x}{A} \hsep
+            \Delta, \tmty{x}{A^\bot}
+          }$}
+        \AXC{\added{$\tm{x} \not\in \ty{\mathcal{G}}$}}
+        \NOM{H-Cut}
+        \BIC{$\seq[{ \piNew{x}{P} }]{
+            \mathcal{G}\hsep
+            \ty{\Gamma}, \ty{\Delta}
+          }$}
+      \end{prooftree*}
+  \end{center}
+  \begin{center}
+    \hcpInfMix
+    \hcpInfHalt
+  \end{center}
+%  \vspace{.3ex}
+  {Logical rules} %\vspace{-3ex}
+  \begin{center}
+    \begin{prooftree*}
+      \AXC{$\seq[{ P }]{
+          \removed*{\mathcal{G} \hsep}\;
+          \ty{\Gamma}, \tmty{y}{A} \hsep
+          \ty{\Delta}, \tmty{x}{B}
+        }$}
+      \SYM{\tens}
+      \UIC{$\seq[{ \piBoundSend{x}{y}{P} }]{
+          \removed*{\mathcal{G} \hsep}\;
+          \ty{\Gamma}, \ty{\Delta}, \tmty{x}{A \tens B}
+        }$}
+    \end{prooftree*}
+    \begin{prooftree*}
+      \AXC{$\seq[ P ]{%
+          \removed*{\mathcal{G} \hsep}\;
+          \Gamma , \tmty{y}{A} , \tmty{x}{B} }$}
+      \SYM{(\parr)}
+      \UIC{$\seq[ \cpRecv{x}{y}{P} ]{
+          \removed*{\mathcal{G} \hsep}\;
+          \Gamma , \tmty{x}{A \parr B} }$}
+    \end{prooftree*}
+  \end{center}
+  \begin{center}
+    \begin{prooftree*}
+      \AXC{$\seq[{ P }]{\removed*{\mathcal{G}}}\added*{\vphantom{\mathcal{G}}\emptyhypercontext}$}
+      \SYM{\one}
+      \UIC{$\seq[{ \piBoundSend{x}{}{P} }]{
+          \removed*{\mathcal{G} \hsep}\; \tmty{x}{\one}
+        }$}
+    \end{prooftree*}
+    \begin{prooftree*}
+      \AXC{$\seq[ P ]{
+          \removed*{\mathcal{G} \hsep}\; \Gamma }$}
+      \SYM{(\bot)}
+      \UIC{$\seq[ \cpWait{x}{P} ]{
+          \removed*{\mathcal{G} \hsep}\; \Gamma , \tmty{x}{\bot} }$}
+    \end{prooftree*}
+  \end{center}
+  \begin{center}
+    \begin{prooftree*}
+      \AXC{$\seq[ P ]{
+          \removed*{\mathcal{G} \hsep}\;
+          \Gamma , \tmty{x}{A} }$}
+      \SYM{(\plus_1)}
+      \UIC{$\seq[{ \cpInl{x}{P} }]{
+          \removed*{\mathcal{G} \hsep}\;
+          \Gamma , \tmty{x}{A \plus B} }$}
+    \end{prooftree*}
+    \begin{prooftree*}
+      \AXC{$\seq[ P ]{
+          \removed*{\mathcal{G} \hsep}\;
+          \Gamma , \tmty{x}{B} }$}
+      \SYM{(\plus_2)}
+      \UIC{$\seq[ \cpInr{x}{P} ]{
+          \removed*{\mathcal{G} \hsep}\;
+          \Gamma , \tmty{x}{A \plus B} }$}
+    \end{prooftree*}
+  \end{center}
+  \begin{center}
+    \begin{prooftree*}
+      \AXC{$\seq[ P ]{
+          \Gamma , \tmty{x}{A} }$}
+      \AXC{$\seq[ Q ]{
+          \Gamma, \tmty{x}{B} }$}
+      \SYM{(\with)}
+      \BIC{$\seq[ \cpCase{x}{P}{Q} ]{
+          \Gamma , \tmty{x}{A \with B} }$}
+    \end{prooftree*}
+  \end{center}
+  \begin{center}
+    \hcpInfNil
+    \hcpInfTop
+  \end{center}
+  \removed{Furthermore, each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.}
+\end{definition}
+}
 \end{document}

### 2019-07-29 doc/paper/main.tex
(\ /) (O.o) (> <) Bunny approves these changes.

@@
 \end{definition}
-Note that the logical rules disallow hyperenvironments. If they did not, the following processes would be well-typed, even though they are stuck (unless we allow delayed actions as in \dhcp):
+Note that the logical rules disallow hyper-environments. If they did not, the following processes would be well-typed, even though they are stuck (unless we allow delayed actions as in \dhcp):
 \begin{center}
@@
 We can abuse this failure of readiness by asking the process to communicate on $\tm{y}$, which it is incapable of doing immediately.
-This is not a property of the $(\one)$ rule allowing hyperenvironments.
+This is not a property of the $(\one)$ rule allowing hyper-environments.
 Similar examples can be constructed using the $(\tens)$ rule.
@@
 	\item introduce delayed actions as in \cite{kokke2019};
-	\item remove hypersequents from all logical rules as in \cite{montesi2018}.
+	\item remove hyper-environments from all logical rules as in \cite{montesi2018}.
 \end{enumerate*}
-For this revision, we opted for the second solution as it only required minimal changes to \cref{def:hcp} (all other definitions and theorems in the paper are unchanged).
+For this revision, we opted for the second solution as it only requires minimal changes to \cref{def:hcp} (all other definitions and theorems in the paper are unchanged).
 Below we include the published version of the type system of \hcp highlighting \added{additions} and \removed{deletions} introduced by this revision.

### 2019-08-22 doc/paper/eptcsdata.tex
replaced the footer on page 1

@@
 \providecommand{\firstpage}{90}
-\providecommand{\publicationstatus}{T. Ehrhard, M. Fern\'andez, V. de Paiva, L. Tortora de Falco (Eds.):\\ Linearity-TLLA 2018\\
-EPTCS 292, 2019, pp.\ \pageref*{FirstPage}--\pageref{LastPage},
-doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}}
+%\providecommand{\publicationstatus}{T.
+Ehrhard, M.
+Fern\'andez, V.
+de Paiva, L.
+Tortora de Falco (Eds.):\\ Linearity-TLLA 2018\\ EPTCS 292, 2019, pp.\ \pageref*{FirstPage}--\pageref{LastPage}, doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}}
+\providecommand{\publicationstatus}{This is a revision of a paper with the same title,\\published in EPTCS 292, 2019, pp.90--103,\\ doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}}

### 2020-12-21 doc/paper/main.tex
replaced the footer on page 1
typos

@@
 
-\title{Taking Linear Logic Apart\\{\large Post-publication version: 2019-07-17}}
+\title{Taking Linear Logic Apart} %\\{\large Post-publication version: 2019-07-17}}
 \author{%
@@
 This work is distinct from our approach in that \hcp is based on classical linear logic and manipulates hypersequents differently: in Carbone \etal~\cite{carbone2018}, hypersequents can be formed only when sequents share resources (\cf \textsc{H-Mix}), and resource sharing is then tracked using an additional connection modality (which is not present in \hcp).
-Montesi and Peressotti \cite{montesi2018} revisited \cp in the light of hypersequents to derive the first correspondence between the labelled transition system semantics on proof transformations, later refined in \cite{kokke2019}.
+Montesi and Peressotti \cite{montesi2018} revisited \cp in the light of hypersequents to derive the first correspondence between the labelled transition system semantics and proof transformations, later refined in \cite{kokke2019}.
 The type system of \hcp is that of \cite{montesi2018} save for rule \textsc{H-Mix\textsubscript{0}} which is from \cite{kokke2019}.
-This is difference means that \cite{montesi2018} does not enjoy the translation to CLL that \hcp and \dhcp enjoy.
+This difference means that \cite{montesi2018} does not enjoy the translation to CLL that \hcp and \dhcp enjoy.
 

### 2021-09-01 doc/paper/eptcsdata.tex
erratum

@@
 Tortora de Falco (Eds.):\\ Linearity-TLLA 2018\\ EPTCS 292, 2019, pp.\ \pageref*{FirstPage}--\pageref{LastPage}, doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}}
-\providecommand{\publicationstatus}{This is a revision of a paper with the same title,\\published in EPTCS 292, 2019, pp.90--103,\\ doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}}
+\providecommand{\publicationstatus}{This is a revision of a paper with the same title,\\published in EPTCS 292, 2019, pp.90--103,\\ doi:\href{http://dx.doi.org/10.4204/EPTCS.292.5}{10.4204/EPTCS.292.5}.
+This revision has been\\communicated to EPTCS on July 29, 2019.}
